### 2019-07-16 LaTeX-Master-Vorlage/chapter/Background.tex
First Commit, upload already existing files

\chapter{Background} \label{c:Background}
This chapter will provide the necessary background in continuum mechanics and mathematics in order to understand the next chapters.

In this chapter we will examine the topic of the paper \textit{Stable Neo-Hookean Flesh Simulation}. The goal of the paper was to model deformations for virtual characters that have human-like features.

\section{Notation}
At first we will declare the notation used in this thesis to avoid misunderstandings. We will use the common notation used in continuum mechanics.

\section{Mathematical Background}

Since mathematics plays an important role in our field of interest we will build a solid background in this chapter. A basic understanding of linear algebra is assumed.

\subsection{Matrices}
At first we will discuss the geometrical meaning of some common matrix properties.

\subsection{Singular Value Decomposition}

The singular value decomposition (SVD) will play an important role in the following. It is important for our application since it represents the best possible approximation of a given matrix by a matrix of low rank. This approximation can be looked at as a compression of the data given (\cite{LiesenMehrmann2015}, S. 295).

\section{Continuum Mechanics}
In this section we will give a broad introduction the field of Continuum Mechanics.
In Continuum Mechanics we are less interested in small particles like atoms or molecules of an object but concentrate on pieces of matter which are in comparison very large. We are therefore concerned with the mechanical behavior of solids and fluids on the macroscopic scale (\cite{Spencer1980}, S. 1).

\section{Deformation}
Graphically we can imagine a deformation with the help of a deformation map. In Fig. \ref{fig:deformationmap} we have on the left side an ellipse that signifies an object in its rest state. On the right side in the same image we can see the ellipse in a deformed state. We can map each point from its rest state to the deformed one with the help of the function $\phi$.

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=0.5\textwidth]{resources/deformation_map}
	\caption{Deformation Map {\cite{STREAM2018}}}
	\label{fig:deformationmap}
\end{figure}

When applying a force over an object naturally the object itself undergoes a deformation. In the following we will be consistent with most previous literature in continuum mechanics and use the term strain as a measure of deformation and stress as the force per unit area.

\begin{addmargin}[2cm]{2cm}
\textit{Strain = measure of deformation}  \\
\textit{Stress = force per unit area} 
\end{addmargin}

\section{Deformation Gradient}

The deformation gradient $F$ is also shown in Fig. \ref{fig:deformationmap}. It offers us a measurement of the deformation. With its help we can amongst other things calculate the volume and length change an object undergoes during a deformation.
For our needs we define the deformation gradient as followed:

\[
F = \left[ \,f_0\, \bigg| \,f_1\, \bigg| \,f_2\, \right] = \begin{bmatrix} f_0 & f_3 & f_6 \\ f_1 & f_4 & f_7 \\ f_2 & f_5 & f_8 \end{bmatrix}
\]

Measure for the deformation, length and volume change etc.
Nonlinear deformations
http://www.continuummechanics.org/deformationgradient.html
also add some examples

\section{Material Constants}

Naturally the properties of the material the object consists of play an important rule in the deformation process. The two constants $\mu$ and $\lambda$ that are crucial for us are called \textit{Lamé Parameters}. The formula in which they appear is called \textit{Poisso's Ratio} and is of the following form:

\[ \sigma =  \frac{\lambda}{2(\lambda + \mu)} \in [-1, 0.5] \]

The poisson's ratio is of importance for us since it characterizes the materials resistance to volume change. Usually the poisson's ratio of a material is positive.
\\
For the simulation of human-like flesh we have to choose a poisson's ratio that is almost 0.5 to get realistic results.
\\ further reading: http://silver.neep.wisc.edu/~lakes/PoissonIntro.html

\section{Deformation Energy}

In order to get a convincing simulation of high quality we must choose an appropriate energy. In the case of modelling deformations on human-like characters we have to choose an elastic energy. The key property that makes an energy elastic is that if all the forces that are applied over an object add up to zero the object must come back to its rest shape.
\\
The energy then has to be minimized to get the results we want.

\begin{definition}
  This is a definition.
\end{definition}

### 2019-07-16 LaTeX-Master-Vorlage/chapter/paper.tex
First Commit, upload already existing files

--- 2019-07-16 LaTeX-Master-Vorlage/chapter/Background.tex
@@
-\chapter{Background} \label{c:Background}
-This chapter will provide the necessary background in continuum mechanics and mathematics in order to understand the next chapters.
-
+\chapter{Paper} \label{c:Paper}
 In this chapter we will examine the topic of the paper \textit{Stable Neo-Hookean Flesh Simulation}.
 The goal of the paper was to model deformations for virtual characters that have human-like features.
-
-\section{Notation}
-At first we will declare the notation used in this thesis to avoid misunderstandings. We will use the common notation used in continuum mechanics.
-
-\section{Mathematical Background}
-
-Since mathematics plays an important role in our field of interest we will build a solid background in this chapter. A basic understanding of linear algebra is assumed.
-
-\subsection{Matrices}
-At first we will discuss the geometrical meaning of some common matrix properties.
-
-\subsection{Singular Value Decomposition}
-
-The singular value decomposition (SVD) will play an important role in the following.
-It is important for our application since it represents the best possible approximation of a given matrix by a matrix of low rank.
-This approximation can be looked at as a compression of the data given (\cite{LiesenMehrmann2015}, S.
-295).
-
-\section{Continuum Mechanics}
-In this section we will give a broad introduction the field of Continuum Mechanics.
-In Continuum Mechanics we are less interested in small particles like atoms or molecules of an object but concentrate on pieces of matter which are in comparison very large.
-We are therefore concerned with the mechanical behavior of solids and fluids on the macroscopic scale (\cite{Spencer1980}, S.
-1).
 
@@
 
-\[
-F = \left[ \,f_0\, \bigg| \,f_1\, \bigg| \,f_2\, \right] = \begin{bmatrix} f_0 & f_3 & f_6 \\ f_1 & f_4 & f_7 \\ f_2 & f_5 & f_8 \end{bmatrix}
+\[ F =  \begin{bmatrix}
+  		f_0 & f_3 & f_6 \\
+  		f_1 & f_4 & f_7 \\
+  		f_2 & f_5 & f_8 \\
+		\end{bmatrix} 
 \]

### 2019-07-16 LaTeX-Master-Vorlage/glossary_and_acronyms.tex
First Commit, upload already existing files

\newglossaryentry{berlin}{name={Berlin},description={Berlin ist die Bundeshauptstadt der Bundesrepublik Deutschland und zugleich eines ihrer Länder. Die Stadt Berlin ist mit über 3,4 Millionen Einwohnern die bevölkerungsreichste und mit 892 Quadratkilometern die flächengrößte Gemeinde Deutschlands sowie nach Einwohnern die zweitgrößte der Europäischen Union. Sie bildet das Zentrum der Metropolregion Berlin/Brandenburg (6 Millionen Einw.) und der Agglomeration Berlin (4,4 Millionen Einw.). Der Stadtstaat unterteilt sich in zwölf Bezirke. Neben den Flüssen Spree und Havel befinden sich im Stadtgebiet kleinere Fließgewässer sowie zahlreiche Seen und Wälder}}
\newglossaryentry{outsourcing}{name={Outsourcing},description={Outsourcing bzw. Auslagerung bezeichnet in der Ökonomie die Abgabe von Unternehmensaufgaben und -strukturen an externe oder interne Dienstleister. Es ist eine spezielle Form des Fremdbezugs von bisher intern erbrachter Leistung, wobei Verträge die Dauer und den Gegenstand der Leistung fixieren. Das grenzt Outsourcing von sonstigen Partnerschaften ab}}
\newglossaryentry{asp}{name={Application Service Providing},description={Der Application Service Provider (Abkürzung ASP) bzw. Anwendungsdienstleister ist ein Dienstleister, der eine Anwendung (z. B. ein ERP-System) zum Informationsaustausch über ein öffentliches Netz (z. B. Internet) oder über ein privates Datennetz anbietet. Der ASP kümmert sich um die gesamte Administration, wie Datensicherung, das Einspielen von Patches usw. Anders als beim Applikations-Hosting ist Teil der ASP-Dienstleistung auch ein Service (z.B. Benutzerbetreuung) um die Anwendung herum}}
\newglossaryentry{policy}{name={Policy},description={Im geschäftlichen Bereich bezeichnet Policy eine interne Leit- bzw. Richtlinie, die formal durch das Unternehmen dokumentiert und über ihr Management verantwortet wird}}
\newglossaryentry{pcie}{name={PCI Express},description={PCI Express („Peripheral Component Interconnect Express“, abgekürzt PCIe oder PCI-E) ist ein Standard zur Verbindung von Peripheriegeräten mit dem Chipsatz eines Hauptprozessors. PCIe ist der Nachfolger von PCI, PCI-X und AGP und bietet im Vergleich zu seinen Vorgängern eine höhere Datenübertragungsrate pro Pin.}}

\newacronym{cd}{CD}{Compact Disk}
\newacronym{lan}{LAN}{Local Area Network}
\newacronym{iso}{ISO}{Internationale Organisation für Normung}
\newacronym{sas}{SAS}{Serial Attached SCSI}
\newacronym{abbvz}{Abbvz.}{Abbildungsverzeichnis}

### 2019-07-16 LaTeX-Master-Vorlage/main.tex
First Commit, upload already existing files

\include{settings}

%%Titles - Uncomment one section of titles

%%Used for titleGraduation
\include{titles/titleGraduation}
\logoPathL{} %just leave empty to hide logo
\logoWidthL{0.5}
\logoPathR{resources/uni_bern_logo.jpg} %just leave empty to hide logo
\logoWidthR{1}
\gradeType{Bachelor of Science (B.Sc.)}
\secondExaminer{Max Mustermann}

%%Used for titleResearchPaper
%\include{titles/titleResearchPaper}
%\subTitle{Ein optionaler Untertitel der Arbeit}
%\researchPart{A}

%%Used by all titles
\title{Stable Neo-Hookean Flesh Simulation}
\author{Corina Danja Masanti}
\matrikelnr{15-128-655} % just leave empty to hide number
\submitDate{01.09.2019}
\firstExaminer{Prof. Dr. David Bommes}
%%End Titles

\makeindex[title=Stichwortverzeichnis, options=-s indexstyle.ist, intoc]
\indexsetup{level=\chapter*,toclevel=chapter}

\makeglossaries
\loadglsentries{glossary_and_acronyms.tex}
\setacronymstyle{long-short}

\begin{document}

\pagenumbering{alph} %fix for same identifier warning, character is not show in title
\maketitle

\pagenumbering{Roman}

\include{chapter/Vorwort} \clearpage
\include{chapter/Abstract} \clearpage

\tableofcontents \newpage

\pagenumbering{arabic}
\input{chapter/Einleitung} \clearpage
\input{chapter/Background} \clearpage
\input{chapter/Beispiele} \clearpage
\input{chapter/paper} \clearpage

\pagenumbering{Alph}
\listoffigures \clearpage
\listoftables \clearpage
\lstlistoflistings \clearpage

\printindex \clearpage

\printglossary[title={Glossar}] \clearpage
\printglossary[style=dottedlocations,type=\acronymtype,title={Abkürzungsverzeichnis}] \clearpage

\printbibliography[heading=bibintoc, keyword={book}, title={Literaturverzeichnis}]\clearpage
\printbibliography[heading=bibintoc, keyword={online}, title={Onlinequellen}]\clearpage
\printbibliography[heading=bibintoc, keyword={image}, title={Bildquellen}]\clearpage

% Anhang
\input{chapter/Anhang}

% Eigenständigkeitserklärung
\input{chapter/Eigenstaendigkeitserklaerung}

\end{document}

### 2019-07-16 LaTeX-Master-Vorlage/chapter/Background.tex
test
working on Background -> Notation

@@
 
-\section{Notation}
-At first we will declare the notation used in this thesis to avoid misunderstandings. We will use the common notation used in continuum mechanics.
+\section{Notation and Convention}
+At first we will declare the notation used in this thesis to avoid misunderstandings.
+We will use the common notation used in continuum mechanics and additionally we will include the declarations in the paper \textit{Stable Neo-Hookean Flesh Simulation}.
+\\
+Scalars are represented by regular, normal-weight variables whereas 
+tensors and matrices are represented by upper-case bold variables such as \textbf{F}. Vectors will be denoted by bold lower-case variables.
+\\
+Furthermore we will use the tensor notation used in the paper \textit{Stable Neo-Hookean Flesh Simulation}.
+They decided to to define vectorization vec(.) as column-wise flattening of a matrix into a vector (\cite{Smith:2018:SNF:3191713.3180491}, 12:5) similar to Golub and Van Loan (2012):
+
+\[
+\textbf{A} = \begin{bmatrix} a & c \\ b & d \end{bmatrix} \qquad vec(\textbf{A}) = \boldsymbol{\check{a}} = \begin{bmatrix} a \\ b \\ c \\ d \end{bmatrix}.
+\]
+
+In order to indicate that we are dealing with a vectorized matrix we will use the symbol $\check{.}$ as shown above.
 
@@
 \[
-F = \left[ \,f_0\, \bigg| \,f_1\, \bigg| \,f_2\, \right] = \begin{bmatrix} f_0 & f_3 & f_6 \\ f_1 & f_4 & f_7 \\ f_2 & f_5 & f_8 \end{bmatrix}
+\textbf{F} = \left[ \,f_0\, \bigg| \,f_1\, \bigg| \,f_2\, \right] = \begin{bmatrix} f_0 & f_3 & f_6 \\ f_1 & f_4 & f_7 \\ f_2 & f_5 & f_8 \end{bmatrix}
 \]

### 2019-07-16 LaTeX-Master-Vorlage/chapter/Background.tex
Notation, still to do: 2nd order tensor

@@
 \section{Notation and Convention}
+
+\subsection{General Notation}
 At first we will declare the notation used in this thesis to avoid misunderstandings.
@@
 Scalars are represented by regular, normal-weight variables whereas 
-tensors and matrices are represented by upper-case bold variables such as \textbf{F}. Vectors will be denoted by bold lower-case variables.
-\\
+tensors and matrices are represented by upper-case bold letters. Vectors will be denoted by bold lower-case variables.
+
+\subsection{Tensor Notation}
+
 Furthermore we will use the tensor notation used in the paper \textit{Stable Neo-Hookean Flesh Simulation}.
@@
 In order to indicate that we are dealing with a vectorized matrix we will use the symbol $\check{.}$ as shown above.
+
+Additionally we well have to deal with $4^{th}$ order tensors in the following matrix-of-matrices form:
+
+\[
+\mathbb{A} = 
+\left[\begin{array}{cc}{\begin{bmatrix} a & c \\ b & d \end{bmatrix}} & {\begin{bmatrix} a & c \\ b & d \end{bmatrix}} \\ {\begin{bmatrix} a & c \\ b & d \end{bmatrix}} & {\begin{bmatrix} a & c \\ b & d \end{bmatrix}}\end{array}\right]
+=
+\left[\begin{array}{cc}{\left[\mathbf{A}_{00}\right]} & {\left[\mathbf{A}_{01}\right]} \\ {\left[\mathbf{A}_{10}\right]} & {\left[\mathbf{A}_{11}\right]}\end{array}\right]
+\]
+
+These matrices are denoted by using blackboard bold.
+
+TODO: 2nd order matrix, see paper 4.1 Tensor Notation
+
+\subsection{Summary}
+A quick overview of the used notation:
+
+\begin{addmargin}[2cm]{2cm}
+a: scalar \\
+\textbf{A}: matrix or tensor \\
+\textbf{a}: vector \\
+vec(\textbf{A}) = $\boldsymbol{\check{a}}$: vectorized matrix \\
+\end{addmargin}
 

### 2019-07-16 LaTeX-Master-Vorlage/chapter/Background.tex
working on chapter Paper, a lot to do, a lot of confusion, starting with structure

@@
 \subsection{Matrices}
-At first we will discuss the geometrical meaning of some common matrix properties.
+At first we will discuss the physical or geometrical meaning of some common matrix properties.
 
@@
 In Continuum Mechanics we are less interested in small particles like atoms or molecules of an object but concentrate on pieces of matter which are in comparison very large.
-We are therefore concerned with the mechanical behavior of solids and fluids on the macroscopic scale (\cite{Spencer1980}, S.
+We are therefore concerned with the mechanical behavior of solids and fluids on the macroscopic scale (\cite{Spencer1980}, p.
 1).

### 2019-07-16 LaTeX-Master-Vorlage/chapter/paper.tex
working on chapter Paper, a lot to do, a lot of confusion, starting with structure

@@
 The goal of the paper was to model deformations for virtual characters that have human-like features.
+They concentrated on the deformation energy.
 
-\section{Deformation}
-Graphically we can imagine a deformation with the help of a deformation map.
-In Fig.
-\ref{fig:deformationmap} we have on the left side an ellipse that signifies an object in its rest state.
-On the right side in the same image we can see the ellipse in a deformed state.
-We can map each point from its rest state to the deformed one with the help of the function $\phi$.
+\section{Energy Formulation}
 
-\begin{figure}[!htbp]
-	\centering
-	\includegraphics[width=0.5\textwidth]{resources/deformation_map}
-	\caption{Deformation Map {\cite{STREAM2018}}}
-	\label{fig:deformationmap}
-\end{figure}
+For our needs we need a hyperelastic energy that is stable in the following four important ways:
 
-When applying a force over an object naturally the object itself undergoes a deformation.
-In the following we will be consistent with most previous literature in continuum mechanics and use the term strain as a measure of deformation and stress as the force per unit area.
+\begin{itemize}
+\item Inversion stability
+\item Reflection stability
+\item Rest stability
+\item Meta-stability under degeneracy
+\end{itemize}
 
-\begin{addmargin}[2cm]{2cm}
-\textit{Strain = measure of deformation}  \\
-\textit{Stress = force per unit area} 
-\end{addmargin}
+TODO: explain each step
 
-\section{Deformation Gradient}
-
-The deformation gradient $F$ is also shown in Fig.
-\ref{fig:deformationmap}.
-It offers us a measurement of the deformation.
-With its help we can amongst other things calculate the volume and length change an object undergoes during a deformation.
-For our needs we define the deformation gradient as followed:
-
-\[ F =  \begin{bmatrix}
-  		f_0 & f_3 & f_6 \\
-  		f_1 & f_4 & f_7 \\
-  		f_2 & f_5 & f_8 \\
-		\end{bmatrix} 
-\]
-
-Measure for the deformation, length and volume change etc.
-Nonlinear deformations
-http://www.continuummechanics.org/deformationgradient.html
-also add some examples
-
-\section{Material Constants}
-
-Naturally the properties of the material the object consists of play an important rule in the deformation process.
-The two constants $\mu$ and $\lambda$ that are crucial for us are called \textit{Lamé Parameters}.
-The formula in which they appear is called \textit{Poisso's Ratio} and is of the following form:
-
-\[ \sigma =  \frac{\lambda}{2(\lambda + \mu)} \in [-1, 0.5] \]
-
-The poisson's ratio is of importance for us since it characterizes the materials resistance to volume change. Usually the poisson's ratio of a material is positive.
-\\
-For the simulation of human-like flesh we have to choose a poisson's ratio that is almost 0.5 to get realistic results.
-\\ further reading: http://silver.neep.wisc.edu/~lakes/PoissonIntro.html
-
-\section{Deformation Energy}
-
-In order to get a convincing simulation of high quality we must choose an appropriate energy.
-In the case of modelling deformations on human-like characters we have to choose an elastic energy.
-The key property that makes an energy elastic is that if all the forces that are applied over an object add up to zero the object must come back to its rest shape.
-\\
-The energy then has to be minimized to get the results we want.
-
-\begin{definition}
-  This is a definition.
-\end{definition}
+\subsection{Previous Work}
+Here comes previous work in neo-hookean energy formulation. What is neo-hookean and why do we need it here?

### 2019-09-17 LaTeX-Master-Vorlage/chapter/paper.tex
working on structure in Energy
paper
working on paper illustration

@@
 Here comes previous work in neo-hookean energy formulation. What is neo-hookean and why do we need it here?
+And what is wrong with each one.
+
+\subsection{Stable Neo-Hookean Energy}
+Conclude to the energy proposed in the paper.
+
+\section{Energy Analysis}
+Calculations and Herleitungen
+
+\subsection{First Piola-Kirchhoff Stress (PK1)}
+Explain.
+
+\subsection{The Energy Hessian Terms}
+Calculations
+
+\subsection{The Tikhonov, Mu, and Gradient Terms}
+Calculations
+
+\subsection{The Volume Hessian}
+Calculations
+
+\subsection{The Complete Eigensystem}
+Calculations
+
+\section{Experiments with the Code}
+The authors of the paper \textit{Stable Neo-Hookean Flesh Simulation} \cite{Smith:2018:SNF:3191713.3180491} kindly provided the implementation for an application of their formulated energy.
+In this code they implemented the stretch test on a cube.
+\\
+The following images show the stretch test with $\mu = 1.0$, $\lambda = 10.0$ and a resolution of 10.0 on a tetrahedral and a hexahedral mesh.
+
+\section{Discussion}
+Stuff, Taylor approx.

### 2019-09-27 LaTeX-Master-Vorlage/chapter/Background.tex
working on structure in Energy
working working doing stuff

@@
 \section{Notation and Convention}
+At first we will declare the notation used in this thesis to avoid misunderstandings.
+We will use the common notation used in continuum mechanics taken from \cite{Spencer1980}.
+Additionally we will include the declarations formulated in the paper \textit{Stable Neo-Hookean Flesh Simulation}.
 
 \subsection{General Notation}
-At first we will declare the notation used in this thesis to avoid misunderstandings.
-We will use the common notation used in continuum mechanics and additionally we will include the declarations in the paper \textit{Stable Neo-Hookean Flesh Simulation}.
-\\
-Scalars are represented by regular, normal-weight variables whereas 
-tensors and matrices are represented by upper-case bold letters. Vectors will be denoted by bold lower-case variables.
+Scalars are represented by regular, normal-weight variables such as $a$ whereas 
+tensors and matrices are represented by upper-case bold letters as for example $\textbf{A}$. Vectors will be denoted by bold lower-case variables like $\textbf{a}$.
 
 \subsection{Tensor Notation}
-
 Furthermore we will use the tensor notation used in the paper \textit{Stable Neo-Hookean Flesh Simulation}.
-They decided to to define vectorization vec(.) as column-wise flattening of a matrix into a vector (\cite{Smith:2018:SNF:3191713.3180491}, 12:5) similar to Golub and Van Loan (2012):
+They decided to to define vectorization vec(.) as column-wise flattening of a matrix into a vector (\cite{Smith:2018:SNF:3191713.3180491}, 12:5) similar to Golub and Van Loan (2012) \cite{golub2012matrix}.
 
 \[
-\textbf{A} = \begin{bmatrix} a & c \\ b & d \end{bmatrix} \qquad vec(\textbf{A}) = \boldsymbol{\check{a}} = \begin{bmatrix} a \\ b \\ c \\ d \end{bmatrix}.
+\textbf{A} = \begin{bmatrix} a & c \\ b & d \end{bmatrix} \qquad \operatorname{vec}(\textbf{A}) = \boldsymbol{\check{a}} = \begin{bmatrix} a \\ b \\ c \\ d \end{bmatrix}.
 \]
@@
 
-Additionally we well have to deal with $4^{th}$ order tensors in the following matrix-of-matrices form:
+Additionally we will have to deal with $4^{th}$ order tensors in the following form of matrix-of-matrices:
 
@@
 These matrices are denoted by using blackboard bold.
+\\
+If we now vectorize $\mathbb{A}$ we receive the following form:
 
-TODO: 2nd order matrix, see paper 4.1 Tensor Notation
+\[
+\mathbb{A} = \operatorname{vec}(\mathbb{A})=\left[\operatorname{vec}\left(\mathrm{A}_{00}\right)\left|\operatorname{vec}\left(\mathrm{A}_{10}\right)\right| \operatorname{vec}\left(\mathrm{A}_{01}\right) | \operatorname{vec}\left(\mathrm{A}_{11}\right)\right]
+=\left[\begin{array}{llll}{a} & {e} & {i} & {m} \\ {b} & {f} & {j} & {n} \\ {c} & {g} & {k} & {o} \\ {d} & {h} & {l} & {p}\end{array}\right]=\boldsymbol{\check{A}}
+\]
+
+The advantage of this form is that we can write several expressions as a cross product which we will need later.
 
@@
 \end{definition}
+
+To include: Piola-Kirchhoff Stress, Cauchy Green invariant, polar decomposition, cauchy green tensor

### 2019-09-27 LaTeX-Master-Vorlage/main.tex
working on chapter Paper, a lot to do, a lot of confusion, starting with structure
working working doing stuff

@@
 \input{chapter/Background} \clearpage
-\input{chapter/Beispiele} \clearpage
-\input{chapter/paper} \clearpage
+%\input{chapter/Beispiele} \clearpage
+\input{chapter/Paper} \clearpage
 
@@
 
-\printbibliography[heading=bibintoc, keyword={book}, title={Literaturverzeichnis}]\clearpage
-\printbibliography[heading=bibintoc, keyword={online}, title={Onlinequellen}]\clearpage
-\printbibliography[heading=bibintoc, keyword={image}, title={Bildquellen}]\clearpage
+\printbibliography[heading=bibintoc, keyword={book}, title={Literature}]\clearpage
+\printbibliography[heading=bibintoc, keyword={article}, title={Articles}]\clearpage
+\printbibliography[heading=bibintoc, keyword={online}, title={Online Resources}]\clearpage
+\printbibliography[heading=bibintoc, type=misc,title={Various References}] \clearpage
+\printbibliography[heading=bibintoc, keyword={image}, title={Images Resources}]\clearpage
 

### 2019-09-30 LaTeX-Master-Vorlage/chapter/Background.tex
fixed literaturverzeichnis, added todo package, fixed some warnings

@@
 \mathbb{A} = \operatorname{vec}(\mathbb{A})=\left[\operatorname{vec}\left(\mathrm{A}_{00}\right)\left|\operatorname{vec}\left(\mathrm{A}_{10}\right)\right| \operatorname{vec}\left(\mathrm{A}_{01}\right) | \operatorname{vec}\left(\mathrm{A}_{11}\right)\right]
-=\left[\begin{array}{llll}{a} & {e} & {i} & {m} \\ {b} & {f} & {j} & {n} \\ {c} & {g} & {k} & {o} \\ {d} & {h} & {l} & {p}\end{array}\right]=\boldsymbol{\check{A}}
+\]
+
+This term is equivalent to the following notation:
+
+\[
+\mathbb{A}=\left[\begin{array}{llll}{a} & {e} & {i} & {m} \\ {b} & {f} & {j} & {n} \\ {c} & {g} & {k} & {o} \\ {d} & {h} & {l} & {p}\end{array}\right] 
+=\boldsymbol{\check{A}}
 \]
@@
 \textbf{a}: vector \\
-vec(\textbf{A}) = $\boldsymbol{\check{a}}$: vectorized matrix \\
+vec(\textbf{A}) = $\boldsymbol{\check{a}}$: vectorized matrix
 \end{addmargin}
@@
 
-Measure for the deformation, length and volume change etc.
-Nonlinear deformations
+\todoredefined[inline]{
+TODO: Include measure for the deformation, length and volume change etc. \\
+Nonlinear deformations: \\
 http://www.continuummechanics.org/deformationgradient.html
-also add some examples
+\\ also add some examples
+}
 

### 2019-09-30 LaTeX-Master-Vorlage/main.tex
fixed literaturverzeichnis, added todo package, fixed some warnings

--- 2019-07-16 LaTeX-Master-Vorlage/main.tex
@@
 
-\printbibliography[heading=bibintoc, keyword={book}, title={Literaturverzeichnis}]\clearpage
-\printbibliography[heading=bibintoc, keyword={online}, title={Onlinequellen}]\clearpage
-\printbibliography[heading=bibintoc, keyword={image}, title={Bildquellen}]\clearpage
+% trying to make bibliography work
+\defbibfilter{booksAndPapers}{
+  type=article or
+  type=inproceedings or
+  type=incollection or
+  type=book or
+  type=inbook or
+  type=misc
+}
+\defbibfilter{onlineSource}{
+  type=online
+}
+
+\printbibliography[heading=bibintoc, filter=booksAndPapers, title={Bibliography}]\clearpage
+\printbibliography[heading=bibintoc, filter=onlineSource, title={Online Sources}]\clearpage
+\printbibliography[heading=bibintoc, keyword={image}, title={Figure Sources}]\clearpage
+
+%\printbibliography[heading=bibintoc, keyword={book}, title={Literature}]\clearpage
+%\printbibliography[heading=bibintoc, keyword={article}, title={Articles}]\clearpage
+%\printbibliography[heading=bibintoc, keyword={online}, title={Online Resources}]\clearpage
+%\printbibliography[heading=bibintoc, type=misc,title={Various References}] \clearpage
+%\printbibliography[heading=bibintoc, keyword={image}, title={Images Resources}]\clearpage
 

### 2019-09-30 LaTeX-Master-Vorlage/chapter/Introduction.tex
eigenstaendigkeitserklaerung, table of contents ueberarbeitet

\chapter{Introduction}
\section{Motivation}
The goal of this work is for a regular computer science student to give the necessary physical and mathematical background to understand the field of animation.

\section{Structure}
I will start with the background and then go on to the actual paper.

### 2019-10-07 LaTeX-Master-Vorlage/chapter/Background.tex
nothing works

@@
 \chapter{Background} \label{c:Background}
-This chapter will provide the necessary background in continuum mechanics and mathematics in order to understand the next chapters.
+In order to understand the thematics of simulating human-like flesh it is necessary to have a basic mathematical background and knowledge of continuum mechanics.
+This goal of this chapter is to deliver an understanding in the topic mentioned.
 

### 2019-10-07 LaTeX-Master-Vorlage/chapter/paper.tex
what
bilderreihe hexcli, tetcli, tetcli fehlt step24
nothing works

@@
 In this code they implemented the stretch test on a cube.
+The output were 26 static images with show the deformation in 25 steps.
+TODO: EXPLAIN HOW THEY DID IT IN SIMPLE WORDS
 \\
-The following images show the stretch test with $\mu = 1.0$, $\lambda = 10.0$ and a resolution of 10.0 on a tetrahedral and a hexahedral mesh.
+The following images show the stretch test with $\mu = 1.0$, $\lambda = 10.0$ and a resolution of 10.0 on a tetrahedral and a hexahedral mesh:
+
+\begin{figure}[!htbp]
+	\centering
+	\begin{subfigure}[b]{\textwidth}
+        \centering
+        \includegraphics[width=0.24\textwidth]{resources/hexcli_step0.png}
+        \hfill
+        \includegraphics[width=0.24\textwidth]{resources/hexcli_step8.png}
+        \hfill
+        \includegraphics[width=0.24\textwidth]{resources/hexcli_step16.png}
+        \hfill
+        \includegraphics[width=0.24\textwidth]{resources/hexcli_step24.png}
+        \caption{Stretch test on a hexahedral mesh}
+    \end{subfigure}
+    \vskip\baselineskip
+    \begin{subfigure}[b]{\textwidth}
+        \centering
+        \includegraphics[width=0.24\textwidth]{resources/tetcli_step0.png}
+        \hfill
+        \includegraphics[width=0.24\textwidth]{resources/tetcli_step8.png}
+        \hfill
+        \includegraphics[width=0.24\textwidth]{resources/tetcli_step16.png}
+        \hfill
+        \includegraphics[width=0.24\textwidth]{resources/tetcli_step24.png}
+        \caption{Stretch test on a tetrahedral mesh}
+    \end{subfigure}
+    \caption{Stretch test performed on a cube with (a) a hexahedral mesh and (b) a tetrahedral mesh}
+\end{figure}
 

### 2019-10-07 LaTeX-Master-Vorlage/chapter/Background.tex
fixed stuff, works again

--- 2019-09-30 LaTeX-Master-Vorlage/chapter/Background.tex
@@
 \chapter{Background} \label{c:Background}
-This chapter will provide the necessary background in continuum mechanics and mathematics in order to understand the next chapters.
+The goal we are striving for is to simulate human-like characters. In order to narrow it down even further we concentrate on the behaviour of the flesh of the character. 
+For understanding the thematics of simulating human-like flesh it is necessary to have a basic mathematical background and knowledge of continuum mechanics.
+The goal of this chapter is to deliver an understanding in the topics mentioned.
 

### 2019-10-07 LaTeX-Master-Vorlage/chapter/Introduction.tex
fixed stuff, works again

@@
 \chapter{Introduction}
+\textit{"Animation offers a medium of story telling and visual entertainment which can bring pleasure and information to people of all ages everywhere in the world."} \\
+- Walt Disney
+
 \section{Motivation}
-The goal of this work is for a regular computer science student to give the necessary physical and mathematical background to understand the field of animation.
+With steadily increasing computational power the demand of better results is constantly increasing. Especially in the field of animation and simulation we are no longer happy with mediocre results. 
+In the entertainment sector the gaming industry and animation studios like Pixar\textsuperscript{\textcopyright} or Disney\textsuperscript{\textcopyright} brought us games and movies of highest quality.
+Both of them have made groundbreaking progress over the years.
+This is easily seen when we compare today's work with that ten years ago.
+
+As always we have different requirements for each use.
+In some cases we want to exaggerate a movement or a reaction in a certain way. We can for example create a massive explosion in a movie that would not be half as spectacular in the real world.
+
+In other scenarios we want to come as close as possible to reality.
+For instance we want an animated character to move and physically interact with its environment as a real human being would.
+Otherwise our brain would immediately recognize that some things do not add up.
+The goal here is to bring characters quite literally to life.
+We can add small details like visible breathing and small wrinkles to have an even more convincing effect.
+The goal is to create the illusion of a character with personality, thought and emotions.
+In order to achieve this effect we need the character to move and react nearly physically correct.
+
+In the paper \textit{Stable Neo-Hookean Flesh Simulation} \cite{Smith:2018:SNF:3191713.3180491} the authors addressed exactly the problem of making an animated movement of a human-like character look as natural as possible.
+In order to animate a physical movement we need to understand the physics behind it which lies in the field of continuum mechanics.
+Unfortunately most of the time it has yet to be learned.
+The goal of this thesis is for a regular computer science student to give the necessary physical and mathematical background to understand the field of animation and maybe make a contribution to the field.
 
 \section{Structure}
-I will start with the background and then go on to the actual paper.
+Following up I will give a brief overview of the necessary mathematical background and deliver an introduction in continuum mechanics.
+Next up I will go through the ideas made in the paper mentioned and include some calculations and visualisations that help for a better understanding.
+\\
+
+\todoredefined[inline]{
+TODO: Adjust the introduction according to additions in text. Improve quote at beginning. Maybe add some images taken from Incredibles 2 for better visualisation?
+}

### 2019-10-07 LaTeX-Master-Vorlage/chapter/Background.tex
working mostly on background

@@
 \chapter{Background} \label{c:Background}
-The goal we are striving for is to simulate human-like characters. In order to narrow it down even further we concentrate on the behaviour of the flesh of the character. 
+The goal we are striving for is to animate human-like characters. In order to narrow it down even further we concentrate on the behaviour of the flesh of the character. 
 For understanding the thematics of simulating human-like flesh it is necessary to have a basic mathematical background and knowledge of continuum mechanics.
@@
 
-In this chapter we will examine the topic of the paper \textit{Stable Neo-Hookean Flesh Simulation}.
-The goal of the paper was to model deformations for virtual characters that have human-like features.
-
 \section{Notation and Convention}
 At first we will declare the notation used in this thesis to avoid misunderstandings.
-We will use the common notation used in continuum mechanics taken from \cite{Spencer1980}.
-Additionally we will include the declarations formulated in the paper \textit{Stable Neo-Hookean Flesh Simulation}.
+We will use the common notation used in continuum mechanics taken from the book \textit{Continuum Mechanics} \cite{Spencer1980}.
+Additionally we will include some more specific declarations formulated in the paper \textit{Stable Neo-Hookean Flesh Simulation} \cite{Smith:2018:SNF:3191713.3180491}.
 
@@
 
+In order to indicate that we are dealing with a vectorized matrix we will use the symbol $\check{.}$ as shown in the following equation:
+
 \[
@@
 
-In order to indicate that we are dealing with a vectorized matrix we will use the symbol $\check{.}$ as shown above.
-
-Additionally we will have to deal with $4^{th}$ order tensors in the following form of matrix-of-matrices:
+Additionally we will have to deal with $4^{th}$ order tensors in a form of matrix-of-matrices. These matrices are denoted by using blackboard bold:
 
@@
 
-These matrices are denoted by using blackboard bold.
-\\
-If we now vectorize $\mathbb{A}$ we receive the following form:
+If we now vectorize $\mathbb{A}$ we receive the form described in the following:
 
@@
 
-This term is equivalent to the following notation:
+This term above is equivalent to the following notation:
 
@@
 
-The advantage of this form is that we can write several expressions as a cross product which we will need later.
+The advantage of this form is that we can write several expressions as a cross product. We will need this property later to simplify complicated expressions and calculations.
 
 \subsection{Summary}
-A quick overview of the used notation:
+A quick overview of the notation used so far:
 
-\begin{addmargin}[2cm]{2cm}
-a: scalar \\
-\textbf{A}: matrix or tensor \\
-\textbf{a}: vector \\
-vec(\textbf{A}) = $\boldsymbol{\check{a}}$: vectorized matrix
+\begin{addmargin}[1cm]{1cm}
+a: Scalar \\
+\textbf{A}: Matrix or tensor \\
+\textbf{a}: Vector \\
+vec(\textbf{A}) = $\boldsymbol{\check{a}}$: Vectorized matrix
 \end{addmargin}
@@
 \section{Mathematical Background}
-
-Since mathematics plays an important role in our field of interest we will build a solid background in this chapter. A basic understanding of linear algebra is assumed.
+Since mathematics play an important role in our field of interest we need to build a solid background before we go further into the physics part.
+This chapter should cover all the important concepts used later in the calculations.
+A basic understanding of linear algebra is assumed.
 
@@
 
+\todoredefined[inline]{
+TODO: Complete this section. Add lemmas and theorems used afterwards in the calculations. Possible adjustments may come at the end.
+}
+
 \section{Continuum Mechanics}
-In this section we will give a broad introduction the field of Continuum Mechanics.
-In Continuum Mechanics we are less interested in small particles like atoms or molecules of an object but concentrate on pieces of matter which are in comparison very large.
+In this section we will give a broad introduction into the field of Continuum Mechanics.
+In Continuum Mechanics we are less interested in small particles like atoms or molecules of an object but rather concentrate on pieces of matter which are in comparison very large.
 We are therefore concerned with the mechanical behavior of solids and fluids on the macroscopic scale (\cite{Spencer1980}, p.
@@
 \section{Deformation}
-Graphically we can imagine a deformation with the help of a deformation map.
-In Fig.
-\ref{fig:deformationmap} we have on the left side an ellipse that signifies an object in its rest state.
-On the right side in the same image we can see the ellipse in a deformed state.
-We can map each point from its rest state to the deformed one with the help of the function $\phi$.
+When applying a force over an object naturally the object itself undergoes a deformation.
+In the following we will be consistent with most previous literature in continuum mechanics and use the term strain as a measure of deformation and stress as the force per unit area.
+
+\begin{addmargin}[2cm]{2cm}
+\textit{Strain = measure of deformation}  \\
+\textit{Stress = force per unit area} 
+\end{addmargin}
+
+\todoredefined[inline]{
+TODO: Decide whether to include the above paragraph and how to connect it better to the paper.
+}
+
+Now let us have a look at a deformation in a rather mathematical sense.
+Graphically we can imagine a deformation with the help of a two dimensional deformation map as shown in Fig.
+\ref{fig:deformationmap}.
+Here we have on the left side an ellipse that represents an object or material in its rest state.
+A function $\phi$ maps this rest state of the ellipse to a deformed state shown in Fig.
+\ref{fig:deformationmap} on the right side.
+Mathematically spoken this means that we can map each point of a chosen object from its rest state to a deformed one.
 
@@
 
-When applying a force over an object naturally the object itself undergoes a deformation.
-In the following we will be consistent with most previous literature in continuum mechanics and use the term strain as a measure of deformation and stress as the force per unit area.
+In conclusion the function $\phi$ describes our deformation.
+If we derive $\phi$ we can calculate the deformation gradient \textbf{F} which serves as a measure of the deformation in the following sense:
 
-\begin{addmargin}[2cm]{2cm}
-\textit{Strain = measure of deformation}  \\
-\textit{Stress = force per unit area} 
-\end{addmargin}
+\[
+\begin{array}{l}
+{\text { Deformation gradient: }} {\mathbf{F}=\operatorname{\nabla} \phi}
+\\
+{\text { Length changes: }} {\qquad I_{C}=\operatorname{tr}\left(\mathbf{F}^{T} \mathbf{F}\right)} 
+\\ 
+{\text { Volume changes: }} {\qquad J=\operatorname{det}(\mathbf{F})}\end{array}
+\]
+
+\todoredefined[inline]{
+TODO: Adjust so the equal sign is at the same place in each column.
+}
 

### 2019-10-07 LaTeX-Master-Vorlage/chapter/Introduction.tex
working mostly on background

@@
 \chapter{Introduction}
-\textit{"Animation offers a medium of story telling and visual entertainment which can bring pleasure and information to people of all ages everywhere in the world."} \\
+\textit{``Animation offers a medium of story telling and visual entertainment which can bring pleasure and information to people of all ages everywhere in the world.``} \\
 - Walt Disney
@@
 In the paper \textit{Stable Neo-Hookean Flesh Simulation} \cite{Smith:2018:SNF:3191713.3180491} the authors addressed exactly the problem of making an animated movement of a human-like character look as natural as possible.
-In order to animate a physical movement we need to understand the physics behind it which lies in the field of continuum mechanics.
-Unfortunately most of the time it has yet to be learned.
+In order to animate a physical movement we first need to understand the physics behind it which lies in the field of continuum mechanics.
+Unfortunately for most of us it has yet to be learned.
 The goal of this thesis is for a regular computer science student to give the necessary physical and mathematical background to understand the field of animation and maybe make a contribution to the field.

### 2019-10-07 LaTeX-Master-Vorlage/chapter/Background.tex
background done so far, def grad must be altered

@@
 
-\section{Deformation Gradient}
-
-The deformation gradient $F$ is also shown in Fig.
-\ref{fig:deformationmap}.
-It offers us a measurement of the deformation.
+\subsection{Deformation Gradient}
+The deformation gradient \textbf{F} offers us as said previously a measurement of the deformation.
 With its help we can amongst other things calculate the volume and length change an object undergoes during a deformation.
-For our needs we define the deformation gradient as followed:
+For our needs we define the deformation gradient exactely as the authors of the paper \cite{Smith:2018:SNF:3191713.3180491} did:
 
@@
 \todoredefined[inline]{
-TODO: Include measure for the deformation, length and volume change etc. \\
-Nonlinear deformations: \\
-http://www.continuummechanics.org/deformationgradient.html
-\\ also add some examples
+TODO: Add some examples. Already include definitions of the paper?
+\\ Some more sources:
+\\ http://www.continuummechanics.org/deformationgradient.html
 }
@@
 \section{Material Constants}
+When we look at a deformation of an object we need to consider the material the object consists of. A material can be very stiff like steel or easily deformable ones like robber.
 
-Naturally the properties of the material the object consists of play an important rule in the deformation process.
-The two constants $\mu$ and $\lambda$ that are crucial for us are called \textit{Lamé Parameters}.
-The formula in which they appear is called \textit{Poisso's Ratio} and is of the following form:
+The two constants $\mu$ and $\lambda$ that are crucial for us are called \textit{Lamé Parameters}. With the help of these two constants we can calculate the \textit{Poisson's Ratio}:
 
@@
 
-The poisson's ratio is of importance for us since it characterizes the materials resistance to volume change. Usually the poisson's ratio of a material is positive.
+The poisson's ratio is of importance for us because it characterizes the materials resistance to volume change.
+Usually the poisson's ratio of a material is positive.
+A negative value would mean that the material becomes wider in the cross section when it is stretched.
+This behaviour is very uncommon in nature.
+Here are some examples of the poisson's ratio of common materials:
+
+\begin{table}[h!]
+\centering
+    \begin{tabular}{ | l | l |}
+    \hline
+    Material & Poisson's ratio \\ \hline
+    rubber & 0.4999 \\ \hline
+    titanium & 0.265-0.34 \\ \hline
+    glass & 0.18–0.3 \\ \hline
+    cork & 0.0 \\ \hline
+    \end{tabular}
+    \caption{Different materials with their poisson's ratio}
+\label{table:1}
+\end{table}
+
+For the simulation of human-like flesh we have to choose a poisson's ratio that is almost 0.5 in order to get realistic results.
 \\
-For the simulation of human-like flesh we have to choose a poisson's ratio that is almost 0.5 to get realistic results.
-\\ further reading: http://silver.neep.wisc.edu/~lakes/PoissonIntro.html
+
+\todoredefined[inline]{
+TODO: Add some examples and images.
+Explain poisson's ratio a bit better.
+Why must poisson's ratio be 0.5?
+Add some references.
+Make table more beautiful.
+Add reference to table, now it is wikipedia (https://en.wikipedia.org/wiki/Poisson%27s_ratio).
+\\
+Further reading: http://silver.neep.wisc.edu/~lakes/PoissonIntro.html
+}
 
 \section{Deformation Energy}
-
 In order to get a convincing simulation of high quality we must choose an appropriate energy.
 In the case of modelling deformations on human-like characters we have to choose an elastic energy.
-The key property that makes an energy elastic is that if all the forces that are applied over an object add up to zero the object must come back to its rest shape.
+The key property that makes an energy elastic is that if all the forces that are applied over an object add up to zero the object must come back into its rest shape.
 \\
-The energy then has to be minimized to get the results we want.
+The energy then has to be minimized in order to get the results we want.
 
@@
 
-To include: Piola-Kirchhoff Stress, Cauchy Green invariant, polar decomposition, cauchy green tensor
+\todoredefined[inline]{
+TODO: Add some exaples and visualisations. What exactly is it and what role does it play in a deformation process?
+\\ To include: Piola-Kirchhoff Stress, Cauchy Green invariant, polar decomposition, cauchy green tensor
+}

### 2019-10-07 LaTeX-Master-Vorlage/chapter/paper.tex
background done so far, def grad must be altered

@@
 
+\todoredefined[inline]{
 TODO: explain each step
+}
 
@@
 The output were 26 static images with show the deformation in 25 steps.
-TODO: EXPLAIN HOW THEY DID IT IN SIMPLE WORDS
-\\
+
+\todoredefined[inline]{
+TODO: Explain how the code is implemented in simple words and how the energy is taken in account with the poisson's ratio.
+}
+
 The following images show the stretch test with $\mu = 1.0$, $\lambda = 10.0$ and a resolution of 10.0 on a tetrahedral and a hexahedral mesh:

### 2019-10-07 LaTeX-Master-Vorlage/chapter/paper.tex
improving experiments with the code

@@
 \chapter{Paper} \label{c:Paper}
-In this chapter we will examine the topic of the paper \textit{Stable Neo-Hookean Flesh Simulation}.
-The goal of the paper was to model deformations for virtual characters that have human-like features.
-They concentrated on the deformation energy.
+In this chapter we will examine the topic of the paper \textit{Stable Neo-Hookean Flesh Simulation} \cite{Smith:2018:SNF:3191713.3180491}.
+In the interest of understanding the thought process of the authors I will include some of their calculations a bit more detailed.
+In addition examples and visualisations should help for a better understanding.
 
 \section{Energy Formulation}
-
-For our needs we need a hyperelastic energy that is stable in the following four important ways:
+The core goal of the paper was to model deformations for virtual characters that have human-like features.
+They concentrated on the deformation energy.
+In order to achieve a convincing result as a first step we need to specify some requirements.
+For our needs in this case the stability of the energy is important.
+More precisely we need a hyperelastic energy that is stable in the following four important ways:
 
@@
 In this code they implemented the stretch test on a cube.
-The output were 26 static images with show the deformation in 25 steps.
+The outputs were 26 static images with show the deformation in 25 steps.
+The parameters the code expects are the two lamé parameters $\mu$ and $\lambda$ and a value for defining the desired resolution the objects should have.
 
 \todoredefined[inline]{
-TODO: Explain how the code is implemented in simple words and how the energy is taken in account with the poisson's ratio.
+TODO: Explain how the code is implemented in simple words and how the energy is taken in account with the poisson's ratio. Make scheme with input - box / code - output. Do I have to reference code?
 }
 
-The following images show the stretch test with $\mu = 1.0$, $\lambda = 10.0$ and a resolution of 10.0 on a tetrahedral and a hexahedral mesh:
+For starters let us take common values for $\mu$ and $\lambda$. We first start with $\mu = 1.0$, $\lambda = 10.0$ and a resolution of 10.0. For the poisson's ratio we get the value $0.4545$:
+
+\[ \sigma =  \frac{10.0}{2 (10.0 + 1.0)} = 0.4545 \in [-1, 0.5] \]
+
+The following images in figure \ref{fig:stretchtest} show the stretch test with $\mu = 1.0$, $\lambda = 10.0$ and a resolution of 10.0 on a tetrahedral and a hexahedral mesh.
 
@@
     \caption{Stretch test performed on a cube with (a) a hexahedral mesh and (b) a tetrahedral mesh}
+    \label{fig:stretchtest}
 \end{figure}

### 2019-10-18 LaTeX-Master-Vorlage/chapter/Background.tex
improving experiments with the code
working on paper, energy and code

@@
 We will use the common notation used in continuum mechanics taken from the book \textit{Continuum Mechanics} \cite{Spencer1980}.
-Additionally we will include some more specific declarations formulated in the paper \textit{Stable Neo-Hookean Flesh Simulation} \cite{Smith:2018:SNF:3191713.3180491}.
+Additionally we will include some more specific declarations formulated and used in the paper \textit{Stable Neo-Hookean Flesh Simulation} \cite{Smith:2018:SNF:3191713.3180491}.
 
@@
 
-If we now vectorize $\mathbb{A}$ we receive the form described in the following:
+If we now vectorize $\mathbb{A}$ we receive the form described in the following line:
 
@@
 
-This term above is equivalent to the following notation:
+This term above is equivalent to the notation described here:
 
@@
 \textbf{a}: Vector \\
-vec(\textbf{A}) = $\boldsymbol{\check{a}}$: Vectorized matrix
+vec(\textbf{A}) = $\boldsymbol{\check{a}}$: Vectorized matrix \\
+$\mathbb{A} = \boldsymbol{\check{A}}$: matrix-of-matrices
 \end{addmargin}
 
+\todoredefined[inline]{
+TODO: Check if all notations are declared when adding something.
+}
+
 \section{Mathematical Background}
-Since mathematics play an important role in our field of interest we need to build a solid background before we go further into the physics part.
+Since mathematics play an important role in our field of interest we need to build a solid background before we go further into more complex calculations.
 This chapter should cover all the important concepts used later in the calculations.
@@
 
-The singular value decomposition (SVD) will play an important role in the following.
+The singular value decomposition (SVD) will play an important role in formulating the deformation gradient.
 It is important for our application since it represents the best possible approximation of a given matrix by a matrix of low rank.
@@
 \todoredefined[inline]{
-TODO: Adjust so the equal sign is at the same place in each column.
+TODO: Adjust so the equal sign is at the same place in each column. Explain strain and stress and their meaning for later use in material constants (not explained in paper).
 }
@@
 
-\section{Material Constants}
+\subsection{Material Constants}
 When we look at a deformation of an object we need to consider the material the object consists of. A material can be very stiff like steel or easily deformable ones like robber.
@@
 
-\section{Deformation Energy}
+\subsection{Deformation Energy}
 In order to get a convincing simulation of high quality we must choose an appropriate energy.
@@
 \todoredefined[inline]{
-TODO: Add some exaples and visualisations. What exactly is it and what role does it play in a deformation process?
+TODO: Add some exaples and visualisations. What exactly is it and what role does it play in a deformation process? Hyperelastic energy, connect with paper.
 \\ To include: Piola-Kirchhoff Stress, Cauchy Green invariant, polar decomposition, cauchy green tensor

### 2019-10-18 LaTeX-Master-Vorlage/chapter/Introduction.tex
working on paper, energy and code

@@
 \section{Motivation}
-With steadily increasing computational power the demand of better results is constantly increasing. Especially in the field of animation and simulation we are no longer happy with mediocre results. 
-In the entertainment sector the gaming industry and animation studios like Pixar\textsuperscript{\textcopyright} or Disney\textsuperscript{\textcopyright} brought us games and movies of highest quality.
+With steadily increasing computational power the demand of better results is constantly growing. Especially in the field of animation and simulation we are no longer happy with mediocre results. 
+In the entertainment sector gaming industries and animation studios like Pixar\textsuperscript{\textcopyright} or Disney\textsuperscript{\textcopyright} brought us games and movies of highest quality.
 Both of them have made groundbreaking progress over the years.
-This is easily seen when we compare today's work with that ten years ago.
+This is easily observed when we compare today's work with that from ten years ago.
 
@@
 Unfortunately for most of us it has yet to be learned.
-The goal of this thesis is for a regular computer science student to give the necessary physical and mathematical background to understand the field of animation and maybe make a contribution to the field.
+The goal of this thesis is to give the necessary physical and mathematical background for a regular computer science student to understand the field of animation.
 
@@
 Following up I will give a brief overview of the necessary mathematical background and deliver an introduction in continuum mechanics.
-Next up I will go through the ideas made in the paper mentioned and include some calculations and visualisations that help for a better understanding.
+Next I will go through the ideas made in the paper mentioned and include some calculations and visualisations that help for a better understanding.
 \\
@@
 \todoredefined[inline]{
-TODO: Adjust the introduction according to additions in text. Improve quote at beginning. Maybe add some images taken from Incredibles 2 for better visualisation?
+TODO: Improve intorduction (goals etc.). Adjust according to additions in text. Improve quote at beginning. Maybe add other applications as well (physical simulation) and how to go over to it?
 }

### 2019-10-18 LaTeX-Master-Vorlage/chapter/paper.tex
working on paper, energy and code

@@
 In the interest of understanding the thought process of the authors I will include some of their calculations a bit more detailed.
-In addition examples and visualisations should help for a better understanding.
+In addition examples and visualisations should help for a better perception.
 
@@
 
-\begin{itemize}
-\item Inversion stability
-\item Reflection stability
-\item Rest stability
-\item Meta-stability under degeneracy
-\end{itemize}
+\textbf{1.
+Inversion Stability:} Given some arbitrary object it is possible that while deforming the object we can arrive at a zero volume state or even an entire inversion.
+Take for example the tetrahedron shown in figure \ref{fig:inversion_1}.
+In figure \ref{fig:inversion_2} we see a deformed state of this tetrahedron where the volume is scaled down to zero and we are left with a simple triangle.
+In figure \ref{fig:inversion_3} image we have an inversion of the object.
+The needed deformation energy has to be able to deal with both cases.
+
+\begin{figure}[!ht]
+\centering
+\begin{subfigure}{.3\textwidth}
+  \centering
+  % include first image
+  \includegraphics[width=.8\linewidth]{resources/inversion_1}  
+  \caption{Rest state}
+  \label{fig:inversion_1}
+\end{subfigure}
+\begin{subfigure}{.3\textwidth}
+  \centering
+  % include first image
+  \includegraphics[width=.8\linewidth]{resources/inversion_2}  
+  \caption{Zero-volume state}
+  \label{fig:inversion_2}
+\end{subfigure}
+\begin{subfigure}{.3\textwidth}
+  \centering
+  % include second image
+  \includegraphics[width=.8\linewidth]{resources/inversion_3}  
+  \caption{Inversed state}
+  \label{fig:inversion_3}
+\end{subfigure}
+\caption{Inversion of a tetrahedron {\cite{STREAM2018}}}
+\label{fig:inversion}
+\end{figure}
+
+\textbf{2. Reflection stability:} A reflection is rotation around the coordinate origin.
+
+\textbf{3.
+Rest stability:} When deforming an object in a certain way we apply one or multiple forces over that object.
+With rest stability we want that if the sum of forces is equal to zero the object must be back in its rest state.
+
+\textbf{4.
+Meta-stability under degeneracy:} We can crush an object into an arbitrary shape like a plane, line or point.
+That process is illustrated for a cube in figure \ref{fig:meta_stability}.
+The cube should now be able to recover to its actual shape after the deformation.
+
+\begin{figure}[!htbp]
+	\centering
+	\includegraphics[width=0.5\textwidth]{resources/meta_stability}
+	\caption{Illustration of meta stability {\cite{STREAM2018}}}
+	\label{fig:meta_stability}
+\end{figure}
+
+Based on these four requirements we will in the following determine if a deformation energy is suited for our needs.
 
 \todoredefined[inline]{
-TODO: explain each step
+TODO: Finish reflection stability. Maybe add own images? Some more sources?
 }
@@
 \subsection{Previous Work}
-Here comes previous work in neo-hookean energy formulation. What is neo-hookean and why do we need it here?
+\todoredefined[inline]{
+TODO: Here comes previous work in neo-hookean energy formulation. What is neo-hookean and why do we need it here?
 And what is wrong with each one.
+}
 
@@
 
+\todoredefined[inline]{
+TODO: Load into OpenFlipper and screenshot results. Include more examples and what went right and what went wrong.
+}
+
 \section{Discussion}

### 2019-10-25 LaTeX-Master-Vorlage/chapter/paper.tex
working on paper, forgot to git it

@@
 The needed deformation energy has to be able to deal with both cases.
+That means that the energy has to be singularity-free and does not need any filters or threshold (\cite{Smith:2018:SNF:3191713.3180491}, 12:3).
+
+\todoredefined[inline]{
+TODO: Explain what last sentence means. Reference correct like this?
+}
 
@@
 \textbf{2. Reflection stability:} A reflection is rotation around the coordinate origin.
+For the deformation energy we need it to be well behaved regardless of the reflection convention used in the singular value decomposition.
 

### 2019-10-31 LaTeX-Master-Vorlage/chapter/Background.tex
working on mahtematical background

@@
 
+\begin{definition}[\textbf{Singular Values}]
+The singular values of a matrix A $\in$ $\mathbb{R}^{m x n}$ are the square roots of the eigenvalues of $AA^{\mathrm{T}}$.
+\end{definition}
+
+The theorem of the singular value decomposition tells us that we can factor every m-by-n matrix into one orthogonal m-by-m, one diagonal m-by-n and one orthogonal n-by-n matrix. More formally:
+
+\begin{theorem}[\textbf{The SVD Theorem}]
+Let A $\in$ $\mathbb{R}^{m x n}$ be a matrix having r positive singular values, m $\geq$ n.
+Then there exist orthogonal matrices U $\in$ $\mathbb{R}^{m x m}$, V $\in$ $\mathbb{R}^{n x n}$ and a diagonal matrix $\tilde{\Sigma}$ $\in$ $\mathbb{R}^{m x n}$ such that
+
+\[
+\begin{array}{l}{A=U \tilde{\Sigma} V^{\mathrm{T}}} \\ {\tilde{\Sigma}=\left[\begin{array}{ll}{\Sigma} & {0} \\ {0} & {0}\end{array}\right]}\end{array}
+\]
+
+where $\Sigma$ = diag ($\sigma$1, $\sigma$2, . . . , $\sigma$r), and $\sigma$1 $\geq$ $\sigma$2 $\geq$ · · · $\geq$ $\sigma$r $>$ 0 are the positive singular values of A.
+
+\end{theorem}
+Reference: \cite{ford2014numerical}, chap. 15
+
+\todoredefined[inline]{
+TODO: Check reference. Make paragraphs work together. Add examples.
+}
+
+\subsection{Polar Decomposition}
+
 \todoredefined[inline]{
@@
 
+\subsection{Polar Decomposition of the Deformation Gradient}
+With the help of mathematics we can decompose the deformation gradient in the following form:
+
+\[
+F = R S
+\]
+
 \subsection{Material Constants}

### 2019-11-07 LaTeX-Master-Vorlage/chapter/Background.tex
working on background, material constants

@@
 \begin{definition}[\textbf{Singular Values}]
+\label{singular_values}
 The singular values of a matrix A $\in$ $\mathbb{R}^{m x n}$ are the square roots of the eigenvalues of $AA^{\mathrm{T}}$.
@@
 \begin{theorem}[\textbf{The SVD Theorem}]
+\label{SVD}
 Let A $\in$ $\mathbb{R}^{m x n}$ be a matrix having r positive singular values, m $\geq$ n.
@@
 \end{theorem}
-Reference: \cite{ford2014numerical}, chap. 15
+The definition and theorem were taken from \cite{ford2014numerical} (def. \ref{SVD} S.113, thm. \ref{singular_values} S.300).
 
@@
 \subsection{Polar Decomposition}
+
+\begin{theorem}[\textbf{The Polar Decomposition Theorem}]
+\label{PD}
+
+Let \textbf{F} be a non-singular square matrix. Then \textbf{F} can be decomposed uniquely into either of the following two products
+\[
+\boldsymbol{F} = \boldsymbol{RU}, \quad \boldsymbol{F} = \boldsymbol{VR}
+\]
+where \textbf{R} is orthogonal and \textbf{U} and \textbf{V} are positive definite symmetric matrices.
+\end{theorem}
+
+A matrix \textbf{A} is positive definite if $\textbf{x}^{T}\textbf{Ax}$ is positive for all of the non-zero values of the column matrix \textbf{x}.
+
+The definition and theorem were taken from \cite{Spencer1980} (thm. \ref{PD} S.12).
 
@@
 \subsection{Material Constants}
-When we look at a deformation of an object we need to consider the material the object consists of. A material can be very stiff like steel or easily deformable ones like robber.
+When we look at a deformation of an object we need to consider the material the object consists of.
+A material can be very stiff like steel or easily deformable like rubber.
+In order to measure the deformation in a specific material we need the \textit{Poisson's Ratio} of said material.
+The poisson's ratio is a material constant that is defined as
+
+\[
+	\sigma = - \frac{\epsilon_{11}}{\epsilon_{22}} \in [-1, 0.5]
+\]
+
+where $\epsilon_{11}$ is the lateral and $\epsilon_{22}$ the axial strain.
+The range in which $\sigma$ lies in starts at $-1$ and goes up to $0.5$ \cite{PhysRevB.80.132104}.
+Usually the poisson's ratio of a material is positive.
+A negative value would mean that the material becomes wider in the cross section when it is stretched.
+This behaviour is very uncommon in nature.
+In our use case we need the poisson's ratio as a characterization for the resistance to volume change of a given material.
+
+Here are some examples of the poisson's ratio of various materials:
+
+\begin{table}[!htbp]
+\centering
+    \begin{tabular}{ | l | l |}
+    \hline
+    \textbf{Material} & \textbf{Poisson's ratio} \\ \hline
+    C (graphite) & 0.31 \\ \hline
+    Sn (metal) & 0.357 \\ \hline
+    Cu & 0.355 \\ \hline
+    Zn & 0.25 \\ \hline
+    Ag & 0.36 \\ \hline
+    Au & 0.45 \\ \hline
+    Concrete & 0.20–0.37 \\ \hline
+    Titanium (dental alloy) & 0.30–0.31 \\ \hline
+    Bronze & 0.34 \\ \hline
+    18–8 Stainless steel & 0.305 \\ \hline
+    Natural rubber & 0.4999 \\ \hline
+	B\textsubscript{2}O\textsubscript{3} glass & 0.30 \\ \hline
+	GeO\textsubscript{2} glass & 0.20 \\ \hline	
+    \end{tabular}
+    \caption{Different materials with their poisson's ratio taken from \cite{PhysRevB.80.132104}}
+\label{table:1}
+\end{table}
 
@@
 
-\[ \sigma =  \frac{\lambda}{2(\lambda + \mu)} \in [-1, 0.5] \]
-
-The poisson's ratio is of importance for us because it characterizes the materials resistance to volume change.
-Usually the poisson's ratio of a material is positive.
-A negative value would mean that the material becomes wider in the cross section when it is stretched.
-This behaviour is very uncommon in nature.
-Here are some examples of the poisson's ratio of common materials:
-
-\begin{table}[h!]
-\centering
-    \begin{tabular}{ | l | l |}
-    \hline
-    Material & Poisson's ratio \\ \hline
-    rubber & 0.4999 \\ \hline
-    titanium & 0.265-0.34 \\ \hline
-    glass & 0.18–0.3 \\ \hline
-    cork & 0.0 \\ \hline
-    \end{tabular}
-    \caption{Different materials with their poisson's ratio}
-\label{table:1}
-\end{table}
+\[ \sigma =  \frac{\lambda}{2(\lambda + \mu)}  \]
 

### 2019-11-07 LaTeX-Master-Vorlage/chapter/Background.tex
Material constants more or less done

@@
 
-\[
+\begin{equation}\label{eq:poisson}
 \sigma = - \frac{\epsilon_{11}}{\epsilon_{22}} \in [-1, 0.5]
-\]
+\end{equation}
 
@@
 This behaviour is very uncommon in nature.
-In our use case we need the poisson's ratio as a characterization for the resistance to volume change of a given material.
+Examples of materials with a negative poisson's ratio are for instance discussed in \textit{Foam structures with a negative Poisson's ratio} \cite{lakes1987foam} or \textit{Advances in negative Poisson's ratio materials} \cite{lakes1993advances}.
 
@@
 
-The two constants $\mu$ and $\lambda$ that are crucial for us are called \textit{Lamé Parameters}. With the help of these two constants we can calculate the \textit{Poisson's Ratio}:
+In the context of flesh simulations we use the poisson's ratio as a characterization for the resistance to volume change of flesh.
+Biological tissues such as flesh, fat and muscles have one important property: Volume preservation.
+As a result the poisson's ratio is a higher value, meaning it is found in the range between 0.45 and 0.5 \cite{Smith:2018:SNF:3191713.3180491}.
 
-\[ \sigma =  \frac{\lambda}{2(\lambda + \mu)}  \]
+The calculation of the poisson's ratio defined as in equation \ref{eq:poisson} is a challenge.
+Fortunately we can make use of the \textit{Lamé Parameters}.
+These are the two constants $\mu$ and $\lambda$ that are specific for a material.
+With the help of these two constants we can transform equation \ref{eq:poisson} into the following form:
 
-For the simulation of human-like flesh we have to choose a poisson's ratio that is almost 0.5 in order to get realistic results.
-\\
+\begin{equation}\label{eq:poisson_ratio}
+\sigma =  \frac{\lambda}{2(\lambda + \mu)}
+\end{equation}
+
+This equation allows us to calculate the poisson's ratio much easier.
 
 \todoredefined[inline]{
-TODO: Add some examples and images.
-Explain poisson's ratio a bit better.
-Why must poisson's ratio be 0.5?
-Add some references.
-Make table more beautiful.
-Add reference to table, now it is wikipedia (https://en.wikipedia.org/wiki/Poisson%27s_ratio).
+TODO: Topic generally covered, maybe adjust the following:
+Explain why volume preservation => high poisson's ratio. Explain how to get formula with lamé parameters, explain lamé parameters.
+Explain more on negative poisson's value?
 \\

### 2019-11-25 LaTeX-Master-Vorlage/chapter/Background.tex
working on background and paper

@@
 
+A matrix \textbf{A} is positive definite if $\textbf{x}^{T}\textbf{Ax}$ is positive for all of the non-zero values of the column matrix \textbf{x}.
+
+\todoredefined[inline]{
+TODO: positive definite matrices definition and lemmas, orthogonal, etc.
+}
+
 \subsection{Singular Value Decomposition}
@@
 
-A matrix \textbf{A} is positive definite if $\textbf{x}^{T}\textbf{Ax}$ is positive for all of the non-zero values of the column matrix \textbf{x}.
-
 The definition and theorem were taken from \cite{Spencer1980} (thm. \ref{PD} S.12).
@@
 When applying a force over an object naturally the object itself undergoes a deformation.
-In the following we will be consistent with most previous literature in continuum mechanics and use the term strain as a measure of deformation and stress as the force per unit area.
+In the following we will be consistent with most previous literature in continuum mechanics and use the term strain as a measure of deformation and stress as the force per unit area:
 

### 2019-11-25 LaTeX-Master-Vorlage/chapter/paper.tex
working on background and paper

@@
 
+\section{Deformation Gradient}
+
+\begin{table}[!htbp]
+\centering
+    \begin{tabular}{ | l | l |}
+    \hline
+    \textbf{Symbol} & \textbf{Definition} \\ \hline
+    $\mathrm{F=RS}$ & Polar decomposition \\ \hline
+    $J=\operatorname{det}(\mathrm{F})$ & Relative volume change \\ \hline
+    $\mathrm{C}=\mathrm{F}^{T} \mathrm{F}$ & Right Cauchy-Green  \\ \hline	
+    $I_{C}=\operatorname{tr}(\mathrm{C})$ & First right Cauchy-Green invariant \\ \hline
+    \end{tabular}
+    \caption{Quantities Derived from the Deformation Gradient \textbf{F} taken from \cite{Smith:2018:SNF:3191713.3180491}}
+\label{table:1}
+\end{table}
+
+\todoredefined[inline]{
+TODO: Add in Background? Explain more each entity
+}
+
 \section{Energy Formulation}
+
+\subsection{Stability}
 The core goal of the paper was to model deformations for virtual characters that have human-like features.
@@
 }
+
+\subsection{Existing Neo-Hookean Energies}
+A commonly used energy function is defined as follows (see e.g. \cite{bonet1997nonlinear}, p.148):
+
+\[
+\Psi=\frac{\mu}{2}\left(I_{C}-3\right)-\mu \ln J+\frac{\lambda}{2}(\ln J)^{2}
+\]
+
+where $\lambda$ and $\mu$ are the material constants and $J = det(F)$.
+
+In the literature appear many more different formulations of the energy. Each one consists of a 1D length term and a 3D volume term.
+
+\textbf{1D Length Term:} This term penalizes length changes.
+
+\textbf{3D Volume Term:} Here we are dealing with a volume-preserving penalty term.
+
+\subsection{Rest Stabilization}
+
+\subsection{Lamé Reparametrization}
 

### 2019-11-25 LaTeX-Master-Vorlage/chapter/paper.tex
working on existing energies, still not happy with it

@@
 \subsection{Existing Neo-Hookean Energies}
-A commonly used energy function is defined as follows (see e.g. \cite{bonet1997nonlinear}, p.148):
 
+In previous literature a few energies were proposed.
+
+\begin{table}[!htbp]
+\centering
+    \begin{tabular}{ | l | l |}
+    \hline
+    \textbf{Energy} & \textbf{Author(s)} \\ \hline
+    $\Psi_{Neo}=\frac{\mu}{2}\left(I_{C}-3\right)-\mu \ln J+\frac{\lambda}{2}(\ln J)^{2}$ & Mooney 1940 \\ \hline
+    $\Psi_{\mathrm{A}}=\frac{\mu}{2}\left(I_{C}-3\right)-\mu \log J+\frac{\lambda}{2}(J-1)^{2}$ & Odgen 1997 \\ \hline
+    $\Psi_{\mathrm{B}}=\frac{\mu}{2}\left(J^{-2 / 3} I_{C}-3\right)+\frac{\lambda}{2}(J-1)^{2}$ & Bower 2009 \\ \hline
+    $\Psi_{\mathrm{C}}=\frac{\mu}{2}\left(J^{-2 / 3} I_{C}-3\right)+\frac{\lambda}{2}(J-1)$ & Wang and Yang 2016 \\ \hline
+    \end{tabular}
+    \caption{Summary of proposed energies taken from \cite{Smith:2018:SNF:3191713.3180491}}
+\label{table:1}
+\end{table}
+
+Each energy formulation can be split up into a 1D length term and a 3D volume term.
+
+\begin{table}[!htbp]
+\centering
+    \begin{tabular}{ | l | l | l |}
+    \hline
+    \textbf{Energy} & \textbf{1D length term} & \textbf{3D volume term} \\ \hline
+    $\Psi_{Neo}$ & $\frac{\mu}{2}\left(I_{C}-3\right)$ & $-\mu \ln J+\frac{\lambda}{2}(\ln J)^{2}$ \\ \hline
+    $\Psi_{\mathrm{A}}$ & $\frac{\mu}{2}\left(I_{C}-3\right)$ & $-\mu \log J+\frac{\lambda}{2}(J-1)^{2}$ \\ \hline
+    $\Psi_{\mathrm{B}}$ & $\frac{\mu}{2}\left(J^{-2 / 3} I_{C}-3\right)$ & $+\frac{\lambda}{2}(J-1)^{2}$ \\ \hline
+    $\Psi_{\mathrm{C}}$ & $\frac{\mu}{2}\left(J^{-2 / 3} I_{C}-3\right)+$ & $\frac{\lambda}{2}(J-1)$ \\ \hline
+    \end{tabular}
+    \caption{Energies split up into its 1D length and 3D volume term}
+\label{table:1}
+\end{table}
+
+\textbf{1D Length Term:} This term penalizes length changes. Mooney proposed the energy (\cite{mooney1940theory})
 \[
-\Psi=\frac{\mu}{2}\left(I_{C}-3\right)-\mu \ln J+\frac{\lambda}{2}(\ln J)^{2}
+\Psi_{M}=\frac{\mu}{2}\left(I_{C}-3\right)
+\]
+which was later known as "Neo-Hookean" energy.
+
+If we expand the energy with the singular values of the deformation gradient \textbf{F} we get the following term:
+\[
+\Psi_{M}=\frac{\mu}{2}\left(I_{C}-3\right) = \frac{\mu}{2}\left(\sigma_{0}^2 + \sigma_{1}^2 + \sigma_{2}^2 - 3\right)
 \]
 
-where $\lambda$ and $\mu$ are the material constants and $J = det(F)$.
-
-In the literature appear many more different formulations of the energy. Each one consists of a 1D length term and a 3D volume term.
-
-\textbf{1D Length Term:} This term penalizes length changes.
+The energy as it is formulated reaches its minimum at a zero volume change, meaning $I_{C}=0$ and $\Psi_{M}=-3$.
+Mooney added the hard constraint that $J=1$ so that the energy is minimized at the volume preserving configuration.
+Note that the energy is singularity free and well defined under inversion.
 
 \textbf{3D Volume Term:} Here we are dealing with a volume-preserving penalty term.
+
+\todoredefined[inline]{
+TODO: Bonet and Wood 2008 or 1997? Table looks ugly, improve and add resources.
+}
 

### 2019-11-25 LaTeX-Master-Vorlage/chapter/paper.tex
existing energies getting better

@@
     \textbf{Energy} & \textbf{Author(s)} \\ \hline
-    $\Psi_{Neo}=\frac{\mu}{2}\left(I_{C}-3\right)-\mu \ln J+\frac{\lambda}{2}(\ln J)^{2}$ & Mooney 1940 \\ \hline
+    $\Psi_{Neo}=\frac{\mu}{2}\left(I_{C}-3\right)-\mu \ln J+\frac{\lambda}{2}(\ln J)^{2}$ & e.g. Bonet and Wood 2008 \\ \hline
     $\Psi_{\mathrm{A}}=\frac{\mu}{2}\left(I_{C}-3\right)-\mu \log J+\frac{\lambda}{2}(J-1)^{2}$ & Odgen 1997 \\ \hline
@@
     $\Psi_{\mathrm{A}}$ & $\frac{\mu}{2}\left(I_{C}-3\right)$ & $-\mu \log J+\frac{\lambda}{2}(J-1)^{2}$ \\ \hline
-    $\Psi_{\mathrm{B}}$ & $\frac{\mu}{2}\left(J^{-2 / 3} I_{C}-3\right)$ & $+\frac{\lambda}{2}(J-1)^{2}$ \\ \hline
-    $\Psi_{\mathrm{C}}$ & $\frac{\mu}{2}\left(J^{-2 / 3} I_{C}-3\right)+$ & $\frac{\lambda}{2}(J-1)$ \\ \hline
+    $\Psi_{\mathrm{B}}$ & $\frac{\mu}{2}\left(J^{-2 / 3} I_{C}-3\right)$ & $\frac{\lambda}{2}(J-1)^{2}$ \\ \hline
+    $\Psi_{\mathrm{C}}$ & $\frac{\mu}{2}\left(J^{-2 / 3} I_{C}-3\right)$ & $\frac{\lambda}{2}(J-1)$ \\ \hline
     \end{tabular}
@@
 
-\textbf{1D Length Term:} This term penalizes length changes. Mooney proposed the energy (\cite{mooney1940theory})
+\textbf{1D Length Term:} This term penalizes length changes. Mooney (\cite{mooney1940theory}) originally proposed the 1D length term 
 \[
@@
 \]
-which was later known as "Neo-Hookean" energy.
-
-If we expand the energy with the singular values of the deformation gradient \textbf{F} we get the following term:
+that is used in $\Psi_{Neo}$ and $\Psi_{A}$. If we expand the energy with the singular values of the deformation gradient \textbf{F} we get the following term:
 \[
@@
 \]
-
 The energy as it is formulated reaches its minimum at a zero volume change, meaning $I_{C}=0$ and $\Psi_{M}=-3$.
@@
 Note that the energy is singularity free and well defined under inversion.
+
+The second term 
+\[
+\Psi_{R} = \frac{\mu}{2}\left(J^{-2 / 3} I_{C}-3\right)
+\]
+is used in $\Psi_{B}$ and $\Psi_{C}$ was introduced by Rivlin in 1948. Using the singular values of F we get the following term:
+\[
+\Psi_{R} = \frac{\mu}{2}\left(J^{-2 / 3} I_{C}-3\right) = \frac{\mu}{2}\left(\frac{\sigma_{0}^2 + \sigma_{1}^2 + \sigma_{2}^2}{(\sigma_{0}  \sigma_{1}  \sigma_{2})^\frac{2}{3}}
+ - 3\right)
+\]
+Unfortunately this term is not singularity free. If either $\sigma_{0}$, $\sigma_{1}$ or $\sigma_{2}$ is equal to zero the result is not defined anymore.
 

### 2019-11-25 LaTeX-Master-Vorlage/chapter/paper.tex
rest stability

@@
     \textbf{Energy} & \textbf{Author(s)} \\ \hline
-    $\Psi_{Neo}=\frac{\mu}{2}\left(I_{C}-3\right)-\mu \ln J+\frac{\lambda}{2}(\ln J)^{2}$ & e.g. Bonet and Wood 2008 \\ \hline
+    $\Psi_{Neo}=\frac{\mu}{2}\left(I_{C}-3\right)-\mu \log J+\frac{\lambda}{2}(\log J)^{2}$ & e.g. Bonet and Wood 2008 \\ \hline
     $\Psi_{\mathrm{A}}=\frac{\mu}{2}\left(I_{C}-3\right)-\mu \log J+\frac{\lambda}{2}(J-1)^{2}$ & Odgen 1997 \\ \hline
     $\Psi_{\mathrm{B}}=\frac{\mu}{2}\left(J^{-2 / 3} I_{C}-3\right)+\frac{\lambda}{2}(J-1)^{2}$ & Bower 2009 \\ \hline
-    $\Psi_{\mathrm{C}}=\frac{\mu}{2}\left(J^{-2 / 3} I_{C}-3\right)+\frac{\lambda}{2}(J-1)$ & Wang and Yang 2016 \\ \hline
+    $\Psi_{\mathrm{C}}=\frac{\mu}{2}\left(J^{-2 / 3} I_{C}-3\right)+\frac{\lambda}{2}(J-1)^{2}$ & Wang and Yang 2016 \\ \hline
     \end{tabular}
@@
     \textbf{Energy} & \textbf{1D length term} & \textbf{3D volume term} \\ \hline
-    $\Psi_{Neo}$ & $\frac{\mu}{2}\left(I_{C}-3\right)$ & $-\mu \ln J+\frac{\lambda}{2}(\ln J)^{2}$ \\ \hline
+    $\Psi_{Neo}$ & $\frac{\mu}{2}\left(I_{C}-3\right)$ & $-\mu \log J+\frac{\lambda}{2}(\log J)^{2}$ \\ \hline
     $\Psi_{\mathrm{A}}$ & $\frac{\mu}{2}\left(I_{C}-3\right)$ & $-\mu \log J+\frac{\lambda}{2}(J-1)^{2}$ \\ \hline
     $\Psi_{\mathrm{B}}$ & $\frac{\mu}{2}\left(J^{-2 / 3} I_{C}-3\right)$ & $\frac{\lambda}{2}(J-1)^{2}$ \\ \hline
-    $\Psi_{\mathrm{C}}$ & $\frac{\mu}{2}\left(J^{-2 / 3} I_{C}-3\right)$ & $\frac{\lambda}{2}(J-1)$ \\ \hline
+    $\Psi_{\mathrm{C}}$ & $\frac{\mu}{2}\left(J^{-2 / 3} I_{C}-3\right)$ & $\frac{\lambda}{2}(J-1)^{2}$ \\ \hline
     \end{tabular}
@@
 \[
-\Psi_{M}=\frac{\mu}{2}\left(I_{C}-3\right) = \frac{\mu}{2}\left(\sigma_{0}^2 + \sigma_{1}^2 + \sigma_{2}^2 - 3\right)
+\Psi_{M}=\frac{\mu}{2}\left(\sigma_{0}^2 + \sigma_{1}^2 + \sigma_{2}^2 - 3\right)
 \]
-The energy as it is formulated reaches its minimum at a zero volume change, meaning $I_{C}=0$ and $\Psi_{M}=-3$.
+The energy as it is formulated reaches its minimum at a zero volume change, meaning $I_{C}=0$ which results in $\Psi_{M}=-3$.
 Mooney added the hard constraint that $J=1$ so that the energy is minimized at the volume preserving configuration.
@@
 \[
-\Psi_{R} = \frac{\mu}{2}\left(J^{-2 / 3} I_{C}-3\right) = \frac{\mu}{2}\left(\frac{\sigma_{0}^2 + \sigma_{1}^2 + \sigma_{2}^2}{(\sigma_{0}  \sigma_{1}  \sigma_{2})^\frac{2}{3}}
+\Psi_{R} = \frac{\mu}{2}\left(\frac{\sigma_{0}^2 + \sigma_{1}^2 + \sigma_{2}^2}{(\sigma_{0}  \sigma_{1}  \sigma_{2})^\frac{2}{3}}
  - 3\right)
@@
 
-\textbf{3D Volume Term:} Here we are dealing with a volume-preserving penalty term.
+\textbf{3D Volume Term:} Here we are dealing with a volume-preserving penalty term. The volume term of $\Psi_{Neo}$, meaning
+\[
+\Psi_{Neo, volume} = -\mu \log J+\frac{\lambda}{2}(\log J)^{2}
+\]
+results in some numerical problems since the logarithmic function is not defined for $J<0$ and grows unbounded for $J \rightarrow 0$. In conclusion $\Psi_{Neo, volume}$ is not singularity free. 
+The same applies for the 3D volume term of $\Psi_{A}$
+\[
+\Psi_{A, volume} = -\mu \log J+\frac{\lambda}{2}(J-1)^{2}.
+\]
+The term of $\Psi_{A}$ and $\Psi_{B}$
+\[
+\Psi_{M} = \frac{\lambda}{2}(J-1)^{2}
+\]
+does not have these noted difficulties. It is bounded, well defined and invertible. After these observations we combine the robust length with the robust volume term
+\[
+\Psi_{D} = \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-1)^{2}
+\]
+which is singularity free and well defined under inversion.
 
 \todoredefined[inline]{
-TODO: Bonet and Wood 2008 or 1997? Table looks ugly, improve and add resources.
+TODO: Bonet and Wood 2008 or 1997? Table looks ugly, improve and add resources. minimum at IC=0 or J=0? Overall okay?
 }
@@
 \subsection{Rest Stabilization}
+Although $\Psi_{D}$ meets almost all of our requirements it is not rest stable. This can be shown with the Piola-Kirchhoff (PK1) stress tensor:
+\[
+P_{D}(I) = \frac{\partial \Psi_{D}}{\partial F} (I) = \frac{\partial \Psi_{D}}{\partial F} \left[ \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-1)^{2} \right]
+\]
+\[
+= \frac{\partial \Psi_{D}}{\partial F}  \frac{\mu}{2}\left(\operatorname{tr}(\mathrm{I}^{T} \mathrm{I})-3\right) +\frac{\partial \Psi_{D}}{\partial F} \frac{\lambda}{2}(\operatorname{tr}(\mathrm{I})-1)^{2}
+\]
+\[
+= \mu I + \lambda (\operatorname{det}(I)-1)  \frac{\partial}{\partial F} \operatorname{det}(I) = \mu I \neq 0
+\]
+
+If the energy had rest stability $P_{D}(I)$ would resolve to zero. Unfortunately this is not the case here. In order to solve that problem the authors modified $(J-1)^{2}$ to $(J-\alpha)^{2}$:
+\[
+\Psi_{E} = \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-\alpha)^{2}
+\]
+therefore resulting to:
+\[
+P_{E}(F) = \frac{\partial \Psi_{D}}{\partial F} \left[ \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-\alpha)^{2} \right]
+\]
+\[
+= \mu F + \lambda (\operatorname{det}(F)-\alpha)  \frac{\partial}{\partial F} \operatorname{det}(F)
+\]
+Solving for an alpha that satisfies $P_{E}(I)=0$ gives us $\alpha=1+\frac{\mu}{\lambda}$.
 

### 2019-11-25 LaTeX-Master-Vorlage/chapter/paper.tex
now at eigenanalysis..... no cannot do

@@
 \]
-Solving for an alpha that satisfies $P_{E}(I)=0$ gives us $\alpha=1+\frac{\mu}{\lambda}$.
+Solving for an alpha that satisfies $P_{E}(I)=0$ gives us $\alpha=1+\frac{\mu}{\lambda}$. Now $\Psi_{E}$ has to be changed accordingly:
+\[
+\Psi_{E} = \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-1-\frac{\mu}{\lambda})^{2}
+\]
+\[
+= \frac{\mu}{2}\left(I_{C}-3\right) - \mu\left(J-1\right) + \frac{\lambda}{2}(J-1)^{2} + \left(\frac{\mu}{\lambda}\right)^{2}
+\]
+Since constant disappear under differentiation this expression is functionally equivalent to 
+\[
+\Psi_{E} = \frac{\mu}{2}\left(I_{C}-3\right) - \mu\left(J-1\right) + \frac{\lambda}{2}(J-1)^{2}.
+\]
+Now one can notice that $\Psi_{E}$ looks very similar to $\Psi_{Neo}$.
+The difference is that we replaced $log(J)$ with $(J-1)$ in $\Psi_{E}$.
+Remember that $(J-1)$ is the first term in the taylor approximation of $log(J)$ at $J=1$.
+
+\todoredefined[inline]{
+TODO: Add "Zwischenschritte"? Include all calculations? Do we need a bit of a better conclusion of what we did (taylor, neo, sing. free, rest stable)?
+}
+
+\subsection{Meta-Stability under Degeneracy}
+The final energy is
+\begin{equation}\label{eq:stable_energy}
+\Psi_{new} = \frac{\mu}{2}\left(I_{C}-3\right) + \frac{\lambda}{2}(J-\alpha)^{2} - \frac{\mu}{2}\left(I_{C}+1\right).
+\end{equation}
+With that adjustment the rest stability term shifts to $\alpha=1+\frac{\mu}{\lambda}-\left(\frac{\mu}{4}\right)\lambda$.
+
+\todoredefined[inline]{
+TODO: How much needs to be explained here?
+}
 
 \subsection{Lamé Reparametrization}
-
-\subsection{Previous Work}
 \todoredefined[inline]{
-TODO: Here comes previous work in neo-hookean energy formulation. What is neo-hookean and why do we need it here?
-And what is wrong with each one.
+TODO: How much needs to be explained here?
 }
 
-\subsection{Stable Neo-Hookean Energy}
-Conclude to the energy proposed in the paper.
-
 \section{Energy Analysis}
-Calculations and Herleitungen
+In this chapter it is shown that one can perform a complete eigenanalysis on equation \ref{eq:stable_energy}.
 

### 2019-11-29 LaTeX-Master-Vorlage/chapter/paper.tex
trying flowcharts, getting there someday still looks ugly
working on paper

@@
 The difference is that we replaced $log(J)$ with $(J-1)$ in $\Psi_{E}$.
-Remember that $(J-1)$ is the first term in the taylor approximation of $log(J)$ at $J=1$.
+Remember that $(J-1)$ is the first term in the taylor approximation of $log(J)$ at $J=1$:
+\[
+\sum_{n=0}^{\infty} = \frac{f^{(n)}(1)}{n!} (J-1)^{n} =
+\]
+\[
+= (J-1) - \frac{1}{2} (J-1)^{2} + \frac{1}{3} (J-1)^{3} -\frac{1}{4} (J-1)^{4} + ...
+\]
 
@@
 \subsection{First Piola-Kirchhoff Stress (PK1)}
-Explain.
+We start with PK1 for equation \ref{eq:stable_energy}:
+\[
+P(F) = \frac{\partial \Psi_{D}}{\partial F} \left[ \frac{\mu}{2}\left(I_{C}-3\right) + \frac{\lambda}{2}(J-\alpha)^{2} - \frac{\mu}{2}\left(I_{C}+1\right) \right]
+\]
 
@@
 \section{Experiments with the Code}
-The authors of the paper \textit{Stable Neo-Hookean Flesh Simulation} \cite{Smith:2018:SNF:3191713.3180491} kindly provided the implementation for an application of their formulated energy.
-In this code they implemented the stretch test on a cube.
-The outputs were 26 static images with show the deformation in 25 steps.
-The parameters the code expects are the two lamé parameters $\mu$ and $\lambda$ and a value for defining the desired resolution the objects should have.
+The authors of the paper \textit{Stable Neo-Hookean Flesh Simulation} \cite{Smith:2018:SNF:3191713.3180491} provided the implementation for an application of their formulated energy.
+In said code they implemented the stretch test on a cube.
+Their implementation demands a directory into which the output files should be saved, the two lamé parameters $\mu$ and $\lambda$ and a value for defining the desired resolution as input data.
+Here is an example for a command with resolution = 10, $\mu=1.0$, $\lambda=10.0$ and asks the output files to be written into the directory \textit{output}:
+\begin{lstlisting}[language=bash]
+$ ./tetcli 10 stable_neo_hookean 1.0 10.0 output
+\end{lstlisting}
+
+The algorithm then calculates the deformation in 25 steps and the deformation increases in each step.
+The outputs are 26 static objects that show the object in its rest state and the 25 steps of deformation.
+
+\begin{tikzpicture}[node distance=2cm]
+\node (input) [process] {$\mu$, $\lambda$, resolution};
+\node (code) [decision, right of=input, xshift=3cm] {Code};
+\node (output) [process, right of=code, xshift=3cm] {26 objects};
+
+\draw [arrow] (input) -- node[anchor=south] {Input}(code);
+\draw [arrow] (code) -- node[anchor=south] {Output}(output);
+\end{tikzpicture}
 
 \todoredefined[inline]{
-TODO: Explain how the code is implemented in simple words and how the energy is taken in account with the poisson's ratio. Make scheme with input - box / code - output. Do I have to reference code?
+TODO: Explain how the code is implemented in simple words and how the energy is taken in account with the poisson's ratio. Do I have to reference code? Explain tetcli and Hexcli.
 }

### 2019-11-29 LaTeX-Master-Vorlage/chapter/paper.tex
loooots of calculations

@@
 \]
-\[
+\begin{equation}\label{eq:pk1_unstable}
 = \mu F + \lambda (\operatorname{det}(F)-\alpha)  \frac{\partial}{\partial F} \operatorname{det}(F)
-\]
+\end{equation}
+
 Solving for an alpha that satisfies $P_{E}(I)=0$ gives us $\alpha=1+\frac{\mu}{\lambda}$. Now $\Psi_{E}$ has to be changed accordingly:
@@
 \[
-= (J-1) - \frac{1}{2} (J-1)^{2} + \frac{1}{3} (J-1)^{3} -\frac{1}{4} (J-1)^{4} + ...
+= \boldsymbol{(J-1)} - \frac{1}{2} (J-1)^{2} + \frac{1}{3} (J-1)^{3} -\frac{1}{4} (J-1)^{4} + ...
 \]
@@
 \begin{equation}\label{eq:stable_energy}
-\Psi_{new} = \frac{\mu}{2}\left(I_{C}-3\right) + \frac{\lambda}{2}(J-\alpha)^{2} - \frac{\mu}{2}\left(I_{C}+1\right).
+\Psi_{new} = \frac{\mu}{2}\left(I_{C}-3\right) + \frac{\lambda}{2}(J-\alpha)^{2} - \frac{\mu}{2} \operatorname{log}\left(I_{C}+1\right).
 \end{equation}
@@
 P(F) = \frac{\partial \Psi_{D}}{\partial F} \left[ \frac{\mu}{2}\left(I_{C}-3\right) + \frac{\lambda}{2}(J-\alpha)^{2} - \frac{\mu}{2}\left(I_{C}+1\right) \right]
+\]
+\[
+\stackrel{\text{eq.\ref{eq:pk1_unstable}}}{=} \mu F + \lambda (\operatorname{det}(F)-\alpha)  \frac{\partial}{\partial F} \operatorname{det}(F) - \frac{\partial}{\partial F} \left[\operatorname{log}\left(\operatorname{tr}(\mathrm{F}^{T}F)+1\right)\right]
+\]
+\[
+= \mu F + \lambda (\operatorname{det}(F)-\alpha)  \frac{\partial}{\partial F} \operatorname{det}(F) - \mu F \frac{1}{\operatorname{tr}(\mathrm{F}^{T}F) + 1}
+\]
+\[
+= \mu \left( 1 - \frac{1}{\operatorname{tr}(\mathrm{F}^{T}F) + 1}\right) F + \lambda(J-\alpha)\frac{\partial J}{\partial F}
+\]
+
+with $\alpha=1+\frac{\mu}{\lambda}-\left(\frac{\mu}{4}\right)\lambda$. For future use we write $\frac{\partial J}{\partial F}$ as cross products:
+\[
+\frac{\partial J}{\partial F} = \left[ \,f_1 \times f_2\, \bigg| \,f_2 \times f_0\, \bigg| \,f_0 \times f_1\, \right].
 \]

### 2019-12-01 LaTeX-Master-Vorlage/chapter/paper.tex
even more calculations
aaaaand even more calculations
cal cal cal everywhere cannot do this anymore

@@
 \subsection{The Energy Hessian Terms}
-Calculations
+Using the scalar notation for F the hessian of the energy can be written in a fourth-order matrix-of-matrices:
+\[
+\frac{\partial^2 \psi}{\partial F^2} = \frac{\partial P(F)}{\partial F} = 
+\left[\begin{array}{ccc}{\left[\frac{\partial P(F)}{\partial f_0}\right]} & {\left[\frac{\partial P(F)}{\partial f_3}\right]} & {\left[\frac{\partial P(F)}{\partial f_6}\right]} \\ {\left[\frac{\partial P(F)}{\partial f_1}\right]} & {\left[\frac{\partial P(F)}{\partial f_4}\right]} & {\left[\frac{\partial P(F)}{\partial f_7}\right]} \\ {\left[\frac{\partial P(F)}{\partial f_2}\right]} & {\left[\frac{\partial P(F)}{\partial f_5}\right]} & {\left[\frac{\partial P(F)}{\partial f_8}\right]} \end{array}\right]
+\]
+
+in which each entry is defined as
+\[
+\frac{\partial P(F)}{\partial f_i} = \frac{\partial}{\partial f_i} \left[ \mu \left( 1 - \frac{1}{\operatorname{tr}(\mathrm{F}^{T}F) + 1}\right) F + \lambda(J-\alpha)\frac{\partial J}{\partial F} \right]
+\]
+\[
+\stackrel{\text{prod.rule}}{=} \underbrace{\frac{\partial F}{\partial f_i} \mu \left( 1 - \frac{1}{\operatorname{tr}(\mathrm{F}^{T}F) + 1}\right)}_{\mathrm{T}_{i}}  + \underbrace{F \mu \frac{2}{\left(\operatorname{tr}(\mathrm{F}^{T}F) + 1\right)^2} f_i}_{_{\mathrm{M}_{i}}}
+\]
+\[
+r+ \underbrace{\lambda \frac{\partial J}{\partial f_i} \frac{\partial J}{\partial F}}_{_{\mathrm{G}_{i}}}+ \underbrace{\lambda (J- \alpha) \frac{\partial^2 J}{\partial F\partial f_i}}_{_{\mathrm{H}_{i}}} \in \mathbb{R}^{3}
+\]
+Each term in the final equation $\mathrm{T}_i$, $\mathrm{M}_i$, $\mathrm{G}_i$, $\mathrm{H}_i$ respectively the Tikohonov, Mu, volume Gradient and volume Hessian term will be examined separately in the following.
 
 \subsection{The Tikhonov, Mu, and Gradient Terms}
-Calculations
+\textbf{Tikhonov}: We start with the Tikhonov term:
+\[
+\mathbb{T} = \frac{\partial F}{\partial f_i} = \left[\begin{array}{ccc}{\begin{bmatrix} 1 & 0 & 0 \\ 0 & 0 & 0 \\ 0 & 0 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 1 & 0 \\ 0 & 0 & 0 \\ 0 & 0 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 0 & 1 \\ 0 & 0 & 0 \\ 0 & 0 & 0 \end{bmatrix}} \\ {\begin{bmatrix} 0 & 0 & 0 \\ 1 & 0 & 0 \\ 0 & 0 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 0 & 0 \\ 0 & 1 & 0 \\ 0 & 0 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 0 & 0 \\ 0 & 0 & 1 \\ 0 & 0 & 0 \end{bmatrix}} \\ {\begin{bmatrix} 0 & 0 & 0 \\ 0 & 0 & 0 \\ 1 & 0 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 0 & 0 \\ 0 & 0 & 0 \\ 0 & 1 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 0 & 0 \\ 0 & 0 & 0 \\ 0 & 0 & 1 \end{bmatrix}} \end{array}\right].
+\]
+If we vectorize $\mathbb{T}$ we get the identity matrix $\mathbb{I} \in \mathbb{R}^{9x9}$ which is full rank, positive definite and independent of the values in F.
+It serves as a regularizer for the rest of the energy:
+\[
+\operatorname{vec}(\mathbb{T}) = \mathbb{I} = \in \mathbb{R}^{9x9}.
+\]
+
+\textbf{Mu}: 
+\[
+\mathbb{M} = F f_i = \left[\begin{array}{ccc}{\begin{bmatrix} f_0^2 & f_0f_3 & f_0f_6 \\ f_0f_1 & f_0f_4 & f_0f_7 \\ f_0f_2 & f_0f_5 & f_0f_8 \end{bmatrix}} & {\begin{bmatrix} f_3f_0 & f_3^2 & f_3f_6 \\ f_3f_1 & f_3f_4 & f_3f_7 \\ f_3f_2 & f_3f_5 & f_3f_8 \end{bmatrix}} & {\begin{bmatrix} f_6f_0 & f_6f_3 & f_6f_6 \\ f_6f_1 & f_6f_4 & f_6f_7 \\ f_6f_2 & f_6f_5 & f_6f_8 \end{bmatrix}} \\ {\begin{bmatrix} f_1f_0 & f_1f_3 & f_1f_6 \\ f_1^2 & f_1f_4 & f_1f_7 \\ f_1f_2 & f_1f_5 & f_1f_8 \end{bmatrix}} & {\begin{bmatrix} f_4f_0 & f_4f_3 & f_4f_6 \\ f_4f_1 & f_4^2 & f_4f_7 \\ f_4f_2 & f_4f_5 & f_4f_8 \end{bmatrix}} & {\begin{bmatrix} f_7f_0 & f_7f_3 & f_7f_6 \\ f_7f_1 & f_7f_4 & f_7^2 \\ f_7f_2 & f_7f_5 & f_7f_8 \end{bmatrix}} \\ {\begin{bmatrix} f_2f_0 & f_2f_3 & f_2f_6 \\ f_2f_1 & f_2f_4 & f_2f_7 \\ f_2^2 & f_2f_5 & f_2f_8 \end{bmatrix}} & {\begin{bmatrix} f_5f_0 & f_5f_3 & f_5f_6 \\ f_5f_1 & f_5f_4 & f_5f_7 \\ f_5f_2 & f_5^2 & f_5f_8 \end{bmatrix}} & {\begin{bmatrix} f_8f_0 & f_8f_3 & f_8f_6 \\ f_8f_1 & f_8f_4 & f_8f_7 \\ f_8f_2 & f_8f_5 & f_8^2 \end{bmatrix}} \end{array}\right]
+\]
+\[
+\operatorname{vec}(\mathbb{M})= \begin{bmatrix} f_0^2 & f_1f_0 & f_2f_0 & f_3f_0 & f_4f_0 & f_5f_0 & f_6f_0 & f_7f_0 & f_8f_0 \\ f_0f_1 & f_1^2 & f_2f_1 & f_3f_1 & f_4f_1 & f_5f_1 & f_6f_1 & f_7f_1 & f_8f_1 \\ f_0f_2 & f_1f_2 & f_2^2 & f_3f_2 & f_4f_2 & f_5f_2 & f_6f_2 & f_7f_2 & f_8f_2 \\ f_0f_3 & f_1f_3 & f_2f_3 & f_3^2 & f_4f_2^3 & f_5f_3 & f_6f_3 & f_7f_3 & f_8f_3 \\ f_0f_4 & f_1f_4 & f_2f_4 & f_3f_4 & f_4^2 & f_5f_4 & f_6f_4 & f_7f_4 & f_8f_4 \\ f_0f_5 & f_1f_5 & f_2f_5 & f_3f_5 & f_4f_5 & f_5^2 & f_6f_5 & f_7f_5 & f_8f_5 \\ f_0f_6 & f_1f_6 & f_2f_6 & f_3f_6 & f_4f_6 & f_5f_6 & f_6^2 & f_7f_6 & f_8f_6 \\ f_0f_7 & f_1f_7 & f_2f_7 & f_3f_7 & f_4f_7 & f_5f_7 & f_6f_7 & f_7^2 & f_8f_7 \\ f_0f_8 & f_1f_8 & f_2f_8 & f_3f_8 & f_4f_8 & f_5f_8 & f_6f_8 & f_7f_8 & f_8^2 \end{bmatrix}
+\]
 

### 2019-12-02 LaTeX-Master-Vorlage/chapter/Background.tex
cal cal cal

@@
 \textbf{a}: Vector \\
-vec(\textbf{A}) = $\boldsymbol{\check{a}}$: Vectorized matrix \\
-$\mathbb{A} = \boldsymbol{\check{A}}$: matrix-of-matrices
+vec(\textbf{A}) = $\mathbf{\check{a}}$: Vectorized matrix \\
+$\mathbb{A} = \mathbf{\check{A}}$: matrix-of-matrices
 \end{addmargin}
@@
 \todoredefined[inline]{
-TODO: Complete this section. Add lemmas and theorems used afterwards in the calculations. Possible adjustments may come at the end.
+TODO: Complete this section. Add lemmas and theorems used afterwards in the calculations. Possible adjustments may come at the end. Add Frobenius norm?
 }
@@
 
-\[
-\textbf{F} = \left[ \,f_0\, \bigg| \,f_1\, \bigg| \,f_2\, \right] = \begin{bmatrix} f_0 & f_3 & f_6 \\ f_1 & f_4 & f_7 \\ f_2 & f_5 & f_8 \end{bmatrix}
-\]
+\begin{equation}\label{eq:deformation_gradient}
+\textbf{F} = \left[ \,f_0\, \bigg| \,f_1\, \bigg| \,f_2\, \right] = \begin{bmatrix} f_0 & f_3 & f_6 \\ f_1 & f_4 & f_7 \\ f_2 & f_5 & f_8 \end{bmatrix}.
+\end{equation}
+
+Using the SVD theorem mentioned in theorem \ref{SVD} $\mathbf{F}$ can be written in the form of
+
+\begin{equation}\label{eq:svd_gradient}
+\mathbf{F} = \mathbf{U \Sigma V\intercal}
+\end{equation}
+
+in which $\mathbf{\Sigma}$ stands for
+\begin{equation}\label{eq:svd_simga}
+\mathbf{\Sigma} = \left[\begin{matrix}  \sigma_0 & 0 & 0 \\ 0 & \sigma_1 & 0 \\ 0 & 0 & \sigma_2 \end{matrix}\right] .
+\end{equation}
+
+The $\sigma_i$ denote the singular values of $\mathbf{\Sigma}$.
+Unlike the normal convention the authors of the paper \textit{Stable Neo-Hookean Flesh Simulation} the rotation variant moves reflections to $\mathbf{\Sigma}$.
+This results into $\operatorname{det}(\mathbf{U})=\operatorname{det}(\mathbf{V})=1$ and the property that $\Sigma$ is allowed to have negative entries.
 
@@
 \[
-F = R S
+\mathbf{F} = \mathbf{RS}
 \]

### 2019-12-02 LaTeX-Master-Vorlage/chapter/paper.tex
game over
cal cal cal

--- 2019-11-29 LaTeX-Master-Vorlage/chapter/paper.tex
@@
 \subsection{The Energy Hessian Terms}
-Calculations
+Using the scalar notation for F the hessian of the energy can be written in a fourth-order matrix-of-matrices:
+\[
+\frac{\partial^2 \psi}{\partial F^2} = \frac{\partial P(F)}{\partial F} = 
+\left[\begin{array}{ccc}{\left[\frac{\partial P(F)}{\partial f_0}\right]} & {\left[\frac{\partial P(F)}{\partial f_3}\right]} & {\left[\frac{\partial P(F)}{\partial f_6}\right]} \\ {\left[\frac{\partial P(F)}{\partial f_1}\right]} & {\left[\frac{\partial P(F)}{\partial f_4}\right]} & {\left[\frac{\partial P(F)}{\partial f_7}\right]} \\ {\left[\frac{\partial P(F)}{\partial f_2}\right]} & {\left[\frac{\partial P(F)}{\partial f_5}\right]} & {\left[\frac{\partial P(F)}{\partial f_8}\right]} \end{array}\right]
+\]
+
+in which each entry is defined as
+\[
+\frac{\partial P(F)}{\partial f_i} = \frac{\partial}{\partial f_i} \left[ \mu \left( 1 - \frac{1}{\operatorname{tr}(\mathrm{F}^{T}F) + 1}\right) F + \lambda(J-\alpha)\frac{\partial J}{\partial F} \right]
+\]
+\[
+\stackrel{\text{prod.rule}}{=} \underbrace{\frac{\partial F}{\partial f_i} \mu \left( 1 - \frac{1}{\operatorname{tr}(\mathrm{F}^{T}F) + 1}\right)}_{\mathrm{T}_{i}}  + \underbrace{F \mu \frac{2}{\left(\operatorname{tr}(\mathrm{F}^{T}F) + 1\right)^2} f_i}_{_{\mathrm{M}_{i}}}
+\]
+\[
+r+ \underbrace{\lambda \frac{\partial J}{\partial f_i} \frac{\partial J}{\partial F}}_{_{\mathrm{G}_{i}}}+ \underbrace{\lambda (J- \alpha) \frac{\partial^2 J}{\partial F\partial f_i}}_{_{\mathrm{H}_{i}}} \in \mathbb{R}^{3}
+\]
+Each term in the final equation $\mathrm{T}_i$, $\mathrm{M}_i$, $\mathrm{G}_i$, $\mathrm{H}_i$ respectively the Tikohonov, Mu, volume Gradient and volume Hessian term will be examined separately in the following.
 
 \subsection{The Tikhonov, Mu, and Gradient Terms}
-Calculations
+\textbf{Tikhonov}: The Tikhonov term can be viewed as a fourth-order matrix-of-matrices
+\[
+\mathbb{T} = \frac{\partial \mathbf{F}}{\partial f_i} = \left[\begin{array}{ccc}{\begin{bmatrix} 1 & 0 & 0 \\ 0 & 0 & 0 \\ 0 & 0 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 1 & 0 \\ 0 & 0 & 0 \\ 0 & 0 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 0 & 1 \\ 0 & 0 & 0 \\ 0 & 0 & 0 \end{bmatrix}} \\ {\begin{bmatrix} 0 & 0 & 0 \\ 1 & 0 & 0 \\ 0 & 0 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 0 & 0 \\ 0 & 1 & 0 \\ 0 & 0 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 0 & 0 \\ 0 & 0 & 1 \\ 0 & 0 & 0 \end{bmatrix}} \\ {\begin{bmatrix} 0 & 0 & 0 \\ 0 & 0 & 0 \\ 1 & 0 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 0 & 0 \\ 0 & 0 & 0 \\ 0 & 1 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 0 & 0 \\ 0 & 0 & 0 \\ 0 & 0 & 1 \end{bmatrix}} \end{array}\right].
+\]
+If we vectorize $\mathbb{T}$ we get the identity matrix $\mathbb{I} \in \mathbb{R}^{9x9}$ which is full rank, positive definite and independent of the values in F.
+It serves as a regularizer for the rest of the energy
+\[
+\operatorname{vec}(\mathbb{T}) =  \mathbf{\check{T}} = \mathbb{I} = \in \mathbb{R}^{9x9}.
+\]
+
+\textbf{Mu}: The Mu term has the same structure with different entries
+\[
+\mathbb{M} = \mathbf{F} f_i = \left[\begin{array}{ccc}{\begin{bmatrix} f_0^2 & f_0f_3 & f_0f_6 \\ f_0f_1 & f_0f_4 & f_0f_7 \\ f_0f_2 & f_0f_5 & f_0f_8 \end{bmatrix}} & {\begin{bmatrix} f_3f_0 & f_3^2 & f_3f_6 \\ f_3f_1 & f_3f_4 & f_3f_7 \\ f_3f_2 & f_3f_5 & f_3f_8 \end{bmatrix}} & {\begin{bmatrix} f_6f_0 & f_6f_3 & f_6f_6 \\ f_6f_1 & f_6f_4 & f_6f_7 \\ f_6f_2 & f_6f_5 & f_6f_8 \end{bmatrix}} \\ {\begin{bmatrix} f_1f_0 & f_1f_3 & f_1f_6 \\ f_1^2 & f_1f_4 & f_1f_7 \\ f_1f_2 & f_1f_5 & f_1f_8 \end{bmatrix}} & {\begin{bmatrix} f_4f_0 & f_4f_3 & f_4f_6 \\ f_4f_1 & f_4^2 & f_4f_7 \\ f_4f_2 & f_4f_5 & f_4f_8 \end{bmatrix}} & {\begin{bmatrix} f_7f_0 & f_7f_3 & f_7f_6 \\ f_7f_1 & f_7f_4 & f_7^2 \\ f_7f_2 & f_7f_5 & f_7f_8 \end{bmatrix}} \\ {\begin{bmatrix} f_2f_0 & f_2f_3 & f_2f_6 \\ f_2f_1 & f_2f_4 & f_2f_7 \\ f_2^2 & f_2f_5 & f_2f_8 \end{bmatrix}} & {\begin{bmatrix} f_5f_0 & f_5f_3 & f_5f_6 \\ f_5f_1 & f_5f_4 & f_5f_7 \\ f_5f_2 & f_5^2 & f_5f_8 \end{bmatrix}} & {\begin{bmatrix} f_8f_0 & f_8f_3 & f_8f_6 \\ f_8f_1 & f_8f_4 & f_8f_7 \\ f_8f_2 & f_8f_5 & f_8^2 \end{bmatrix}} \end{array}\right].
+\]
+When vectorizing $\mathbb{M}$ the resulting matrix has the squared values of $f_i$ placed on the diagonal
+\[
+\operatorname{vec}(\mathbb{M})= \mathbf{\check{M}} = \begin{bmatrix} f_0^2 & f_1f_0 & f_2f_0 & f_3f_0 & f_4f_0 & f_5f_0 & f_6f_0 & f_7f_0 & f_8f_0 \\ f_0f_1 & f_1^2 & f_2f_1 & f_3f_1 & f_4f_1 & f_5f_1 & f_6f_1 & f_7f_1 & f_8f_1 \\ f_0f_2 & f_1f_2 & f_2^2 & f_3f_2 & f_4f_2 & f_5f_2 & f_6f_2 & f_7f_2 & f_8f_2 \\ f_0f_3 & f_1f_3 & f_2f_3 & f_3^2 & f_4f_3 & f_5f_3 & f_6f_3 & f_7f_3 & f_8f_3 \\ f_0f_4 & f_1f_4 & f_2f_4 & f_3f_4 & f_4^2 & f_5f_4 & f_6f_4 & f_7f_4 & f_8f_4 \\ f_0f_5 & f_1f_5 & f_2f_5 & f_3f_5 & f_4f_5 & f_5^2 & f_6f_5 & f_7f_5 & f_8f_5 \\ f_0f_6 & f_1f_6 & f_2f_6 & f_3f_6 & f_4f_6 & f_5f_6 & f_6^2 & f_7f_6 & f_8f_6 \\ f_0f_7 & f_1f_7 & f_2f_7 & f_3f_7 & f_4f_7 & f_5f_7 & f_6f_7 & f_7^2 & f_8f_7 \\ f_0f_8 & f_1f_8 & f_2f_8 & f_3f_8 & f_4f_8 & f_5f_8 & f_6f_8 & f_7f_8 & f_8^2 \end{bmatrix}.
+\]
+This structure makes it possible to write $\mathbf{\check{M}}$ as an outer product of $\operatorname{vec}(\mathbf{F})$
+\[
+\mathbf{\check{M}}= \operatorname{vec}(\mathbf{F})\operatorname{vec}(\mathbf{F})^\intercal = \mathbf{\check{f}} \mathbf{\check{f}}^\intercal.
+\]
+This matrix has rank one and has a single non-zero eigenvalue. In order to examine the eigenvalues one can calculate
+\[
+\| \mathbf{\check{f}} \|^{2}_{2} = \sum_{n=0}^8 | f_n |^2 = \| \mathbf{F} \|^{2}_{F} = \sum_{n=0}^3 \sigma^2_i = \left( \sigma_0^2 + \sigma_1^2 + \sigma_2^2 \right)
+\]
+in which $\|\cdot\|_F$ stands for the Frobenius norm and $\sigma_i$ for the singular values from $\mathbf{\Sigma}$ in the SVD of $\mathbf{F}$ stated in eq.
+\ref{eq:svd_simga}.
+The eigenvector is $\mathbf{\check{f}} / \| \mathbf{\check{f}} \|$.
+The eigenvalue is always non-negative and large if $\mathbf{F}$ contains a large strech.
+
+\textbf{Gradient}:
+\begin{align*}
+\mathbb{G}(\mathbf{F}) &= \frac{\partial J}{\partial \mathbf{F}} \frac{\partial J}{\partial fi} \\ \\
+\operatorname{vec}(\mathbb{G}(\mathbf{F})) &= \mathbf{\check{G}} = \operatorname{vec}\left(\frac{\partial J}{\partial \mathbf{F}}\right) \operatorname{vec}\left(\frac{\partial J}{\partial \mathbf{F}}\right)^\intercal = \mathbf{\check{g}} \mathbf{\check{g}}^\intercal
+\end{align*}
 
@@
 Calculations
+
+\todoredefined[inline]{
+TODO: Make notation consistent (bold, cursive etc.) Explain better each step. Include all calculations? Make matrix of matrices more beautiful (more space). Eigenvalues of Mu term?
+}
 

### 2019-12-02 LaTeX-Master-Vorlage/chapter/paper.tex
finally term finished, except hessian

@@
 
-with $\alpha=1+\frac{\mu}{\lambda}-\left(\frac{\mu}{4}\right)\lambda$. For future use we write $\frac{\partial J}{\partial F}$ as cross products:
-\[
-\frac{\partial J}{\partial F} = \left[ \,f_1 \times f_2\, \bigg| \,f_2 \times f_0\, \bigg| \,f_0 \times f_1\, \right].
-\]
+with $\alpha=1+\frac{\mu}{\lambda}-\left(\frac{\mu}{4}\right)\lambda$. For future use we write $\frac{\partial J}{\partial \mathbf{F}}$ as cross products:
+\begin{equation}\label{eq:cross_product}
+\frac{\partial J}{\partial \mathbf{F}} = \left[ \,f_1 \times f_2\, \bigg| \,f_2 \times f_0\, \bigg| \,f_0 \times f_1\, \right].
+\end{equation}
 
@@
 
-\textbf{Gradient}:
-\begin{align*}
-\mathbb{G}(\mathbf{F}) &= \frac{\partial J}{\partial \mathbf{F}} \frac{\partial J}{\partial fi} \\ \\
-\operatorname{vec}(\mathbb{G}(\mathbf{F})) &= \mathbf{\check{G}} = \operatorname{vec}\left(\frac{\partial J}{\partial \mathbf{F}}\right) \operatorname{vec}\left(\frac{\partial J}{\partial \mathbf{F}}\right)^\intercal = \mathbf{\check{g}} \mathbf{\check{g}}^\intercal
-\end{align*}
+\textbf{Gradient}: The gradient term also has the same structure as the two terms before with different entries defined by
+\[
+\mathbb{G}(\mathbf{F}) = \frac{\partial J}{\partial \mathbf{F}} \frac{\partial J}{\partial fi}.
+\]
+The vectorized matrix $\mathbf{\check{G}}$ can be written in a similar form as for the Mu term.
+With the help of the cross product of $\partial J / \partial \mathbf{F}$ stated in eq.
+\ref{eq:cross_product} $\mathbf{\check{G}}$ can be written as an outer product in the following way:
+\[
+\operatorname{vec}(\mathbb{G}(\mathbf{F})) = \mathbf{\check{G}} = \operatorname{vec}\left(\frac{\partial J}{\partial \mathbf{F}}\right) \operatorname{vec}\left(\frac{\partial J}{\partial \mathbf{F}}\right)^\intercal = \mathbf{\check{g}} \mathbf{\check{g}}^\intercal.
+\]
+As in the Mu term one can notice a single non-zero, non-negative:
+\[
+\| \mathbf{\check{g}} \|^2_2 = \left\| \frac{\partial J}{\partial \mathbf{F}} \right \|^2_F = \left[ (\sigma_0 \sigma_1)^2 + (\sigma_0 \sigma_2)^2 + (\sigma_1 \sigma_2)^2 \right].
+\]
+The eigenvector is $\mathbf{\check{g}} / \| \mathbf{\check{g}} \|$.
 
@@
 \todoredefined[inline]{
-TODO: Make notation consistent (bold, cursive etc.) Explain better each step. Include all calculations? Make matrix of matrices more beautiful (more space). Eigenvalues of Mu term?
+TODO: Make notation consistent (bold, cursive etc.) Explain better each step.
+Include all calculations?
+Make matrix of matrices more beautiful (more space).
+Eigenvalues of Mu and Gradient term better explain?
 }

### 2019-12-02 LaTeX-Master-Vorlage/chapter/paper.tex
volume hessian

@@
     \caption{Quantities Derived from the Deformation Gradient \textbf{F} taken from \cite{Smith:2018:SNF:3191713.3180491}}
-\label{table:1}
+\label{table:gradient_quantities}
 \end{table}
@@
     \caption{Summary of proposed energies taken from \cite{Smith:2018:SNF:3191713.3180491}}
-\label{table:1}
+\label{table:energies}
 \end{table}
@@
     \caption{Energies split up into its 1D length and 3D volume term}
-\label{table:1}
+\label{table:energies_split}
 \end{table}
@@
 \subsection{The Tikhonov, Mu, and Gradient Terms}
-\textbf{Tikhonov}: The Tikhonov term can be viewed as a fourth-order matrix-of-matrices
+\subsubsection{Tikhonov}
+The Tikhonov term can be viewed as a fourth-order matrix-of-matrices
 \[
@@
 
-\textbf{Mu}: The Mu term has the same structure with different entries
+\subsubsection{Mu}
+The Mu term has the same structure with different entries
 \[
@@
 
-\textbf{Gradient}: The gradient term also has the same structure as the two terms before with different entries defined by
+\subsubsection{Gradient}
+The gradient term also has the same structure as the two terms before with different entries defined by
 \[
@@
 \subsection{The Volume Hessian}
-Calculations
+The volume Hessian term is of the form
+\[
+\mathbb{H} = \frac{\partial^2 J}{\partial \mathbf{F} \partial f_i} \in \mathbb{R}^{9\times 9}.
+\]
+Vectorizing $\mathbb{H}$ reveals the structure
+\[
+\operatorname{vec}(\mathbb{H}) = \mathbf{\check{H}} = \left[ \begin{matrix}
+0 & -\mathbf{\widehat{f_2}} & \mathbf{\widehat{f_1}} \\ \mathbf{\widehat{f_2}} & 0 & -\mathbf{\widehat{f_0}} \\ -\mathbf{\widehat{f_1}} & \mathbf{\widehat{f_0}} & 0 \end{matrix} \right]
+\]
+where $\mathbf{\widehat{f_1}}$ stands for a cross-product matrix:
+\[
+\mathbf{\widehat{x}} = \left[ \begin{matrix}
+0 & -x_2 & x_1 \\ x_2 & 0 & -x_0 \\ -x_1 & x_0 & 0 \end{matrix} \right].
+\]
+One can easily observe that $\mathbf{\check{H}}$ is a \textit{self-similar} cross-product matrix. Meaning that the macro structure of the matrix is the same as the micro structure.
+
+\subsubsection{Volume Hessian Eigenvalues}
+For determining the eigenvalues of $\mathbf{\check{H}}$ one needs to examine the two characteristic polynomials:
+
+\begin{align*}
+&\epsilon^3 - \operatorname{tr}(\mathbf{C}) \epsilon - 2 J = 0 \tag{1}  \\
+&\epsilon^3 - \operatorname{tr}(\mathbf{C}) \epsilon^2 + \frac{1}{2} \left( \operatorname{tr^2}(\mathbf{C}) - \operatorname{tr}(\mathbf{C}^2) \right) \epsilon - \operatorname{det}(\mathbf{C}) = 0 \tag(2)
+\end{align*}
+
+where $\epsilon$ denote the eigenvalues of $\mathbf{\check{H}}$ and $\mathbf{C}$ is taken from table \ref{table:gradient_quantities}. Equation (1) is easier to solve and
 
@@
 Eigenvalues of Mu and Gradient term better explain?
+Check each equation if correctly written.
 }

### 2019-12-02 LaTeX-Master-Vorlage/chapter/Background.tex
improving everything

@@
 Furthermore we will use the tensor notation used in the paper \textit{Stable Neo-Hookean Flesh Simulation}.
-They decided to to define vectorization vec(.) as column-wise flattening of a matrix into a vector (\cite{Smith:2018:SNF:3191713.3180491}, 12:5) similar to Golub and Van Loan (2012) \cite{golub2012matrix}.
+They decided to to define vectorization vec(\cdot) as column-wise flattening of a matrix into a vector (\cite{Smith:2018:SNF:3191713.3180491}, 12:5) similar to Golub and Van Loan (2012) \cite{golub2012matrix}.
 
-In order to indicate that we are dealing with a vectorized matrix we will use the symbol $\check{.}$ as shown in the following equation:
+In order to indicate that we are dealing with a vectorized matrix we will use the symbol $\check{\cdot}$ as shown in the following equation:
 
 \[
-\textbf{A} = \begin{bmatrix} a & c \\ b & d \end{bmatrix} \qquad \operatorname{vec}(\textbf{A}) = \boldsymbol{\check{a}} = \begin{bmatrix} a \\ b \\ c \\ d \end{bmatrix}.
+\textbf{A} = \begin{bmatrix} a & c \\ b & d \end{bmatrix} \qquad \operatorname{vec}(\textbf{A}) = \mathbf{\check{a}} = \begin{bmatrix} a \\ b \\ c \\ d \end{bmatrix}.
 \]
@@
 \mathbb{A} = 
-\left[\begin{array}{cc}{\begin{bmatrix} a & c \\ b & d \end{bmatrix}} & {\begin{bmatrix} a & c \\ b & d \end{bmatrix}} \\ {\begin{bmatrix} a & c \\ b & d \end{bmatrix}} & {\begin{bmatrix} a & c \\ b & d \end{bmatrix}}\end{array}\right]
+\left[\begin{array}{cc}{\begin{bmatrix} a & c \\ b & d \end{bmatrix}} & {\begin{bmatrix} i & k \\ j & l \end{bmatrix}} \\ {\begin{bmatrix} e & g \\ f & h \end{bmatrix}} & {\begin{bmatrix} m & o \\ n & p \end{bmatrix}}\end{array}\right]
 =
@@
 \[
-\mathbb{A} = \operatorname{vec}(\mathbb{A})=\left[\operatorname{vec}\left(\mathrm{A}_{00}\right)\left|\operatorname{vec}\left(\mathrm{A}_{10}\right)\right| \operatorname{vec}\left(\mathrm{A}_{01}\right) | \operatorname{vec}\left(\mathrm{A}_{11}\right)\right]
+\mathbb{A} = \operatorname{vec}(\mathbb{A})= \left[ \,\operatorname{vec}\left(\mathbf{A}_{00}\right)\, \bigg| \,\operatorname{vec}\left(\mathbf{A}_{10}\right)\, \bigg| \,\operatorname{vec}\left(\mathbf{A}_{01}\right)\, \bigg| \,\operatorname{vec}\left(\mathbf{A}_{11}\right)\, \right]
 \]
@@
 \todoredefined[inline]{
-TODO: Check if all notations are declared when adding something.
+TODO: Check if all notations used later are declared. Make matrix of matrices better looking.
 }
@@
 \label{singular_values}
-The singular values of a matrix A $\in$ $\mathbb{R}^{m x n}$ are the square roots of the eigenvalues of $AA^{\mathrm{T}}$.
+The singular values of a matrix $\mathbf{A}$ $\in$ $\mathbb{R}^{m x n}$ are the square roots of the eigenvalues of $\mathbf{AA}^{\intercal}$.
 \end{definition}
@@
 \label{SVD}
-Let A $\in$ $\mathbb{R}^{m x n}$ be a matrix having r positive singular values, m $\geq$ n.
-Then there exist orthogonal matrices U $\in$ $\mathbb{R}^{m x m}$, V $\in$ $\mathbb{R}^{n x n}$ and a diagonal matrix $\tilde{\Sigma}$ $\in$ $\mathbb{R}^{m x n}$ such that
+Let $\mathbf{A}$ $\in$ $\mathbb{R}^{m x n}$ be a matrix having r positive singular values, m $\geq$ n.
+Then there exist orthogonal matrices $\mathbf{U}$ $\in$ $\mathbb{R}^{m x m}$, $\mathbf{V}$ $\in$ $\mathbb{R}^{n x n}$ and a diagonal matrix $\mathbf{\tilde{\Sigma}}$ $\in$ $\mathbb{R}^{m x n}$ such that
 
-\[
-\begin{array}{l}{A=U \tilde{\Sigma} V^{\mathrm{T}}} \\ {\tilde{\Sigma}=\left[\begin{array}{ll}{\Sigma} & {0} \\ {0} & {0}\end{array}\right]}\end{array}
-\]
+\begin{align*}
+\mathbf{A} &= \mathbf{U \tilde{\Sigma} V^\intercal} \\
+\mathbf{\tilde{\Sigma}} &= \left[ \begin{array}{cc} \mathbf{\Sigma} & 0 \\ 0 & 0 \end{array} \right]
+\end{align*}
 
-where $\Sigma$ = diag ($\sigma$1, $\sigma$2, . . . , $\sigma$r), and $\sigma$1 $\geq$ $\sigma$2 $\geq$ · · · $\geq$ $\sigma$r $>$ 0 are the positive singular values of A.
+where $\mathbf{\Sigma}$ = diag ($\sigma$1, $\sigma$2, . . . , $\sigma$r), and $\sigma$1 $\geq$ $\sigma$2 $\geq$ · · · $\geq$ $\sigma$r $>$ 0 are the positive singular values of $\mathbf{A}$.
 
@@
 
-Let \textbf{F} be a non-singular square matrix. Then \textbf{F} can be decomposed uniquely into either of the following two products
+Let $\mathbf{F}$ be a non-singular square matrix. Then $\mathbf{F}$ can be decomposed uniquely into either of the following two products
 \[
-\boldsymbol{F} = \boldsymbol{RU}, \quad \boldsymbol{F} = \boldsymbol{VR}
+\mathbf{F} = \mathbf{RU}, \quad \mathbf{F} = \mathbf{VR}
 \]
-where \textbf{R} is orthogonal and \textbf{U} and \textbf{V} are positive definite symmetric matrices.
+where $\mathbf{R}$ is orthogonal and $\mathbf{U}$ and $\mathbf{V}$ are positive definite symmetric matrices.
 \end{theorem}
@@
 Unlike the normal convention the authors of the paper \textit{Stable Neo-Hookean Flesh Simulation} the rotation variant moves reflections to $\mathbf{\Sigma}$.
-This results into $\operatorname{det}(\mathbf{U})=\operatorname{det}(\mathbf{V})=1$ and the property that $\Sigma$ is allowed to have negative entries.
+This results into $\operatorname{det}(\mathbf{U})=\operatorname{det}(\mathbf{V})=1$ and the property that $\mathbf{\Sigma}$ is allowed to have negative entries.
 

### 2019-12-02 LaTeX-Master-Vorlage/chapter/paper.tex
improving everything

@@
 \section{Deformation Gradient}
+In the following calculations some properties of the deformation gradient $\mathbf{F}$ covered in the background chapter will be used.
+These properties are summarized in table \ref{table:gradient_quantities} for a better overview:
 
@@
     \textbf{Symbol} & \textbf{Definition} \\ \hline
-    $\mathrm{F=RS}$ & Polar decomposition \\ \hline
-    $J=\operatorname{det}(\mathrm{F})$ & Relative volume change \\ \hline
-    $\mathrm{C}=\mathrm{F}^{T} \mathrm{F}$ & Right Cauchy-Green  \\ \hline	
-    $I_{C}=\operatorname{tr}(\mathrm{C})$ & First right Cauchy-Green invariant \\ \hline
+    $\mathbf{F} = \mathbf{RS}$ & Polar decomposition \\ \hline
+    $J=\operatorname{det}(\mathbf{F})$ & Relative volume change \\ \hline
+    $\mathbf{C}=\mathbf{F}^\intercal \mathbf{F}$ & Right Cauchy-Green  \\ \hline	
+    $I_{C}=\operatorname{tr}(\mathbf{C})$ & First right Cauchy-Green invariant \\ \hline
     \end{tabular}
@@
 \todoredefined[inline]{
-TODO: Add in Background? Explain more each entity
+TODO: Check if everything is explained enough in Background.
 }
@@
 
-In previous literature a few energies were proposed.
+In previous literature a few energies were proposed that should be analysed properly.
 
@@
 Each energy formulation can be split up into a 1D length term and a 3D volume term.
+The 1D length term penalizes length changes the object undergoes whereas the 3D volume term is a volume-preserving penalty term.
 
@@
 
-\textbf{1D Length Term:} This term penalizes length changes. Mooney (\cite{mooney1940theory}) originally proposed the 1D length term 
+\subsubsection{1D Length Term}
+Mooney (\cite{mooney1940theory}) originally proposed the 1D length term 
 \[
@@
 \]
-The energy as it is formulated reaches its minimum at a zero volume change, meaning $I_{C}=0$ which results in $\Psi_{M}=-3$.
-Mooney added the hard constraint that $J=1$ so that the energy is minimized at the volume preserving configuration.
+The energy as it is formulated reaches its minimum at a zero volume state, meaning $I_{C}=0$ which results in $\Psi_{M}=-3$.
+Mooney added the hard constraint that $J=1$ so that the energy is minimized at the volume preserving configuration that is closest to the stretch space origin.
 Note that the energy is singularity free and well defined under inversion.
@@
 \]
-is used in $\Psi_{B}$ and $\Psi_{C}$ was introduced by Rivlin in 1948. Using the singular values of F we get the following term:
+is used in $\Psi_{B}$ and $\Psi_{C}$ and was introduced by Rivlin in 1948. Using the singular values of \textbf{F} we get the following term:
 \[
@@
 
-\textbf{3D Volume Term:} Here we are dealing with a volume-preserving penalty term. The volume term of $\Psi_{Neo}$, meaning
+\subsubsection{3D Volume Term}
+The volume term of $\Psi_{Neo}$, meaning
 \[
@@
 results in some numerical problems since the logarithmic function is not defined for $J<0$ and grows unbounded for $J \rightarrow 0$. In conclusion $\Psi_{Neo, volume}$ is not singularity free. 
-The same applies for the 3D volume term of $\Psi_{A}$
+The same applies for the 3D volume term of $\Psi_{A}$, namely
 \[
@@
 \]
-The term of $\Psi_{A}$ and $\Psi_{B}$
+The term of $\Psi_{A}$ and $\Psi_{B}$ which is of the form
 \[
@@
 \]
-does not have these noted difficulties. It is bounded, well defined and invertible. After these observations we combine the robust length with the robust volume term
+does not have these noted difficulties.
+It is bounded, well defined and invertible.
+After these observations we combine the robust length with the robust volume term and receive $\Psi_D$ that is defined as
 \[
@@
 \]
-which is singularity free and well defined under inversion.
+and is singularity free and well defined under inversion. Unfortunately $\Psi_D$ does not satisfy the requirement of being rest stable which will be discussed in the next section.
 
 \todoredefined[inline]{
-TODO: Bonet and Wood 2008 or 1997? Table looks ugly, improve and add resources. minimum at IC=0 or J=0? Overall okay?
+TODO: Bonet and Wood 2008 or 1997? Table looks ugly, improve and add resources. Overall okay?
 }
@@
 \subsection{Rest Stabilization}
-Although $\Psi_{D}$ meets almost all of our requirements it is not rest stable. This can be shown with the Piola-Kirchhoff (PK1) stress tensor:
+Although $\Psi_{D}$ meets almost all stated requirements it is not rest stable.
+This can be shown with the Piola-Kirchhoff (PK1) stress tensor for $\Psi_D$ depending on the identity matrix $\mathbf{I}$:
+\begin{align*}
+P_{D}(\mathbf{I}) &= \frac{\partial \Psi_{D}}{\partial \mathbf{F}} (\mathbf{I}) = \frac{\partial \Psi_{D}}{\partial \mathbf{F}} \left[ \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-1)^{2} \right] \\
+&= \frac{\partial \Psi_{D}}{\partial \mathbf{F}}  \frac{\mu}{2}\left(\operatorname{tr}(\mathbf{I}^\intercal \mathbf{I})-3\right) +\frac{\partial \Psi_{D}}{\partial \mathbf{F}} \frac{\lambda}{2}(\operatorname{tr}(\mathbf{I})-1)^{2} \\
+&= \mu I + \lambda (\operatorname{det}(\mathbf{I})-1)  \frac{\partial}{\partial \mathbf{F}} \operatorname{det}(\mathbf{I}) = \mu \mathbf{I} \neq 0
+\end{align*}
+
+If the energy had rest stability $P_{D}(\mathbf{I})$ would resolve to zero.
+Unfortunately this is not the case here.
+In order to solve that problem the authors modified $(J-1)^{2}$ to $(J-\alpha)^{2}$.
+Using this modification the energy shifts to
 \[
-P_{D}(I) = \frac{\partial \Psi_{D}}{\partial F} (I) = \frac{\partial \Psi_{D}}{\partial F} \left[ \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-1)^{2} \right]
-\]
-\[
-= \frac{\partial \Psi_{D}}{\partial F}  \frac{\mu}{2}\left(\operatorname{tr}(\mathrm{I}^{T} \mathrm{I})-3\right) +\frac{\partial \Psi_{D}}{\partial F} \frac{\lambda}{2}(\operatorname{tr}(\mathrm{I})-1)^{2}
-\]
-\[
-= \mu I + \lambda (\operatorname{det}(I)-1)  \frac{\partial}{\partial F} \operatorname{det}(I) = \mu I \neq 0
+\Psi_{E} = \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-\alpha)^{2}.
 \]
 
-If the energy had rest stability $P_{D}(I)$ would resolve to zero. Unfortunately this is not the case here. In order to solve that problem the authors modified $(J-1)^{2}$ to $(J-\alpha)^{2}$:
-\[
-\Psi_{E} = \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-\alpha)^{2}
-\]
-therefore resulting to:
-\[
-P_{E}(F) = \frac{\partial \Psi_{D}}{\partial F} \left[ \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-\alpha)^{2} \right]
-\]
-\begin{equation}\label{eq:pk1_unstable}
-= \mu F + \lambda (\operatorname{det}(F)-\alpha)  \frac{\partial}{\partial F} \operatorname{det}(F)
-\end{equation}
-
-Solving for an alpha that satisfies $P_{E}(I)=0$ gives us $\alpha=1+\frac{\mu}{\lambda}$. Now $\Psi_{E}$ has to be changed accordingly:
-\[
-\Psi_{E} = \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-1-\frac{\mu}{\lambda})^{2}
-\]
-\[
-= \frac{\mu}{2}\left(I_{C}-3\right) - \mu\left(J-1\right) + \frac{\lambda}{2}(J-1)^{2} + \left(\frac{\mu}{\lambda}\right)^{2}
-\]
+Taking $\Psi_E$ in the PK1 equation from before we get
+\begin{align*}
+P_{E}(\mathbf{F}) &= \frac{\partial \Psi_{E}}{\partial \mathbf{F}} \left[ \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-\alpha)^{2} \right] \\
+&= \mu \mathbf{F} + \lambda (\operatorname{det}(\mathbf{F})-\alpha)  \frac{\partial}{\partial \mathbf{F}} \operatorname{det}(\mathbf{F}).
+\end{align*}
+Solving for an alpha that satisfies $P_{E}(\mathbf{I})=0$ gives us $\alpha=1+\frac{\mu}{\lambda}$. Now $\Psi_{E}$ has to be changed accordingly:
+\begin{align*}
+\Psi_{E} &= \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-1-\frac{\mu}{\lambda})^{2} \\
+&= \frac{\mu}{2}\left(I_{C}-3\right) - \mu\left(J-1\right) + \frac{\lambda}{2}(J-1)^{2} + \left(\frac{\mu}{\lambda}\right)^{2}.
+\end{align*}
 Since constant disappear under differentiation this expression is functionally equivalent to 
@@
 Now one can notice that $\Psi_{E}$ looks very similar to $\Psi_{Neo}$.
-The difference is that we replaced $log(J)$ with $(J-1)$ in $\Psi_{E}$.
-Remember that $(J-1)$ is the first term in the taylor approximation of $log(J)$ at $J=1$:
-\[
-\sum_{n=0}^{\infty} = \frac{f^{(n)}(1)}{n!} (J-1)^{n} =
-\]
-\[
-= \boldsymbol{(J-1)} - \frac{1}{2} (J-1)^{2} + \frac{1}{3} (J-1)^{3} -\frac{1}{4} (J-1)^{4} + ...
-\]
+The difference is that $log(J)$ is replaced with $(J-1)$ in $\Psi_{E}$.
+Remember that $(J-1)$ is the first term in the taylor approximation of $\operatorname{log}(J)$ at $J=1$:
+\begin{align*}
+\sum_{n=0}^{\infty} &= \frac{f^{(n)}(1)}{n!} (J-1)^{n} \\
+&= \boldsymbol{(J-1)} - \frac{1}{2} (J-1)^{2} + \frac{1}{3} (J-1)^{3} -\frac{1}{4} (J-1)^{4} + ...
+\end{align*}
 
 \todoredefined[inline]{
-TODO: Add "Zwischenschritte"? Include all calculations? Do we need a bit of a better conclusion of what we did (taylor, neo, sing. free, rest stable)?
+TODO: Add "Zwischenschritte"?
+Include all calculations?
+Do we need a bit of a better conclusion of what we did (taylor, neo, sing.
+free, rest stable)?
+Check consistency of calculations (when trace when $I_C$ etc.).
 }
@@
 \section{Energy Analysis}
-In this chapter it is shown that one can perform a complete eigenanalysis on equation \ref{eq:stable_energy}.
+The goal of this chapter is to show that a complete eigenanalysis can be performed on equation \ref{eq:stable_energy}.
 
 \subsection{First Piola-Kirchhoff Stress (PK1)}
-We start with PK1 for equation \ref{eq:stable_energy}:
-\[
-P(F) = \frac{\partial \Psi_{D}}{\partial F} \left[ \frac{\mu}{2}\left(I_{C}-3\right) + \frac{\lambda}{2}(J-\alpha)^{2} - \frac{\mu}{2}\left(I_{C}+1\right) \right]
-\]
-\[
-\stackrel{\text{eq.\ref{eq:pk1_unstable}}}{=} \mu F + \lambda (\operatorname{det}(F)-\alpha)  \frac{\partial}{\partial F} \operatorname{det}(F) - \frac{\partial}{\partial F} \left[\operatorname{log}\left(\operatorname{tr}(\mathrm{F}^{T}F)+1\right)\right]
-\]
-\[
-= \mu F + \lambda (\operatorname{det}(F)-\alpha)  \frac{\partial}{\partial F} \operatorname{det}(F) - \mu F \frac{1}{\operatorname{tr}(\mathrm{F}^{T}F) + 1}
-\]
-\[
-= \mu \left( 1 - \frac{1}{\operatorname{tr}(\mathrm{F}^{T}F) + 1}\right) F + \lambda(J-\alpha)\frac{\partial J}{\partial F}
-\]
+In order to analyse the energy PK1 can be used for equation \ref{eq:stable_energy}:
+\begin{align*}
+P(\mathbf{F}) &= \frac{\partial \Psi_{D}}{\partial \mathbf{F}} \left[ \frac{\mu}{2}\left(I_{C}-3\right) + \frac{\lambda}{2}(J-\alpha)^{2} - \frac{\mu}{2}\left(I_{C}+1\right) \right] \\
+&= \mu \mathbf{F} + \lambda (\operatorname{det}(\mathbf{F})-\alpha)  \frac{\partial}{\partial \mathbf{F}} \operatorname{det}(\mathbf{F}) - \frac{\partial}{\partial \mathbf{F}} \left[\operatorname{log}\left(\operatorname{tr}(\mathbf{F}^\intercal \mathbf{F})+1\right)\right] \\
+&= \mu \mathbf{F} + \lambda (\operatorname{det}(\mathbf{F})-\alpha)  \frac{\partial}{\partial \mathbf{F}} \operatorname{det}(\mathbf{F}) - \mu \mathbf{F} \frac{1}{\operatorname{tr}(\mathbf{F}^\intercal \mathbf{F}) + 1} \\
+&= \mu \left( 1 - \frac{1}{\operatorname{tr}(\mathbf{F}^\intercal \mathbf{F}) + 1}\right) \mathbf{F} + \lambda(J-\alpha)\frac{\partial J}{\partial \mathbf{F}}
+\end{align*}
 
-with $\alpha=1+\frac{\mu}{\lambda}-\left(\frac{\mu}{4}\right)\lambda$. For future use we write $\frac{\partial J}{\partial \mathbf{F}}$ as cross products:
+with $\alpha=1+\frac{\mu}{\lambda}-\left(\frac{\mu}{4}\right)\lambda$. For future use it can be more practical to write $\frac{\partial J}{\partial \mathbf{F}}$ as a result of cross products:
 \begin{equation}\label{eq:cross_product}
@@
 
+\todoredefined[inline]{
+TODO: Is it easy to follow? Maybe add some explanations of some steps? Maybe move cross product into background instead of here.
+}
+
 \subsection{The Energy Hessian Terms}
-Using the scalar notation for F the hessian of the energy can be written in a fourth-order matrix-of-matrices:
+Using the scalar notation for $\mathbf{F}$ the hessian of the energy can be written in a fourth-order matrix-of-matrices:
 \[
-\frac{\partial^2 \psi}{\partial F^2} = \frac{\partial P(F)}{\partial F} = 
-\left[\begin{array}{ccc}{\left[\frac{\partial P(F)}{\partial f_0}\right]} & {\left[\frac{\partial P(F)}{\partial f_3}\right]} & {\left[\frac{\partial P(F)}{\partial f_6}\right]} \\ {\left[\frac{\partial P(F)}{\partial f_1}\right]} & {\left[\frac{\partial P(F)}{\partial f_4}\right]} & {\left[\frac{\partial P(F)}{\partial f_7}\right]} \\ {\left[\frac{\partial P(F)}{\partial f_2}\right]} & {\left[\frac{\partial P(F)}{\partial f_5}\right]} & {\left[\frac{\partial P(F)}{\partial f_8}\right]} \end{array}\right]
+\frac{\partial^2 \psi}{\partial \mathbf{F}^2} = \frac{\partial P(\mathbf{F})}{\partial \mathbf{F}} = 
+\left[\begin{array}{ccc}{\left[\frac{\partial P(\mathbf{F})}{\partial f_0}\right]} & {\left[\frac{\partial P(\mathbf{F})}{\partial f_3}\right]} & {\left[\frac{\partial P(\mathbf{F})}{\partial f_6}\right]} \\ {\left[\frac{\partial P(\mathbf{F})}{\partial f_1}\right]} & {\left[\frac{\partial P(\mathbf{F})}{\partial f_4}\right]} & {\left[\frac{\partial P(\mathbf{F})}{\partial f_7}\right]} \\ {\left[\frac{\partial P(\mathbf{F})}{\partial f_2}\right]} & {\left[\frac{\partial P(\mathbf{F})}{\partial f_5}\right]} & {\left[\frac{\partial P(\mathbf{F})}{\partial f_8}\right]} \end{array}\right]
 \]
@@
 \[
-\frac{\partial P(F)}{\partial f_i} = \frac{\partial}{\partial f_i} \left[ \mu \left( 1 - \frac{1}{\operatorname{tr}(\mathrm{F}^{T}F) + 1}\right) F + \lambda(J-\alpha)\frac{\partial J}{\partial F} \right]
+\frac{\partial P(\mathbf{F})}{\partial f_i} = \frac{\partial}{\partial f_i} \left[ \mu \left( 1 - \frac{1}{\operatorname{tr}(\mathbf{F}^\intercal \mathbf{F}) + 1}\right) \mathbf{F} + \lambda(J-\alpha)\frac{\partial J}{\partial \mathbf{F}} \right]
 \]
 \[
-\stackrel{\text{prod.rule}}{=} \underbrace{\frac{\partial F}{\partial f_i} \mu \left( 1 - \frac{1}{\operatorname{tr}(\mathrm{F}^{T}F) + 1}\right)}_{\mathrm{T}_{i}}  + \underbrace{F \mu \frac{2}{\left(\operatorname{tr}(\mathrm{F}^{T}F) + 1\right)^2} f_i}_{_{\mathrm{M}_{i}}}
+\stackrel{\text{prod.rule}}{=} \underbrace{\frac{\partial \mathbf{F}}{\partial f_i} \mu \left( 1 - \frac{1}{\operatorname{tr}(\mathbf{F}^\intercal \mathbf{F}) + 1}\right)}_{\mathrm{T}_{i}}  + \underbrace{\mathbf{F} \mu \frac{2}{\left(\operatorname{tr}(\mathbf{F^\intercal}\mathbf{F}) + 1\right)^2} f_i}_{_{\mathrm{M}_{i}}}
 \]
 \[
-r+ \underbrace{\lambda \frac{\partial J}{\partial f_i} \frac{\partial J}{\partial F}}_{_{\mathrm{G}_{i}}}+ \underbrace{\lambda (J- \alpha) \frac{\partial^2 J}{\partial F\partial f_i}}_{_{\mathrm{H}_{i}}} \in \mathbb{R}^{3}
+r+ \underbrace{\lambda \frac{\partial J}{\partial f_i} \frac{\partial J}{\partial \mathbf{F}}}_{_{\mathrm{G}_{i}}}+ \underbrace{\lambda (J- \alpha) \frac{\partial^2 J}{\partial \mathbf{F}\partial f_i}}_{_{\mathrm{H}_{i}}} \in \mathbb{R}^{3}.
 \]
-Each term in the final equation $\mathrm{T}_i$, $\mathrm{M}_i$, $\mathrm{G}_i$, $\mathrm{H}_i$ respectively the Tikohonov, Mu, volume Gradient and volume Hessian term will be examined separately in the following.
+Each term in the final equation $\mathrm{T}_i$, $\mathrm{M}_i$, $\mathrm{G}_i$, $\mathrm{H}_i$ respectively the Tikohonov, Mu, volume Gradient and volume Hessian term will be examined separately in the following sections.
 
@@
 \]
-If we vectorize $\mathbb{T}$ we get the identity matrix $\mathbb{I} \in \mathbb{R}^{9x9}$ which is full rank, positive definite and independent of the values in F.
+If we vectorize $\mathbb{T}$ we get the identity matrix $\mathbf{I} \in \mathbb{R}^{9x9}$ which is full rank, positive definite and independent of the values in F.
 It serves as a regularizer for the rest of the energy
 \[
-\operatorname{vec}(\mathbb{T}) =  \mathbf{\check{T}} = \mathbb{I} = \in \mathbb{R}^{9x9}.
+\operatorname{vec}(\mathbb{T}) =  \mathbf{\check{T}} = \mathbf{I} = \in \mathbb{R}^{9x9}.
 \]
@@
 For determining the eigenvalues of $\mathbf{\check{H}}$ one needs to examine the two characteristic polynomials:
-
 \begin{align*}
 &\epsilon^3 - \operatorname{tr}(\mathbf{C}) \epsilon - 2 J = 0 \tag{1}  \\
-&\epsilon^3 - \operatorname{tr}(\mathbf{C}) \epsilon^2 + \frac{1}{2} \left( \operatorname{tr^2}(\mathbf{C}) - \operatorname{tr}(\mathbf{C}^2) \right) \epsilon - \operatorname{det}(\mathbf{C}) = 0 \tag(2)
+&\epsilon^3 - \operatorname{tr}(\mathbf{C}) \epsilon^2 + \frac{1}{2} \left( \operatorname{tr^2}(\mathbf{C}) - \operatorname{tr}(\mathbf{C}^2) \right) \epsilon - \operatorname{det}(\mathbf{C}) = 0 \tag{2}
 \end{align*}

### 2019-12-02 LaTeX-Master-Vorlage/chapter/Background.tex
improving improving

@@
 \chapter{Background} \label{c:Background}
-The goal we are striving for is to animate human-like characters. In order to narrow it down even further we concentrate on the behaviour of the flesh of the character. 
+The goal I am striving for is to animate human-like characters. In order to narrow it down even further I concentrate on the behaviour of the flesh of the character. 
 For understanding the thematics of simulating human-like flesh it is necessary to have a basic mathematical background and knowledge of continuum mechanics.
@@
 \section{Notation and Convention}
-At first we will declare the notation used in this thesis to avoid misunderstandings.
-We will use the common notation used in continuum mechanics taken from the book \textit{Continuum Mechanics} \cite{Spencer1980}.
-Additionally we will include some more specific declarations formulated and used in the paper \textit{Stable Neo-Hookean Flesh Simulation} \cite{Smith:2018:SNF:3191713.3180491}.
+At first I will declare the notation used in this thesis to avoid misunderstandings.
+I will use the common notation used in continuum mechanics taken from the book \textit{Continuum Mechanics} \cite{Spencer1980}.
+Additionally I will include some more specific declarations formulated and used by the authors of the paper \textit{Stable Neo-Hookean Flesh Simulation} \cite{Smith:2018:SNF:3191713.3180491}.
 
@@
 \subsection{Tensor Notation}
-Furthermore we will use the tensor notation used in the paper \textit{Stable Neo-Hookean Flesh Simulation}.
+Furthermore I will use the tensor notation used in the paper \textit{Stable Neo-Hookean Flesh Simulation}.
 They decided to to define vectorization vec(\cdot) as column-wise flattening of a matrix into a vector (\cite{Smith:2018:SNF:3191713.3180491}, 12:5) similar to Golub and Van Loan (2012) \cite{golub2012matrix}.
 
-In order to indicate that we are dealing with a vectorized matrix we will use the symbol $\check{\cdot}$ as shown in the following equation:
+In order to indicate that I am dealing with a vectorized matrix I will use the symbol $\check{\cdot}$ as shown in the following equation:
 
@@
 
-Additionally we will have to deal with $4^{th}$ order tensors in a form of matrix-of-matrices. These matrices are denoted by using blackboard bold:
+Additionally I will have to deal with $4^{th}$ order tensors in a form of matrix-of-matrices. These matrices are denoted by using blackboard bold:
 
@@
 
-If we now vectorize $\mathbb{A}$ we receive the form described in the following line:
+When vectorizing $\mathbb{A}$ the received form looks as described in the following line:
 
 \[
-\mathbb{A} = \operatorname{vec}(\mathbb{A})= \left[ \,\operatorname{vec}\left(\mathbf{A}_{00}\right)\, \bigg| \,\operatorname{vec}\left(\mathbf{A}_{10}\right)\, \bigg| \,\operatorname{vec}\left(\mathbf{A}_{01}\right)\, \bigg| \,\operatorname{vec}\left(\mathbf{A}_{11}\right)\, \right]
+\mathbb{A} = \operatorname{vec}(\mathbb{A})= \left[ \,\operatorname{vec}\left(\mathbf{A}_{00}\right)\, \bigg| \,\operatorname{vec}\left(\mathbf{A}_{10}\right)\, \bigg| \,\operatorname{vec}\left(\mathbf{A}_{01}\right)\, \bigg| \,\operatorname{vec}\left(\mathbf{A}_{11}\right)\, \right].
 \]
@@
 \mathbb{A}=\left[\begin{array}{llll}{a} & {e} & {i} & {m} \\ {b} & {f} & {j} & {n} \\ {c} & {g} & {k} & {o} \\ {d} & {h} & {l} & {p}\end{array}\right] 
-=\boldsymbol{\check{A}}
+=\boldsymbol{\check{A}}.
 \]
 
-The advantage of this form is that we can write several expressions as a cross product. We will need this property later to simplify complicated expressions and calculations.
+The advantage of this form is that one can write several expressions as a cross product. I will need this property later to simplify complicated expressions and calculations.
 
@@
 \section{Mathematical Background}
-Since mathematics play an important role in our field of interest we need to build a solid background before we go further into more complex calculations.
+Since mathematics play an important role in the field of interest the first step is to build a solid background before diving further into more complex calculations.
 This chapter should cover all the important concepts used later in the calculations.
@@
 \subsection{Matrices}
-At first we will discuss the physical or geometrical meaning of some common matrix properties.
+At first I will discuss the physical or geometrical meaning of some common matrix properties.
 
-A matrix \textbf{A} is positive definite if $\textbf{x}^{T}\textbf{Ax}$ is positive for all of the non-zero values of the column matrix \textbf{x}.
+A matrix \textbf{A} is positive definite if $\textbf{x}^\intercal \textbf{Ax}$ is positive for all of the non-zero values of the column matrix \textbf{x}.
 
 \todoredefined[inline]{
-TODO: positive definite matrices definition and lemmas, orthogonal, etc.
+TODO: Not done yet. What needs to be covered here? positive definite matrices definition and lemmas, orthogonal, etc. Should it even be included?
 }
@@
 The singular value decomposition (SVD) will play an important role in formulating the deformation gradient.
-It is important for our application since it represents the best possible approximation of a given matrix by a matrix of low rank.
+It is important for this application since it represents the best possible approximation of a given matrix by a matrix of low rank.
 This approximation can be looked at as a compression of the data given (\cite{LiesenMehrmann2015}, S.
@@
 Then there exist orthogonal matrices $\mathbf{U}$ $\in$ $\mathbb{R}^{m x m}$, $\mathbf{V}$ $\in$ $\mathbb{R}^{n x n}$ and a diagonal matrix $\mathbf{\tilde{\Sigma}}$ $\in$ $\mathbb{R}^{m x n}$ such that
-
 \begin{align*}
@@
 \end{align*}
-
 where $\mathbf{\Sigma}$ = diag ($\sigma$1, $\sigma$2, . . . , $\sigma$r), and $\sigma$1 $\geq$ $\sigma$2 $\geq$ · · · $\geq$ $\sigma$r $>$ 0 are the positive singular values of $\mathbf{A}$.
@@
 \section{Continuum Mechanics}
-In this section we will give a broad introduction into the field of Continuum Mechanics.
-In Continuum Mechanics we are less interested in small particles like atoms or molecules of an object but rather concentrate on pieces of matter which are in comparison very large.
-We are therefore concerned with the mechanical behavior of solids and fluids on the macroscopic scale (\cite{Spencer1980}, p.
+In this section I will give a broad introduction into the field of Continuum Mechanics.
+In Continuum Mechanics one is less interested in small particles like atoms or molecules of an object but rather in pieces of matter which are in comparison very large.
+I are therefore concerned with the mechanical behavior of solids and fluids on the macroscopic scale (\cite{Spencer1980}, p.
 1).
@@
 When applying a force over an object naturally the object itself undergoes a deformation.
-In the following we will be consistent with most previous literature in continuum mechanics and use the term strain as a measure of deformation and stress as the force per unit area:
+In the following I will be consistent with most previous literature in continuum mechanics and use the term strain as a measure of deformation and stress as the force per unit area:
 
@@
 Now let us have a look at a deformation in a rather mathematical sense.
-Graphically we can imagine a deformation with the help of a two dimensional deformation map as shown in Fig.
+Graphically one can imagine a deformation with the help of a two dimensional deformation map as shown in Fig.
 \ref{fig:deformationmap}.
-Here we have on the left side an ellipse that represents an object or material in its rest state.
+Here on the left side there is an ellipse that represents an object or material in its rest state.
 A function $\phi$ maps this rest state of the ellipse to a deformed state shown in Fig.
 \ref{fig:deformationmap} on the right side.
-Mathematically spoken this means that we can map each point of a chosen object from its rest state to a deformed one.
+Mathematically spoken this means that one can map each point of a chosen object from its rest state to a deformed one.
 
@@
 
-In conclusion the function $\phi$ describes our deformation.
-If we derive $\phi$ we can calculate the deformation gradient \textbf{F} which serves as a measure of the deformation in the following sense:
+In conclusion the function $\phi$ describes the deformation.
+When deriving $\phi$ one can calculate the deformation gradient \textbf{F} which serves as a measure of the deformation in the following sense:
 
@@
 \todoredefined[inline]{
-TODO: Adjust so the equal sign is at the same place in each column. Explain strain and stress and their meaning for later use in material constants (not explained in paper).
+TODO: Adjust so the equal sign is at the same place in each column.
+Explain strain and stress and their meaning for later use in material constants (not explained in paper).
+Include own image instead of the one here?
 }
@@
 \subsection{Deformation Gradient}
-The deformation gradient \textbf{F} offers us as said previously a measurement of the deformation.
-With its help we can amongst other things calculate the volume and length change an object undergoes during a deformation.
-For our needs we define the deformation gradient exactely as the authors of the paper \cite{Smith:2018:SNF:3191713.3180491} did:
+The deformation gradient \textbf{F} offers as said previously a measurement of the deformation.
+With its help one can amongst other things calculate the volume and length change an object undergoes during a deformation.
+For my needs I define the deformation gradient exactely as the authors of the paper \cite{Smith:2018:SNF:3191713.3180491} did:
 
@@
 
-Using the SVD theorem mentioned in theorem \ref{SVD} $\mathbf{F}$ can be written in the form of
+Using the SVD theorem mentioned in thm.\ref{SVD} $\mathbf{F}$ can be written in the form of
 
 \begin{equation}\label{eq:svd_gradient}
-\mathbf{F} = \mathbf{U \Sigma V\intercal}
+\mathbf{F} = \mathbf{U \Sigma V^\intercal}
 \end{equation}
@@
 The $\sigma_i$ denote the singular values of $\mathbf{\Sigma}$.
-Unlike the normal convention the authors of the paper \textit{Stable Neo-Hookean Flesh Simulation} the rotation variant moves reflections to $\mathbf{\Sigma}$.
+Unlike the normal convention the authors of the paper \textit{Stable Neo-Hookean Flesh Simulation} decided that the rotation variant moves reflections to $\mathbf{\Sigma}$.
 This results into $\operatorname{det}(\mathbf{U})=\operatorname{det}(\mathbf{V})=1$ and the property that $\mathbf{\Sigma}$ is allowed to have negative entries.

### 2019-12-02 LaTeX-Master-Vorlage/chapter/paper.tex
improving improving

@@
 
+\todoredefined[inline]{
+TODO: Not all proofs and calculations included yet. Add or leave out some if too confusing.
+}
+
 \subsection{The Volume Hessian}
@@
 \[
-\mathbb{H} = \frac{\partial^2 J}{\partial \mathbf{F} \partial f_i} \in \mathbb{R}^{9\times 9}.
+\mathbb{H} = \frac{\partial^2 J}{\partial \mathbf{F} \partial f_i} = \left[\begin{array}{ccc}{\frac{\partial}{\partial \mathbf{F}}\left[\frac{\partial J}{\partial f_0}\right]} & {\frac{\partial}{\partial \mathbf{F}}\left[\frac{\partial J}{\partial f_3}\right]} & {\frac{\partial}{\partial \mathbf{F}}\left[\frac{\partial J}{\partial f_6}\right]} \\ {\frac{\partial}{\partial \mathbf{F}}\left[\frac{\partial J}{\partial f_1}\right]} & {\frac{\partial}{\partial \mathbf{F}}\left[\frac{\partial J}{\partial f_4}\right]} & {\frac{\partial}{\partial \mathbf{F}}\left[\frac{\partial J}{\partial f_7}\right]} \\ {\frac{\partial}{\partial \mathbf{F}}\left[\frac{\partial J}{\partial f_2}\right]} & {\frac{\partial}{\partial \mathbf{F}}\left[\frac{\partial J}{\partial f_5}\right]} & {\frac{\partial}{\partial \mathbf{F}}\left[\frac{\partial J}{\partial f_8}\right]} \end{array}\right].
 \]
@@
 \[
-\operatorname{vec}(\mathbb{H}) = \mathbf{\check{H}} = \left[ \begin{matrix}
+\operatorname{vec}(\mathbb{H}) = \mathbf{\check{H}} = \begin{bmatrix} 0 & 0 & 0 & 0 & f_8 & 0 & 0 & -f_5 & f_4 \\ 0 & 0 & 0 & -f_8 & 0 & f_6 & f_5 & 0 & -f_3 \\ 0 & 0 & 0 & f_7 & -f_6 & 0 & -f_4 & f_3 & 0 \\ 0 & -f_8 & f_7 & 0 & 0 & 0 & 0 & f_2 & -f_1 \\ f_8 & 0 & -f_6 & 0 & 0 & 0 & -f_2 & 0 & f_0 \\ -f_7 & f_6 & 0 & 0 & 0 & 0 & f_1 & -f_0 & 0 \\ 0 & f_5 & -f_4 & 0 & -f_2 & f_1 & 0 & 0 & 0 \\ -f_5 & 0 & f_3 & f_2 & 0 & -f_0 & 0 & 0 & 0 \\ f_4 & -f_3 & 0 & -f_1 & f_0 & 0 & 0 & 0 & 0 \end{bmatrix}.
+\]
+We can write $\mathbf{\check{H}}$ as a cross-product matrix in the form
+\[
+\mathbf{\check{H}} = \left[ \begin{matrix}
 0 & -\mathbf{\widehat{f_2}} & \mathbf{\widehat{f_1}} \\ \mathbf{\widehat{f_2}} & 0 & -\mathbf{\widehat{f_0}} \\ -\mathbf{\widehat{f_1}} & \mathbf{\widehat{f_0}} & 0 \end{matrix} \right]
@@
 
+\todoredefined[inline]{
+TODO: Check each $f_1$ and $-$ in vectorization of H because it's exhausting.
+}
+
 \subsubsection{Volume Hessian Eigenvalues}
@@
 
-where $\epsilon$ denote the eigenvalues of $\mathbf{\check{H}}$ and $\mathbf{C}$ is taken from table \ref{table:gradient_quantities}. Equation (1) is easier to solve and
+where $\epsilon$ denote the eigenvalues of $\mathbf{\check{H}}$ and $\mathbf{C}$ is taken from table \ref{table:gradient_quantities}.
+Equation (1) is easier to solve and corresponds o the characteristic polynomial of $\mathbf{C}$.
+Given its roots $\epsilon_\alpha$, $\epsilon_\beta$, $\epsilon_\gamma$ the eigenvalues of $\mathbf{\check{H}}$ are: $\pm \sqrt{\epsilon_\alpha}$, $\pm \sqrt{\epsilon_\beta}$, $\pm \sqrt{\epsilon_\gamma}$.
+Using the singular values of $\mathbf{F}$ the eigenvalues can be written nicely in the following way:
+\begin{align*}
+&\epsilon_3 = \sigma_0 &\epsilon_6 = -\sigma_0 \\
+&\epsilon_4 = \sigma_1 &\epsilon_7 = -\sigma_1 \\
+&\epsilon_5 = \sigma_2 &\epsilon_8 = -\sigma_2.
+\end{align*}
+The remaining eigenvalues can be obtained by equation (2). This equation represents a depressed cube and the roots can be obtained by
+\[
+\epsilon_k = 2 \sqrt{\frac{I_C}{3}} \operatorname{cos}\left[ \frac{1}{3} \left( \operatorname{arccos}\left(\frac{3 J}{I_C} \sqrt{\frac{3}{I_C}} \right) + 2 \pi k \right) \right] \quad  k= 0,1,2.
+\]
+
+\todoredefined[inline]{
+TODO: Not happy with this section, improve and complete
+}
 
 \subsection{The Complete Eigensystem}
-Calculations
+\todoredefined[inline]{
+TODO: Include what is necessary.
+}
 

### 2019-12-02 LaTeX-Master-Vorlage/chapter/Background.tex
i dont even know

@@
 
-\subsection{Polar Decomposition of the Deformation Gradient}
-With the help of mathematics we can decompose the deformation gradient in the following form:
+\subsubsection{Polar Decomposition of the Deformation Gradient}
+With the help of mathematics one can decompose the deformation gradient in the following form:
 
@@
 \]
+
+\todoredefined[inline]{
+TODO: Explain more here.
+}
 
@@
 
-In the context of flesh simulations we use the poisson's ratio as a characterization for the resistance to volume change of flesh.
+In the context of flesh simulations I use the poisson's ratio as a characterization for the resistance to volume change of flesh.
 Biological tissues such as flesh, fat and muscles have one important property: Volume preservation.
@@
 
-The calculation of the poisson's ratio defined as in equation \ref{eq:poisson} is a challenge.
+The calculation of the poisson's ratio defined in equation \ref{eq:poisson} is a challenge.
 Fortunately we can make use of the \textit{Lamé Parameters}.
 These are the two constants $\mu$ and $\lambda$ that are specific for a material.
-With the help of these two constants we can transform equation \ref{eq:poisson} into the following form:
+With the help of these two constants one can transform the equation \ref{eq:poisson} into the following form:
 
@@
 
-This equation allows us to calculate the poisson's ratio much easier.
+This equation allows to calculate the poisson's ratio much easier.
 
@@
 \subsection{Deformation Energy}
-In order to get a convincing simulation of high quality we must choose an appropriate energy.
-In the case of modelling deformations on human-like characters we have to choose an elastic energy.
+In order to get a convincing simulation of high quality one must choose an appropriate energy.
+In the case of modelling deformations on human-like characters an elastic energy needs to be chosen.
 The key property that makes an energy elastic is that if all the forces that are applied over an object add up to zero the object must come back into its rest shape.
@@
 The energy then has to be minimized in order to get the results we want.
-
-\begin{definition}
-  This is a definition.
-\end{definition}
 

### 2019-12-02 LaTeX-Master-Vorlage/chapter/paper.tex
i dont even know

@@
 \chapter{Paper} \label{c:Paper}
-In this chapter we will examine the topic of the paper \textit{Stable Neo-Hookean Flesh Simulation} \cite{Smith:2018:SNF:3191713.3180491}.
+In this chapter I will examine the topic of the paper \textit{Stable Neo-Hookean Flesh Simulation} \cite{Smith:2018:SNF:3191713.3180491}.
 In the interest of understanding the thought process of the authors I will include some of their calculations a bit more detailed.

### 2019-12-05 LaTeX-Master-Vorlage/chapter/Background.tex
small adjustments

@@
 \mathbb{A}=\left[\begin{array}{llll}{a} & {e} & {i} & {m} \\ {b} & {f} & {j} & {n} \\ {c} & {g} & {k} & {o} \\ {d} & {h} & {l} & {p}\end{array}\right] 
-=\boldsymbol{\check{A}}.
+=\mathbf{\check{A}}.
 \]
@@
 In Continuum Mechanics one is less interested in small particles like atoms or molecules of an object but rather in pieces of matter which are in comparison very large.
-I are therefore concerned with the mechanical behavior of solids and fluids on the macroscopic scale (\cite{Spencer1980}, p.
+I am therefore concerned with the mechanical behavior of solids and fluids on the macroscopic scale (\cite{Spencer1980}, p.
 1).
@@
 \subsubsection{Polar Decomposition of the Deformation Gradient}
-With the help of mathematics one can decompose the deformation gradient in the following form:
+With the help of theorem \ref{PD} one can decompose the deformation gradient in the following form:
 
 \[
-\mathbf{F} = \mathbf{RS}
+\mathbf{F} = \mathbf{RS}.
 \]
@@
 
-In the context of flesh simulations I use the poisson's ratio as a characterization for the resistance to volume change of flesh.
+In the context of flesh simulations I am using the poisson's ratio as a characterization for the resistance to volume change of flesh.
 Biological tissues such as flesh, fat and muscles have one important property: Volume preservation.
@@
 These are the two constants $\mu$ and $\lambda$ that are specific for a material.
-With the help of these two constants one can transform the equation \ref{eq:poisson} into the following form:
+With the help of these two constants one can transform equation \ref{eq:poisson} into the following form:
 
 \begin{equation}\label{eq:poisson_ratio}
-\sigma =  \frac{\lambda}{2(\lambda + \mu)}
+\sigma =  \frac{\lambda}{2(\lambda + \mu)}.
 \end{equation}

### 2019-12-05 LaTeX-Master-Vorlage/chapter/paper.tex
small adjustments

@@
 They concentrated on the deformation energy.
-In order to achieve a convincing result as a first step we need to specify some requirements.
+In order to achieve a convincing result the first step is to specify some requirements.
 For our needs in this case the stability of the energy is important.
@@
 \textbf{1.
-Inversion Stability:} Given some arbitrary object it is possible that while deforming the object we can arrive at a zero volume state or even an entire inversion.
+Inversion Stability:} Given some arbitrary object it is possible that while deforming the object one can arrive at a zero volume state or even an entire inversion.
 Take for example the tetrahedron shown in figure \ref{fig:inversion_1}.
@@
 
-\textbf{2. Reflection stability:} A reflection is rotation around the coordinate origin.
-For the deformation energy we need it to be well behaved regardless of the reflection convention used in the singular value decomposition.
+\textbf{2.
+Reflection stability:} A reflection is rotation around the coordinate origin.
+The deformation energy needs to be well behaved regardless of the reflection convention used in the singular value decomposition.
 
@@
 \todoredefined[inline]{
-TODO: Finish reflection stability. Maybe add own images? Some more sources?
+TODO: Finish reflection stability. Maybe add own images and more sources. Improve English in this section.
 }
@@
 
-In previous literature a few energies were proposed that should be analysed properly.
+In previous literature a few energies were proposed that should be analysed properly. They are listed in table \ref{table:energies} below.
 
@@
 \todoredefined[inline]{
-TODO: Bonet and Wood 2008 or 1997? Table looks ugly, improve and add resources. Overall okay?
+TODO: Bonet and Wood 2008 or 1997? Table looks ugly, improve and add resources. Improve English sentences. Overall okay concerning the content?
 }
@@
 \todoredefined[inline]{
-TODO: Load into OpenFlipper and screenshot results. Include more examples and what went right and what went wrong.
+TODO: Load into OpenFlipper and screenshot results. Include remaining examples (diff. lamé param. and changes in method) and what went right and what went wrong.
 }

### 2020-02-24 LaTeX-Master-Vorlage/chapter/Introduction.tex
correcting stuff

@@
 \section{Motivation}
-With steadily increasing computational power the demand of better results is constantly growing. Especially in the field of animation and simulation we are no longer happy with mediocre results. 
-In the entertainment sector gaming industries and animation studios like Pixar\textsuperscript{\textcopyright} or Disney\textsuperscript{\textcopyright} brought us games and movies of highest quality.
+With steadily increasing computational power, the demand of better results is constantly growing. Especially in the field of animation and simulation we are no longer happy with mediocre results. 
+In the entertainment sector and gaming industry animation studios like Pixar\textsuperscript{\textcopyright} or Disney\textsuperscript{\textcopyright} brought us games and movies of highest quality.
 Both of them have made groundbreaking progress over the years.
@@
 
-As always we have different requirements for each use.
+As always, we have different requirements for each use.
 In some cases we want to exaggerate a movement or a reaction in a certain way. We can for example create a massive explosion in a movie that would not be half as spectacular in the real world.
@@
 In other scenarios we want to come as close as possible to reality.
-For instance we want an animated character to move and physically interact with its environment as a real human being would.
-Otherwise our brain would immediately recognize that some things do not add up.
+For instance, we may want an animated character to move and physically interact with its environment as a real human being would.
+Otherwise, the human brain would immediately recognize that some things do not add up.
 The goal here is to bring characters quite literally to life.
 We can add small details like visible breathing and small wrinkles to have an even more convincing effect.
-The goal is to create the illusion of a character with personality, thought and emotions.
-In order to achieve this effect we need the character to move and react nearly physically correct.
+We aim to create the illusion of a character with personality, thought and emotions.
+In order to achieve this effect, we need the character to move and react physically correct.
 
-In the paper \textit{Stable Neo-Hookean Flesh Simulation} \cite{Smith:2018:SNF:3191713.3180491} the authors addressed exactly the problem of making an animated movement of a human-like character look as natural as possible.
-In order to animate a physical movement we first need to understand the physics behind it which lies in the field of continuum mechanics.
-Unfortunately for most of us it has yet to be learned.
+In the paper \textit{Stable Neo-Hookean Flesh Simulation} \cite{Smith:2018:SNF:3191713.3180491}, the authors addressed exactly this problem of making an animated movement of a human-like character look as natural as possible.
+In order to animate a physical movement, we first need to understand the physics behind it which requires some knowledge in the field of continuum mechanics.
+Unfortunately, for most of us it has yet to be learned.
 The goal of this thesis is to give the necessary physical and mathematical background for a regular computer science student to understand the field of animation.
+In addition I will go deeper into the thematics of the paper mentioned before.
+I aim to get an understanding of their contribution in the field and implement their proposed energy myself.
 
 \section{Structure}
-Following up I will give a brief overview of the necessary mathematical background and deliver an introduction in continuum mechanics.
-Next I will go through the ideas made in the paper mentioned and include some calculations and visualisations that help for a better understanding.
+In the following, I will give a brief overview of the necessary mathematical background and deliver an introduction into the field of continuum mechanics.
+Next, I will go through the ideas mentioned in the paper and include some calculations and visualisations that help for a better understanding.
 \\
@@
 \todoredefined[inline]{
-TODO: Improve intorduction (goals etc.). Adjust according to additions in text. Improve quote at beginning. Maybe add other applications as well (physical simulation) and how to go over to it?
+TODO: Add goals in introduction. Adjust according to additions in text. Improve quote at beginning. Maybe add other applications as well (physical simulation) and how to go over to it?
 }

### 2020-02-24 LaTeX-Master-Vorlage/glossary_and_acronyms.tex
correcting stuff

@@
-\newglossaryentry{berlin}{name={Berlin},description={Berlin ist die Bundeshauptstadt der Bundesrepublik Deutschland und zugleich eines ihrer Länder.
-Die Stadt Berlin ist mit über 3,4 Millionen Einwohnern die bevölkerungsreichste und mit 892 Quadratkilometern die flächengrößte Gemeinde Deutschlands sowie nach Einwohnern die zweitgrößte der Europäischen Union.
-Sie bildet das Zentrum der Metropolregion Berlin/Brandenburg (6 Millionen Einw.) und der Agglomeration Berlin (4,4 Millionen Einw.).
-Der Stadtstaat unterteilt sich in zwölf Bezirke.
-Neben den Flüssen Spree und Havel befinden sich im Stadtgebiet kleinere Fließgewässer sowie zahlreiche Seen und Wälder}}
-\newglossaryentry{outsourcing}{name={Outsourcing},description={Outsourcing bzw.
-Auslagerung bezeichnet in der Ökonomie die Abgabe von Unternehmensaufgaben und -strukturen an externe oder interne Dienstleister.
-Es ist eine spezielle Form des Fremdbezugs von bisher intern erbrachter Leistung, wobei Verträge die Dauer und den Gegenstand der Leistung fixieren.
-Das grenzt Outsourcing von sonstigen Partnerschaften ab}}
-\newglossaryentry{asp}{name={Application Service Providing},description={Der Application Service Provider (Abkürzung ASP) bzw.
-Anwendungsdienstleister ist ein Dienstleister, der eine Anwendung (z.
-B.
-ein ERP-System) zum Informationsaustausch über ein öffentliches Netz (z.
-B.
-Internet) oder über ein privates Datennetz anbietet.
-Der ASP kümmert sich um die gesamte Administration, wie Datensicherung, das Einspielen von Patches usw.
-Anders als beim Applikations-Hosting ist Teil der ASP-Dienstleistung auch ein Service (z.B.
-Benutzerbetreuung) um die Anwendung herum}}
-\newglossaryentry{policy}{name={Policy},description={Im geschäftlichen Bereich bezeichnet Policy eine interne Leit- bzw.
-Richtlinie, die formal durch das Unternehmen dokumentiert und über ihr Management verantwortet wird}}
-\newglossaryentry{pcie}{name={PCI Express},description={PCI Express („Peripheral Component Interconnect Express“, abgekürzt PCIe oder PCI-E) ist ein Standard zur Verbindung von Peripheriegeräten mit dem Chipsatz eines Hauptprozessors.
-PCIe ist der Nachfolger von PCI, PCI-X und AGP und bietet im Vergleich zu seinen Vorgängern eine höhere Datenübertragungsrate pro Pin.}}
+\newglossaryentry{latex}
+{
+        name=latex,
+        description={Is a mark up language specially suited for 
+scientific documents}
+}
 
-\newacronym{cd}{CD}{Compact Disk}
-\newacronym{lan}{LAN}{Local Area Network}
-\newacronym{iso}{ISO}{Internationale Organisation für Normung}
-\newacronym{sas}{SAS}{Serial Attached SCSI}
-\newacronym{abbvz}{Abbvz.}{Abbildungsverzeichnis}
+\newacronym{gcd}{GCD}{Greatest Common Divisor}
+\newacronym{svd}{SVD}{Singular Value Decomposition}

### 2020-02-24 LaTeX-Master-Vorlage/chapter/Background.tex
correcting stuff
working on introduction, background and glossary

@@
 \chapter{Background} \label{c:Background}
-The goal I am striving for is to animate human-like characters. In order to narrow it down even further I concentrate on the behaviour of the flesh of the character. 
-For understanding the thematics of simulating human-like flesh it is necessary to have a basic mathematical background and knowledge of continuum mechanics.
-The goal of this chapter is to deliver an understanding in the topics mentioned.
+As in the paper \textit{\acrshort{snh}}, my goal is to animate human-like characters.
+More precisely, the focus is on the behaviour of the character's flesh.
+This chapter serves as an introduction into the mathematical as well as physical background, needed to understand the upcoming calculations and conclusions.
+At the beginning of this chapter I will define the notation and convention used throughout this whole thesis.
+Next, I will give insights in the mathematics used and present some of the concepts used in continuum mechanics.
+However, I will not include each proof explicitly, as there are already many good resources for an interested reader.
 
@@
 
-The singular value decomposition (SVD) will play an important role in formulating the deformation gradient.
+The \acrlong{svd}, which is abbreviated \acrshort{svd}, will play an important role in formulating the deformation gradient.
 It is important for this application since it represents the best possible approximation of a given matrix by a matrix of low rank.

### 2020-02-24 LaTeX-Master-Vorlage/chapter/Introduction.tex
working on introduction, background and glossary

@@
 
-In the paper \textit{Stable Neo-Hookean Flesh Simulation} \cite{Smith:2018:SNF:3191713.3180491}, the authors addressed exactly this problem of making an animated movement of a human-like character look as natural as possible.
+In the paper \textit{\acrlong{snh}} \cite{Smith:2018:SNF:3191713.3180491}, the authors addressed exactly this problem of making an animated movement of a human-like character look as natural as possible.
+Consequently this thesis is based heavily on this paper.
+In the following, I will abbreviate the name of the paper with \textit{\acrshort{snh}}.
+\\
+But before diving further into the content of the paper, a fundamental background is needed.
 In order to animate a physical movement, we first need to understand the physics behind it which requires some knowledge in the field of continuum mechanics.
@@
 The goal of this thesis is to give the necessary physical and mathematical background for a regular computer science student to understand the field of animation.
-In addition I will go deeper into the thematics of the paper mentioned before.
+In addition I will go deeper into the thematics of the paper \textit{\acrshort {snh}}.
 I aim to get an understanding of their contribution in the field and implement their proposed energy myself.
@@
 In the following, I will give a brief overview of the necessary mathematical background and deliver an introduction into the field of continuum mechanics.
-Next, I will go through the ideas mentioned in the paper and include some calculations and visualisations that help for a better understanding.
+Next, I will go through the ideas mentioned in the paper and include some calculations and visualisations that serve for a better understanding.
+Lastly I will give an insight into the process of implementing the energy.
 \\
@@
 \todoredefined[inline]{
-TODO: Add goals in introduction. Adjust according to additions in text. Improve quote at beginning. Maybe add other applications as well (physical simulation) and how to go over to it?
+TODO: Adjust according to additions in text. Maybe add other applications as well (physical simulation) and how to go over to it?
 }

### 2020-02-24 LaTeX-Master-Vorlage/chapter/Background.tex
working on background

@@
 I will use the common notation used in continuum mechanics taken from the book \textit{Continuum Mechanics} \cite{Spencer1980}.
-Additionally I will include some more specific declarations formulated and used by the authors of the paper \textit{Stable Neo-Hookean Flesh Simulation} \cite{Smith:2018:SNF:3191713.3180491}.
+Additionally I will include some more specific declarations formulated and used by the authors of the paper \textit{\acrshort{snh}}.
 
 \subsection{General Notation}
-Scalars are represented by regular, normal-weight variables such as $a$ whereas 
-tensors and matrices are represented by upper-case bold letters as for example $\textbf{A}$. Vectors will be denoted by bold lower-case variables like $\textbf{a}$.
+Scalars are represented by regular, normal-weight variables such as $a$, whereas 
+tensors and matrices are represented by upper-case bold letters such as for example $\textbf{A}$. Vectors will be denoted by bold lower-case variables like $\textbf{a}$.
 
 \subsection{Tensor Notation}
-Furthermore I will use the tensor notation used in the paper \textit{Stable Neo-Hookean Flesh Simulation}.
-They decided to to define vectorization vec(\cdot) as column-wise flattening of a matrix into a vector (\cite{Smith:2018:SNF:3191713.3180491}, 12:5) similar to Golub and Van Loan (2012) \cite{golub2012matrix}.
+Furthermore, I will use the tensor notation used in \textit{\acrshort{snh}}.
+They decided to define the vectorization vec(\cdot) as column-wise flattening of a matrix into a vector (\cite{Smith:2018:SNF:3191713.3180491}, 12:5) similar to Golub and Van Loan (2012) \cite{golub2012matrix}.
 
@@
 \[
-\textbf{A} = \begin{bmatrix} a & c \\ b & d \end{bmatrix} \qquad \operatorname{vec}(\textbf{A}) = \mathbf{\check{a}} = \begin{bmatrix} a \\ b \\ c \\ d \end{bmatrix}.
+\mathbf{A} = \begin{bmatrix} a & c \\ b & d \end{bmatrix} \qquad \operatorname{vec}(\mathbf{A}) = \mathbf{\check{a}} = \begin{bmatrix} a \\ b \\ c \\ d \end{bmatrix}.
 \]
 
-Additionally I will have to deal with $4^{th}$ order tensors in a form of matrix-of-matrices. These matrices are denoted by using blackboard bold:
+Additionally, I will have to deal with $4^{th}$ order tensors in a form of matrix-of-matrices. These matrices are denoted by using blackboard bold:
 
@@
 
-When vectorizing $\mathbb{A}$ the received form looks as described in the following line:
+We can now vectorize $\mathbb{A}$ and get the following result
 
 \[
-\mathbb{A} = \operatorname{vec}(\mathbb{A})= \left[ \,\operatorname{vec}\left(\mathbf{A}_{00}\right)\, \bigg| \,\operatorname{vec}\left(\mathbf{A}_{10}\right)\, \bigg| \,\operatorname{vec}\left(\mathbf{A}_{01}\right)\, \bigg| \,\operatorname{vec}\left(\mathbf{A}_{11}\right)\, \right].
+\operatorname{vec}(\mathbb{A}) = \left[ \,\operatorname{vec}\left(\mathbf{A}_{00}\right)\, \bigg| \,\operatorname{vec}\left(\mathbf{A}_{10}\right)\, \bigg| \,\operatorname{vec}\left(\mathbf{A}_{01}\right)\, \bigg| \,\operatorname{vec}\left(\mathbf{A}_{11}\right)\, \right] = \mathbf{\check{A}}.
 \]
 
-This term above is equivalent to the notation described here:
+This term above is equivalent to the subsequent notation
 
 \[
-\mathbb{A}=\left[\begin{array}{llll}{a} & {e} & {i} & {m} \\ {b} & {f} & {j} & {n} \\ {c} & {g} & {k} & {o} \\ {d} & {h} & {l} & {p}\end{array}\right] 
-=\mathbf{\check{A}}.
+\mathbf{\check{A}}=\left[\begin{array}{llll}{a} & {e} & {i} & {m} \\ {b} & {f} & {j} & {n} \\ {c} & {g} & {k} & {o} \\ {d} & {h} & {l} & {p}\end{array}\right].
 \]
 
-The advantage of this form is that one can write several expressions as a cross product. I will need this property later to simplify complicated expressions and calculations.
+The advantage of this form is that we can write several expressions as a cross product. I will need this property later to simplify complicated expressions and calculations.
 
 \subsection{Summary}
-A quick overview of the notation used so far:
-
-\begin{addmargin}[1cm]{1cm}
-a: Scalar \\
-\textbf{A}: Matrix or tensor \\
-\textbf{a}: Vector \\
-vec(\textbf{A}) = $\mathbf{\check{a}}$: Vectorized matrix \\
-$\mathbb{A} = \mathbf{\check{A}}$: matrix-of-matrices
-\end{addmargin}
+Here is a quick overview of the introduced notation:
+\begin{align*}
+\text{a}&: \text{Scalar} \\
+\mathbf{A}&: \text{Matrix or tensor} \\
+\mathbf{a}&: \text{Vector} \\
+\mathbf{\check{a}}&: \text{Vectorized matrix (also written as vec($\mathbb{A}$))} \\
+\mathbf{\check{A}}&: \text{matrix-of-matrices}
+\end{align*}
 
 \todoredefined[inline]{
-TODO: Check if all notations used later are declared. Make matrix of matrices better looking.
+TODO: Check if all notations used later are declared.
 }
@@
 \section{Mathematical Background}
-Since mathematics play an important role in the field of interest the first step is to build a solid background before diving further into more complex calculations.
-This chapter should cover all the important concepts used later in the calculations.
+Since mathematics play an important role in the field of interest, the first step is to build a solid background before diving further into more complex calculations.
+This section covers all the important concepts used later in the calculations.
 A basic understanding of linear algebra is assumed.
@@
 \subsection{Matrices}
-At first I will discuss the physical or geometrical meaning of some common matrix properties.
+In the upcoming chapters I will mainly be using matrices  in the calculations. This subsection lists an overview of the matrix properties used later:
 
-A matrix \textbf{A} is positive definite if $\textbf{x}^\intercal \textbf{Ax}$ is positive for all of the non-zero values of the column matrix \textbf{x}.
+\begin{property}[\textbf{Positive Definiteness}]
+A matrix $\mathbf{A}$ is positive definite if $\mathbf{x}^\intercal \mathbf{Ax}$ is positive for all of the non-zero values of the column matrix $\mathbf{x}$.
+\end{property}
 
 \todoredefined[inline]{
-TODO: Not done yet. What needs to be covered here? positive definite matrices definition and lemmas, orthogonal, etc. Should it even be included?
+TODO: Not done yet. Include determinant and what is used later
 }
@@
 
-The \acrlong{svd}, which is abbreviated \acrshort{svd}, will play an important role in formulating the deformation gradient.
-It is important for this application since it represents the best possible approximation of a given matrix by a matrix of low rank.
+The \acrlong{svd} (\acrshort{svd}) will play an important role in the formulation of the deformation gradient.
+It represents the best possible approximation of a given matrix by a matrix of low rank.
 This approximation can be looked at as a compression of the data given (\cite{LiesenMehrmann2015}, S.
@@
 In this section I will give a broad introduction into the field of Continuum Mechanics.
-In Continuum Mechanics one is less interested in small particles like atoms or molecules of an object but rather in pieces of matter which are in comparison very large.
-I am therefore concerned with the mechanical behavior of solids and fluids on the macroscopic scale (\cite{Spencer1980}, p.
+In Continuum Mechanics we are less interested in small particles like atoms or molecules of an object but rather in pieces of matter which are in comparison very large.
+We are therefore concerned with the mechanical behavior of solids and fluids on the macroscopic scale (\cite{Spencer1980}, p.
 1).
@@
 \section{Deformation}
-When applying a force over an object naturally the object itself undergoes a deformation.
-In the following I will be consistent with most previous literature in continuum mechanics and use the term strain as a measure of deformation and stress as the force per unit area:
+If we apply a force over an object, the object itself undergoes a deformation. This behavior is intuitively clear. But how do we formalize this in a mathematical construct?
 
-\begin{addmargin}[2cm]{2cm}
-\textit{Strain = measure of deformation}  \\
-\textit{Stress = force per unit area} 
-\end{addmargin}
+In the following, I will be consistent with most previous literature in continuum mechanics and use the term \textit{strain} as a measure of deformation and \textit{stress} as the force per unit area.
 
@@
 Now let us have a look at a deformation in a rather mathematical sense.
-Graphically one can imagine a deformation with the help of a two dimensional deformation map as shown in Fig.
+Graphically, one can imagine a deformation with the help of a two dimensional deformation map as shown in Fig.
 \ref{fig:deformationmap}.
-Here on the left side there is an ellipse that represents an object or material in its rest state.
-A function $\phi$ maps this rest state of the ellipse to a deformed state shown in Fig.
-\ref{fig:deformationmap} on the right side.
-Mathematically spoken this means that one can map each point of a chosen object from its rest state to a deformed one.
+The ellipse on the left side represents an object or material in its rest state.
+A function $\phi$ maps this rest state of the ellipse to a deformed state as shown on the right side.
+Mathematically speaking, this means that we can map each point of a chosen object from its rest state to a deformed one.
 

### 2020-02-29 LaTeX-Master-Vorlage/chapter/Background.tex
working on backgroun

@@
 \end{align*}
-where $\mathbf{\Sigma}$ = diag ($\sigma$1, $\sigma$2, . . . , $\sigma$r), and $\sigma$1 $\geq$ $\sigma$2 $\geq$ · · · $\geq$ $\sigma$r $>$ 0 are the positive singular values of $\mathbf{A}$.
+where $\mathbf{\Sigma}$ = diag ($\sigma_1$, $\sigma_2$, . . . , $\sigma_r$), and $\sigma_1$ $\geq$ $\sigma_2$ $\geq$ · · · $\geq$ $\sigma_r$ $>$ 0 are the positive singular values of $\mathbf{A}$.
 
@@
 \section{Continuum Mechanics}
-In this section I will give a broad introduction into the field of Continuum Mechanics.
-In Continuum Mechanics we are less interested in small particles like atoms or molecules of an object but rather in pieces of matter which are in comparison very large.
+In this section, I will give a broad introduction into the field of Continuum Mechanics.
+In Continuum Mechanics, we are less interested in small particles like atoms or molecules of an object but rather in pieces of matter which are in comparison very large.
 We are therefore concerned with the mechanical behavior of solids and fluids on the macroscopic scale (\cite{Spencer1980}, p.
@@
 
-In conclusion the function $\phi$ describes the deformation.
-When deriving $\phi$ one can calculate the deformation gradient \textbf{F} which serves as a measure of the deformation in the following sense:
+When deriving $\phi$, we can calculate the deformation gradient \textbf{F} which serves as a measure of the deformation in the following sense:
 
-\[
-\begin{array}{l}
-{\text { Deformation gradient: }} {\mathbf{F}=\operatorname{\nabla} \phi}
-\\
-{\text { Length changes: }} {\qquad I_{C}=\operatorname{tr}\left(\mathbf{F}^{T} \mathbf{F}\right)} 
-\\ 
-{\text { Volume changes: }} {\qquad J=\operatorname{det}(\mathbf{F})}\end{array}
-\]
+\begin{align*}
+&\text{Deformation gradient:} & \mathbf{F}&=\operatorname{\nabla} \phi \\
+&\text{Length changes:} & \qquad I_{C}&=\operatorname{tr}\left(\mathbf{F}^{T} \mathbf{F}\right) \\
+&\text{Volume changes:} & \qquad J&=\operatorname{det}(\mathbf{F})
+\end{align*}
 
 \todoredefined[inline]{
-TODO: Adjust so the equal sign is at the same place in each column.
-Explain strain and stress and their meaning for later use in material constants (not explained in paper).
-Include own image instead of the one here?
+TODO: Explain strain and stress and their meaning for later use in material constants (not explained in paper). Include own image instead of the one here?
 }
@@
 \subsection{Deformation Gradient}
-The deformation gradient \textbf{F} offers as said previously a measurement of the deformation.
-With its help one can amongst other things calculate the volume and length change an object undergoes during a deformation.
-For my needs I define the deformation gradient exactely as the authors of the paper \cite{Smith:2018:SNF:3191713.3180491} did:
+With the help of the deformation gradient \textbf{F}, we can calculate the change in volume and length of an object during a deformation.
+For my needs, I am defining the deformation gradient analogous to the authors of \textit{\acrshort{snh}}:
 
@@
 
-Using the SVD theorem mentioned in thm.\ref{SVD} $\mathbf{F}$ can be written in the form of
+Using the SVD theorem shown in Thm.\ref{SVD}, \textbf{F} can be written in the form of
 
@@
 The $\sigma_i$ denote the singular values of $\mathbf{\Sigma}$.
-Unlike the normal convention the authors of the paper \textit{Stable Neo-Hookean Flesh Simulation} decided that the rotation variant moves reflections to $\mathbf{\Sigma}$.
-This results into $\operatorname{det}(\mathbf{U})=\operatorname{det}(\mathbf{V})=1$ and the property that $\mathbf{\Sigma}$ is allowed to have negative entries.
+Unlike the normal convention, the authors of \textit{\acrshort{snh}} decided that the rotation variant moves reflections to $\mathbf{\Sigma}$.
+This results in $\operatorname{det}(\mathbf{U})$ and $\operatorname{det}(\mathbf{V})$ being equal to 1 and the property that $\mathbf{\Sigma}$ is allowed to have negative entries.
 
@@
 \subsubsection{Polar Decomposition of the Deformation Gradient}
-With the help of theorem \ref{PD} one can decompose the deformation gradient in the following form:
+With the help of Thm. \ref{PD} we can decompose the deformation gradient into the following form:
 
@@
 \subsection{Material Constants}
-When we look at a deformation of an object we need to consider the material the object consists of.
+When we look at a deformation of an object, we need to consider the material the object consists of.
 A material can be very stiff like steel or easily deformable like rubber.
-In order to measure the deformation in a specific material we need the \textit{Poisson's Ratio} of said material.
+In order to measure the deformation of a specific material, we need the \textit{Poisson's Ratio} of said material.
 The poisson's ratio is a material constant that is defined as
@@
 
-In the context of flesh simulations I am using the poisson's ratio as a characterization for the resistance to volume change of flesh.
+In the context of flesh simulations, I am using the poisson's ratio as a characterization for the resistance to volume change of flesh.
 Biological tissues such as flesh, fat and muscles have one important property: Volume preservation.
-As a result the poisson's ratio is a higher value, meaning it is found in the range between 0.45 and 0.5 \cite{Smith:2018:SNF:3191713.3180491}.
+As a result the poisson's ratio takes on higher values in the range of 0.45 and 0.5 \cite{Smith:2018:SNF:3191713.3180491}.
 
-The calculation of the poisson's ratio defined in equation \ref{eq:poisson} is a challenge.
-Fortunately we can make use of the \textit{Lamé Parameters}.
-These are the two constants $\mu$ and $\lambda$ that are specific for a material.
-With the help of these two constants one can transform equation \ref{eq:poisson} into the following form:
+The calculation of the poisson's ratio defined in Eq.
+\ref{eq:poisson} is a challenge.
+Fortunately, we can make use of the \textit{Lamé Parameters}, the two material specific constants $\mu$ and $\lambda$.
+With the help of these two constants we can transform Eq.
+\ref{eq:poisson} into the following form:
 

### 2020-02-29 LaTeX-Master-Vorlage/chapter/Background.tex
improving paper chapter

@@
 
-\section{Deformation}
+\subsection{Deformation}
 If we apply a force over an object, the object itself undergoes a deformation. This behavior is intuitively clear. But how do we formalize this in a mathematical construct?
@@
 When deriving $\phi$, we can calculate the deformation gradient \textbf{F} which serves as a measure of the deformation in the following sense: 
-
 \begin{align*}
@@
 \subsubsection{Polar Decomposition of the Deformation Gradient}
-With the help of Thm. \ref{PD} we can decompose the deformation gradient into the following form:
+With the help of Thm.\ref{PD} we can decompose the deformation gradient into the following form:
 
@@
 \subsection{Deformation Energy}
-In order to get a convincing simulation of high quality one must choose an appropriate energy.
+In order to get a convincing simulation of high quality, we have to choose an appropriate energy.
 In the case of modelling deformations on human-like characters an elastic energy needs to be chosen.
-The key property that makes an energy elastic is that if all the forces that are applied over an object add up to zero the object must come back into its rest shape.
+The key property that makes an energy elastic is that if all the forces that are applied over an object add up to zero, the object must come back into its rest shape.
 \\

### 2020-02-29 LaTeX-Master-Vorlage/chapter/paper.tex
improving paper chapter

@@
-\chapter{Paper} \label{c:Paper}
-In this chapter I will examine the topic of the paper \textit{Stable Neo-Hookean Flesh Simulation} \cite{Smith:2018:SNF:3191713.3180491}.
-In the interest of understanding the thought process of the authors I will include some of their calculations a bit more detailed.
-In addition examples and visualisations should help for a better perception.
+\chapter{Stable Neo-Hookean Flesh Simulation} \label{c:Paper}
+In this chapter, I will examine further the topic of the paper \textit{\acrshort{snh}}.
+In the interest of understanding the thought process of the authors, I will include some of their calculations more detailed.
+In addition, examples and visualisations are presented for a better understanding.
 
 \section{Deformation Gradient}
-In the following calculations some properties of the deformation gradient $\mathbf{F}$ covered in the background chapter will be used.
+In the following calculations some properties of the deformation gradient $\mathbf{F}$ covered in chapter 2 will be used.
 These properties are summarized in table \ref{table:gradient_quantities} for a better overview:
@@
     \end{tabular}
-    \caption{Quantities Derived from the Deformation Gradient \textbf{F} taken from \cite{Smith:2018:SNF:3191713.3180491}}
+    \caption{Quantities derived from the Deformation Gradient \textbf{F} taken from \cite{Smith:2018:SNF:3191713.3180491}}
 \label{table:gradient_quantities}
@@
 The core goal of the paper was to model deformations for virtual characters that have human-like features.
-They concentrated on the deformation energy.
+The focus of the authors was the deformation energy.
 In order to achieve a convincing result the first step is to specify some requirements.
-For our needs in this case the stability of the energy is important.
-More precisely we need a hyperelastic energy that is stable in the following four important ways:
+Firstly the energy has to be stable.
+More precisely, we need a hyperelastic energy that is stable in the following four important ways:
 
 \textbf{1.
-Inversion Stability:} Given some arbitrary object it is possible that while deforming the object one can arrive at a zero volume state or even an entire inversion.
-Take for example the tetrahedron shown in figure \ref{fig:inversion_1}.
-In figure \ref{fig:inversion_2} we see a deformed state of this tetrahedron where the volume is scaled down to zero and we are left with a simple triangle.
-In figure \ref{fig:inversion_3} image we have an inversion of the object.
-The needed deformation energy has to be able to deal with both cases.
+Inversion Stability:} Given some arbitrary object, it is possible that while deforming the object one can arrive at a zero volume state or even an entire inversion.
+Take for example the tetrahedron shown in Fig.
+\ref{fig:inversion_1}.
+In Fig.
+\ref{fig:inversion_2} we see a deformed state of this tetrahedron where the volume is scaled down to zero and we are left with a simple triangle.
+In Fig.
+\ref{fig:inversion_3} we have an inversion of the object.
+The deformation energy has to be able to deal with both cases.
 That means that the energy has to be singularity-free and does not need any filters or threshold (\cite{Smith:2018:SNF:3191713.3180491}, 12:3).

### 2020-03-03 LaTeX-Master-Vorlage/chapter/paper.tex
working on paper section

@@
 \textbf{1.
-Inversion Stability:} Given some arbitrary object, it is possible that while deforming the object one can arrive at a zero volume state or even an entire inversion.
+Inversion Stability:} Given some arbitrary object, it is possible that while deforming the object we can arrive at a zero volume state or even an entire inversion.
 Take for example the tetrahedron shown in Fig.
@@
 \textbf{2.
-Reflection stability:} A reflection is rotation around the coordinate origin.
+Reflection stability:} A reflection is a rotation around the coordinate origin.
 The deformation energy needs to be well behaved regardless of the reflection convention used in the singular value decomposition.
+\todoredefined[inline]{
+TODO: Explain a bit better what this means. What means well behaved?
+}
 
 \textbf{3.
-Rest stability:} When deforming an object in a certain way we apply one or multiple forces over that object.
-With rest stability we want that if the sum of forces is equal to zero the object must be back in its rest state.
+Rest stability:} When deforming an object in a certain way, we apply one or multiple forces to that object.
+When we achieve rest stability, we ensure that if the sum of all forces is equal to zero, the object must be back in its rest state.
 
@@
 Meta-stability under degeneracy:} We can crush an object into an arbitrary shape like a plane, line or point.
-That process is illustrated for a cube in figure \ref{fig:meta_stability}.
-The cube should now be able to recover to its actual shape after the deformation.
+This process is illustrated for a cube in Fig.
+\ref{fig:meta_stability}.
+The cube should be able to recover to its actual shape after the deformation.
 
@@
 
-Based on these four requirements we will in the following determine if a deformation energy is suited for our needs.
+Based on these four requirements, we will in the following determine if a deformation energy is suited for our needs.
 
 \todoredefined[inline]{
-TODO: Finish reflection stability. Maybe add own images and more sources. Improve English in this section.
+TODO: Maybe add own images and more sources.
 }
@@
 
-In previous literature a few energies were proposed that should be analysed properly. They are listed in table \ref{table:energies} below.
+In previous literature, a few energies were proposed that I will analyse in this section. They are listed in table \ref{table:energies} below.
 
@@
     \end{tabular}
-    \caption{Summary of proposed energies taken from \cite{Smith:2018:SNF:3191713.3180491}}
+    \caption{Summary of proposed energies (\cite{Smith:2018:SNF:3191713.3180491}, 12:3)}
 \label{table:energies}
@@
 Each energy formulation can be split up into a 1D length term and a 3D volume term.
-The 1D length term penalizes length changes the object undergoes whereas the 3D volume term is a volume-preserving penalty term.
+The 1D length term penalizes the length changes an object undergoes, whereas the 3D volume term is a volume-preserving penalty term.
 
@@
     \end{tabular}
-    \caption{Energies split up into its 1D length and 3D volume term}
+    \caption{Energies split up into their 1D length and 3D volume term}
 \label{table:energies_split}
@@
 \]
-that is used in $\Psi_{Neo}$ and $\Psi_{A}$. If we expand the energy with the singular values of the deformation gradient \textbf{F} we get the following term:
+that is used in $\Psi_{Neo}$ and $\Psi_{A}$. If we expand the energy with the singular values of the deformation gradient \textbf{F}, we get the following term:
 \[
@@
 \]
-The energy as it is formulated reaches its minimum at a zero volume state, meaning $I_{C}=0$ which results in $\Psi_{M}=-3$.
-Mooney added the hard constraint that $J=1$ so that the energy is minimized at the volume preserving configuration that is closest to the stretch space origin.
+This energy reaches its minimum at a zero volume state, meaning $I_{C}=0$ which results in $\Psi_{M}=-3$.
+Mooney added the hard constraint that $J=1$, so that the energy is minimized at the volume preserving configuration that is closest to the stretch space origin.
 Note that the energy is singularity free and well defined under inversion.
@@
 \]
-is used in $\Psi_{B}$ and $\Psi_{C}$ and was introduced by Rivlin in 1948. Using the singular values of \textbf{F} we get the following term:
+is used in $\Psi_{B}$ and $\Psi_{C}$ and was introduced by Rivlin (\cite{rivlin1948large}). Using the singular values of \textbf{F}, we get the following term:
 \[

### 2020-03-07 LaTeX-Master-Vorlage/chapter/paper.tex
paper, depressed cube

@@
 \]
-does not have these noted difficulties.
-It is bounded, well defined and invertible.
-After these observations we combine the robust length with the robust volume term and receive $\Psi_D$ that is defined as
+does not have these problems. It is bounded, well defined and invertible. After these observations we combine the robust length with the robust volume term and receive $\Psi_D$ that is defined as
 \[
@@
 \]
-and is singularity free and well defined under inversion. Unfortunately $\Psi_D$ does not satisfy the requirement of being rest stable which will be discussed in the next section.
+and is singularity free and well defined under inversion. Unfortunately, $\Psi_D$ does not satisfy the requirement of being rest stable which will be discussed in the next section.
 
 \todoredefined[inline]{
-TODO: Bonet and Wood 2008 or 1997? Table looks ugly, improve and add resources. Improve English sentences. Overall okay concerning the content?
+TODO: Bonet and Wood 2008 or 1997?
 }
@@
 \subsection{Rest Stabilization}
-Although $\Psi_{D}$ meets almost all stated requirements it is not rest stable.
-This can be shown with the Piola-Kirchhoff (PK1) stress tensor for $\Psi_D$ depending on the identity matrix $\mathbf{I}$:
+Although $\Psi_{D}$ meets almost all stated requirements, it is not rest stable.
+This can be shown with the Piola-Kirchhoff (PK1) stress tensor for $\Psi_D$ derived by the deformation gradient \textbf{F}:
 \begin{align*}
@@
 
-If the energy had rest stability $P_{D}(\mathbf{I})$ would resolve to zero.
-Unfortunately this is not the case here.
-In order to solve that problem the authors modified $(J-1)^{2}$ to $(J-\alpha)^{2}$.
-Using this modification the energy shifts to
+If the energy had rest stability, $P_{D}(\mathbf{I})$ would resolve to zero.
+Unfortunately, this is not the case here.
+In order to solve that problem, the authors modified $(J-1)^{2}$ to $(J-\alpha)^{2}$.
+Using this modification the energy can written as
 \[
@@
 
-Taking $\Psi_E$ in the PK1 equation from before we get
+Inserting $\Psi_E$ into the PK1 equation from before, we get
 \begin{align*}
@@
 \end{align*}
-Since constant disappear under differentiation this expression is functionally equivalent to 
+Since constants disappear under differentiation this expression is functionally equivalent to 
 \[
@@
 \]
-Now one can notice that $\Psi_{E}$ looks very similar to $\Psi_{Neo}$.
+Now we can see that $\Psi_{E}$ looks very similar to $\Psi_{Neo}$.
 The difference is that $log(J)$ is replaced with $(J-1)$ in $\Psi_{E}$.
-Remember that $(J-1)$ is the first term in the taylor approximation of $\operatorname{log}(J)$ at $J=1$:
+Keep in mind that $(J-1)$ is the first term in the taylor approximation of $\operatorname{log}(J)$ at $J=1$:
 \begin{align*}
 \sum_{n=0}^{\infty} &= \frac{f^{(n)}(1)}{n!} (J-1)^{n} \\
-&= \boldsymbol{(J-1)} - \frac{1}{2} (J-1)^{2} + \frac{1}{3} (J-1)^{3} -\frac{1}{4} (J-1)^{4} + ...
+&= \boldsymbol{(J-1)} - \frac{1}{2} (J-1)^{2} + \frac{1}{3} (J-1)^{3} -\frac{1}{4} (J-1)^{4} + \text{...}
 \end{align*}
+Thus $\Psi_{E}$ is an approximation of $\Psi_{Neo}$.
 
@@
 \end{equation}
-With that adjustment the rest stability term shifts to $\alpha=1+\frac{\mu}{\lambda}-\left(\frac{\mu}{4}\right)\lambda$.
+With that adjustment the rest stability term can be written as $\alpha=1+\frac{\mu}{\lambda}-\left(\frac{\mu}{4}\right)\lambda$.
 
@@
 \section{Energy Analysis}
-The goal of this chapter is to show that a complete eigenanalysis can be performed on equation \ref{eq:stable_energy}.
+The goal of this chapter is to show that a complete eigenanalysis can be performed on Eq. \ref{eq:stable_energy}.
 
 \subsection{First Piola-Kirchhoff Stress (PK1)}
-In order to analyse the energy PK1 can be used for equation \ref{eq:stable_energy}:
+In order to analyse the energy PK1 can be used for Eq. \ref{eq:stable_energy}:
 \begin{align*}
@@
 
-with $\alpha=1+\frac{\mu}{\lambda}-\left(\frac{\mu}{4}\right)\lambda$. For future use it can be more practical to write $\frac{\partial J}{\partial \mathbf{F}}$ as a result of cross products:
+with $\alpha=1+\frac{\mu}{\lambda}-\left(\frac{\mu}{4}\right)\lambda$. For further use it can be more practical to write $\frac{\partial J}{\partial \mathbf{F}}$ as a result of cross products:
 \begin{equation}\label{eq:cross_product}
@@
 \subsection{The Energy Hessian Terms}
-Using the scalar notation for $\mathbf{F}$ the hessian of the energy can be written in a fourth-order matrix-of-matrices:
+Using the scalar notation for $\mathbf{F}$, the Hessian of the energy can be written as a fourth-order matrix-of-matrices:
 \[
@@
 \]
-Each term in the final equation $\mathrm{T}_i$, $\mathrm{M}_i$, $\mathrm{G}_i$, $\mathrm{H}_i$ respectively the Tikohonov, Mu, volume Gradient and volume Hessian term will be examined separately in the following sections.
+We can split up this final equation into these four term: $\mathrm{T}_i$ (Tikohonov), $\mathrm{M}_i$ (Mu), $\mathrm{G}_i$ (Volume Gradient), $\mathrm{H}_i$ (Volume Hessian).
+I will examine them separately in the next section.
 
@@
 \subsubsection{Tikhonov}
-The Tikhonov term can be viewed as a fourth-order matrix-of-matrices
+The Tikhonov term is a fourth-order matrix-of-matrices
 \[
@@
 \]
-If we vectorize $\mathbb{T}$ we get the identity matrix $\mathbf{I} \in \mathbb{R}^{9x9}$ which is full rank, positive definite and independent of the values in F.
-It serves as a regularizer for the rest of the energy
+If we vectorize $\mathbb{T}$, we get the identity matrix $\mathbf{I} \in \mathbb{R}^{9x9}$ which is of full rank, positive definite and independent of the values in \textbf{F}. 
 \[
@@
 \]
+It serves as a regularizer for the rest of the energy.
 
@@
 \]
-When vectorizing $\mathbb{M}$ the resulting matrix has the squared values of $f_i$ placed on the diagonal
+When vectorizing $\mathbb{M}$, the resulting matrix $\mathbf{\check{M}}$ has the squared values of $f_i$ placed on the diagonal
 \[
@@
 \]
-This matrix has rank one and has a single non-zero eigenvalue. In order to examine the eigenvalues one can calculate
+This matrix has rank one and has a single non-zero eigenvalue. In order to examine the eigenvalues, we can calculate
 \[
@@
 \]
-in which $\|\cdot\|_F$ stands for the Frobenius norm and $\sigma_i$ for the singular values from $\mathbf{\Sigma}$ in the SVD of $\mathbf{F}$ stated in eq.
+in which $\|\cdot\|_F$ stands for the Frobenius norm and $\sigma_i$ for the singular values from $\mathbf{\Sigma}$ in the SVD of $\mathbf{F}$ stated in Eq.
 \ref{eq:svd_simga}.
@@
 The vectorized matrix $\mathbf{\check{G}}$ can be written in a similar form as for the Mu term.
-With the help of the cross product of $\partial J / \partial \mathbf{F}$ stated in eq.
-\ref{eq:cross_product} $\mathbf{\check{G}}$ can be written as an outer product in the following way:
+With the help of the cross product of $\partial J / \partial \mathbf{F}$ stated in Eq.
+\ref{eq:cross_product}, $\mathbf{\check{G}}$ can be written as an outer product in the following way:
 \[
@@
 \]
-As in the Mu term one can notice a single non-zero, non-negative:
+As in the Mu term, we again have a single non-zero, non-negative eigenvalue calculated by
 \[
@@
 \]
-One can easily observe that $\mathbf{\check{H}}$ is a \textit{self-similar} cross-product matrix. Meaning that the macro structure of the matrix is the same as the micro structure.
+We can easily observe that $\mathbf{\check{H}}$ is a \textit{self-similar} cross-product matrix. This means that  the macro structure of the matrix is the same as the micro structure.
 
@@
 \subsubsection{Volume Hessian Eigenvalues}
-For determining the eigenvalues of $\mathbf{\check{H}}$ one needs to examine the two characteristic polynomials:
+For determining the eigenvalues of $\mathbf{\check{H}}$, we need to examine the two characteristic polynomials
 \begin{align*}
@@
 
-where $\epsilon$ denote the eigenvalues of $\mathbf{\check{H}}$ and $\mathbf{C}$ is taken from table \ref{table:gradient_quantities}.
-Equation (1) is easier to solve and corresponds o the characteristic polynomial of $\mathbf{C}$.
-Given its roots $\epsilon_\alpha$, $\epsilon_\beta$, $\epsilon_\gamma$ the eigenvalues of $\mathbf{\check{H}}$ are: $\pm \sqrt{\epsilon_\alpha}$, $\pm \sqrt{\epsilon_\beta}$, $\pm \sqrt{\epsilon_\gamma}$.
-Using the singular values of $\mathbf{F}$ the eigenvalues can be written nicely in the following way:
+where $\epsilon$ denotes the eigenvalues of $\mathbf{\check{H}}$ and $\mathbf{C}$ is taken from Table \ref{table:gradient_quantities}.
+Eq.
+(1) is easier to solve and corresponds to the characteristic polynomial of $\mathbf{C}$.
+Given its roots $\epsilon_\alpha$, $\epsilon_\beta$, $\epsilon_\gamma$, the eigenvalues of $\mathbf{\check{H}}$ are: $\pm \sqrt{\epsilon_\alpha}$, $\pm \sqrt{\epsilon_\beta}$, $\pm \sqrt{\epsilon_\gamma}$.
+Using the singular values of $\mathbf{F}$, the eigenvalues can be written nicely in the following way:
 \begin{align*}
-&\epsilon_3 = \sigma_0 &\epsilon_6 = -\sigma_0 \\
-&\epsilon_4 = \sigma_1 &\epsilon_7 = -\sigma_1 \\
-&\epsilon_5 = \sigma_2 &\epsilon_8 = -\sigma_2.
+\epsilon_3 &= \sigma_0 & \epsilon_6 &= -\sigma_0 \\
+\epsilon_4 &= \sigma_1 & \epsilon_7 &= -\sigma_1 \\
+\epsilon_5 &= \sigma_2 & \epsilon_8 &= -\sigma_2.
 \end{align*}
-The remaining eigenvalues can be obtained by equation (2). This equation represents a depressed cube and the roots can be obtained by
+The remaining eigenvalues can be obtained by using Eq.(2). This equation represents a depressed cube. A depressed cube is a cubic of the form
+\[
+t^3 + pt + q. 
+\]
+Eq.(2) can be written in this form with $p=-\operatorname{tr}(\mathbf{C})$ and $q= -2$. Using this knowledge, the roots of Eq.(2) can be obtained by
 \[
@@
 
+For further reading about how to solve depressed cubic equations, see e.g. \textit{How to Solve a Cubic Equation, Part 4: The 111 Case} \cite{4052506}.
+
 \todoredefined[inline]{
-TODO: Not happy with this section, improve and complete
+TODO: Not happy with this section, improve and complete. Change Nummerierung falsch? Explain what a depressed cube is.
 }
@@
 \section{Experiments with the Code}
-The authors of the paper \textit{Stable Neo-Hookean Flesh Simulation} \cite{Smith:2018:SNF:3191713.3180491} provided the implementation for an application of their formulated energy.
-In said code they implemented the stretch test on a cube.
+The authors of the paper \textit{\acrshort{snh}} provided the implementation for an application of their formulated energy.
+In said code, they implemented the stretch test on a cube.
 Their implementation demands a directory into which the output files should be saved, the two lamé parameters $\mu$ and $\lambda$ and a value for defining the desired resolution as input data.
-Here is an example for a command with resolution = 10, $\mu=1.0$, $\lambda=10.0$ and asks the output files to be written into the directory \textit{output}:
+Here is an example for a command with resolution = 10, $\mu=1.0$, $\lambda=10.0$ and output directory \textit{output}:
 \begin{lstlisting}[language=bash]
@@
 
-The algorithm then calculates the deformation in 25 steps and the deformation increases in each step.
-The outputs are 26 static objects that show the object in its rest state and the 25 steps of deformation.
+The algorithm progressively calculates the deformation in 25 steps. The outputs are 26 static objects that show the object in its rest state and the 25 steps of deformation.
 
@@
 
-\[ \sigma =  \frac{10.0}{2 (10.0 + 1.0)} = 0.4545 \in [-1, 0.5] \]
+\[ \sigma =  \frac{10.0}{2 (10.0 + 1.0)} = 0.4545 \]
 
-The following images in figure \ref{fig:stretchtest} show the stretch test with $\mu = 1.0$, $\lambda = 10.0$ and a resolution of 10.0 on a tetrahedral and a hexahedral mesh.
+The images in Fig. \ref{fig:stretchtest} show the stretch test with $\mu = 1.0$, $\lambda = 10.0$ and a resolution of 10.0 on a tetrahedral and a hexahedral mesh.
 

### 2020-03-08 LaTeX-Master-Vorlage/chapter/paper.tex
paper

@@
 For determining the eigenvalues of $\mathbf{\check{H}}$, we need to examine the two characteristic polynomials
-\begin{align*}
-&\epsilon^3 - \operatorname{tr}(\mathbf{C}) \epsilon - 2 J = 0 \tag{1}  \\
-&\epsilon^3 - \operatorname{tr}(\mathbf{C}) \epsilon^2 + \frac{1}{2} \left( \operatorname{tr^2}(\mathbf{C}) - \operatorname{tr}(\mathbf{C}^2) \right) \epsilon - \operatorname{det}(\mathbf{C}) = 0 \tag{2}
-\end{align*}
+\begin{align}
+&\epsilon^3 - \operatorname{tr}(\mathbf{C}) \epsilon - 2 J = 0  \label{vol_hessian_eq1} \\
+&\epsilon^3 - \operatorname{tr}(\mathbf{C}) \epsilon^2 + \frac{1}{2} \left( \operatorname{tr^2}(\mathbf{C}) - \operatorname{tr}(\mathbf{C}^2) \right) \epsilon - \operatorname{det}(\mathbf{C}) = 0 \label{vol_hessian_eq2}
+\end{align}
 
@@
 Eq.
-(1) is easier to solve and corresponds to the characteristic polynomial of $\mathbf{C}$.
+\ref{vol_hessian_eq1} is easier to solve and corresponds to the characteristic polynomial of $\mathbf{C}$.
 Given its roots $\epsilon_\alpha$, $\epsilon_\beta$, $\epsilon_\gamma$, the eigenvalues of $\mathbf{\check{H}}$ are: $\pm \sqrt{\epsilon_\alpha}$, $\pm \sqrt{\epsilon_\beta}$, $\pm \sqrt{\epsilon_\gamma}$.
@@
 \end{align*}
-The remaining eigenvalues can be obtained by using Eq.(2). This equation represents a depressed cube. A depressed cube is a cubic of the form
+The remaining eigenvalues can be obtained by using Eq. \ref{vol_hessian_eq2}. This equation represents a depressed cube. A depressed cube is a cubic of the form
 \[
@@
 \]
-Eq.(2) can be written in this form with $p=-\operatorname{tr}(\mathbf{C})$ and $q= -2$. Using this knowledge, the roots of Eq.(2) can be obtained by
+Eq. \ref{vol_hessian_eq2} can be written in this form with $p=-\operatorname{tr}(\mathbf{C})$ and $q= -2$. Using this knowledge, the roots of Eq. \ref{vol_hessian_eq2} can be obtained by
 \[
@@
 \]
-
 For further reading about how to solve depressed cubic equations, see e.g. \textit{How to Solve a Cubic Equation, Part 4: The 111 Case} \cite{4052506}.
 
+These are all of the eigenvalues of $\mathbf{\check{H}}$.
+We know that three of the six eigenvalues ($\epsilon_3$, ...
+$\epsilon_8$) have to negative or equal to zero since we take the positive and negative roots.
+In addition, the cosine function for calculating $\epsilon_0$, $\epsilon_1$ and $\epsilon_2$ ensures that one or two of these eigenvalues are also negative.
+As we have seen in the previous sections, the other terms of $\frac{\partial^2 \psi}{\partial \mathbf{F}^2}$ all only have nonnegative eigenvalues.
+So the volume Hessian is the only possible source of negative eigenvalues (\cite{Smith:2018:SNF:3191713.3180491}, 12:6).
+
 \todoredefined[inline]{
-TODO: Not happy with this section, improve and complete. Change Nummerierung falsch? Explain what a depressed cube is.
+TODO: include reflection convention? check with background
 }

### 2020-03-10 LaTeX-Master-Vorlage/chapter/Background.tex
background

@@
 \todoredefined[inline]{
-TODO: Not done yet. Include determinant and what is used later
+TODO: Not done yet. Include what is used later
 }
@@
 
+\subsection{Frobenius Norm}
+
+\begin{definition}[\textbf{Frobenius Norm}]
+\label{FN}
+Let \textbf{A} be a (m $\times$ n) matrix in the real or complex space. Then the Frobenius norm is defined as 
+\[
+\| \mathbf{A} \|_{F} := \sqrt{\sum\limits_{i=1}^{m} \sum\limits_{j=1}^{n} |a_{ij}|^2}.
+\]
+\end{definition}
+
+We can further represent the norm with the trace of the matrix, in which $\mathbf{A}^*$ is the conjugate transpose of \textbf{A}.
+Going from there, we can use the \acrshort{svd} of \textbf{A} and write the norm with respect to the singular values of \textbf{A}, denoted by $\sigma_i$
+\[
+\| \mathbf{A} \|_{F} = \sqrt{\operatorname{trace}(\mathbf{A} \mathbf{A}^*)} = \sqrt{\sum\limits_{i=1}^{\operatorname{min}\{m,n\}} \sigma_i^2}.
+\]
+
 \todoredefined[inline]{
-TODO: Complete this section. Add lemmas and theorems used afterwards in the calculations. Possible adjustments may come at the end. Add Frobenius norm?
+TODO: Complete this section. Add lemmas and theorems used afterwards in the calculations. Possible adjustments may come at the end.
 }
@@
 The $\sigma_i$ denote the singular values of $\mathbf{\Sigma}$.
-Unlike the normal convention, the authors of \textit{\acrshort{snh}} decided that the rotation variant moves reflections to $\mathbf{\Sigma}$.
-This results in $\operatorname{det}(\mathbf{U})$ and $\operatorname{det}(\mathbf{V})$ being equal to 1 and the property that $\mathbf{\Sigma}$ is allowed to have negative entries.
+Unlike the normal convention, \textbf{U} and \textbf{V} are rotations, which results in $\operatorname{det}(\mathbf{U})$ and $\operatorname{det}(\mathbf{V})$ being equal to 1.
+In addition, $\mathbf{\Sigma}$ is allowed to have negative entries.
 
 \todoredefined[inline]{
-TODO: Add some examples. Already include definitions of the paper?
+TODO: Add some examples.
 \\ Some more sources:
@@
 \subsubsection{Polar Decomposition of the Deformation Gradient}
-With the help of Thm.\ref{PD} we can decompose the deformation gradient into the following form:
+With the help of Thm.\ref{PD} we can decompose the deformation gradient into the following form
+\[
+\mathbf{F} = \mathbf{RS}
+\]
+where \textbf{R} is orthogonal and \textbf{S} is a positive definite symmetric matrix.
+\textbf{R} symbolises the rotation (with possible reflection) that \textbf{F} undergoes, whereas \textbf{S} contains the scaling along orthogonal directions of \textbf{F}.
 
-\[
-\mathbf{F} = \mathbf{RS}.
-\]
+\subsubsection{Relative volume change}
 
-\todoredefined[inline]{
-TODO: Explain more here.
-}
+\subsubsection{Right Cauchy-Green}
+
+\subsubsection{First right Cuachy-Green invariant}
 

### 2020-03-10 LaTeX-Master-Vorlage/chapter/paper.tex
background

@@
 
+In order to investigate the behaviour of the volume Hessian term further, let us look at J = det(\textbf{F}) a bit more in detail.
+J is not convex which is problematic since we want to use the Newton method for the optimization process.
+Fortunately, the other terms of $\frac{\partial^2 \psi}{\partial \mathbf{F}^2}$ serve as an additional regularization.
+
 \todoredefined[inline]{
-TODO: include reflection convention? check with background
+TODO: include reflection convention? check with background. Regularisation?
 }
 
+\subsubsection{Volume Hessian Eigenvectors}
+$\mathbf{\check{H}}$ can be factorized as $\mathbf{\check{H}} = \mathbf{\check{Q}}\mathbf{\Lambda}\mathbf{\check{H}}^\intercal$ according to its eigendecomposition.
+The eigenvectors can then be obtained by $\mathbf{\check{Q}}$.
+In the tensor form signified by $\mathbb{Q}$ each eigenvector is a 3 \times	 3 matrix:
+\[
+\mathbb{Q} = \left[\begin{array}{ccc}{\left[\mathbf{Q}_0\right]} & {\left[\mathbf{Q}_3\right]} & {\left[\mathbf{Q}_6\right]} \\ {\left[\mathbf{Q}_1\right]} & {\left[\mathbf{Q}_4\right]} & {\left[\mathbf{Q}_7\right]} \\ {\left[\mathbf{Q}_2\right]} & {\left[\mathbf{Q}_5\right]} & {\left[\mathbf{Q}_8\right]} \end{array}\right].
+\]
+The eigenvector corresponding to $\epsilon_3$ can be written as
+\[
+\mathbf{Q}_3 = \frac{1}{\sqrt{2}} \mathbf{U} \mathbf{D}_3 \mathbf{V}\intercal
+\]
+where \textbf{U} and \textbf{V} are taken from the \acrshort{svd} of \textbf{F}, $\frac{1}{\sqrt{•}}$
+
 \subsection{The Complete Eigensystem}
+
 \todoredefined[inline]{
@@
 \todoredefined[inline]{
-TODO: Make notation consistent (bold, cursive etc.) Explain better each step.
-Include all calculations?
-Make matrix of matrices more beautiful (more space).
-Eigenvalues of Mu and Gradient term better explain?
-Check each equation if correctly written.
+TODO: Eigenvalues of Mu and Gradient term better explain?
 }

### 2020-03-19 LaTeX-Master-Vorlage/chapter/Background.tex
working on background, deformation

@@
 \todoredefined[inline]{
-TODO: Not done yet. Include what is used later
+TODO: Is this necessary?
 }
@@
 Going from there, we can use the \acrshort{svd} of \textbf{A} and write the norm with respect to the singular values of \textbf{A}, denoted by $\sigma_i$
-\[
+\begin{equation} \label{eq:FN}
 \| \mathbf{A} \|_{F} = \sqrt{\operatorname{trace}(\mathbf{A} \mathbf{A}^*)} = \sqrt{\sum\limits_{i=1}^{\operatorname{min}\{m,n\}} \sigma_i^2}.
-\]
+\end{equation}
 
@@
 
-Now let us have a look at a deformation in a rather mathematical sense.
+We can formalize the behaviour of a deformation.
 Graphically, one can imagine a deformation with the help of a two dimensional deformation map as shown in Fig.
@@
 \end{figure}
+
+Each particle $X$ of a body can be characterized by a vector $\mathbf{x}$ containing its coordinates. If the particles undergo a displacement, we can describe their new coordinate vector with 
+\[
+	\check{\mathbf{x}} = \phi (\mathbf{x}).
+\]
 
@@
 
+\textbf{F} can be factorized in various ways. The next few sections show these factorizations.
+
+\subsubsection{Singular Value Decomposition of F}
+
 Using the SVD theorem shown in Thm.\ref{SVD}, \textbf{F} can be written in the form of
@@
 The $\sigma_i$ denote the singular values of $\mathbf{\Sigma}$.
-Unlike the normal convention, \textbf{U} and \textbf{V} are rotations, which results in $\operatorname{det}(\mathbf{U})$ and $\operatorname{det}(\mathbf{V})$ being equal to 1.
-In addition, $\mathbf{\Sigma}$ is allowed to have negative entries.
+\textbf{U} and $\mathbf{V^\intercal}$ are both orthogonal matrices that represent the rotation of \textbf{F}.
+$\Sigma$ on the other hand indicates the scaling of each coordinate $x_i$ by the factor $\sigma_i$.
 
 \todoredefined[inline]{
-TODO: Add some examples.
+TODO: Unlike the normal convention, $\mathbf{\Sigma}$ is allowed to have negative entries. --> reflection, maybe add subchapter
+\\ Add some examples.
 \\ Some more sources:
@@
 \subsubsection{Relative volume change}
+A useful information about a deformation is the volume change of the deformed object. It can be calculated by the determinate of \textbf{F}
+\[
+J = \operatorname{det}(\mathbf{F}).
+\]
+For a normal deformation, $J$ is a positive value.
+A determinant of zero would mean that the object is being deformed into a zero volume state e.g.
+a plane or a point.
+A negative determinant, on the other hand, indicates an inversion.
 
-\subsubsection{Right Cauchy-Green}
+\subsubsection{Right Cauchy-Green tensor}
 
-\subsubsection{First right Cuachy-Green invariant}
+\[
+\mathbf{C} = \mathbf{F^\intercal F}
+\]
+
+\subsubsection{First right Cauchy -Green invariant}
+
+\[
+I_C = \operatorname{\mathbf{C}}
+\]
+
+\subsection{Deformation Energy}
+In order to get a convincing simulation of high quality, we have to choose an appropriate energy.
+In the case of modelling deformations on human-like characters an elastic energy needs to be chosen.
+The key property that makes an energy elastic is that if all the forces that are applied over an object add up to zero, the object must come back into its rest shape.
+\\
+The energy then has to be minimized in order to get the results we want.
 
@@
 
-\subsection{Deformation Energy}
-In order to get a convincing simulation of high quality, we have to choose an appropriate energy.
-In the case of modelling deformations on human-like characters an elastic energy needs to be chosen.
-The key property that makes an energy elastic is that if all the forces that are applied over an object add up to zero, the object must come back into its rest shape.
-\\
-The energy then has to be minimized in order to get the results we want.
-
 \todoredefined[inline]{

### 2020-03-19 LaTeX-Master-Vorlage/chapter/paper.tex
working on background, deformation

@@
     \end{tabular}
-    \caption{Quantities derived from the Deformation Gradient \textbf{F} taken from \cite{Smith:2018:SNF:3191713.3180491}}
+    \caption{Quantities derived from the Deformation Gradient \textbf{F}}
 \label{table:gradient_quantities}
@@
 \]
-in which $\|\cdot\|_F$ stands for the Frobenius norm and $\sigma_i$ for the singular values from $\mathbf{\Sigma}$ in the SVD of $\mathbf{F}$ stated in Eq.
+in which $\|\cdot\|_F$ stands for the Frobenius norm introduced in Def.
+\ref{FN} and $\sigma_i$ for the singular values from $\mathbf{\Sigma}$ in the SVD of $\mathbf{F}$ stated in Eq.
 \ref{eq:svd_simga}.
+The equation can be obtained by using Eq.
+\ref{eq:FN}.
 The eigenvector is $\mathbf{\check{f}} / \| \mathbf{\check{f}} \|$.

### 2020-03-24 LaTeX-Master-Vorlage/chapter/Background.tex
working on bg, def. gradient

@@
 \subsection{Deformation}
-If we apply a force over an object, the object itself undergoes a deformation. This behavior is intuitively clear. But how do we formalize this in a mathematical construct?
+If we apply a force over an object, the object itself undergoes a deformation. This behavior is intuitively clear. But how can we formalize it?
 
-In the following, I will be consistent with most previous literature in continuum mechanics and use the term \textit{strain} as a measure of deformation and \textit{stress} as the force per unit area.
-
-\todoredefined[inline]{
-TODO: Decide whether to include the above paragraph and how to connect it better to the paper.
-}
-
-We can formalize the behaviour of a deformation.
-Graphically, one can imagine a deformation with the help of a two dimensional deformation map as shown in Fig.
+Graphically, we can imagine a deformation with the help of a two dimensional deformation map as shown in Fig.
 \ref{fig:deformationmap}.
@@
 A function $\phi$ maps this rest state of the ellipse to a deformed state as shown on the right side.
-Mathematically speaking, this means that we can map each point of a chosen object from its rest state to a deformed one.
 
@@
 
-Each particle $X$ of a body can be characterized by a vector $\mathbf{x}$ containing its coordinates. If the particles undergo a displacement, we can describe their new coordinate vector with 
+This means that we can map each particle of a chosen object from its rest state (at time $t_0 = 0$) to a deformed one.
+Each particle $X$ of a body can be characterized by a vector $\mathbf{x}$ containing its coordinates.
+If the particles are displaced after a time $t$, we can describe their new coordinate vector with
 \[
-	\check{\mathbf{x}} = \phi (\mathbf{x}).
+	\check{\mathbf{x}} = \phi (\mathbf{x}, t).
 \]
+If we for example consider a \textit{Translation}, every particle is displaced by the same distance and direction. Thus we can calculate $\check{\mathbf{x}}$ with
+\[
+	\check{\mathbf{x}} = \mathbf{x} + \mathbf{c}(t)
+\]
+where $\mathbf{c}$ is a vector that only depends on $t$ (\cite{Spencer1980}, p.63).
+
+\todoredefined[inline]{
+TODO: Include own image instead of the one here? \\
+Include this? \\
+In the following, I will be consistent with most previous literature in continuum mechanics and use the term \textit{strain} as a measure of deformation and \textit{stress} as the force per unit area.
+}
+
+\subsection{Deformation Gradient}
+The deformation gradient \textbf{F} can be obtained by deriving $\phi$. It is therefore the derivative of...
+
+\begin{wrapfigure}{r}{5.5cm}
+\centering
+	\includegraphics[width=6.5cm]{resources/stretch_plot.png}
+	\caption{Stretching of a rectangle}
+	\label{stretch:1}
+\end{wrapfigure}
+
+We can take a simple deformation in 2D to illustrate \textbf{F}. We can stretch an area in the following way:
+\[
+	Here comes formulas
+\]
+This is illustrated in \ref{stretch:1}.
 
@@
 
-\todoredefined[inline]{
-TODO: Explain strain and stress and their meaning for later use in material constants (not explained in paper). Include own image instead of the one here?
-}
-
-\subsection{Deformation Gradient}
 With the help of the deformation gradient \textbf{F}, we can calculate the change in volume and length of an object during a deformation.

### 2020-03-26 LaTeX-Master-Vorlage/chapter/Background.tex
continuum mechanics worked over, now cauchy green & def. energy left in background

@@
 \subsection{General Notation}
-Scalars are represented by regular, normal-weight variables such as $a$, whereas 
-tensors and matrices are represented by upper-case bold letters such as for example $\textbf{A}$. Vectors will be denoted by bold lower-case variables like $\textbf{a}$.
+Scalars are represented by regular, normal-weight variables such as $a$, whereas tensors and matrices are represented by upper-case bold letters such as for example $\textbf{A}$.
+Vectors will be denoted by bold lower-case variables like $\textbf{a}$.
 
@@
 In Continuum Mechanics, we are less interested in small particles like atoms or molecules of an object but rather in pieces of matter which are in comparison very large.
-We are therefore concerned with the mechanical behavior of solids and fluids on the macroscopic scale (\cite{Spencer1980}, p.
+The reason for this is that the calculation for the behaviour of individual atoms is very difficult for larger systems.
+We are therefore concerned with the mechanical behavior of solids and fluids on the macroscopic scale and we treat material as uniformly distribeted throughout regions of space.
+With this approach, it is possible to define quantities such as displacement, density, etc.
+as continuous functions of position (\cite{Spencer1980}, p.
 1).
@@
 \subsection{Deformation}
-If we apply a force over an object, the object itself undergoes a deformation. This behavior is intuitively clear. But how can we formalize it?
-
+If we apply a force over an object, the object itself undergoes a deformation.
+This behavior is intuitively clear.
 Graphically, we can imagine a deformation with the help of a two dimensional deformation map as shown in Fig.
 \ref{fig:deformationmap}.
-The ellipse on the left side represents an object or material in its rest state.
+The ellipse on the left side represents an object in its rest state.
 A function $\phi$ maps this rest state of the ellipse to a deformed state as shown on the right side.
@@
 
-This means that we can map each particle of a chosen object from its rest state (at time $t_0 = 0$) to a deformed one.
-Each particle $X$ of a body can be characterized by a vector $\mathbf{x}$ containing its coordinates.
+We can imagine, that we map each particle of a chosen object from its rest state to a deformed one.
+Each particle $X$ of a body can be characterized by a vector $\mathbf{x}$ containing its positional coordinates at time $t_0=0$.
+This is the reference configuration.
 If the particles are displaced after a time $t$, we can describe their new coordinate vector with
@@
 \]
-If we for example consider a \textit{Translation}, every particle is displaced by the same distance and direction. Thus we can calculate $\check{\mathbf{x}}$ with
+If we consider, for example a \textit{Translation}, every particle is displaced by the same distance and direction. Hence, we can calculate $\check{\mathbf{x}}$ with
 \[
@@
 \todoredefined[inline]{
-TODO: Include own image instead of the one here? \\
+TODO: Include own image instead of the one here? Other example than translation? \\
 Include this? \\
@@
 \subsection{Deformation Gradient}
-The deformation gradient \textbf{F} can be obtained by deriving $\phi$. It is therefore the derivative of...
+The next quantity, I will use in the upcoming chapters, is the deformation gradient \textbf{F}.
+With its help, we can calculate the change in volume and length of an object during a deformation.
+We can obtain \textbf{F} by taking the gradient of the function $\phi$ discussed in the last section.
 
-\begin{wrapfigure}{r}{5.5cm}
+\begin{wrapfigure}[10]{r}{5.5cm}
 \centering
-	\includegraphics[width=6.5cm]{resources/stretch_plot.png}
+	\includegraphics[width=5.5cm]{resources/stretch_plot.png}
 	\caption{Stretching of a rectangle}
@@
 \end{wrapfigure} 
-
-We can take a simple deformation in 2D to illustrate \textbf{F}. We can stretch an area in the following way:
-\[
-	Here comes formulas
-\]
-This is illustrated in \ref{stretch:1}.
-
-When deriving $\phi$, we can calculate the deformation gradient \textbf{F} which serves as a measure of the deformation in the following sense: 
+As an example, I am taking a simple deformation in 2D. Consider the coloured area in Fig. \ref{stretch:1}. We can stretch this area in the following way:
 \begin{align*}
-&\text{Deformation gradient:} & \mathbf{F}&=\operatorname{\nabla} \phi \\
-&\text{Length changes:} & \qquad I_{C}&=\operatorname{tr}\left(\mathbf{F}^{T} \mathbf{F}\right) \\
-&\text{Volume changes:} & \qquad J&=\operatorname{det}(\mathbf{F})
+	\check{x} &= 1.5x + 0y		\\
+	\check{y} &= 0x + 2y	
 \end{align*}
 
-With the help of the deformation gradient \textbf{F}, we can calculate the change in volume and length of an object during a deformation.
-For my needs, I am defining the deformation gradient analogous to the authors of \textit{\acrshort{snh}}:
-
+The resulting deformation gradient is then calculated by
+\[
+	\mathbf{F} = \begin{bmatrix} \frac{\partial [1.5x + 0y]}{\partial x} & \frac{\partial [1.5x + 0y]}{\partial y} \\ \frac{\partial [0x + 2y]}{\partial x} & \frac{\partial [0x + 2y]}{\partial y} \end{bmatrix} = \begin{bmatrix} 1.5 & 0.0 \\ 0.0 & 2.0 \end{bmatrix}.
+\]
+If \textbf{F} is equal to the identity matrix \textbf{I}, there is no deformation present. This would be the case, if we look at rigid body displacements.
+Since we will be handling deformation in the 3D space, the deformation gradient will have the form of a $3 \times 3$ matrix: 
 \begin{equation}\label{eq:deformation_gradient}
@@
 \end{equation}
-
-\textbf{F} can be factorized in various ways. The next few sections show these factorizations.
+\textbf{F} can be factorized and used to calculate other quantities. The next few sections show these factorizations and calculations.
 
@@
 The $\sigma_i$ denote the singular values of $\mathbf{\Sigma}$.
-\textbf{U} and $\mathbf{V^\intercal}$ are both orthogonal matrices that represent the rotation of \textbf{F}.
+\textbf{U} and $\mathbf{V}$ are both orthogonal matrices that represent the rotation of \textbf{F}.
 $\Sigma$ on the other hand indicates the scaling of each coordinate $x_i$ by the factor $\sigma_i$.
-
-\todoredefined[inline]{
-TODO: Unlike the normal convention, $\mathbf{\Sigma}$ is allowed to have negative entries. --> reflection, maybe add subchapter
-\\ Add some examples.
-\\ Some more sources:
-\\ http://www.continuummechanics.org/deformationgradient.html
-}
+Unlike the standard convention, where a possible reflection lies in the rotation variants (meaning \textbf{U} and \textbf{V}), here the reflections are moved to $\mathbf{\Sigma}$ and it is allowed to have a negative entry.
 
 \subsubsection{Polar Decomposition of the Deformation Gradient}
-With the help of Thm.\ref{PD} we can decompose the deformation gradient into the following form
+With the help of Thm.\ref{PD} we can decompose the deformation gradient into the form
 \[
@@
 where \textbf{R} is orthogonal and \textbf{S} is a positive definite symmetric matrix.
-\textbf{R} symbolises the rotation (with possible reflection) that \textbf{F} undergoes, whereas \textbf{S} contains the scaling along orthogonal directions of \textbf{F}.
+\textbf{R} symbolises the rotation (with possible reflection) that \textbf{F} undergoes, whereas \textbf{S} contains the scaling along the orthogonal directions of \textbf{F}.
 
@@
 For a normal deformation, $J$ is a positive value.
-A determinant of zero would mean that the object is being deformed into a zero volume state e.g.
+A determinant of zero would mean that the object is being deformed into a zero volume state, e.g.
 a plane or a point.
@@
 \subsubsection{Right Cauchy-Green tensor}
+The right Cauchy-Green tensor \textbf{C} can be calculated by multiplying \textbf{F} with itself:
+\[
+\mathbf{C} = \mathbf{F^\intercal F}.
+\]
+It serves as a direct measurement of the deformation.
 
+\subsubsection{First right Cauchy-Green invariant}
+This quantity describes the length change of the object after a deformation.
 \[
-\mathbf{C} = \mathbf{F^\intercal F}
-\]
-
-\subsubsection{First right Cauchy -Green invariant}
-
-\[
-I_C = \operatorname{\mathbf{C}}
+I_C = \operatorname{tr}(\mathbf{C})
 \]

### 2020-03-31 LaTeX-Master-Vorlage/chapter/Background.tex
working on strain energy

@@
 \subsection{Deformation}
+In continuum mechanics the term \textit{strain} is used as a measure of deformation and we denote \textit{stress} as the force per unit area.
 If we apply a force over an object, the object itself undergoes a deformation.
@@
 \todoredefined[inline]{
-TODO: Include own image instead of the one here? Other example than translation? \\
-Include this? \\
-In the following, I will be consistent with most previous literature in continuum mechanics and use the term \textit{strain} as a measure of deformation and \textit{stress} as the force per unit area.
+TODO: Include own image instead of the one here? Other example than translation? Explain strain and stress more?
 }
@@
 With its help, we can calculate the change in volume and length of an object during a deformation.
-We can obtain \textbf{F} by taking the gradient of the function $\phi$ discussed in the last section.
+We can obtain \textbf{F} by taking the gradient of the function $\phi$ discussed in the previous section.
 
@@
 
-The resulting deformation gradient is then calculated by
+The resulting deformation gradient can then be obtained by
 \[
@@
 \]
-If \textbf{F} is equal to the identity matrix \textbf{I}, there is no deformation present. This would be the case, if we look at rigid body displacements.
+If \textbf{F} is equal to the identity matrix \textbf{I}, there is no deformation present.
+This would be the case for rigid body displacements.
 Since we will be handling deformation in the 3D space, the deformation gradient will have the form of a $3 \times 3$ matrix:
@@
 \textbf{U} and $\mathbf{V}$ are both orthogonal matrices that represent the rotation of \textbf{F}.
-$\Sigma$ on the other hand indicates the scaling of each coordinate $x_i$ by the factor $\sigma_i$.
-Unlike the standard convention, where a possible reflection lies in the rotation variants (meaning \textbf{U} and \textbf{V}), here the reflections are moved to $\mathbf{\Sigma}$ and it is allowed to have a negative entry.
+$\mathbf{\Sigma}$ on the other hand indicates the scaling of each coordinate $x_i$ by the factor $\sigma_i$.
+Unlike the standard convention, where a possible reflection lies in the rotation variants (meaning \textbf{U} and \textbf{V}), here the reflections are moved to $\mathbf{\Sigma}$ and it is therefore allowed to have a negative entry.
+This has the effect that $\operatorname{det}(\mathbf{U}) = \operatorname{det}(\mathbf{V}) =1$.
 
@@
 With the help of Thm.\ref{PD} we can decompose the deformation gradient into the form
-\[
+\begin{equation}\label{PD_DG}
 	\mathbf{F} = \mathbf{RS}
-\]
+\end{equation}
 where \textbf{R} is orthogonal and \textbf{S} is a positive definite symmetric matrix.
@@
 \subsubsection{Relative volume change}
-A useful information about a deformation is the volume change of the deformed object. It can be calculated by the determinate of \textbf{F}
-\[
+A useful information about a deformation is the relative volume change of the deformed object. It can be calculated by the determinate of \textbf{F}
+\begin{equation}\label{det_DG}
 	J = \operatorname{det}(\mathbf{F}).
-\]
+\end{equation}
 For a normal deformation, $J$ is a positive value.
@@
 
-\subsubsection{Right Cauchy-Green tensor}
-The right Cauchy-Green tensor \textbf{C} can be calculated by multiplying \textbf{F} with itself:
-\[
-\mathbf{C} = \mathbf{F^\intercal F}.
-\]
-It serves as a direct measurement of the deformation.
-
-\subsubsection{First right Cauchy-Green invariant}
+\subsubsection{Cauchy-Green}
+The right Cauchy-Green tensor \textbf{C} can be calculated by 
+\begin{equation}\label{CG_DG}
+	\mathbf{C} = \mathbf{F^\intercal F}
+\end{equation}
+and is a $3 \times 3$ matrix for deformations in the 3D space. Using \textbf{C}, we can calculate the first right Cauchy-Green invariant $I_C$ with
+\begin{equation} \label{tr_CG_DG}
+	I_C = \operatorname{tr}(\mathbf{C}).
+\end{equation}
 This quantity describes the length change of the object after a deformation.
-\[
-I_C = \operatorname{tr}(\mathbf{C})
-\]
 
 \subsection{Deformation Energy}
+The deformation energy or strain energy $\Psi$ is a scalar that defines the stored energy of a object undergoing a deformation.
+The strain energy density is then the strain energy per unit volume.
+It equal to the work that has to be done by the stresses in order to alter the strains (\cite{KORSUNSKY20175}, p.10).
+This means that it is an indicator of how much force must be applied in order for an object to be deformed in a certain way.
+We can use the deformation energy to express the relationship between the stresses and strains.
+We can illustrate this with a stress-strain curve:
+
+\begin{figure}[!htbp]
+	\centering
+	\includegraphics[width=0.5\textwidth]{resources/stress_strain_curve.png}
+	\caption{Example for a stress-strain curve}
+	\label{fig:stress_strain}
+\end{figure}
+
+Unfortunately, this relationship is not always linear, which makes it harder to find a suitable model.
+For example if we reach a stress state that produces yielding, we cannot assume that the relationship is linear.
+If the material reaches the yield point, it can no longer recover into its rest shape due to permanent fractures during the deformation.
+This point is illustrated in Fig.
+\ref{fig:stress_strain} with \textit{Yield stress}.
+\textit{UTS} in Fig.
+\ref{fig:stress_strain} is abbreviated for Ultimate tensile strength and defines the maximal stress an object can bear before breaking.
+The area under the stress-strain curve corresponds to the strain energy.
+
 In order to get a convincing simulation of high quality, we have to choose an appropriate energy.

### 2020-04-01 LaTeX-Master-Vorlage/chapter/Background.tex
working on deformation energy

@@
 This means that it is an indicator of how much force must be applied in order for an object to be deformed in a certain way.
-We can use the deformation energy to express the relationship between the stresses and strains.
-We can illustrate this with a stress-strain curve:
+Thus we can use the deformation energy to express the relationship between the stresses and strains.
+We can illustrate this with a stress-strain curve shown in Fig.
+\ref{fig:stress_strain}.
+The area under the stress-strain curve corresponds to the strain energy.
 
@@
 \ref{fig:stress_strain} is abbreviated for Ultimate tensile strength and defines the maximal stress an object can bear before breaking.
-The area under the stress-strain curve corresponds to the strain energy.
 
-In order to get a convincing simulation of high quality, we have to choose an appropriate energy.
-In the case of modelling deformations on human-like characters an elastic energy needs to be chosen.
-The key property that makes an energy elastic is that if all the forces that are applied over an object add up to zero, the object must come back into its rest shape.
-\\
-The energy then has to be minimized in order to get the results we want.
+The behaviour of the object depends heavily on the material it consists of.
+This will be further explained in the next section concerning \textit{Material Constants}.
+In order to get a convincing simulation for a specific material, we have to choose an appropriate energy function.
+The behaviour of human flesh can be put into the category of hyperelastic materials.
+One key property of elasticity is, that if all the forces that are applied over an object add up to zero, the object must come back into its rest shape.
 

### 2020-04-01 LaTeX-Master-Vorlage/chapter/Background.tex
background done, now paper

@@
 
-\todoredefined[inline]{
-TODO: Check if all notations used later are declared.
-}
-
 \section{Mathematical Background}
@@
 A basic understanding of linear algebra is assumed.
-
-\subsection{Matrices}
-In the upcoming chapters I will mainly be using matrices  in the calculations. This subsection lists an overview of the matrix properties used later:
-
-\begin{property}[\textbf{Positive Definiteness}]
-A matrix $\mathbf{A}$ is positive definite if $\mathbf{x}^\intercal \mathbf{Ax}$ is positive for all of the non-zero values of the column matrix $\mathbf{x}$.
-\end{property}
-
-\todoredefined[inline]{
-TODO: Is this necessary?
-}
 
@@
 where $\mathbf{\Sigma}$ = diag ($\sigma_1$, $\sigma_2$, . . . , $\sigma_r$), and $\sigma_1$ $\geq$ $\sigma_2$ $\geq$ · · · $\geq$ $\sigma_r$ $>$ 0 are the positive singular values of $\mathbf{A}$.
+\end{theorem}
 
-\end{theorem}
-The definition and theorem were taken from \cite{ford2014numerical} (def. \ref{SVD} S.113, thm. \ref{singular_values} S.300).
-
-\todoredefined[inline]{
-TODO: Check reference. Make paragraphs work together. Add examples.
-}
+This definition and theorem were taken from \cite{ford2014numerical} (p.113, p.300).
 
@@
 
-The definition and theorem were taken from \cite{Spencer1980} (thm. \ref{PD} S.12).
+This theorem was taken from \cite{Spencer1980} (p.12).
 
@@
 \label{FN}
-Let \textbf{A} be a (m $\times$ n) matrix in the real or complex space. Then the Frobenius norm is defined as 
+Let \textbf{A} be a (m $\times$ n) matrix in the real or complex domain. Then the Frobenius norm is defined as 
 \[
@@
 \end{equation}
-
-\todoredefined[inline]{
-TODO: Complete this section. Add lemmas and theorems used afterwards in the calculations. Possible adjustments may come at the end.
-}
 
@@
 	\includegraphics[width=0.5\textwidth]{resources/deformation_map}
-	\caption{Deformation Map {\cite{STREAM2018}}}
+	\caption[Deformation Map]{Deformation Map {\cite{STREAM2018}}}
 	\label{fig:deformationmap}
@@
 
-\begin{wrapfigure}[10]{r}{5.5cm}
+\begin{wrapfigure}[11]{r}{5.5cm}
 \centering
 	\includegraphics[width=5.5cm]{resources/stretch_plot.png}
-	\caption{Stretching of a rectangle}
+	\caption[Stretching of a rectangle]{Stretching of a rectangle}
 	\label{stretch:1}
@@
 The deformation energy or strain energy $\Psi$ is a scalar that defines the stored energy of a object undergoing a deformation.
-The strain energy density is then the strain energy per unit volume.
+The strain energy density is the strain energy per unit volume.
 It equal to the work that has to be done by the stresses in order to alter the strains (\cite{KORSUNSKY20175}, p.10).
-This means that it is an indicator of how much force must be applied in order for an object to be deformed in a certain way.
+This means that the energy is an indicator of how much force must be applied in order for an object to be deformed in a certain way.
 Thus we can use the deformation energy to express the relationship between the stresses and strains.
@@
 	\includegraphics[width=0.5\textwidth]{resources/stress_strain_curve.png}
-	\caption{Example for a stress-strain curve}
+	\caption[Stress-strain curve]{Example for a stress-strain curve\footnotemark}
 	\label{fig:stress_strain}
 \end{figure}
+\footnotetext{https://commons.wikimedia.org/wiki/File:Stress-strain\_curve.svg}
 
@@
 Examples of materials with a negative poisson's ratio are for instance discussed in \textit{Foam structures with a negative Poisson's ratio} \cite{lakes1987foam} or \textit{Advances in negative Poisson's ratio materials} \cite{lakes1993advances}.
-
-Here are some examples of the poisson's ratio of various materials:
+In table \ref{table:1} are some examples of the poisson's ratio of various materials.
 
@@
     \end{tabular}
-    \caption{Different materials with their poisson's ratio taken from \cite{PhysRevB.80.132104}}
+    \caption[Materials with their poisson's ratio]{Different materials with their poisson's ratio (\cite{PhysRevB.80.132104}, p. 3)}
 \label{table:1}
@@
 \todoredefined[inline]{
-TODO: Topic generally covered, maybe adjust the following:
-Explain why volume preservation => high poisson's ratio. Explain how to get formula with lamé parameters, explain lamé parameters.
-Explain more on negative poisson's value?
-\\
-Further reading: http://silver.neep.wisc.edu/~lakes/PoissonIntro.html
+TODO: To include: Piola-Kirchhoff Stress
 }
-
-\todoredefined[inline]{
-TODO: Add some exaples and visualisations. What exactly is it and what role does it play in a deformation process? Hyperelastic energy, connect with paper.
-\\ To include: Piola-Kirchhoff Stress, Cauchy Green invariant, polar decomposition, cauchy green tensor
-}

### 2020-04-01 LaTeX-Master-Vorlage/chapter/paper.tex
background done, now paper

@@
     \end{tabular}
-    \caption{Quantities derived from the Deformation Gradient \textbf{F}}
+    \caption[Quantities derived from the Deformation Gradient]{Quantities derived from the Deformation Gradient \textbf{F}}
 \label{table:gradient_quantities}
@@
 
-\todoredefined[inline]{
-TODO: Check if everything is explained enough in Background.
-}
-
 \section{Energy Formulation}
-
 \subsection{Stability}
@@
 \todoredefined[inline]{
-TODO: Explain what last sentence means. Reference correct like this?
+TODO: Explain what last sentence means.
 }
@@
 \end{subfigure}
-\caption{Inversion of a tetrahedron {\cite{STREAM2018}}}
+\caption[Inversion of a tetrahedron]{Inversion of a tetrahedron {\cite{STREAM2018}}}
 \label{fig:inversion}
@@
 	\includegraphics[width=0.5\textwidth]{resources/meta_stability}
-	\caption{Illustration of meta stability {\cite{STREAM2018}}}
+	\caption[Illustration of meta stability]{Illustration of meta stability {\cite{STREAM2018}}}
 	\label{fig:meta_stability}
@@
     \end{tabular}
-    \caption{Summary of proposed energies (\cite{Smith:2018:SNF:3191713.3180491}, 12:3)}
+    \caption[Summary of proposed energies]{Summary of proposed energies (\cite{Smith:2018:SNF:3191713.3180491}, 12:3)}
 \label{table:energies}
@@
 \todoredefined[inline]{
-TODO: Not all proofs and calculations included yet. Add or leave out some if too confusing.
+TODO: Not all proofs and calculations included. Add or leave out some if too confusing.
 }
@@
     \end{subfigure}
-    \caption{Stretch test performed on a cube with (a) a hexahedral mesh and (b) a tetrahedral mesh}
+    \caption[Stretch test performed on a cube]{Stretch test performed on a cube with (a) a hexahedral mesh and (b) a tetrahedral mesh}
     \label{fig:stretchtest}

### 2020-04-04 LaTeX-Master-Vorlage/chapter/Background.tex
working on paper

@@
 \chapter{Background} \label{c:Background}
-As in the paper \textit{\acrshort{snh}}, my goal is to animate human-like characters.
+My goal is the same as in the paper \textit{\acrshort{snh}}, namely to animate human-like characters.
 More precisely, the focus is on the behaviour of the character's flesh.
 This chapter serves as an introduction into the mathematical as well as physical background, needed to understand the upcoming calculations and conclusions.
-At the beginning of this chapter I will define the notation and convention used throughout this whole thesis.
+At the beginning of this chapter, I will define the notation and convention used throughout this whole thesis.
 Next, I will give insights in the mathematics used and present some of the concepts used in continuum mechanics.
@@
 It represents the best possible approximation of a given matrix by a matrix of low rank.
-This approximation can be looked at as a compression of the data given (\cite{LiesenMehrmann2015}, S.
+This approximation can be looked at as a compression of the data given (\cite{LiesenMehrmann2015}, p.
 295).
+Firstly we need to define what singular values are.
 
@@
 
-This definition and theorem were taken from \cite{ford2014numerical} (p.113, p.300).
+This definition and theorem were taken from \textit{Numerical linear algebra with applications: Using MATLAB} (\cite{ford2014numerical}, p.113, p.300).
 
 \subsection{Polar Decomposition}
+Another theorem we will use in the next sections is the the Polar Decomposition Theorem.
 
@@
 
-This theorem was taken from \cite{Spencer1980} (p.12).
+This theorem was taken from \textit{Continuum Mechanics} in which they include the proof for $3 \times 3$ matrices (\cite{Spencer1980}, p.12).
 
@@
 
-We can imagine, that we map each particle of a chosen object from its rest state to a deformed one.
+We can imagine that we map each particle of a chosen object from its rest state to a deformed one.
 Each particle $X$ of a body can be characterized by a vector $\mathbf{x}$ containing its positional coordinates at time $t_0=0$.
@@
 \subsection{Deformation Gradient}
-The next quantity, I will use in the upcoming chapters, is the deformation gradient \textbf{F}.
+The next quantity I will use in the upcoming chapters is the deformation gradient \textbf{F}.
 With its help, we can calculate the change in volume and length of an object during a deformation.
@@
 \end{wrapfigure}
-As an example, I am taking a simple deformation in 2D. Consider the coloured area in Fig. \ref{stretch:1}. We can stretch this area in the following way:
+As an example, I am taking a simple deformation in 2D. The coloured area in Fig. \ref{stretch:1} represents an object in its rest state. We can stretch this area in the following way:
 \begin{align*}
@@
 This would be the case for rigid body displacements.
-Since we will be handling deformation in the 3D space, the deformation gradient will have the form of a $3 \times 3$ matrix:
+Since we will be handling deformation in the 3D space, the deformation gradient will have the form of a $3 \times 3$ matrix
 \begin{equation}\label{eq:deformation_gradient}
@@
 \end{equation}
-\textbf{F} can be factorized and used to calculate other quantities. The next few sections show these factorizations and calculations.
+\textbf{F} can be factorized and used to calculate other quantities. The next few sections will explain this.
 
@@
 \end{equation}
-and is a $3 \times 3$ matrix for deformations in the 3D space. Using \textbf{C}, we can calculate the first right Cauchy-Green invariant $I_C$ with
+and is a $3 \times 3$ matrix for deformations in the 3D domain. Using \textbf{C}, we can calculate the first right Cauchy-Green invariant $I_C$ with
 \begin{equation} \label{tr_CG_DG}
@@
 The area under the stress-strain curve corresponds to the strain energy.
-
 \begin{figure}[!htbp]
@@
 
-Unfortunately, this relationship is not always linear, which makes it harder to find a suitable model.
-For example if we reach a stress state that produces yielding, we cannot assume that the relationship is linear.
+This relationship is not always linear.
+For example if we reach a stress state that produces yielding, we cannot assume that the relationship is linear anymore.
 If the material reaches the yield point, it can no longer recover into its rest shape due to permanent fractures during the deformation.
@@
 The behaviour of human flesh can be put into the category of hyperelastic materials.
-One key property of elasticity is, that if all the forces that are applied over an object add up to zero, the object must come back into its rest shape.
+The key property of elasticity is, that if all the forces that are applied over an object are removed, the object recovers into its original shape and volume (\cite{KORSUNSKY20175}, p.
+5).
 
@@
 Biological tissues such as flesh, fat and muscles have one important property: Volume preservation.
-As a result the poisson's ratio takes on higher values in the range of 0.45 and 0.5 \cite{Smith:2018:SNF:3191713.3180491}.
+As a result the poisson's ratio takes on higher values in the range of 0.45 and 0.5 (\cite{Smith:2018:SNF:3191713.3180491}, 12:1).
 
@@
 With the help of these two constants we can transform Eq.
-\ref{eq:poisson} into the following form:
+\ref{eq:poisson} into the form
 
@@
 
-This equation allows to calculate the poisson's ratio much easier.
+This equation allows to calculate the poisson's ratio much easier (\cite{BERGSTROM2015209}, p. 231).
 

### 2020-04-04 LaTeX-Master-Vorlage/chapter/Introduction.tex
background
working on paper

@@
 \section{Motivation}
-With steadily increasing computational power, the demand of better results is constantly growing. Especially in the field of animation and simulation we are no longer happy with mediocre results. 
-In the entertainment sector and gaming industry animation studios like Pixar\textsuperscript{\textcopyright} or Disney\textsuperscript{\textcopyright} brought us games and movies of highest quality.
-Both of them have made groundbreaking progress over the years.
-This is easily observed when we compare today's work with that from ten years ago.
+With steadily increasing computational power, the demand of better looking results is constantly growing.
+Especially in the field of animation and simulation we are no longer happy with mediocre results.
+In the entertainment sector animation studios like Pixar\textsuperscript{\textcopyright} brought us movies of highest quality.
+They have made groundbreaking progress over the years.
+This can easily be observed when we compare today's work with that from ten years ago.
 
@@
 In the paper \textit{\acrlong{snh}} \cite{Smith:2018:SNF:3191713.3180491}, the authors addressed exactly this problem of making an animated movement of a human-like character look as natural as possible.
-Consequently this thesis is based heavily on this paper.
+Consequently, this thesis is based heavily on this paper.
 In the following, I will abbreviate the name of the paper with \textit{\acrshort{snh}}.
@@
 But before diving further into the content of the paper, a fundamental background is needed.
-In order to animate a physical movement, we first need to understand the physics behind it which requires some knowledge in the field of continuum mechanics.
+In order to animate a physical movement, we first need to understand the physics behind it.
+This requires some knowledge in the field of continuum mechanics.
 Unfortunately, for most of us it has yet to be learned.
@@
 Lastly I will give an insight into the process of implementing the energy.
-\\
-
-\todoredefined[inline]{
-TODO: Adjust according to additions in text. Maybe add other applications as well (physical simulation) and how to go over to it?
-}

### 2020-04-04 LaTeX-Master-Vorlage/chapter/paper.tex
working on paper

@@
 \section{Deformation Gradient}
-In the following calculations some properties of the deformation gradient $\mathbf{F}$ covered in chapter 2 will be used.
-These properties are summarized in table \ref{table:gradient_quantities} for a better overview:
+In the following calculations the properties of the deformation gradient $\mathbf{F}$ covered in chapter 2 will be used.
+These properties are summarized in table \ref{table:gradient_quantities} for a better overview.
 
@@
 The core goal of the paper was to model deformations for virtual characters that have human-like features.
-The focus of the authors was the deformation energy.
-In order to achieve a convincing result the first step is to specify some requirements.
-Firstly the energy has to be stable.
-More precisely, we need a hyperelastic energy that is stable in the following four important ways:
+In order to achieve better results than what has been done in current research, they formulated a new deformation energy.
+In chapter 2 I concluded that the appropriate energy for animating soft tissues as flesh has to be hyperelastic.
+An important property is the stability of the energy.
+We need an energy that is stable in the following four ways:
 

### 2020-04-05 LaTeX-Master-Vorlage/chapter/Background.tex
paper

@@
 
-\begin{theorem}[\textbf{The SVD Theorem}]
+\begin{theorem}[\textbf{The \acrshort{svd} Theorem}]
 \label{SVD}
@@
 
-Using the SVD theorem shown in Thm.\ref{SVD}, \textbf{F} can be written in the form of
+Using the \acrshort{svd} theorem shown in Thm.\ref{SVD}, \textbf{F} can be written in the form of
 
@@
 The range in which $\sigma$ lies in starts at $-1$ and goes up to $0.5$ \cite{PhysRevB.80.132104}.
+If we imagine pulling a rubber band on each of its sides, we can observe that the band gets longer and the middle part gets narrower.
+The poisson's ratio indicates the extend of this process.
+Incompressible materials such as rubber lead to a higher poisson's ratio.
+
 Usually the poisson's ratio of a material is positive.
@@
 \todoredefined[inline]{
-TODO: To include: Piola-Kirchhoff Stress
+TODO: Include Piola-Kirchhoff Stress?
 }

### 2020-04-05 LaTeX-Master-Vorlage/chapter/paper.tex
working on images
illustrations
paper

@@
     \end{tabular}
-    \caption[Quantities derived from the Deformation Gradient]{Quantities derived from the Deformation Gradient \textbf{F}}
+    \caption[Quantities derived from the Deformation Gradient]{Quantities derived from the Deformation Gradient}
 \label{table:gradient_quantities}
@@
 In order to achieve better results than what has been done in current research, they formulated a new deformation energy.
-In chapter 2 I concluded that the appropriate energy for animating soft tissues as flesh has to be hyperelastic.
+In chapter 2, I concluded that the appropriate energy for animating soft tissues such as flesh has to be hyperelastic.
 An important property is the stability of the energy.
@@
 In Fig.
-\ref{fig:inversion_3} we have an inversion of the object.
-The deformation energy has to be able to deal with both cases.
-That means that the energy has to be singularity-free and does not need any filters or threshold (\cite{Smith:2018:SNF:3191713.3180491}, 12:3).
-
-\todoredefined[inline]{
-TODO: Explain what last sentence means.
-}
+\ref{fig:inversion_3} the tetrahedron arrives at an inversed stated.
+The deformation energy has to be able to deal with both cases without creating severe artefacts.
+That means, that the energy has to be singularity-free, meaning that it is defined for every possible point.
+This should hold without needing any filters or threshold (\cite{Smith:2018:SNF:3191713.3180491}, 12:3).
 
@@
 \textbf{2.
-Reflection stability:} A reflection is a rotation around the coordinate origin.
-The deformation energy needs to be well behaved regardless of the reflection convention used in the singular value decomposition.
-\todoredefined[inline]{
-TODO: Explain a bit better what this means. What means well behaved?
-}
+Reflection stability:} While deforming an object, it can occur that we are dealing with reflections.
+An example of a reflection in 2D is shown in Fig.
+\ref{fig:reflection}.
+Here the coloured triangle is reflected over the y-axis.
+A matrix that represents a reflection is orthogonal with determinant $-1$.
+The deformation energy needs to be well behaved under reflections.
+This has to hold, regardless of the reflection convention used in the \acrshort{svd} of \textbf{F}.
+The reflection convention is explained in chapter 2.3.2 in the subsection \textit{Singular Value Decomposition of \textbf{F}}.
+
+\begin{figure}[!htbp]
+	\centering
+	\includegraphics[width=0.5\textwidth]{resources/reflection_plot.png}
+	\caption[Reflection of a triangle over the y-axis]{Reflection of a triangle over the y-axis}
+	\label{fig:reflection}
+\end{figure}
 
 \textbf{3.
-Rest stability:} When deforming an object in a certain way, we apply one or multiple forces to that object.
-When we achieve rest stability, we ensure that if the sum of all forces is equal to zero, the object must be back in its rest state.
+Rest stability:} When deforming an object in a certain way, we apply one or multiple forces to that object which influences the deformation.
+But when we remove all the forces, the object should be back in its rest state.
 
 \textbf{4.
-Meta-stability under degeneracy:} We can crush an object into an arbitrary shape like a plane, line or point.
+Meta-stability under degeneracy:} This is a special case of rest stability.
+We can crush an object into an arbitrary shape like a plane, line or point.
 This process is illustrated for a cube in Fig.
 \ref{fig:meta_stability}.
-The cube should be able to recover to its actual shape after the deformation.
+Afterwards, when the applied forces are removed, the cube should still be able to recover from this arbitrary shape to its actual shape.
 
@@
 
-Based on these four requirements, we will in the following determine if a deformation energy is suited for our needs.
+Based on these four requirements, we will determine if a deformation energy is suited for our needs.
 
 \todoredefined[inline]{
-TODO: Maybe add own images and more sources.
+TODO: Are images ok?
 }
@@
 
-In previous literature, a few energies were proposed that I will analyse in this section. They are listed in table \ref{table:energies} below.
+In previous literature, a few energies were proposed that I will analyse in this section. They are listed in table \ref{table:energies}.
 
@@
     \textbf{Energy} & \textbf{Author(s)} \\ \hline
-    $\Psi_{Neo}=\frac{\mu}{2}\left(I_{C}-3\right)-\mu \log J+\frac{\lambda}{2}(\log J)^{2}$ & e.g. Bonet and Wood 2008 \\ \hline
-    $\Psi_{\mathrm{A}}=\frac{\mu}{2}\left(I_{C}-3\right)-\mu \log J+\frac{\lambda}{2}(J-1)^{2}$ & Odgen 1997 \\ \hline
-    $\Psi_{\mathrm{B}}=\frac{\mu}{2}\left(J^{-2 / 3} I_{C}-3\right)+\frac{\lambda}{2}(J-1)^{2}$ & Bower 2009 \\ \hline
-    $\Psi_{\mathrm{C}}=\frac{\mu}{2}\left(J^{-2 / 3} I_{C}-3\right)+\frac{\lambda}{2}(J-1)^{2}$ & Wang and Yang 2016 \\ \hline
+    $\Psi_{Neo}=\frac{\mu}{2}\left(I_{C}-3\right)-\mu \log J+\frac{\lambda}{2}(\log J)^{2}$ & \begin{tabular}{@{}l@{}}e.g. Bonet and Wood 1997 \\ (\cite{bonet1997nonlinear})\end{tabular}  \\ \hline
+    $\Psi_{\mathrm{A}}=\frac{\mu}{2}\left(I_{C}-3\right)-\mu \log J+\frac{\lambda}{2}(J-1)^{2}$ & Odgen 1997 (\cite{ogden1997non}) \\ \hline
+    $\Psi_{\mathrm{B}}=\frac{\mu}{2}\left(J^{-2 / 3} I_{C}-3\right)+\frac{\lambda}{2}(J-1)^{2}$ & Bower 2009 (\cite{bower2009applied}) \\ \hline
+    $\Psi_{\mathrm{C}}=\frac{\mu}{2}\left(J^{-2 / 3} I_{C}-3\right)+\frac{\lambda}{2}(J-1)^{2}$ & \begin{tabular}{@{}l@{}}Wang and Yang 2016 \\ (\cite{wang2016descent}) \end{tabular} \\ \hline
     \end{tabular}
@@
 \]
-This energy reaches its minimum at a zero volume state, meaning $I_{C}=0$ which results in $\Psi_{M}=-3$.
-Mooney added the hard constraint that $J=1$, so that the energy is minimized at the volume preserving configuration that is closest to the stretch space origin.
+This energy reaches its minimum at a zero volume state, meaning $I_{C}=0$.
+Mooney added the hard constraint that $J$ should be equal to $1$, so that the energy is minimized at the volume preserving configuration that is closest to the stretch space origin.
 Note that the energy is singularity free and well defined under inversion.
 
-The second term 
+The second term is
 \[
@@
 \]
-is used in $\Psi_{B}$ and $\Psi_{C}$ and was introduced by Rivlin (\cite{rivlin1948large}). Using the singular values of \textbf{F}, we get the following term:
+and used in $\Psi_{B}$ and $\Psi_{C}$ and was introduced by Rivlin (\cite{rivlin1948large}). Using the singular values of \textbf{F}, we get the following term:
 \[
@@
 \]
-Unfortunately this term is not singularity free. If either $\sigma_{0}$, $\sigma_{1}$ or $\sigma_{2}$ is equal to zero the result is not defined anymore.
+Unfortunately, this term is not singularity free. If either $\sigma_{0}$, $\sigma_{1}$ or $\sigma_{2}$ is equal to zero the result is not defined anymore.
 
@@
 \]
-results in some numerical problems since the logarithmic function is not defined for $J<0$ and grows unbounded for $J \rightarrow 0$. In conclusion $\Psi_{Neo, volume}$ is not singularity free. 
+results in numerical problems, since the logarithmic function is not defined for $J<0$ and grows unbounded for $J \rightarrow 0$. In conclusion, $\Psi_{Neo, volume}$ is not singularity free. 
 The same applies for the 3D volume term of $\Psi_{A}$, namely
@@
 \]
-does not have these problems. It is bounded, well defined and invertible. After these observations we combine the robust length with the robust volume term and receive $\Psi_D$ that is defined as
+does not have these problems. It is bounded, well defined and invertible. After these observations we combine the robust length with the robust volume term and receive $\Psi_D$, which is defined as
 \[
-\Psi_{D} = \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-1)^{2}
+\Psi_{D} = \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-1)^{2}.
 \]
-and is singularity free and well defined under inversion. Unfortunately, $\Psi_D$ does not satisfy the requirement of being rest stable which will be discussed in the next section.
+$\Psi_{D}$ is singularity free and well defined under inversion. Unfortunately, it does not satisfy the requirement of being rest stable which will be discussed in the next section.
 
 \todoredefined[inline]{
-TODO: Bonet and Wood 2008 or 1997?
+TODO: explain how to get to equation with singular values
 }
@@
 Although $\Psi_{D}$ meets almost all stated requirements, it is not rest stable.
-This can be shown with the Piola-Kirchhoff (PK1) stress tensor for $\Psi_D$ derived by the deformation gradient \textbf{F}:
+This can be shown with the first Piola-Kirchhoff (PK1) stress tensor, defined as $\Psi_D$ derived by the deformation gradient \textbf{F}:
 \begin{align*}
@@
 Unfortunately, this is not the case here.
-In order to solve that problem, the authors modified $(J-1)^{2}$ to $(J-\alpha)^{2}$.
-Using this modification the energy can written as
+In order to solve this problem, the authors modified $(J-1)^{2}$ to $(J-\alpha)^{2}$.
+Using this modification, the energy can written as
 \[
@@
 \end{align*}
-Since constants disappear under differentiation this expression is functionally equivalent to 
+Since constants disappear under differentiation, this expression is functionally equivalent to 
 \[
@@
 \]
-Now we can see that $\Psi_{E}$ looks very similar to $\Psi_{Neo}$.
+Note that $\Psi_{E}$ looks very similar to $\Psi_{Neo}$.
 The difference is that $log(J)$ is replaced with $(J-1)$ in $\Psi_{E}$.
@@
 \todoredefined[inline]{
-TODO: Add "Zwischenschritte"?
-Include all calculations?
-Do we need a bit of a better conclusion of what we did (taylor, neo, sing.
-free, rest stable)?
-Check consistency of calculations (when trace when $I_C$ etc.).
+TODO: Include all calculations? Check consistency of calculations (when trace when $I_C$ etc.).
 }
@@
 \section{Energy Analysis}
-The goal of this chapter is to show that a complete eigenanalysis can be performed on Eq. \ref{eq:stable_energy}.
+The goal of this chapter is to show that a complete eigenanalysis can be performed on Eq. \ref{eq:stable_energy}. This helps us understand the properties and limitations of the new energy.
 
 \subsection{First Piola-Kirchhoff Stress (PK1)}
-In order to analyse the energy PK1 can be used for Eq. \ref{eq:stable_energy}:
+In order to analyse the energy PK1 can be used for Eq. \ref{eq:stable_energy} with $\alpha=1+\frac{\mu}{\lambda}-\left(\frac{\mu}{4}\right)\lambda$:
 \begin{align*}
@@
 
-with $\alpha=1+\frac{\mu}{\lambda}-\left(\frac{\mu}{4}\right)\lambda$. For further use it can be more practical to write $\frac{\partial J}{\partial \mathbf{F}}$ as a result of cross products:
+For further use it can be more practical to write $\frac{\partial J}{\partial \mathbf{F}}$ as a result of cross products:
 \begin{equation}\label{eq:cross_product}
@@
 \todoredefined[inline]{
-TODO: Is it easy to follow? Maybe add some explanations of some steps? Maybe move cross product into background instead of here.
+TODO: Is it easy to follow? Maybe add some explanations of some steps?
 }
@@
 
-in which each entry is defined as
+Each entry of the Hessian is defined as
 \[
@@
 \subsubsection{Tikhonov}
-The Tikhonov term is a fourth-order matrix-of-matrices
+The Tikhonov term is a fourth-order matrix-of-matrices. It is calculated by $\frac{\partial \mathbf{F}}{\partial f_i}$ and takes on the form
 \[
-\mathbb{T} = \frac{\partial \mathbf{F}}{\partial f_i} = \left[\begin{array}{ccc}{\begin{bmatrix} 1 & 0 & 0 \\ 0 & 0 & 0 \\ 0 & 0 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 1 & 0 \\ 0 & 0 & 0 \\ 0 & 0 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 0 & 1 \\ 0 & 0 & 0 \\ 0 & 0 & 0 \end{bmatrix}} \\ {\begin{bmatrix} 0 & 0 & 0 \\ 1 & 0 & 0 \\ 0 & 0 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 0 & 0 \\ 0 & 1 & 0 \\ 0 & 0 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 0 & 0 \\ 0 & 0 & 1 \\ 0 & 0 & 0 \end{bmatrix}} \\ {\begin{bmatrix} 0 & 0 & 0 \\ 0 & 0 & 0 \\ 1 & 0 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 0 & 0 \\ 0 & 0 & 0 \\ 0 & 1 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 0 & 0 \\ 0 & 0 & 0 \\ 0 & 0 & 1 \end{bmatrix}} \end{array}\right].
+\mathbb{T} = \left[\begin{array}{ccc}{\begin{bmatrix} 1 & 0 & 0 \\ 0 & 0 & 0 \\ 0 & 0 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 1 & 0 \\ 0 & 0 & 0 \\ 0 & 0 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 0 & 1 \\ 0 & 0 & 0 \\ 0 & 0 & 0 \end{bmatrix}} \\ {\begin{bmatrix} 0 & 0 & 0 \\ 1 & 0 & 0 \\ 0 & 0 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 0 & 0 \\ 0 & 1 & 0 \\ 0 & 0 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 0 & 0 \\ 0 & 0 & 1 \\ 0 & 0 & 0 \end{bmatrix}} \\ {\begin{bmatrix} 0 & 0 & 0 \\ 0 & 0 & 0 \\ 1 & 0 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 0 & 0 \\ 0 & 0 & 0 \\ 0 & 1 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 0 & 0 \\ 0 & 0 & 0 \\ 0 & 0 & 1 \end{bmatrix}} \end{array}\right].
 \]
-If we vectorize $\mathbb{T}$, we get the identity matrix $\mathbf{I} \in \mathbb{R}^{9x9}$ which is of full rank, positive definite and independent of the values in \textbf{F}. 
+If we vectorize $\mathbb{T}$, we get the identity matrix $\mathbf{I} \in \mathbb{R}^{9x9}$ which is of full rank, positive definite and independent of the values in \textbf{F}: 
 \[
-\operatorname{vec}(\mathbb{T}) =  \mathbf{\check{T}} = \mathbf{I} = \in \mathbb{R}^{9x9}.
+\operatorname{vec}(\mathbb{T}) =  \mathbf{\check{T}} = \mathbf{I} = \in \mathbb{R}^{9x9}
 \]
-It serves as a regularizer for the rest of the energy.
+The Tikhonov term serves as a regularizer for the rest of the energy.
 
 \subsubsection{Mu}
-The Mu term has the same structure with different entries
+The Mu term has the same structure with different entries. It can be obtained by $\mathbf{F} f_i$ and has the form
 \[
-\mathbb{M} = \mathbf{F} f_i = \left[\begin{array}{ccc}{\begin{bmatrix} f_0^2 & f_0f_3 & f_0f_6 \\ f_0f_1 & f_0f_4 & f_0f_7 \\ f_0f_2 & f_0f_5 & f_0f_8 \end{bmatrix}} & {\begin{bmatrix} f_3f_0 & f_3^2 & f_3f_6 \\ f_3f_1 & f_3f_4 & f_3f_7 \\ f_3f_2 & f_3f_5 & f_3f_8 \end{bmatrix}} & {\begin{bmatrix} f_6f_0 & f_6f_3 & f_6f_6 \\ f_6f_1 & f_6f_4 & f_6f_7 \\ f_6f_2 & f_6f_5 & f_6f_8 \end{bmatrix}} \\ {\begin{bmatrix} f_1f_0 & f_1f_3 & f_1f_6 \\ f_1^2 & f_1f_4 & f_1f_7 \\ f_1f_2 & f_1f_5 & f_1f_8 \end{bmatrix}} & {\begin{bmatrix} f_4f_0 & f_4f_3 & f_4f_6 \\ f_4f_1 & f_4^2 & f_4f_7 \\ f_4f_2 & f_4f_5 & f_4f_8 \end{bmatrix}} & {\begin{bmatrix} f_7f_0 & f_7f_3 & f_7f_6 \\ f_7f_1 & f_7f_4 & f_7^2 \\ f_7f_2 & f_7f_5 & f_7f_8 \end{bmatrix}} \\ {\begin{bmatrix} f_2f_0 & f_2f_3 & f_2f_6 \\ f_2f_1 & f_2f_4 & f_2f_7 \\ f_2^2 & f_2f_5 & f_2f_8 \end{bmatrix}} & {\begin{bmatrix} f_5f_0 & f_5f_3 & f_5f_6 \\ f_5f_1 & f_5f_4 & f_5f_7 \\ f_5f_2 & f_5^2 & f_5f_8 \end{bmatrix}} & {\begin{bmatrix} f_8f_0 & f_8f_3 & f_8f_6 \\ f_8f_1 & f_8f_4 & f_8f_7 \\ f_8f_2 & f_8f_5 & f_8^2 \end{bmatrix}} \end{array}\right].
+\mathbb{M} = \left[\begin{array}{ccc}{\begin{bmatrix} f_0^2 & f_0f_3 & f_0f_6 \\ f_0f_1 & f_0f_4 & f_0f_7 \\ f_0f_2 & f_0f_5 & f_0f_8 \end{bmatrix}} & {\begin{bmatrix} f_3f_0 & f_3^2 & f_3f_6 \\ f_3f_1 & f_3f_4 & f_3f_7 \\ f_3f_2 & f_3f_5 & f_3f_8 \end{bmatrix}} & {\begin{bmatrix} f_6f_0 & f_6f_3 & f_6f_6 \\ f_6f_1 & f_6f_4 & f_6f_7 \\ f_6f_2 & f_6f_5 & f_6f_8 \end{bmatrix}} \\ {\begin{bmatrix} f_1f_0 & f_1f_3 & f_1f_6 \\ f_1^2 & f_1f_4 & f_1f_7 \\ f_1f_2 & f_1f_5 & f_1f_8 \end{bmatrix}} & {\begin{bmatrix} f_4f_0 & f_4f_3 & f_4f_6 \\ f_4f_1 & f_4^2 & f_4f_7 \\ f_4f_2 & f_4f_5 & f_4f_8 \end{bmatrix}} & {\begin{bmatrix} f_7f_0 & f_7f_3 & f_7f_6 \\ f_7f_1 & f_7f_4 & f_7^2 \\ f_7f_2 & f_7f_5 & f_7f_8 \end{bmatrix}} \\ {\begin{bmatrix} f_2f_0 & f_2f_3 & f_2f_6 \\ f_2f_1 & f_2f_4 & f_2f_7 \\ f_2^2 & f_2f_5 & f_2f_8 \end{bmatrix}} & {\begin{bmatrix} f_5f_0 & f_5f_3 & f_5f_6 \\ f_5f_1 & f_5f_4 & f_5f_7 \\ f_5f_2 & f_5^2 & f_5f_8 \end{bmatrix}} & {\begin{bmatrix} f_8f_0 & f_8f_3 & f_8f_6 \\ f_8f_1 & f_8f_4 & f_8f_7 \\ f_8f_2 & f_8f_5 & f_8^2 \end{bmatrix}} \end{array}\right].
 \]
-When vectorizing $\mathbb{M}$, the resulting matrix $\mathbf{\check{M}}$ has the squared values of $f_i$ placed on the diagonal
+When vectorizing $\mathbb{M}$, the resulting matrix $\mathbf{\check{M}}$ has the squared values of $f_i$ placed on the diagonal:
 \[
-\operatorname{vec}(\mathbb{M})= \mathbf{\check{M}} = \begin{bmatrix} f_0^2 & f_1f_0 & f_2f_0 & f_3f_0 & f_4f_0 & f_5f_0 & f_6f_0 & f_7f_0 & f_8f_0 \\ f_0f_1 & f_1^2 & f_2f_1 & f_3f_1 & f_4f_1 & f_5f_1 & f_6f_1 & f_7f_1 & f_8f_1 \\ f_0f_2 & f_1f_2 & f_2^2 & f_3f_2 & f_4f_2 & f_5f_2 & f_6f_2 & f_7f_2 & f_8f_2 \\ f_0f_3 & f_1f_3 & f_2f_3 & f_3^2 & f_4f_3 & f_5f_3 & f_6f_3 & f_7f_3 & f_8f_3 \\ f_0f_4 & f_1f_4 & f_2f_4 & f_3f_4 & f_4^2 & f_5f_4 & f_6f_4 & f_7f_4 & f_8f_4 \\ f_0f_5 & f_1f_5 & f_2f_5 & f_3f_5 & f_4f_5 & f_5^2 & f_6f_5 & f_7f_5 & f_8f_5 \\ f_0f_6 & f_1f_6 & f_2f_6 & f_3f_6 & f_4f_6 & f_5f_6 & f_6^2 & f_7f_6 & f_8f_6 \\ f_0f_7 & f_1f_7 & f_2f_7 & f_3f_7 & f_4f_7 & f_5f_7 & f_6f_7 & f_7^2 & f_8f_7 \\ f_0f_8 & f_1f_8 & f_2f_8 & f_3f_8 & f_4f_8 & f_5f_8 & f_6f_8 & f_7f_8 & f_8^2 \end{bmatrix}.
+\operatorname{vec}(\mathbb{M})= \mathbf{\check{M}} = \begin{bmatrix} f_0^2 & f_1f_0 & f_2f_0 & f_3f_0 & f_4f_0 & f_5f_0 & f_6f_0 & f_7f_0 & f_8f_0 \\ f_0f_1 & f_1^2 & f_2f_1 & f_3f_1 & f_4f_1 & f_5f_1 & f_6f_1 & f_7f_1 & f_8f_1 \\ f_0f_2 & f_1f_2 & f_2^2 & f_3f_2 & f_4f_2 & f_5f_2 & f_6f_2 & f_7f_2 & f_8f_2 \\ f_0f_3 & f_1f_3 & f_2f_3 & f_3^2 & f_4f_3 & f_5f_3 & f_6f_3 & f_7f_3 & f_8f_3 \\ f_0f_4 & f_1f_4 & f_2f_4 & f_3f_4 & f_4^2 & f_5f_4 & f_6f_4 & f_7f_4 & f_8f_4 \\ f_0f_5 & f_1f_5 & f_2f_5 & f_3f_5 & f_4f_5 & f_5^2 & f_6f_5 & f_7f_5 & f_8f_5 \\ f_0f_6 & f_1f_6 & f_2f_6 & f_3f_6 & f_4f_6 & f_5f_6 & f_6^2 & f_7f_6 & f_8f_6 \\ f_0f_7 & f_1f_7 & f_2f_7 & f_3f_7 & f_4f_7 & f_5f_7 & f_6f_7 & f_7^2 & f_8f_7 \\ f_0f_8 & f_1f_8 & f_2f_8 & f_3f_8 & f_4f_8 & f_5f_8 & f_6f_8 & f_7f_8 & f_8^2 \end{bmatrix}
 \]
-This structure makes it possible to write $\mathbf{\check{M}}$ as an outer product of $\operatorname{vec}(\mathbf{F})$
+This structure makes it possible to write $\mathbf{\check{M}}$ as an outer product of $\operatorname{vec}(\mathbf{F})$:
 \[
-\mathbf{\check{M}}= \operatorname{vec}(\mathbf{F})\operatorname{vec}(\mathbf{F})^\intercal = \mathbf{\check{f}} \mathbf{\check{f}}^\intercal.
+\mathbf{\check{M}}= \operatorname{vec}(\mathbf{F})\operatorname{vec}(\mathbf{F})^\intercal = \mathbf{\check{f}} \mathbf{\check{f}}^\intercal
 \]
@@
 in which $\|\cdot\|_F$ stands for the Frobenius norm introduced in Def.
-\ref{FN} and $\sigma_i$ for the singular values from $\mathbf{\Sigma}$ in the SVD of $\mathbf{F}$ stated in Eq.
+\ref{FN} and $\sigma_i$ for the singular values from $\mathbf{\Sigma}$ in the \acrshort{svd} of $\mathbf{F}$ stated in Eq.
 \ref{eq:svd_simga}.
 The equation can be obtained by using Eq.
-\ref{eq:FN}.
+\ref{eq:FN}, explained in chapter 2.
 The eigenvector is $\mathbf{\check{f}} / \| \mathbf{\check{f}} \|$.
@@
 \subsection{The Volume Hessian}
-The volume Hessian term is of the form
+To make an analysis of the volume Hessian term is a bit trickier. It is of the form
 \[
@@
 \mathbf{\check{H}} = \left[ \begin{matrix}
-0 & -\mathbf{\widehat{f_2}} & \mathbf{\widehat{f_1}} \\ \mathbf{\widehat{f_2}} & 0 & -\mathbf{\widehat{f_0}} \\ -\mathbf{\widehat{f_1}} & \mathbf{\widehat{f_0}} & 0 \end{matrix} \right]
+0 & -\mathbf{\widehat{f_2}} & \mathbf{\widehat{f_1}} \\ \mathbf{\widehat{f_2}} & 0 & -\mathbf{\widehat{f_0}} \\ -\mathbf{\widehat{f_1}} & \mathbf{\widehat{f_0}} & 0 \end{matrix} \right].
 \]
-where $\mathbf{\widehat{f_1}}$ stands for a cross-product matrix:
+In this form, $\mathbf{\widehat{f_1}}$ stands for the cross-product matrix
 \[
@@
 \todoredefined[inline]{
-TODO: Check each $f_1$ and $-$ in vectorization of H because it's exhausting.
+TODO: Check again each $f_1$ and $-$ in vectorization of H.
 }
@@
 \epsilon_4 &= \sigma_1 & \epsilon_7 &= -\sigma_1 \\
-\epsilon_5 &= \sigma_2 & \epsilon_8 &= -\sigma_2.
+\epsilon_5 &= \sigma_2 & \epsilon_8 &= -\sigma_2
 \end{align*}
@@
 These are all of the eigenvalues of $\mathbf{\check{H}}$.
-We know that three of the six eigenvalues ($\epsilon_3$, ...
-$\epsilon_8$) have to negative or equal to zero since we take the positive and negative roots.
+We know that three of the six eigenvalues ($\epsilon_3$, ..., $\epsilon_8$) have to be negative or equal to zero since the root function yields a positive and a negative value.
 In addition, the cosine function for calculating $\epsilon_0$, $\epsilon_1$ and $\epsilon_2$ ensures that one or two of these eigenvalues are also negative.
 As we have seen in the previous sections, the other terms of $\frac{\partial^2 \psi}{\partial \mathbf{F}^2}$ all only have nonnegative eigenvalues.
-So the volume Hessian is the only possible source of negative eigenvalues (\cite{Smith:2018:SNF:3191713.3180491}, 12:6).
+Thus, the volume Hessian is the only possible source of negative eigenvalues (\cite{Smith:2018:SNF:3191713.3180491}, 12:6).
 
-In order to investigate the behaviour of the volume Hessian term further, let us look at J = det(\textbf{F}) a bit more in detail.
-J is not convex which is problematic since we want to use the Newton method for the optimization process.
-Fortunately, the other terms of $\frac{\partial^2 \psi}{\partial \mathbf{F}^2}$ serve as an additional regularization.
+In order to investigate the behaviour of the volume Hessian term further, let us look at $J = \operatorname{det}(\mathbf{F})$ a bit more in detail.
+$J$ is not convex which is problematic, because we will use the Newton method for the optimization process.
+In order for the Newton method to work correctly, it needs a convex function.
+Fortunately, the other terms of $\frac{\partial^2 \psi}{\partial \mathbf{F}^2}$ serve as an additional regularization as already stated for the Tikhonov term.
 
 \todoredefined[inline]{
-TODO: include reflection convention? check with background. Regularisation?
+TODO: Regularisation?
 }
@@
 
-\todoredefined[inline]{
-TODO: Eigenvalues of Mu and Gradient term better explain?
-}
+\section{Experiments with the Code}
+The authors of the paper \textit{\acrshort{snh}} provided the implementation for an application of their formulated energy\footnote{http://graphics.pixar.com/library/StableElasticity/snh\_code.tar.bz2}.
+The code performs a stretch test on a cube with either a tetrahedral or hexahedral mesh.
+Their implementation demands a string for defining the directory into which the output files should be saved, a value for each of the two lamé parameters $\mu$ and $\lambda$ and a value for defining the desired resolution as input data.
 
-\section{Experiments with the Code}
-The authors of the paper \textit{\acrshort{snh}} provided the implementation for an application of their formulated energy.
-In said code, they implemented the stretch test on a cube.
-Their implementation demands a directory into which the output files should be saved, the two lamé parameters $\mu$ and $\lambda$ and a value for defining the desired resolution as input data.
-Here is an example for a command with resolution = 10, $\mu=1.0$, $\lambda=10.0$ and output directory \textit{output}:
-\begin{lstlisting}[language=bash]
-$ ./tetcli 10 stable_neo_hookean 1.0 10.0 output
-\end{lstlisting}
-
-The algorithm progressively calculates the deformation in 25 steps. The outputs are 26 static objects that show the object in its rest state and the 25 steps of deformation.
+The algorithm progressively calculates the deformation in 25 steps.
+The outputs are 26 static objects in the format .obj that firstly show the object in its rest state and then illustrate the 25 steps of deformation.
 
@@
 
-\todoredefined[inline]{
-TODO: Explain how the code is implemented in simple words and how the energy is taken in account with the poisson's ratio. Do I have to reference code? Explain tetcli and Hexcli.
+\subsection{Example}
+
+I will explain how the implementation works based on an example.
+For this I am taking the input variables $\mu = 1.0$, $\lambda = 10.0$ and a resolution of $10.0$.
+Thus, for the poisson's ratio we get the value
+
+\[ \sigma =  \frac{10.0}{2 (10.0 + 1.0)} = 0.4545. \]
+
+The command to start the execution for a tetrahedral mesh with these input variables is shown in code snippet \ref{lst:bashCommand}.
+\newline
+\begin{lstlisting}[language=bash, numbers=none, label=lst:bashCommand, caption=Bash command for executing the code, captionpos=b]
+$ ./tetcli 10 stable_neo_hookean 1.0 10.0 output
+\end{lstlisting}
+
+The code then creates a cube with $10$ edges (corresponds to the chosen resolution) and $11$ vertices (calculated by resolution + $1$) on each side.
+The cube therefore consists of $1'331$ vertices in total.
+The amount of hexahedra respectively tetrahedra are calculated by
+\begin{align*}
+	&\text{Tet count} = 6 * 10 * 10 * 10 = 6'000 \\
+	&\text{Cube count} = 10 * 10 * 10 = 1'000.
+\end{align*}
+Afterwards the simulation with the $25$ steps of the deformation starts.
+The stretching is done by modifying the y-value of the vertices.
+The cube is stretched by pulling its two faces in the y-axis further away from each other.
+This is done by updating the y-value of a vertex with a new value \textit{newNegativeBoundary} or \textit{newPositiveBoundary} depending on whether the vertex should move in the positive or negative direction of the y-axis.
+The definition of these two values is shown in code snippet \ref{lst:newBoundary}.
+The variable \verb|stepDelta| is equal to $0.1$.
+It is not a fixed value but modifying it which would influence the extend of the deformation.
+The variable \verb|stepNum| is the value of the current step from the $25$ we are in right now.
+\newline
+\begin{lstlisting}[language=C++, numbers=none, label=lst:newBoundary, caption=Updating y-coordinates of vertices, captionpos=b]
+const double newNegativeBoundary = -1.0 - stepNum * stepDelta;
+const double newPositiveBoundary = 1.0 + stepNum * stepDelta;
+\end{lstlisting}
+
+After the new positions are declared, the \verb|TetNewtonSolver| respectively \verb|CubeNewtonSolver| are used to minimize the strain energy over the meshes.
+The final mesh is then saved in an .obj file in the directory \textit{output}.
+
+Table \ref{table:default_tet} and \ref{table:default_hex} show, how many Newton iteration had to be done for solving the system.
+The amount of iterations increase with increasing step size.
+This is not surprising, since the deformation is increased with each step resulting in more complex calculations.
+
+\begin{table}[!htbp]
+\parbox{.45\linewidth}{
+\centering
+\begin{tabular}{ | l | l |}
+\hline
+\textbf{Step size} & \textbf{Iterations} \\ \hline
+1-10 & 2 \\ \hline
+11-21 & 3 \\ \hline
+22-25 & 4 \\ \hline
+\end{tabular}
+\caption{Newton iterations for a tetrahedral mesh}
+\label{table:default_tet}
 }
+\hfill
+\parbox{.45\linewidth}{
+\centering
+\begin{tabular}{ | l | l |}
+\hline
+\textbf{Step size} & \textbf{Iterations} \\ \hline
+1-7 & 3 \\ \hline
+8-14 & 4 \\ \hline
+15-18 & 5 \\ \hline
+19-22 & 6 \\ \hline
+23-25 & 7 \\ \hline
+\end{tabular}
+\caption{Newton iterations for a hexahedral mesh}
+\label{table:default_hex}
+}
+\end{table}
 
-For starters let us take common values for $\mu$ and $\lambda$. We first start with $\mu = 1.0$, $\lambda = 10.0$ and a resolution of 10.0. For the poisson's ratio we get the value $0.4545$:
-
-\[ \sigma =  \frac{10.0}{2 (10.0 + 1.0)} = 0.4545 \]
-
-The images in Fig. \ref{fig:stretchtest} show the stretch test with $\mu = 1.0$, $\lambda = 10.0$ and a resolution of 10.0 on a tetrahedral and a hexahedral mesh.
+The images in Fig.
+\ref{fig:stretchtest} show four of the resulting objects of this example.
+They show step $0$ (initial cube), $8$, $16$ and $24$ for a tetrahedral and hexahedral mesh.
+The result is very good, no artefacts can be seen.
+There is no obvious difference recognizable whether we took a hexahedral or a tetrahedral mesh.
+The snapshots are taken with the help of the software OpenFlipper\footnote{https://www.graphics.rwth-aachen.de/software/openflipper/}.
 
@@
         \centering
-        \includegraphics[width=0.24\textwidth]{resources/hexcli_step0.png}
+        \includegraphics[width=0.24\textwidth]{resources/hexcli_00.png}
         \hfill
-        \includegraphics[width=0.24\textwidth]{resources/hexcli_step8.png}
+        \includegraphics[width=0.24\textwidth]{resources/hexcli_08.png}
         \hfill
-        \includegraphics[width=0.24\textwidth]{resources/hexcli_step16.png}
+        \includegraphics[width=0.24\textwidth]{resources/hexcli_16.png}
         \hfill
-        \includegraphics[width=0.24\textwidth]{resources/hexcli_step24.png}
+        \includegraphics[width=0.24\textwidth]{resources/hexcli_24.png}
         \caption{Stretch test on a hexahedral mesh}
@@
         \centering
-        \includegraphics[width=0.24\textwidth]{resources/tetcli_step0.png}
+        \includegraphics[width=0.24\textwidth]{resources/tetcli_00.png}
         \hfill
-        \includegraphics[width=0.24\textwidth]{resources/tetcli_step8.png}
+        \includegraphics[width=0.24\textwidth]{resources/tetcli_08.png}
         \hfill
-        \includegraphics[width=0.24\textwidth]{resources/tetcli_step16.png}
+        \includegraphics[width=0.24\textwidth]{resources/tetcli_16.png}
         \hfill
-        \includegraphics[width=0.24\textwidth]{resources/tetcli_step24.png}
+        \includegraphics[width=0.24\textwidth]{resources/tetcli_24.png}
         \caption{Stretch test on a tetrahedral mesh}
@@
 
-\todoredefined[inline]{
-TODO: Load into OpenFlipper and screenshot results. Include remaining examples (diff. lamé param. and changes in method) and what went right and what went wrong.
+\subsection{Comparison of different input variables}
+For examining the influence of the input variable, I experimented with different values.
+The importance of the resolution is straight forward.
+For a higher resolution, the cube consists of more vertices and edges.
+This results in smoother results but also a longer runtime.
+If we choose a resolution of $30$, the cube consists of $29'791$ vertices and $162'000$ tetrahedra respectively $27'000$ hexahedra.
+Table \ref{table:res_tet} and \ref{table:res_hex} show the completed Newton iterations.
+The amount of iterations is slightly more than in the example in section 3.4.1.
+
+\begin{table}[!htbp]
+\parbox{.45\linewidth}{
+\centering
+\begin{tabular}{ | l | l |}
+\hline
+\textbf{Step size} & \textbf{Iterations} \\ \hline
+1-7 & 2 \\ \hline
+8-13 & 3 \\ \hline
+14-20 & 4 \\ \hline
+21-25 & 5 \\ \hline
+\end{tabular}
+\caption{Newton iterations for a tetrahedral mesh (res=30)}
+\label{table:res_tet}
 }
+\hfill
+\parbox{.45\linewidth}{
+\centering
+\begin{tabular}{ | l | l |}
+\hline
+\textbf{Step size} & \textbf{Iterations} \\ \hline
+1-4 & 3 \\ \hline
+5-10 & 4 \\ \hline
+11-15 & 5 \\ \hline
+16-19 & 6 \\ \hline
+20-23 & 7 \\ \hline
+24-25 & 8 \\ \hline
+\end{tabular}
+\caption{Newton iterations for a hexahedral mesh (res=30)}
+\label{table:res_hex}
+}
+\end{table}
+
+In addition, we can increase or decrease \textit{\mu} and \textit{\lambda} which changes the poisson's ratio.
+If we decrease \textit{\lambda}, the poisson's ratio also decreases.
+We can set \textit{\lambda} equal to $1.0$ and let the other variables stay the same as in the first example (\textit{\mu} $= 1.0$, resolution $= 10.0$).
+With these inputs the cube gets wider in the middle part, as the poisson's ratio indicated that the material is more resistant to the stretching.
+
+\newpage
 
@@
 Stuff, Taylor approx.
+
+\todoredefined[inline]{
+TODO: Include remaining examples (diff. lamé param. and changes in method) and what went right and what went wrong. \\
+Include other examples with Newton iterations?
+}

### 2020-04-05 LaTeX-Master-Vorlage/chapter/paper.tex
experiments

@@
 There is no obvious difference recognizable whether we took a hexahedral or a tetrahedral mesh.
-The snapshots are taken with the help of the software OpenFlipper\footnote{https://www.graphics.rwth-aachen.de/software/openflipper/}.
+All snapshots in this chapter are taken with the help of the software OpenFlipper\footnote{https://www.graphics.rwth-aachen.de/software/openflipper/}.
 
@@
 
+Fig.
+\ref{fig:res} shows the results with a higher resolution of $30$ compared to a lower resolution of $10$.
+All other input variables are the same.
+The figure shows the results of the deformation step $25$.
+We can see that a higher resolution clearly gives us much nicer results.
+
+\begin{figure}[!ht]
+\centering
+\begin{subfigure}{.47\textwidth}
+  \centering
+  % include first image
+  \includegraphics[width=.8\linewidth]{resources/default_zoom_tet.png}  
+  \caption{Resolution of 10}
+  \label{fig:res_1}
+\end{subfigure}
+\begin{subfigure}{.47\textwidth}
+  \centering
+  % include second image
+  \includegraphics[width=.8\linewidth]{resources/res_zoom_tet.png}  
+  \caption{Resolution of 30}
+  \label{fig:res_2}
+\end{subfigure}
+\caption{Results with a different resolution on a tetrahedral mesh}
+\label{fig:res}
+\end{figure}
+
 In addition, we can increase or decrease \textit{\mu} and \textit{\lambda} which changes the poisson's ratio.

### 2020-04-06 LaTeX-Master-Vorlage/chapter/paper.tex

@@
 \section{Experiments with the Code}
-The authors of the paper \textit{\acrshort{snh}} provided the implementation for an application of their formulated energy\footnote{http://graphics.pixar.com/library/StableElasticity/snh\_code.tar.bz2}.
+The authors of the paper \textit{\acrshort{snh}} provided the implementation for an application of their formulated energy in C++\footnote{http://graphics.pixar.com/library/StableElasticity/snh\_code.tar.bz2}.
 The code performs a stretch test on a cube with either a tetrahedral or hexahedral mesh.
@@
 The algorithm progressively calculates the deformation in 25 steps.
-The outputs are 26 static objects in the format .obj that firstly show the object in its rest state and then illustrate the 25 steps of deformation.
+The outputs are 26 static objects in the format .obj that show the object in its rest state and then illustrate the 25 steps of deformation.
 
@@
 Afterwards the simulation with the $25$ steps of the deformation starts.
-The stretching is done by modifying the y-value of the vertices.
-The cube is stretched by pulling its two faces in the y-axis further away from each other.
-This is done by updating the y-value of a vertex with a new value \textit{newNegativeBoundary} or \textit{newPositiveBoundary} depending on whether the vertex should move in the positive or negative direction of the y-axis.
+The code sets two faces of the cube as a boundary condition.
+The stretching is done by modifying these two boundaries further away from each other in the y-axis.
+This is done by updating the y-value of the vertices with a new value \verb|newNegativeBoundary| or \verb|newPositiveBoundary| depending on whether the vertex should move in the positive or negative direction of the y-axis.
 The definition of these two values is shown in code snippet \ref{lst:newBoundary}.
@@
 The variable \verb|stepNum| is the value of the current step from the $25$ we are in right now.
+The position of the remaining vertices are then kinematically scripted.
 \newline
@@
 They show step $0$ (initial cube), $8$, $16$ and $24$ for a tetrahedral and hexahedral mesh.
-The result is very good, no artefacts can be seen.
+The result is good, no artefacts can be seen.
 There is no obvious difference recognizable whether we took a hexahedral or a tetrahedral mesh.
@@
 If we decrease \textit{\lambda}, the poisson's ratio also decreases.
-We can set \textit{\lambda} equal to $1.0$ and let the other variables stay the same as in the first example (\textit{\mu} $= 1.0$, resolution $= 10.0$).
+We can set \textit{\lambda} equal to $1.0$ and let the other variables stay the same as in the last example (\textit{\mu} $= 1.0$, resolution $= 30.0$).
 With these inputs the cube gets wider in the middle part, as the poisson's ratio indicated that the material is more resistant to the stretching.

### 2020-04-06 LaTeX-Master-Vorlage/chapter/paper.tex
paper

@@
 &= \frac{\partial \Psi_{D}}{\partial \mathbf{F}}  \frac{\mu}{2}\left(\operatorname{tr}(\mathbf{I}^\intercal \mathbf{I})-3\right) +\frac{\partial \Psi_{D}}{\partial \mathbf{F}} \frac{\lambda}{2}(\operatorname{tr}(\mathbf{I})-1)^{2} \\
-&= \mu I + \lambda (\operatorname{det}(\mathbf{I})-1)  \frac{\partial}{\partial \mathbf{F}} \operatorname{det}(\mathbf{I}) = \mu \mathbf{I} \neq 0
+&= \mu \mathbf{I} + \lambda (\operatorname{det}(\mathbf{I})-1)  \frac{\partial}{\partial \mathbf{F}} \operatorname{det}(\mathbf{I}) = \mu \mathbf{I} \neq 0
 \end{align*}
@@
   \includegraphics[width=.8\linewidth]{resources/default_zoom_tet.png}  
-  \caption{Resolution of 10}
+  \caption{Step 25 with a resolution of 10}
   \label{fig:res_1}
@@
   \includegraphics[width=.8\linewidth]{resources/res_zoom_tet.png}  
-  \caption{Resolution of 30}
+  \caption{Step 25 with a resolution of 30}
   \label{fig:res_2}
@@
 We can set \textit{\lambda} equal to $1.0$ and let the other variables stay the same as in the last example (\textit{\mu} $= 1.0$, resolution $= 30.0$).
-With these inputs the cube gets wider in the middle part, as the poisson's ratio indicated that the material is more resistant to the stretching.
+Fig.
+\ref{fig:lambda} shows how the deformation is influenced by changing $\lambda$.
+With these inputs the cube gets wider in the middle part, as the poisson's ratio indicates that the material is more resistant to the stretching.
+
+\begin{figure}[!ht]
+\centering
+\begin{subfigure}{.47\textwidth}
+  \centering
+  % include first image
+  \includegraphics[width=.8\linewidth]{resources/lambda_comparison_res.png}  
+  \caption{Step 25 with $\lambda = 10.0$}
+  \label{fig:res_1}
+\end{subfigure}
+\begin{subfigure}{.47\textwidth}
+  \centering
+  % include second image
+  \includegraphics[width=.8\linewidth]{resources/lambda_comparison_lambda.png}  
+  \caption{Step 25 with $\lambda = 1.0$}
+  \label{fig:res_2}
+\end{subfigure}
+\caption{Results with a different values for $\lambda$ on a hexahedral mesh}
+\label{fig:lambda}
+\end{figure}
+
+Table \ref{table:lambda_tet} and \ref{table:lambda_hex} show the amount of Newton iteration needed for the chosen input values.
+The amount of iterations has decreased for both meshes.
+We need less iterations because the extend of the deformation is smaller.
+
+\begin{table}[!htbp]
+\parbox{.45\linewidth}{
+\centering
+\begin{tabular}{ | l | l |}
+\hline
+\textbf{Step size} & \textbf{Iterations} \\ \hline
+1-25 & 2 \\ \hline
+\end{tabular}
+\caption{Newton iterations for a tetrahedral mesh ($\lambda = 1.0$)}
+\label{table:lambda_tet}
+}
+\hfill
+\parbox{.45\linewidth}{
+\centering
+\begin{tabular}{ | l | l |}
+\hline
+\textbf{Step size} & \textbf{Iterations} \\ \hline
+1-25 & 3 \\ \hline
+\end{tabular}
+\caption{Newton iterations for a hexahedral mesh ($\lambda = 1.0$)}
+\label{table:lambda_hex}
+}
+\end{table}
+
+Now instead of decreasing the poisson's ratio, let's increase it.
+We can achieve that by choosing $\mu = 0.1$ and letting the other variables stay the same as in the first example of this section ($\lambda = 10.0$, res $= 10$).
+This is an extreme case because the poisson's ratio is very close to $0.5$.
+A higher poisson's value makes the cube more susceptible for stretching.
+We can see this effect by comparing the two images in Fig.
+-.
+
+For solving this system, we need more Newton iterations as we can see in Table \ref{table:mu_tet}  and \ref{table:mu_hex}.
+This is caused by the more complex deformation.
+The cube gets a lot narrower in the middle part which increases the difficulty of reaching a solution without artefacts.
+\begin{table}[!htbp]
+\parbox{.45\linewidth}{
+\centering
+\begin{tabular}{ | l | l |}
+\hline
+\textbf{Step size} & \textbf{Iterations} \\ \hline
+1 & 2 \\ \hline
+2-3 & 3 \\ \hline
+4-6 & 4 \\ \hline
+7 & 5 \\ \hline
+8-11 & 6 \\ \hline
+12 & 7 \\ \hline
+13-20 & 8 \\ \hline
+21-25 & 10 \\ \hline
+\end{tabular}
+\caption{Newton iterations for a tetrahedral mesh ($\mu = 0.1$)}
+\label{table:mu_tet}
+}
+\hfill
+\parbox{.45\linewidth}{
+\centering
+\begin{tabular}{ | l | l |}
+\hline
+\textbf{Step size} & \textbf{Iterations} \\ \hline
+1 & 5 \\ \hline
+2 & 6 \\ \hline
+3 & 7 \\ \hline
+4 & 8 \\ \hline
+5-6 & 9 \\ \hline
+7 & 10 \\ \hline
+8-9 & 11 \\ \hline
+10-11 & 12 \\ \hline
+12 & 13 \\ \hline
+13-14 & 14 \\ \hline
+15 & 15 \\ \hline
+16 & 16 \\ \hline
+17-19 & 17 \\ \hline
+20-25 & 19 \\ \hline
+\end{tabular}
+\caption{Newton iterations for a hexahedral mesh ($\mu = 0.1$)}
+\label{table:mu_hex}
+}
+\end{table}
+
+\subsubsection{Extreme values}
+We can test the energy with some extreme values.
+For a very low poisson's value, I choose $\lambda = 0.1$ and $\mu = 10.0$ with a resolution of $30$.
+This takes about $100$ to $200$ Newton iterations.
+I increased the original limit of a maximum of $50$ Newton iterations per step because the solve failed to get the result within these $50$ iterations.
+The finished result gives us some strange looking deformations as shown in Fig.
+-.
+But since the goal is to simulate human flesh, we are not very concerned how the energy performs with a low poissson's ratio.
 
@@
 \todoredefined[inline]{
-TODO: Include remaining examples (diff. lamé param. and changes in method) and what went right and what went wrong. \\
-Include other examples with Newton iterations?
+TODO: Explain difference in iteration with meshes
 }

### 2020-04-06 LaTeX-Master-Vorlage/chapter/paper.tex
waiting
mimimi

@@
   \caption{Step 25 with $\lambda = 10.0$}
-  \label{fig:res_1}
+  \label{fig:lambda_1}
 \end{subfigure}
@@
   \caption{Step 25 with $\lambda = 1.0$}
-  \label{fig:res_2}
+  \label{fig:lambda_2}
 \end{subfigure}
@@
 A higher poisson's value makes the cube more susceptible for stretching.
-We can see this effect by comparing the two images in Fig.
--.
+We can see this effect a bit by comparing the two images in Fig.
+\ref{fig:mu}, although the difference is not extreme.
+The model still behaves well and no artefacts can be seen.
+
+\begin{figure}[!ht]
+\centering
+\begin{subfigure}{.47\textwidth}
+  \centering
+  % include first image
+  \includegraphics[width=.8\linewidth]{resources/mu_res_new.png}  
+  \caption{Step 25 with $\mu = 1.0$}
+  \label{fig:mu_1}
+\end{subfigure}
+\begin{subfigure}{.47\textwidth}
+  \centering
+  % include second image
+  \includegraphics[width=.8\linewidth]{resources/mu_mu_new.png}  
+  \caption{Step 25 with $\mu = 0.1$}
+  \label{fig:mu_2}
+\end{subfigure}
+\caption{Results with a different values for $\mu$ on a tetrahedral mesh}
+\label{fig:mu}
+\end{figure}
 
@@
 This is caused by the more complex deformation.
-The cube gets a lot narrower in the middle part which increases the difficulty of reaching a solution without artefacts.
+The cube gets narrower in the middle part which increases the difficulty of reaching a valid solution.
 \begin{table}[!htbp]
@@
 
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=.7\textwidth]{resources/mu_extreme_small.png}  
+\caption{Results with a different values for $\mu$ on a tetrahedral mesh}
+\label{fig:mu_extreme}
+\end{figure}
+
 \newpage
@@
 \todoredefined[inline]{
-TODO: Explain difference in iteration with meshes
+TODO: Explain difference in iteration with meshes. Explain artefacts.
 }

### 2020-04-07 LaTeX-Master-Vorlage/chapter/Background.tex
left to do: complete eigensystem

@@
 5).
+For deformations of elastic materials, the Hooke's equation holds to some extend.
+Hooke's law describes a linear relationship of the applied force and the distance to the original position of a spring:
+\[
+	F = kx
+\]
+\textit{F} decribes the force, \textit{x} the distance and \textit{k} is a constant value. Material for which this equation holds are called linear-elastic or Hookean.
+
+\todoredefined[inline]{
+TODO: Explain Hooke better and add source for hookean, Neo-Hookean Model in Hyperelasticity
+}
 

### 2020-04-07 LaTeX-Master-Vorlage/chapter/paper.tex
left to do: complete eigensystem

@@
 \todoredefined[inline]{
-TODO: explain how to get to equation with singular values
+TODO: explain how to get to equation with singular values?
 }
@@
 \subsection{Meta-Stability under Degeneracy}
-The final energy is
+We have seen that he energy $\Psi_{E}$ has inversion, reflection and rest stability.
+Now we are interested how it behaves under degeneracy.
+The authors of the paper \textit{\acrshort{snh}} viewed this as a Drucker stability analysis (see \cite{bower2009applied}).
+By Drucker stability, we mean a set of criteria that a material can satisfy or not.
+This is a measurement of the stability of the material.
+The calculations can be found in the supplemental material of \textit{\acrshort{snh}}, I will only present the results here.
+
+The energy remains stable when crushing the object into a \textit{plane}.
+The object is able to return to its rest state.
+Thus, no further adjustments needs to be done.
+When crushing the object into a \textit{line}, the energy is meta-stable.
+A meta-stable state is a weaker state of stability that is resistant to small changes but not to large ones.
+The alternative would be a state that yields singularities, which worsens the situation.
+Hence, we can leave the energy as it is.
+Crushing the object to a \textit{point}, the material cannot recover into its rest state.
+This effect is small for a higher poisson's ratio as for biological tissue.
+For completeness the authors nevertheless added a regularized origin barrier:
+\[
+	\Psi_{origin} = \operatorname{log}(I_C +\delta)
+\]
+This term eliminates the point meta-stability for a positive poisson's ratio without interfering with the other requirements for the energy.
+It can be shown that the value $\delta$ should be set to $1$.
+This is also included in the supplemental material of the paper (\cite{Smith:2018:SNF:3191713.3180491}, 12:4).
+
+The final energy is then
 \begin{equation}\label{eq:stable_energy}
@@
 
+\subsection{Lamé Reparametrization}
+In order to stay consistent with Hooke's law, we need to do a reparametrization of $\mu$ and $\lambda$. For achieving this, we set
+\begin{equation}
+	\mathbf{P}(\mathbf{F}) = 2 \mu_{Lamé} \epsilon + \lambda_{Lamé} \operatorname{tr}(\epsilon) \mathbf{I},
+\end{equation}
+where $\epsilon = \frac{1}{2} (\mathbf{F} + \mathbf{F}^\intercal) - \mathbf{I}$ is the linearized strain tensor.
+We then set $\mu = \frac{4}{3} \mu_{Lamé}$ and $\lambda = \lambda_{Lamé} + \frac{5}{6} \mu_{Lamé}$.
+The equation for the poisson's ratio then shifts to
+\[
+	v= \frac{\lambda - \left( \frac{5}{8} \right) \mu}{2 \left(\lambda + \left( \frac{1}{8} \mu \right) \right)}.
+\]
+
 \todoredefined[inline]{
-TODO: How much needs to be explained here?
-}
-
-\subsection{Lamé Reparametrization}
-\todoredefined[inline]{
-TODO: How much needs to be explained here?
+TODO: Do a better job here.
 }
@@
 We can test the energy with some extreme values.
-For a very low poisson's value, I choose $\lambda = 0.1$ and $\mu = 10.0$ with a resolution of $30$.
+For getting a very low poisson's value near 0, I choose $\lambda = 0.1$ and $\mu = 10.0$ with a resolution of $30$.
 This takes about $100$ to $200$ Newton iterations.
-I increased the original limit of a maximum of $50$ Newton iterations per step because the solve failed to get the result within these $50$ iterations.
-The finished result gives us some strange looking deformations as shown in Fig.
--.
-But since the goal is to simulate human flesh, we are not very concerned how the energy performs with a low poissson's ratio.
+The finished result gives us a strange looking deformations and little artefacts as shown in Fig.
+\ref{fig:mu_extreme}.
+This does not mean that it is a bad model, but rather that is only suited for higher poisson's ratio like it is the case for simulating flesh.
 
-\begin{figure}[!ht]
+\begin{figure}[!htbp]
 	\centering
-\includegraphics[width=.7\textwidth]{resources/mu_extreme_small.png}  
-\caption{Results with a different values for $\mu$ on a tetrahedral mesh}
+	\includegraphics[width=0.5\textwidth]{resources/mu_extreme_1.png}
+	\caption{Step 4 with $\lambda = 0.1$ and $\mu = 10.0$ on a tetrahedral mesh shown from above}
 	\label{fig:mu_extreme}

### 2020-04-09 LaTeX-Master-Vorlage/chapter/Background.tex
changes

@@
 \section{Notation and Convention}
-At first I will declare the notation used in this thesis to avoid misunderstandings.
+At first, I will declare the notation used in this thesis to avoid misunderstandings.
 I will use the common notation used in continuum mechanics taken from the book \textit{Continuum Mechanics} \cite{Spencer1980}.
-Additionally I will include some more specific declarations formulated and used by the authors of the paper \textit{\acrshort{snh}}.
+Additionally, I will include some more specific declarations formulated and used by the authors of the paper \textit{\acrshort{snh}}.
 
@@
 Furthermore, I will use the tensor notation used in \textit{\acrshort{snh}}.
-They decided to define the vectorization vec(\cdot) as column-wise flattening of a matrix into a vector (\cite{Smith:2018:SNF:3191713.3180491}, 12:5) similar to Golub and Van Loan (2012) \cite{golub2012matrix}.
+They decided to define the vectorization vec(\cdot) as column-wise flattening of a matrix into a vector (\cite{Smith:2018:SNF:3191713.3180491}, 12:5) similar to Golub and Van Loan (2012) (\cite{golub2012matrix}).
 
-In order to indicate that I am dealing with a vectorized matrix I will use the symbol $\check{\cdot}$ as shown in the following equation:
+In order to indicate that I am dealing with a vectorized matrix, I will use the symbol $\check{\cdot}$ as shown in the following equation:
 
 \[
-\mathbf{A} = \begin{bmatrix} a & c \\ b & d \end{bmatrix} \qquad \operatorname{vec}(\mathbf{A}) = \mathbf{\check{a}} = \begin{bmatrix} a \\ b \\ c \\ d \end{bmatrix}.
+\mathbf{A} = \begin{bmatrix} a & c \\ b & d \end{bmatrix} \qquad \operatorname{vec}(\mathbf{A}) = \mathbf{\check{a}} = \begin{bmatrix} a \\ b \\ c \\ d \end{bmatrix}
 \]
@@
 
-We can now vectorize $\mathbb{A}$ and get the following result
+We can now vectorize $\mathbb{A}$ and get the following result:
 
 \[
-\operatorname{vec}(\mathbb{A}) = \left[ \,\operatorname{vec}\left(\mathbf{A}_{00}\right)\, \bigg| \,\operatorname{vec}\left(\mathbf{A}_{10}\right)\, \bigg| \,\operatorname{vec}\left(\mathbf{A}_{01}\right)\, \bigg| \,\operatorname{vec}\left(\mathbf{A}_{11}\right)\, \right] = \mathbf{\check{A}}.
+\operatorname{vec}(\mathbb{A}) = \left[ \,\operatorname{vec}\left(\mathbf{A}_{00}\right)\, \bigg| \,\operatorname{vec}\left(\mathbf{A}_{10}\right)\, \bigg| \,\operatorname{vec}\left(\mathbf{A}_{01}\right)\, \bigg| \,\operatorname{vec}\left(\mathbf{A}_{11}\right)\, \right] = \mathbf{\check{A}}
 \]
 
-This term above is equivalent to the subsequent notation
+This term above is equivalent to
 
@@
 \subsection{Polar Decomposition}
-Another theorem we will use in the next sections is the the Polar Decomposition Theorem.
+Another theorem we will use in the next sections is the Polar Decomposition Theorem.
 
@@
 We can further represent the norm with the trace of the matrix, in which $\mathbf{A}^*$ is the conjugate transpose of \textbf{A}.
-Going from there, we can use the \acrshort{svd} of \textbf{A} and write the norm with respect to the singular values of \textbf{A}, denoted by $\sigma_i$
+Going from there, we can use the \acrshort{svd} of \textbf{A} and write the norm with respect to the singular values of \textbf{A}, denoted by $\sigma_i$:
 \begin{equation} \label{eq:FN}
-\| \mathbf{A} \|_{F} = \sqrt{\operatorname{trace}(\mathbf{A} \mathbf{A}^*)} = \sqrt{\sum\limits_{i=1}^{\operatorname{min}\{m,n\}} \sigma_i^2}.
+\| \mathbf{A} \|_{F} = \sqrt{\operatorname{trace}(\mathbf{A} \mathbf{A}^*)} = \sqrt{\sum\limits_{i=1}^{\operatorname{min}\{m,n\}} \sigma_i^2}
 \end{equation}
@@
 This would be the case for rigid body displacements.
-Since we will be handling deformation in the 3D space, the deformation gradient will have the form of a $3 \times 3$ matrix
+Since we will be handling deformation in the 3D space, the deformation gradient will have the form of a $3 \times 3$ matrix:
 \begin{equation}\label{eq:deformation_gradient}
-\textbf{F} = \left[ \,f_0\, \bigg| \,f_1\, \bigg| \,f_2\, \right] = \begin{bmatrix} f_0 & f_3 & f_6 \\ f_1 & f_4 & f_7 \\ f_2 & f_5 & f_8 \end{bmatrix}.
+\textbf{F} = \left[ \,f_0\, \bigg| \,f_1\, \bigg| \,f_2\, \right] = \begin{bmatrix} f_0 & f_3 & f_6 \\ f_1 & f_4 & f_7 \\ f_2 & f_5 & f_8 \end{bmatrix}
 \end{equation}
@@
 \subsubsection{Polar Decomposition of the Deformation Gradient}
-With the help of Thm.\ref{PD} we can decompose the deformation gradient into the form
+With the help of Thm. \ref{PD} we can decompose the deformation gradient into the form
 \begin{equation}\label{PD_DG}
-	\mathbf{F} = \mathbf{RS}
+	\mathbf{F} = \mathbf{RS},
 \end{equation}
@@
 a plane or a point.
-A negative determinant, on the other hand, indicates an inversion.
+A negative determinant indicates an inversion.
 
@@
 \begin{equation}\label{CG_DG}
-	\mathbf{C} = \mathbf{F^\intercal F}
+	\mathbf{C} = \mathbf{F^\intercal F},
 \end{equation}
@@
 This means that the energy is an indicator of how much force must be applied in order for an object to be deformed in a certain way.
-Thus we can use the deformation energy to express the relationship between the stresses and strains.
+Thus, we can use the deformation energy to express the relationship between the stresses and strains.
 We can illustrate this with a stress-strain curve shown in Fig.
@@
 The behaviour of human flesh can be put into the category of hyperelastic materials.
+So we need a hyperelastic energy.
 The key property of elasticity is, that if all the forces that are applied over an object are removed, the object recovers into its original shape and volume (\cite{KORSUNSKY20175}, p.
@@
 \todoredefined[inline]{
-TODO: Explain Hooke better and add source for hookean, Neo-Hookean Model in Hyperelasticity
+TODO: Explain Hooke better and add source for hookean, Neo-Hookean Model in Hyperelasticity. Not happy with last paragraph, maybe additional subsection?
 }
@@
 In the context of flesh simulations, I am using the poisson's ratio as a characterization for the resistance to volume change of flesh.
-Biological tissues such as flesh, fat and muscles have one important property: Volume preservation.
-As a result the poisson's ratio takes on higher values in the range of 0.45 and 0.5 (\cite{Smith:2018:SNF:3191713.3180491}, 12:1).
+The poisson's ratio of biological tissues such as flesh, fat and muscles takes on higher values in the range of 0.45 and 0.5 (\cite{Smith:2018:SNF:3191713.3180491}, 12:1).
 

### 2020-04-09 LaTeX-Master-Vorlage/chapter/Introduction.tex
changes

@@
 They have made groundbreaking progress over the years.
-This can easily be observed when we compare today's work with that from ten years ago.
+This can easily be observed, when we compare today's work with that from ten years ago.
 
@@
 In the paper \textit{\acrlong{snh}} \cite{Smith:2018:SNF:3191713.3180491}, the authors addressed exactly this problem of making an animated movement of a human-like character look as natural as possible.
-Consequently, this thesis is based heavily on this paper.
+This thesis is based heavily on this paper.
 In the following, I will abbreviate the name of the paper with \textit{\acrshort{snh}}.
@@
 Next, I will go through the ideas mentioned in the paper and include some calculations and visualisations that serve for a better understanding.
-Lastly I will give an insight into the process of implementing the energy.
+Lastly, I will give an insight into the process of implementing the energy.

### 2020-04-09 LaTeX-Master-Vorlage/chapter/paper.tex
changes

@@
 \textbf{3.
-Rest stability:} When deforming an object in a certain way, we apply one or multiple forces to that object which influences the deformation.
+Rest stability:} When deforming an object in a certain way, we apply one or multiple forces to that object, which influences the deformation.
 But when we remove all the forces, the object should be back in its rest state.
@@
 \[
-\Psi_{M}=\frac{\mu}{2}\left(I_{C}-3\right)
+\Psi_{M}=\frac{\mu}{2}\left(I_{C}-3\right),
 \]
-that is used in $\Psi_{Neo}$ and $\Psi_{A}$. If we expand the energy with the singular values of the deformation gradient \textbf{F}, we get the following term:
+which is used in $\Psi_{Neo}$ and $\Psi_{A}$. If we expand the energy with the singular values of the deformation gradient \textbf{F}, we get the following term:
 \[
@@
 \[
-\Psi_{Neo, volume} = -\mu \log J+\frac{\lambda}{2}(\log J)^{2}
+\Psi_{Neo, volume} = -\mu \log J+\frac{\lambda}{2}(\log J)^{2},
 \]
@@
 \]
-The term of $\Psi_{A}$ and $\Psi_{B}$ which is of the form
+The term of $\Psi_{A}$ and $\Psi_{B}$, which is of the form
 \[
-\Psi_{M} = \frac{\lambda}{2}(J-1)^{2}
+\Psi_{M} = \frac{\lambda}{2}(J-1)^{2},
 \]
@@
 \]
-$\Psi_{D}$ is singularity free and well defined under inversion. Unfortunately, it does not satisfy the requirement of being rest stable which will be discussed in the next section.
+$\Psi_{D}$ is singularity free and well defined under inversion. Unfortunately, it does not satisfy the requirement of being rest stable, which will be discussed in the next section.
 
@@
 In order to solve this problem, the authors modified $(J-1)^{2}$ to $(J-\alpha)^{2}$.
-Using this modification, the energy can written as
+Using this modification, the energy can be written as
 \[
@@
 We have seen that he energy $\Psi_{E}$ has inversion, reflection and rest stability.
-Now we are interested how it behaves under degeneracy.
+Now we are interested in how it behaves under degeneracy.
 The authors of the paper \textit{\acrshort{snh}} viewed this as a Drucker stability analysis (see \cite{bower2009applied}).
@@
 The object is able to return to its rest state.
-Thus, no further adjustments needs to be done.
+Thus, no further adjustments need to be done.
 When crushing the object into a \textit{line}, the energy is meta-stable.
@@
 Hence, we can leave the energy as it is.
-Crushing the object to a \textit{point}, the material cannot recover into its rest state.
-This effect is small for a higher poisson's ratio as for biological tissue.
+After crushing the object to a \textit{point}, the material cannot recover into its rest state.
+This effect is small for a higher poisson's ratio.
 For completeness the authors nevertheless added a regularized origin barrier:
@@
 \]
-This term eliminates the point meta-stability for a positive poisson's ratio without interfering with the other requirements for the energy.
+This term eliminates the point meta-stability for a positive poisson's ratio, without interfering with the other requirements for the energy.
 It can be shown that the value $\delta$ should be set to $1$.
@@
 \subsection{First Piola-Kirchhoff Stress (PK1)}
-In order to analyse the energy PK1 can be used for Eq. \ref{eq:stable_energy} with $\alpha=1+\frac{\mu}{\lambda}-\left(\frac{\mu}{4}\right)\lambda$:
+In order to analyse the energy, PK1 can be used for Eq. \ref{eq:stable_energy} with $\alpha=1+\frac{\mu}{\lambda}-\left(\frac{\mu}{4}\right)\lambda$:
 \begin{align*}
@@
 \[
-\| \mathbf{\check{f}} \|^{2}_{2} = \sum_{n=0}^8 | f_n |^2 = \| \mathbf{F} \|^{2}_{F} = \sum_{n=0}^3 \sigma^2_i = \left( \sigma_0^2 + \sigma_1^2 + \sigma_2^2 \right)
+\| \mathbf{\check{f}} \|^{2}_{2} = \sum_{n=0}^8 | f_n |^2 = \| \mathbf{F} \|^{2}_{F} = \sum_{n=0}^3 \sigma^2_i = \left( \sigma_0^2 + \sigma_1^2 + \sigma_2^2 \right),
 \]
@@
 We can easily observe that $\mathbf{\check{H}}$ is a \textit{self-similar} cross-product matrix. This means that  the macro structure of the matrix is the same as the micro structure.
-
-\todoredefined[inline]{
-TODO: Check again each $f_1$ and $-$ in vectorization of H.
-}
 
@@
 \subsection{The Complete Eigensystem}
+With these expressions for each individual term, we can now analyse the complete system, which will be called $\mathbf{\check{A}}$.
+\[
+	\mathbf{\check{A}} = \mu \left(1-\frac{1}{I_C+1} \right) \mathbf{I} + \mu \frac{2}{(I_C +1)^2} \mathbf{\check{f}\check{f}}^\intercal + \lambda \mathbf{\check{g}\check{g}}^\intercal + \lambda (J-\alpha) \mathbf{\check{H}}
+\]
+Deriving the eigenvalues from $\mathbf{\check{A}}$ is nontrivial.
+Therefore, I will not include the calculations here and will only present the results.
+An interested reader can have a look at the paper \textit{\acrshort{snh}} on p.12:7 and 12:8.
+
+The final eigenvalues are
+\begin{align*}
+	&\epsilon_k = \lambda (J-\alpha) \bar{\epsilon}_k + \mu_T		&k = 0, 1, 2
+\end{align*}	
+and 
+\begin{align*}
+	&\epsilon_3 = \lambda(J-\alpha)\sigma_0 + \mu_T	&\epsilon_6 = -\lambda (J-\alpha)\sigma_0 + \mu_T \\
+	&\epsilon_4 = \lambda(J-\alpha)\sigma_1 + \mu_T	&\epsilon_7 = -\lambda (J-\alpha)\sigma_1 + \mu_T \\
+	&\epsilon_5 = \lambda(J-\alpha)\sigma_2 + \mu_T	&\epsilon_8 = -\lambda (J-\alpha)\sigma_2 + \mu_T.
+\end{align*}
+
+The variable $\mu_T$ is equal to $\mu(1- \frac{1}{I_C +1})$ and serves as a regularization term. $\bar{\epsilon}_k$ are the roots of the equation
+\[
+	\bar{\epsilon}^3 + c_2 \bar{\epsilon}^2 + c_1 \bar{\epsilon} + c_0 = 0.
+\]
+The variables $c_0$, $c_1$ and $c_2$ are defined as
+\begin{align*}
+	c_2 &= - \|\mathbf{\check{g}}\|^2_2 \rho - I_C \eta \\
+	c_1 &= - (1+ 2J\rho)I_C - 6 J \eta + \left( \|\mathbf{\check{g}}\|^2_2 I_C - 9J^2 \right) \rho \eta	\\
+	c_0 &= - (2 +3J\rho)J + \left( I_C^2 - 4 \|\mathbf{\check{g}}\|^2_2 \right) \eta + 2J \left( I^2_C -3 \|\mathbf{\check{g}}\|^2_2 \right) \rho \eta 	\\
+\end{align*}
+with 
+\begin{align*}
+	&\eta = \frac{2\mu}{(I_C+1)^2 \left( \lambda (J-1) - \frac{3}{4}\mu \right)}		&\rho = \frac{\lambda}{\lambda (J-1) - \frac{3}{4} \mu}.
+\end{align*}
 
 \todoredefined[inline]{
-TODO: Include what is necessary.
+TODO: Not happy with this section.
 }

### 2021-10-19 ba-thesis-masanti/chapter/Abstract.tex
transferred files from gitlab into this github repo

\chapter*{Abstract}
This thesis explores the process of simulating the fleshy appearances of virtual characters. The focus lies on the formulation of the deformation energy. In order to accurately simulate a fleshy look, nonlinear hyperelastic energies have proven to be the best choice. But simulating volume-preserving biological tissues such as flesh yields more than a few mathematical and physical challenges. Achieving rest stability while working with a high Poisson's ratio can be named as an example. Inspired by the complexity of this field, this thesis serves as an entry-level document. Relevant mathematical and physical aspects are presented and explained in an introductory manner. In addition, this thesis includes some more detailed calculations to bridge the gap between an expert in the field and a beginner. At the end of this thesis, I am presenting a few results visually to conclude the studies.

### 2021-10-19 ba-thesis-masanti/chapter/Background.tex
transferred files from gitlab into this github repo

\chapter{Background} 
\label{c:Background}
The goal of the paper \textit{\acrshort{snh}} was to simulate the fleshy appearance of virtual characters. In order to follow their thought process, we first need to understand the physical and mathematical interpretation of a deformation. This chapter serves as an introduction into the field of continuum mechanics and describes the mathematical background needed to understand the calculations and conclusions. At the beginning of this chapter, I will define the notation that I will use throughout this whole thesis. Next, I will present some concepts used in continuum mechanics, which are crucial for this field. Thirdly, I will give some insights into the mathematics used in continuum mechanics. However, I will not include each proof explicitly, as there are already many resources for an interested reader. Finally, I will introduce a few calculations and conclusions that will be useful to understand the methods used in the paper \textit{\acrshort{snh}}.

\section{Notation}
This section defines the notation that is used throughout this thesis to avoid misunderstandings. I am using the common notation used in continuum mechanics taken from the book \textit{Continuum Mechanics} (\cite{Spencer1980}). Additionally, I am including some more specific declarations formulated and used by the authors of the paper \textit{\acrshort{snh}}.

\subsection{General Notation}
Scalars are represented by regular, normal-weight variables such as $a$, whereas tensors and matrices are represented by upper-case bold letters, such as $\textbf{A}$. Vectors will be denoted by bold lower-case variables like $\textbf{a}$.

\subsection{Tensor Notation}
Furthermore, I am using the tensor notation used in \textit{\acrshort{snh}}. Similar to Golub and Van Loan (\cite{golub2012matrix}), the authors decided to define the vectorization vec(\cdot) as column-wise flattening of a matrix into a vector:
\[
\mathbf{A} = \begin{bmatrix} a & c \\ b & d \end{bmatrix} \qquad \operatorname{vec}(\mathbf{A}) = \begin{bmatrix} a \\ b \\ c \\ d \end{bmatrix}
\]
Additionally, $4^{th}$ order tensors in a form of matrix-of-matrices will be used in the calculations in \autoref{c:Paper}. These matrices are denoted by using blackboard bold:
\[
\mathbb{A} = 
\left[\begin{array}{cc}{\begin{bmatrix} a & c \\ b & d \end{bmatrix}} & {\begin{bmatrix} i & k \\ j & l \end{bmatrix}} \\ {\begin{bmatrix} e & g \\ f & h \end{bmatrix}} & {\begin{bmatrix} m & o \\ n & p \end{bmatrix}}\end{array}\right]
=
\left[\begin{array}{cc}{\left[\mathbf{A}_{00}\right]} & {\left[\mathbf{A}_{01}\right]} \\ {\left[\mathbf{A}_{10}\right]} & {\left[\mathbf{A}_{11}\right]}\end{array}\right]
\]
By vectorizing $\mathbb{A}$ we get the following result:
\[
\operatorname{vec}(\mathbb{A}) = \left[ \,\operatorname{vec}\left(\mathbf{A}_{00}\right)\, \bigg| \,\operatorname{vec}\left(\mathbf{A}_{10}\right)\, \bigg| \,\operatorname{vec}\left(\mathbf{A}_{01}\right)\, \bigg| \,\operatorname{vec}\left(\mathbf{A}_{11}\right)\, \right] = \mathbf{\check{A}}
\]
In order to point out that a matrix is vectorized, I am using the symbol $\check{\cdot}$ above the letter. The term above is equivalent to
\[
\mathbf{\check{A}}=\left[\begin{array}{llll}{a} & {e} & {i} & {m} \\ {b} & {f} & {j} & {n} \\ {c} & {g} & {k} & {o} \\ {d} & {h} & {l} & {p}\end{array}\right].
\]
The advantage of this form is that we can write several expressions as a cross product. This property will be used in \autoref{c:Paper} to simplify complicated expressions and calculations.

\subsection{Summary}
Here is a quick overview of the introduced notation:
\begin{align*}
a&: \text{Scalar} \\
\mathbf{A}&: \text{Matrix or tensor} \\
\mathbf{a}&: \text{Vector} \\
\mathbb{A}&: \text{Matrix-of-matrices} \\
\mathbf{\check{A}}&: \text{Vectorized matrix-of-matrices (also written as vec($\mathbb{A}$))}
\end{align*}

\section{Concepts of Continuum Mechanics}
This section gives a broad introduction to some of the concepts used in continuum mechanics. In continuum mechanics, we are less interested in small particles like atoms or molecules of an object but rather in pieces of matter that are large in comparison. The reason for this is that the calculation for the behaviour of individual atoms is challenging for larger systems. Therefore, we are concerned with the mechanical behaviour of solids and fluids on the macroscopic scale and treat the material as uniformly distributed throughout regions of space. With this approach, it is possible to define quantities such as displacement and density as continuous functions of the position (\cite{Spencer1980}, p. 1).

\subsection{Deformation}
When studying an object, we are among other properties interested in how it may change its shape over a certain period of time. If the object undergoes a change of shape, we call this process a deformation. In order to produce a deformation, there must be at least one force present that interacts with the object. Typically, we apply one or multiple forces over an object and are then interested in its deformed state. The term \textit{strain} is used as a measure of deformation, and we denote \textit{stress} as the force per unit area.

Graphically, we can imagine a deformation with the help of a two-dimensional deformation map, as shown in Fig. \ref{fig:deformationmap}. The ellipse on the left side represents an object in its rest state. A function $\phi$ maps this rest state of the ellipse to a deformed state as shown on the right side of the image.
\begin{figure}[!htbp]
	\centering
	\includegraphics[width=0.6\textwidth]{resources/deformation_map_plain.png}
	\caption[Deformation Map]{Deformation Map}
	\label{fig:deformationmap}
\end{figure}

We can imagine that we map each particle of a chosen object from its rest state to a deformed one. We can characterize each particle $X$ of a body by a vector $\mathbf{x}$ containing its positional coordinates. This vector is the reference configuration. If we displace the particle, we can describe its new coordinate vector $\mathbf{x}'$ with 
\[
	\mathbf{x}' = \phi (\mathbf{x}).
\]
\textbf{\textit{Example:}} A simple example of a deformation is the stretching of a cuboid along the x- and y-axis, as illustrated in Fig. \ref{stretch:1}. 
\begin{figure}[!htbp]
	\centering
	\includegraphics[width=0.35\textwidth]{resources/stretch_plot_new.png}
	\caption[Stretching of a cuboid]{Stretching of a cuboid}
	\label{stretch:1}
\end{figure}

The coloured volume in Fig. \ref{stretch:1} represents the cuboid in its rest state. In this case, the vector $\mathbf{x}$ contains the three coordinate values for the x-, y-, and z-axis:
\[
	\mathbf{x} = \begin{bmatrix} x \\ y \\ z\end{bmatrix}
\]
After the stretching, the new position for each particle can be calculated by
\begin{equation} \label{eq:example_phi}
	\mathbf{x}' = \phi (\mathbf{x}) = \begin{bmatrix} 1.5x + 0y + 0z	 \\ 0x + 2y + 0z \\ 0x +0y + 1z \end{bmatrix} = \begin{bmatrix} 1.5x \\ 2y \\ z \end{bmatrix}.
\end{equation}

\subsection{Deformation Gradient}
\label{ss:deformation_gradient}
An essential quantity in continuum mechanics is the deformation gradient \textbf{F}. It serves as a characterization of the deformation. With its help, we can calculate properties like the change of volume or length of an object during a deformation. We can obtain \textbf{F} by using the function $\phi$ discussed in the previous section and taking the derivative of each component of $\phi$ with respect to each component of the reference vector \textbf{x}. In the following, we only work with deformations in the three-dimensional space. In that case, $\mathbf{F}$ is a ($3 \times 3$)-matrix and can be calculated by
\begin{equation}\label{eq:deformation_gradient_general}
\mathbf{F} = \left[ \,\frac{\phi(\mathbf{x})}{\partial x}\, \bigg| \,\frac{\phi(\mathbf{x})}{\partial y}\, \bigg| \,\frac{\phi(\mathbf{x})}{\partial z}\, \right].
\end{equation}
For simplification, I will use this representation of \textbf{F} in the upcoming chapters:
\begin{equation}  \label{eq:deformation_gradient}
\textbf{F} = \left[ \,\mathbf{f_0}\, \bigg| \,\mathbf{f_1}\, \bigg| \,\mathbf{f_2}\, \right] = \begin{bmatrix} f_0 & f_3 & f_6 \\ f_1 & f_4 & f_7 \\ f_2 & f_5 & f_8 \end{bmatrix} 
\end{equation}
In this equation, $\mathbf{f_i}$ are the column vectors, and $f_i$ symbolize the scalar entries of the matrix. \textbf{F} can be useful for us to find out more about the deformation. For example, we know that if \textbf{F} is equal to the identity matrix \textbf{I}, there is no deformation present. That would be the case for rigid body displacements. In addition, \textbf{F} can be factorized and used to calculate other quantities. That will be explained in \autoref{s:deformation_gradient} after introducing the needed theorems in \autoref{s:math_background}.

\textbf{\textit{Example:}} I am again taking the example of stretching the cuboid from Fig. \ref{stretch:1}. We can obtain the resulting deformation gradient of this example with the help of Eq. \eqref{eq:deformation_gradient_general} applied to Eq. \eqref{eq:example_phi}:
\[
	\mathbf{F} = \left[ \,\frac{\phi(\mathbf{x})}{\partial x}\, \bigg| \,\frac{\phi(\mathbf{x})}{\partial y}\, \bigg| \,\frac{\phi(\mathbf{x})}{\partial z}\, \right] 
	= \begin{bmatrix} \frac{\partial [1.5x]}{\partial x} & \frac{\partial [1.5x]}{\partial y} & \frac{\partial [1.5x]}{\partial z} \\ \frac{\partial [2y]}{\partial x} & \frac{\partial [2y]}{\partial y} & \frac{\partial [2y]}{\partial z} \\ \frac{\partial [z]}{\partial x} & \frac{\partial [z]}{\partial y} & \frac{\partial [z]}{\partial z} \end{bmatrix} = \begin{bmatrix} 1.5 & 0.0 & 0.0 \\ 0.0 & 2.0 & 0.0 \\ 0.0 & 0.0 & 1.0 \end{bmatrix}
\]
As we can see, $\mathbf{F}$ is not equal to the identity matrix, so we are sure that the object was indeed deformed. For this simple example, this information might seem unnecessary because the visualisation already shows that the cuboid gets deformed, but for more complex deformations, this information is very useful.

\subsection{Deformation Energy}
\label{ss:deformation_energy}
We can deform an object by putting a certain amount of force into the system. We could, for example, stretch a spring. The spring then stores some amount of potential energy. If we let the spring go, we transfer the potential energy to kinetic energy, and the spring usually recovers into its rest state. This energy that the spring stores during the deformation is called \textit{deformation energy} or \textit{strain energy} $\Psi$. The strain energy density is the strain energy per unit volume. Any increment of the strain energy density is equal to the work done by the stresses in order to alter the strains (\cite{KORSUNSKY20175}, p.10). That means that energy is an indicator of how much force must be applied to deform an object in a certain way. Thus, we can use the deformation energy to express the relationship between the stresses and strains. We can illustrate this with a stress-strain curve shown in Fig. \ref{fig:stress_strain}. The area under the stress-strain curve corresponds to the strain energy density.
\newpage
\begin{figure}[!htbp]
	\centering
	\includegraphics[width=0.7\textwidth]{resources/stress_strain_curve_final.png}
	\caption[Stress-strain curve]{Example for a stress-strain curve\footnotemark}
	\label{fig:stress_strain}
\end{figure}
\footnotetext{the orginial image was taken from: \newline https://commons.wikimedia.org/wiki/File:Stress-strain\_curve.svg}

As we can see in Fig. \ref{fig:stress_strain}, with increasing stress, the object goes through different states. Before reaching the yielding point illustrated with \textit{Yield stress}, the material has the ability to recover into its rest shape. This ability is called \textit{Elasticity} (\cite{BERGSTROM2015209}, p. 211). After this point, the material cannot recover anymore due to permanent fractures during the deformation.

In addition, we can see that at the beginning of the curve, we have a straight line until the first black dot. That means that the relationship between the stresses and strains is linear. This is called \textit{Linear Elasticity} (\cite{KORSUNSKY20175}, p. 5). Linear elasticity is strictly related to \textit{Hooke's law}, which states that the resulting deformation is proportional to the applied force and that the object is able to recover into its rest shape under these conditions. Hence, we can also say that the material is consistent with \textit{Hooke's law} in this interval.

After the straight line, we can spot a non-linear relationship before the yielding point. The material is still able to recover, but there is a non-linear relationship between the stresses and strains. The resulting deformation is larger than how Hooke's law would predict it. Materials that fall into this category are called \textit{Hyperelastic Materials}. Hyperelasticity is a generalization of linear elasticity with a non-linear relationship and is suited for larger strain predictions (\cite{BERGSTROM2015209}, p. 218).

\textit{\acrshort{uts}} in Fig. \ref{fig:stress_strain} is abbreviated for \acrlong{uts} and defines the maximal stress an object can bear before breaking. At the point of \textit{Fracture stress} the material finally tears apart.

The behaviour of the object depends heavily on the material it consists of, and the stress-strain curve looks different for each material. We need to choose the energy function according to the material properties. The behaviour of human flesh can be put into the category of hyperelastic materials. Thus, the energy function also has to be hyperelastic for our purposes.

\subsection{Material Constants}
\label{ss:material_constants}
When we look at a deformation of an object, we need to consider the material the object consists of. Materials can be very stiff like steel or easily deformable like rubber. In order to measure the deformation of a specific material, we need the Poisson's ratio of said material. The Poisson's ratio is a material constant that is defined as 
\begin{equation}\label{eq:poisson}
\nu = - \frac{\epsilon_{11}}{\epsilon_{22}} \in [-1, 0.5],
\end{equation}
where $\epsilon_{11}$ is the lateral and $\epsilon_{22}$ the axial strain. The range in which $\nu$ lies in starts at $-1$ and goes up to $0.5$ (\cite{PhysRevB.80.132104}). In order to understand this quantity better, we can use an example: Imagine pulling a rubber band on each of its sides. After pulling a bit, we can observe that the band gets longer and the middle part gets narrower. The Poisson's ratio indicates the extent of this deformation. Some materials, such as rubber, are more easily deformable and therefore lead to a higher Poisson's ratio.

Usually, the Poisson's ratio of a material is positive. A negative value would mean that the material becomes wider in the cross-section when we stretch it. This behaviour is very uncommon in nature. Examples of materials with a negative Poisson's ratio are for instance discussed in \textit{Foam structures with a negative Poisson's ratio} (\cite{lakes1987foam}) or \textit{Advances in negative Poisson's ratio materials} (\cite{lakes1993advances}). Table \ref{table:1} shows examples of positive Poisson's ratios of various materials.

\setlength{\tabcolsep}{0.5em} % for the horizontal padding
{\renewcommand{\arraystretch}{1.1}% for the vertical padding
\begin{table}[!htbp]
\centering
    \begin{tabular}{ | l | l |}
    \hline
    \textbf{Material} & \textbf{Poisson's ratio} \\ \hline
    C (graphite) & 0.31 \\ \hline
    Sn (metal) & 0.357 \\ \hline
    Cu & 0.355 \\ \hline
    Zn & 0.25 \\ \hline
    Ag & 0.36 \\ \hline
    Au & 0.45 \\ \hline
    Concrete & 0.20–0.37 \\ \hline
    Titanium (dental alloy) & 0.30–0.31 \\ \hline
    Bronze & 0.34 \\ \hline
    18–8 Stainless steel & 0.305 \\ \hline
    Natural rubber & 0.4999 \\ \hline
	B\textsubscript{2}O\textsubscript{3} glass & 0.30 \\ \hline
	GeO\textsubscript{2} glass & 0.20 \\ \hline	
    \end{tabular}
    \caption[Materials with their Poisson's ratio]{Different materials with their Poisson's ratio (\cite{PhysRevB.80.132104}, p. 3)}
\label{table:1}
\end{table}

In the context of flesh simulation, the Poisson's ratio tells us how resistant flesh is to volume change. The
Poisson's ratio of biological tissues such as flesh, fat, and muscles takes on higher values in the range of 0.45 and 0.5 (\cite{Smith:2018:SNF:3191713.3180491}).

The calculation of the Poisson's ratio, as defined in Eq. \eqref{eq:poisson}, is a challenge. Fortunately, we can make use of the \textit{Lamé Parameters}, the two material-specific constants $\mu$ and $\lambda$. With the help of these two constants, we can transform Eq. \eqref{eq:poisson} into the form
\begin{equation}\label{eq:poisson_ratio}
\nu =  \frac{\lambda}{2(\lambda + \mu)}.
\end{equation}
This equation allows us to calculate the Poisson's ratio much easier (\cite{BERGSTROM2015209}, p. 231).

\section{Mathematical Background}
\label{s:math_background}
Now that we have established an understanding of the general concepts of continuum mechanics, we can look at the more technical part. Since mathematics play an important role in the field of interests, we need to build a solid background before diving further into more technical calculations. This section covers all the essential concepts used later in the calculations. A basic understanding of linear algebra is assumed.

\subsection{Singular Value Decomposition}
The \acrlong{svd} (\acrshort{svd}) will play an important role while working with the deformation gradient. It represents the best possible approximation of a given matrix by a matrix of low rank. This approximation can be looked at as a compression of the given data (\cite{LiesenMehrmann2015}, p. 295). Firstly, we need to define what singular values are.
\begin{definition}[\textbf{Singular Values}]
\label{singular_values}
The singular values of a matrix $\mathbf{A}$ $\in$ $\mathbb{R}^{m \times n}$ are the square roots of the eigenvalues of $\mathbf{AA}^{\mathsf{T}}$.
\end{definition}
The theorem of the singular value decomposition states that we can factor every ($m \times n$)-matrix into one orthogonal ($m \times m$)-, one orthogonal ($n \times n$)-, and one diagonal ($m \times n$)-matrix. More formally:
\begin{theorem}[\textbf{The \acrshort{svd} Theorem}]
\label{SVD}
Let $\mathbf{A}$ $\in$ $\mathbb{R}^{m \times n}$ be a matrix having r positive singular values, m $\geq$ n. Then there exist orthogonal matrices $\mathbf{U}$ $\in$ $\mathbb{R}^{m \times m}$, $\mathbf{V}$ $\in$ $\mathbb{R}^{n \times n}$ and a diagonal matrix $\mathbf{\tilde{\Sigma}}$ $\in$ $\mathbb{R}^{m \times n}$ such that
\begin{align*}
\mathbf{A} &= \mathbf{U \tilde{\Sigma} V^\mathsf{T}} \\
\mathbf{\tilde{\Sigma}} &= \left[ \begin{array}{cc} \mathbf{\Sigma} & 0 \\ 0 & 0 \end{array} \right]
\end{align*}
where $\mathbf{\Sigma}$ = diag ($\sigma_1$, $\sigma_2$, . . . , $\sigma_r$), and $\sigma_1$ $\geq$ $\sigma_2$ $\geq$ · · · $\geq$ $\sigma_r$ $>$ 0 are the positive singular values of $\mathbf{A}$.
\end{theorem}
This definition and theorem were taken from \textit{Numerical linear algebra with applications: Using MATLAB} (\cite{ford2014numerical}, p. 113, p. 300).

\subsection{Polar Decomposition}
Another theorem I will be using in \autoref{s:deformation_gradient} is the polar decomposition theorem:
\begin{theorem}[\textbf{The Polar Decomposition Theorem}]
\label{PD}
Let $\mathbf{F}$ be a non-singular square matrix. Then $\mathbf{F}$ can be decomposed uniquely into either of the following two products
\[
\mathbf{F} = \mathbf{RU}, \quad \mathbf{F} = \mathbf{VR}
\]
where $\mathbf{R}$ is an orthogonal matrix, and $\mathbf{U}$ and $\mathbf{V}$ are positive definite symmetric matrices.
\end{theorem}

This theorem was taken from \textit{Continuum Mechanics}, in which they include the proof for ($3 \times 3$)-matrices (\cite{Spencer1980}, p. 12).

\subsection{Frobenius Norm}
The Frobenius norm is a matrix norm. It allows us to measure and compare entities in a multidimensional space.
\begin{definition}[\textbf{Frobenius Norm}]
\label{FN}
Let \textbf{A} be an (m $\times$ n)-matrix in the real or complex domain. Then the Frobenius norm is defined as 
\[
\| \mathbf{A} \|_{F} := \sqrt{\sum\limits_{i=1}^{m} \sum\limits_{j=1}^{n} |a_{ij}|^2}.
\]
\end{definition}
We can further represent the norm with the trace of the matrix, in which $\mathbf{A}^*$ is the conjugate transpose of \textbf{A}. We can then use the \acrshort{svd} of \textbf{A} and write the norm with respect to the singular values of \textbf{A}, denoted by $\sigma_i$:
\begin{equation} \label{eq:FN}
\| \mathbf{A} \|_{F} = \sqrt{\operatorname{trace}(\mathbf{A} \mathbf{A}^*)} = \sqrt{\sum\limits_{i=1}^{\operatorname{min}\{m,n\}} \sigma_i^2}
\end{equation}

\section{Deformation Gradient}
\label{s:deformation_gradient}
Now that we understand the necessary mathematical background, we can factorize the deformation gradient \textbf{F} and use it to calculate other useful quantities. This section describes these factorizations and calculations by using the theorems introduced in the previous section.

\subsection{Singular Value Decomposition of F}
\label{ss:svd_deformation_gradient}
Using the \acrshort{svd} theorem shown in Thm. \ref{SVD}, \textbf{F} can be written in the form of
\begin{equation}\label{eq:svd_gradient}
\mathbf{F} = \mathbf{U \Sigma V^\mathsf{T}}
\end{equation}
in which $\mathbf{\Sigma}$ is defined as
\begin{equation}\label{eq:svd_simga}
\mathbf{\Sigma} = \left[\begin{matrix}  \sigma_0 & 0 & 0 \\ 0 & \sigma_1 & 0 \\ 0 & 0 & \sigma_2 \end{matrix}\right] .
\end{equation}
Each $\sigma_i$ denotes a singular value of $\mathbf{F}$. \textbf{U} and $\mathbf{V}$ are both orthogonal matrices that represent the rotation of \textbf{F}. $\mathbf{\Sigma}$, on the other hand, indicates the scaling of each coordinate $x_i$ by the factor $\sigma_i$. By using the standard convention, we would choose only nonnegative entries for $\mathbf{\Sigma}$. Unfortunately, this approach only works well for $\operatorname{det}(\mathbf{F}) \geq 0$ (\cite{irving2004invertible}, p. 134). Hence, when working with inverted material, we might run into problems. The authors of the paper \acrshort{snh} decided to move the reflections to $\mathbf{\Sigma}$. Therefore, $\mathbf{\Sigma}$ is allowed to have a negative entry. This has the effect that $\operatorname{det}(\mathbf{U})$ and $\operatorname{det}(\mathbf{V})$ are both equal to 1.

\subsection{Polar Decomposition of F}
With the help of Thm. \ref{PD} we can decompose the deformation gradient into the form
\begin{equation}\label{PD_DG}
	\mathbf{F} = \mathbf{RS},
\end{equation}
where \textbf{R} is orthogonal and \textbf{S} is a positive definite symmetric matrix. \textbf{R} symbolises the rotation that \textbf{F} undergoes, whereas \textbf{S} contains the scaling along the orthogonal directions of \textbf{F}.

\subsection{Relative Volume Change}
A piece of useful information about a deformation is the relative volume change of the deformed object. It can be calculated by the determinant of \textbf{F}:
\begin{equation}\label{det_DG}
	J = \operatorname{det}(\mathbf{F})
\end{equation}
For a normal deformation, $J$ is a positive value. A determinant of zero would mean that we deform the object into a zero volume state, e.g. a plane or point. A negative determinant indicates an inversion.

\subsection{Cauchy-Green}
\label{ss:cauchy-green}
In \autoref{c:Paper}, I will also use the right Cauchy-Green tensor \textbf{C}. It can be calculated by 
\begin{equation}\label{CG_DG}
	\mathbf{C} = \mathbf{F^\mathsf{T} F}.
\end{equation}
\textbf{C} is a ($3 \times 3$)-matrix for deformations in the 3D domain. Using \textbf{C}, we can calculate the first right Cauchy-Green invariant $I_C$ with
\begin{equation} \label{tr_CG_DG}
	I_C = \operatorname{tr}(\mathbf{C}).
\end{equation}
Invariants of the Cauchy-Green tensor are often used in formulations of the strain energy density.

### 2021-10-19 ba-thesis-masanti/chapter/Beispiele.tex
transferred files from gitlab into this github repo

\chapter{Background} \label{c:background}

This chapter will provide the necessary background in continuum mechanics and mathematics in order to understand the next chapters.

\section{Notation}
At first we will declare the notation used in this thesis to avoid misunderstandings. We will use the common notation used in continuum mechanics.

\section{Mathematical Background}

Since mathematics plays an important role in our field of interest we will build a solid background in this chapter. A basic understanding of linear algebra is assumed.

\subsection{Matrices}
At first we will discuss the geometrical meaning of some common matrix properties.

\subsection{Singular Value Decomposition}

The singular value decomposition (SVD) will play an important role in the following. It is important for our application since it represents the best possible approximation of a given matrix by a matrix of low rank. This approximation can be looked at as a compression of the data given (\cite{LiesenMehrmann2015}, S. 295).

\section{Continuum Mechanics}
In this section we will give a broad introduction the field of Continuum Mechanics.
In Continuum Mechanics we are less interested in small particles like atoms or molecules of an object but concentrate on pieces of matter which are in comparison very large. We are therefore concerned with the mechanical behavior of solids and fluids on the macroscopic scale (\cite{Spencer1980}, S. 1).

\section{Test}
Nachfolgend der \autoref{lst:helloworld}.

\begin{lstlisting}[caption={Hello World}, captionpos=b, label={lst:helloworld}]
/**
* The HelloWorldApp class implements an application that
* simply prints "Hello World!" to standard output.
*/
class HelloWorldApp {
	public static void main(String[] args) {
		System.out.println("Hello World!"); // Display the string.
	}
}
\end{lstlisting}

\section{Bild}

\begin{wrapfigure}{R}{0.5\textwidth}
	\centering
	\includegraphics[width=0.5\textwidth]{resources/example}
	\caption{Beispielbild {\cite{PEXELS2015}}}
\end{wrapfigure}

Die rechts zu sehende Grafik demonstriert die Möglichkeiten des Paketes \glqq wrapfig\grqq . Grafiken innerhalb einer \glqq wrapfigure\grqq{} können entweder links oder rechts von Text umlaufen werden.

Die nachfolgende \autoref{img:beispielbild} demonstriert die Darstellung\index{Darstellung} eines \glqq *.jpg\grqq{} Bildes innerhalb des Textes (beim Einfügen kann auf die Endung verzichtet werden, solange der Name einzigartig ist). Zusätzlich enthält dieses einen Untertitel der über das bereits verwendete Label verlinkt werden kann. Der Untertitel\index{Untertitel} erscheint im \gls{abbvz}.

\section{Text Formatierungen und sonstiges}
Dieser Text enthält eine Fußnote\footnote{Fußnoten sind Anmerkungen, die im Druck-Layout aus dem Fließtext ausgelagert werden, um den Text flüssig lesbar zu gestalten.}.

\subsection{Listen}
Listen könne sowohl mit Bullet points als auch mit Zahlen erstellt werden
\begin{itemize}
	\item Eine Liste mit Bullet points
	\item Ein weiteres Element
\end{itemize}

\begin{enumerate}
	\item Eine Liste mit Zahlen
	\item Ein weiteres Element
\end{enumerate}

\subsection{Text Hervorhebungen}
\begin{quote}
	The problem with internet quotes is that you can't always depend on their accuracy \par\raggedleft--- \textup{Abraham Lincoln, 1864}
\end{quote}

"Inspirierende Zitate können mit epigraph eingefügt werden
\epigraph{The problem with internet quotes is that you can't always depend on their accuracy}{Abraham Lincoln, 1864}

Seitenumbrüche können nur direkt nach Text geschrieben werden, sonst lässt sich das Latex nicht mehr compilieren.
\\

\begin{figure}[H]
	\centering
	\includegraphics[width=0.7\textwidth]{resources/example}
	\caption{Beispielbild {\cite{PEXELS2015}}}
	\label{img:beispielbild}
\end{figure}

\section{Tabelle}

Nachfolgend \autoref{tbl:DigitalesZertifikat}.

\begin{table}[H]
	\begin{center}
		\renewcommand{\arraystretch}{1.3}
		\begin{tabular}{|l|}
			\hline
			\textbf{Inhaber:}\\
			Alice \\ \hline
			\textbf{Peer (Ersteller):}\\
			Bob \\ \hline
			\textbf{Öffentlicher Schlüssel des Inhabers:}\\
			F2 D2 0E ED FA 4E 9E 0A F2 DD 23 8A 32 44 F3 E9 \\ \hline
			\textbf{Gültigkeit:}\\
			2015-07-01 – 2016-06-30 \\ \hline
		\end{tabular}
	\end{center}
	\caption{Digitales Zertifikat}
	\label{tbl:DigitalesZertifikat}
\end{table}

\section{Long-Table}

Die \glqq Long-Table\grqq kann über definierte Header und Footer über Seitenumbrüche hinweg angezeigt werden.

\begin{longtable}{|l|l|l|l|}
	\hline
	\multicolumn{1}{|c}{\textbf{Version}} & \multicolumn{1}{|c}{\textbf{Codename}} &
	\multicolumn{1}{|c}{\textbf{API}} &
	\multicolumn{1}{|c|}{\textbf{Verteilung}} \\ \hline
	\endfirsthead

	\multicolumn{4}{c}{Fortsetzung - Verteilung der Androidversionen (Stand 01.02.2016)}\\ \hline
	\multicolumn{1}{|c}{\textbf{Version}} & \multicolumn{1}{|c}{\textbf{Codename}} &
	\multicolumn{1}{|c}{\textbf{API}} &
	\multicolumn{1}{|c|}{\textbf{Verteilung}} \\ \hline 
	\endhead

	\multicolumn{4}{c}{Fortsetzung auf nachfolgender Seite}
	\endfoot

	\caption{Verteilung der Androidversionen (Stand: 01.02.2016)}
	\label{tab:androidverteilung}
	\endlastfoot

	2.2 & Froyo & 8 & 0.1\%\\ \hline
	2.3.3 - 2.3.7 & Gingerbread & 10 & 2.7\%\\ \hline
	4.0.3 - 4.0.4 & Ice Cream Sandwich & 15 & 2.5\%\\ \hline
	4.1.x & Jelly Bean & 16 & 8.8\%\\ \cline{1-1} \cline{3-4}
	4.2.x &  & 17 & 11.7\%\\ \cline{1-1} \cline{3-4}
	4.3 &  & 18 & 3.4\%\\ \hline
	4.4 & KitKat & 19 & 35.5\%\\ \hline
	5.0 & Lollipop & 21 & 17.0\%\\ \cline{1-1} \cline{3-4}
	5.1 &  & 22 & 17.1\%\\ \hline
	6.0 & Marshmallow & 23 & 1.2\%\\ \hline
\end{longtable}

\section{Literaturverweis}

Weil für die alte\index{alte} und die neue Rechtschreibung verschiedene Trennregeln\index{Trennregeln} gelten, sind Deutsch mit alter Rechtschreibung und Deutsch mit neuer Rechtschreibung zwei verschiedene Sprachen (\cite{Knappen2009}, S. 192).

\section{Onlineverweise}

Siehe Google.de \cite{Google2015}.

\section{Glossar}
Der Glossar enthält die Beschreibung verwendeter Begriffe für das bessere Verständnis gegenüber dem Leser. Beispiele sind: \gls{berlin}, \gls{outsourcing}, \gls{asp}, \gls{policy} und \gls{pcie}.

\section{Abkürzungsverzeichnis}
Das Abkürzungsverzeichnis listet alle verwendeten Abkürzungen auf. Einige Beispiele sind \gls{sas}, \gls{cd}, \gls{lan} und \gls{iso}. Die erneute Verwendung zeigt nur noch die Abkürzung: \gls{sas}, \gls{cd}, \gls{lan} und\index{und} \gls{iso}.

### 2021-10-19 ba-thesis-masanti/chapter/Experiments.tex
transferred files from gitlab into this github repo

\chapter{Practical Experiments} 
\label{c:Experiments}
After the derivation of the novel deformation energy in \autoref{c:Paper}, this chapter contains some practical experiments to show the robustness of the model and check that each requirement stated in \autoref{ss:stability} is satisfied. The experiments are quasi-static simulations of physical deformations. So, we deform an object in multiple small steps. Quasi-static simulation are well suited for flesh simulations (\cite{teran2005robust}). These simulations are done by posing constraints over the object and then minimizing the deformation energy to find the final position of each vertex.

The authors of the paper \textit{\acrshort{snh}} already provided an implementation for an application of their formulated energy\footnote{available at http://graphics.pixar.com/library/StableElasticity/snh\_code.tar.bz2}. Firstly in this chapter, I will examine their implementation and show the results of the experiments with their code. Later, I will present the results of other scenarios, for which I had to change the code accordingly. In the end, I will include a discussion of this new energy formulation considering the results from this chapter.

\section{Technology}
The code the authors provided was written in C++ using the CMake build system\footnote{https://cmake.org/}. It uses the library Eigen (\cite{eigenweb}), version 3.1.2 or newer. The code consists of a core library \verb|cubesim|, which provides the 3D mesh data structure, an implementation of the Stable Neo-Hookean material model, and Newton solvers that minimize the deformation energy over the meshes.

The images in this chapter were taken with the help of OpenFlipper, which is an open-source geometry processing and rendering framework (\cite{mobius2010openflipper}). Furthermore, I used OpenFlipper to create a plugin for some of the experiments. Inside the plugin, I used the integrated library OpenVolumeMesh, which provides a data structure to handle arbitrary polyhedral meshes (\cite{kremer2013openvolumemesh}).

\section{First Experiments}
In this section, I will show the results of the experiments I did with the provided code. The implementation performs a quasi-static simulation of the stretching of a cube. The cube can either be represented by a tetrahedral or a hexahedral mesh. In order to simulate the deformation, the implementation needs a value for each of the two Lamé parameters and a value for defining the desired resolution as input data. In addition, the user has to specify the directory into which the output files should be saved and the material model that should be selected. Since the simulation is quasi-static, the deformation is subdivided into 25 small steps instead of one large step. The output files are 26 static objects in the format .obj. The first file shows the object in its rest state, and the remaining files illustrate the 25 steps of increased deformation. The procedure of the implementation is roughly illustrated in Fig. \ref{fig:procedure}.
\begin{figure}[!htb]
\centering
\begin{tikzpicture}[node distance=2cm]
\node (input) [process] {$\mu$, $\lambda$, resolution};
\node (code1) [decision, right of=input, xshift=1.9cm] {Initialize material model};
\node (code2) [decision, below of=code1, yshift=-0.5cm] {Mesh generation};
\node (code3) [decision, right of=code2, xshift=1cm] {Update boundary conditions};
\node (code4) [decision, right of=code1, xshift=1cm] {Newton solve};
\node (output) [process, right of=code4, xshift=1.9cm] {26 objects};

\draw [arrow] (input) -- node[anchor=south] {Input}(code1);
\draw [arrow] (code1) -- (code2);
\draw [arrow] (code2) -- (code3);
\draw [arrow] (code3) -- (code4);
\draw [arrow] (code4) -- node[anchor=south] {Output}(output);
\end{tikzpicture}
\caption{Illustration of the procedure} \label{fig:procedure}
\end{figure}

I will explain how the implementation works based on an example. For this, I am taking the input variables $\mu = 1.0$, $\lambda = 10.0$ and a resolution of $10.0$. These values for the Lamé parameters result in a Poisson's ratio of 0.46. The command to start the execution for a tetrahedral mesh with these input variables is shown in \autoref{lst:bashCommand}.
\newline
\begin{lstlisting}[language=bash, numbers=none, label=lst:bashCommand, caption=Bash command for executing the code, captionpos=b]
$ ./tetcli 10 stable_neo_hookean 1.0 10.0 output
\end{lstlisting}

Firstly, the implementation initializes the material model Stable Neo-Hookean. Then the generation of the mesh starts. The code creates a cube with $11$ vertices (calculated by resolution + $1$) in each axis. Hence, the cube consists of $11 * 11 * 11 = 1'331$ vertices in total. The number of hexahedra, respectively tetrahedra, are calculated by the following formulas:
\begin{align*}
	&\text{Tet count} = 6 * 10 * 10 * 10 = 6'000 \\
	&\text{Cube count} = 10 * 10 * 10 = 1'000
\end{align*}
Afterwards, the simulation with the $25$ steps of the deformation starts. The code sets two faces of the cube as a boundary condition. A boundary condition in this context denotes a set of fixed vertices. A boundary face is a face for which each vertex is fixed. Fixed vertices already have their final position for the result of the deformation. By updating the boundary conditions, we stretch the cube. That means that these two boundary faces are moved further away from each other along the y-axis. We do this by updating the y-value of the fixed vertices with a new value \verb|newNegativeBoundary| or \verb|newPositiveBoundary| depending on whether the vertex should move in the positive or negative direction along the y-axis. The definition of these two values is shown in \autoref{lst:newBoundary}. The variable \verb|stepNum| is the value of the current step from the $25$ deformation steps. For each step the stretching should increase. To achieve this, we use the variable \verb|stepDelta|. Its value is equal to $0.1$ and stays constant for these first experiments.
\begin{lstlisting}[language=C++, numbers=none, label=lst:newBoundary, caption=Updating y-coordinates of vertices, captionpos=b]
const double newNegativeBoundary = -1.0 - stepNum * stepDelta;
const double newPositiveBoundary = 1.0 + stepNum * stepDelta;
\end{lstlisting}
After the new positions of the fixed vertices are declared, the \verb|TetNewtonSolver|, respectively \verb|CubeNewtonSolver|, is used to minimize the strain energy over the mesh and determine the position of the remaining vertices. The optimization process will be further explained in \autoref{s:optimization}. Finally, the mesh is saved in a .obj file in the directory \verb|output|.

Tables \ref{table:default_tet} and \ref{table:default_hex} show, the total number of Newton iterations that had to be performed by the solver to reach an acceptable solution. The number of iterations are listed for a specific step number or an interval of step numbers. For example, step number 1 to 10 each required 3 Newton iterations. The step number denotes in which of the 25 steps of deformation we currently are. In \autoref{lst:newBoundary} I called this variable \verb|stepNum|. The amount of iterations increases with increasing step number. This increase is not surprising, since the deformation is also increased with each step resulting in more calculations.

\begin{table}[!htbp]
\parbox{.45\linewidth}{
\centering
\begin{tabular}{ | l | l |}
\hline
\textbf{Step number} & \textbf{Iterations} \\ \hline
1-10 & 3 \\ \hline
11-21 & 4 \\ \hline
22-25 & 5 \\ \hline
\end{tabular}
\caption{Newton iterations for a tetrahedral mesh}
\label{table:default_tet}
}
\hfill
\parbox{.45\linewidth}{
\centering
\begin{tabular}{ | l | l |}
\hline
\textbf{Step number} & \textbf{Iterations} \\ \hline
1-7 & 4 \\ \hline
8-14 & 5 \\ \hline
15-18 & 6 \\ \hline
19-22 & 7 \\ \hline
23-25 & 8 \\ \hline
\end{tabular}
\caption{Newton iterations for a hexahedral mesh}
\label{table:default_hex}
}
\end{table}

The images in Fig. \ref{fig:stretchtest} show four of the resulting objects of this example. The choice of the input parameters is the same for each object. The image shows step $0$, which contains the cube in its rest state, step $8$, $16$, and $24$ for a tetrahedral and a hexahedral mesh. The resulting objects capture the deformation well and are artefact-free even for a larger stretch. Both the hexahedral and tetrahedral mesh show equally good results. Hence, the model performs well without restricting us to use only a certain type of mesh.
\begin{figure}[!htbp]
	\centering
	\begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=0.24\textwidth]{resources/hexcli_00.png}
        \hfill
        \includegraphics[width=0.24\textwidth]{resources/hexcli_08.png}
        \hfill
        \includegraphics[width=0.24\textwidth]{resources/hexcli_16.png}
        \hfill
        \includegraphics[width=0.24\textwidth]{resources/hexcli_24.png}
        \caption{Stretch test on a hexahedral mesh}
    \end{subfigure}
    \vskip\baselineskip
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=0.24\textwidth]{resources/tetcli_00.png}
        \hfill
        \includegraphics[width=0.24\textwidth]{resources/tetcli_08.png}
        \hfill
        \includegraphics[width=0.24\textwidth]{resources/tetcli_16.png}
        \hfill
        \includegraphics[width=0.24\textwidth]{resources/tetcli_24.png}
        \caption{Stretch test on a tetrahedral mesh}
    \end{subfigure}
    \caption[Stretch test performed on a cube]{Stretch test performed on a cube with (a) a hexahedral mesh and (b) a tetrahedral mesh with the same parameters}
    \label{fig:stretchtest}
\end{figure}

\subsection{Comparison of different Input Variables}
\label{ss:comparison_diff_vars}
In order to examine the influence of the input variables, I experimented with different values. The importance of the resolution is straight forward: With a higher resolution, the cube consists of more vertices and hexahedra or tetrahedra. In conclusion, the results are smoother, but we also increase the computational costs. 
For this example, I choose a resolution of 30 and let the other variables stay the same as in the previous example, meaning $\lambda = 10.0$ and $\mu = 1.0$, in order to make a comparison possible. If we choose a resolution of $30$, the cube consists of $29'791$ vertices and $162'000$ tetrahedra, respectively $27'000$ hexahedra. Thus, the cube consists of 27 times more cells than in the previous example.

Tables \ref{table:res_tet} and \ref{table:res_hex} show the amount of Newton iterations until a solution is reached. If we compare the numbers from this example with the ones from Table \ref{table:default_tet} and \ref{table:default_hex}, we can see that there are slightly more iterations needed than in the previous example. This increase can be expected due to the larger number of vertices and cells that the solver needs to consider.

\begin{table}[!htbp]
\parbox{.45\linewidth}{
\centering
\begin{tabular}{ | l | l |}
\hline
\textbf{Step number} & \textbf{Iterations} \\ \hline
1-7 & 3 \\ \hline
8-13 & 4 \\ \hline
14-20 & 5 \\ \hline
21-25 & 6 \\ \hline
\end{tabular}
\caption{Newton iterations for a tetrahedral mesh (res=30)}
\label{table:res_tet}
}
\hfill
\parbox{.45\linewidth}{
\centering
\begin{tabular}{ | l | l |}
\hline
\textbf{Step number} & \textbf{Iterations} \\ \hline
1-4 & 4 \\ \hline
5-10 & 5 \\ \hline
11-15 & 6 \\ \hline
16-19 & 7 \\ \hline
20-23 & 8 \\ \hline
24-25 & 9 \\ \hline
\end{tabular}
\caption{Newton iterations for a hexahedral mesh (res=30)}
\label{table:res_hex}
}
\end{table}

Fig. \ref{fig:res} shows the results with a higher resolution of $30$ compared to the lower resolution of $10$ of the previous example on a tetrahedral mesh. It shows the results of the deformation step $25$. We can see that a higher resolution clearly gives us more realistic results. Analogous, the same conclusion applies to the hexahedral mesh.
\begin{figure}[!ht]
\centering
\begin{subfigure}{.47\textwidth}
  \centering
  % include first image
  \includegraphics[width=.8\linewidth]{resources/default_zoom_tet.png}  
  \caption{Step 25 with a resolution of 10}
  \label{fig:res_1}
\end{subfigure}
\begin{subfigure}{.47\textwidth}
  \centering
  % include second image
  \includegraphics[width=.8\linewidth]{resources/res_zoom_tet.png}  
  \caption{Step 25 with a resolution of 30}
  \label{fig:res_2}
\end{subfigure}
\caption{Results with a different resolution on a tetrahedral mesh}
\label{fig:res}
\end{figure}

In addition, we can increase or decrease the Lamé parameters \textit{\mu} and \textit{\lambda}, which influences the Poisson's ratio directly. If we decrease \textit{\lambda}, the Poisson's ratio also decreases. We can set \textit{\lambda} equal to $1.0$ and let the other variables stay the same as in the previous example. Thus, $\mu$ is equal to 1.0, and the resolution is set to 30.0. The Poisson's ratio indicates the extent of the deformation. Materials with a higher value are more easily deformable, which I explained in \autoref{ss:material_constants}. Therefore, by decreasing the Poisson's ratio, the extent of the deformation is also decreased. That affects the resulting object as well as the computational costs. Tables \ref{table:lambda_tet} and \ref{table:lambda_hex} show the amount of Newton iteration needed for the chosen input values. The amount of iterations has decreased for both meshes. We need fewer iterations because the extent of the deformation is smaller than before.

\begin{table}[!htbp]
\parbox{.45\linewidth}{
\centering
\begin{tabular}{ | l | l |}
\hline
\textbf{Step number} & \textbf{Iterations} \\ \hline
1-25 & 3 \\ \hline
\end{tabular}
\caption{Newton iterations for a tetrahedral mesh ($\lambda = 1.0$)}
\label{table:lambda_tet}
}
\hfill
\parbox{.45\linewidth}{
\centering
\begin{tabular}{ | l | l |}
\hline
\textbf{Step number} & \textbf{Iterations} \\ \hline
1-25 & 4 \\ \hline
\end{tabular}
\caption{Newton iterations for a hexahedral mesh ($\lambda = 1.0$)}
\label{table:lambda_hex}
}
\end{table}

Fig. \ref{fig:lambda} shows how the deformation is influenced by changing $\lambda$. With these inputs, the cube gets wider in the middle part, as a lower Poisson's ratio indicates that the material is more resistant to stretching.
\begin{figure}[!ht]
\centering
\begin{subfigure}{.47\textwidth}
  \centering
  % include first image
  \includegraphics[width=.75\linewidth]{resources/lambda_comparison_res.png}  
  \caption{Step 25 with $\lambda = 10.0$}
  \label{fig:lambda_1}
\end{subfigure}
\begin{subfigure}{.47\textwidth}
  \centering
  % include second image
  \includegraphics[width=.75\linewidth]{resources/lambda_comparison_lambda.png}  
  \caption{Step 25 with $\lambda = 1.0$}
  \label{fig:lambda_2}
\end{subfigure}
\caption{Results with different values for $\lambda$ on a hexahedral mesh}
\label{fig:lambda}
\end{figure}

Now instead of decreasing the Poisson's ratio, let's increase it. We can achieve that by choosing $\mu = 0.1$ and set $\lambda$ equal to 10.0 and let the resolution be 30. This is an extreme case because the Poisson's ratio is very close to $0.5$. It is also an appropriate value for simulating flesh behaviour. Tables \ref{table:mu_tet} and \ref{table:mu_hex} illustrate the amount of Newton iterations needed for this configuration. As we can see, we need more Newton iterations to solve the system. That is caused by the increased deformation, as the cube gets narrower in the middle part, which makes reaching a good solution more difficult.

\begin{table}[!htbp]
\parbox{.45\linewidth}{
\centering
\begin{tabular}{ | l | l |}
\hline
\textbf{Step number} & \textbf{Iterations} \\ \hline
1 & 3 \\ \hline
2-3 & 4 \\ \hline
4-6 & 5 \\ \hline
7 & 6 \\ \hline
8-11 & 7 \\ \hline
12 & 8 \\ \hline
13-20 & 9 \\ \hline
21-25 & 11 \\ \hline
\end{tabular}
\caption{Newton iterations for a tetrahedral mesh ($\mu = 0.1$)}
\label{table:mu_tet}
}
\hfill
\parbox{.45\linewidth}{
\centering
\begin{tabular}{ | l | l |}
\hline
\textbf{Step number} & \textbf{Iterations} \\ \hline
1 & 6 \\ \hline
2 & 7 \\ \hline
3 & 8 \\ \hline
4 & 9 \\ \hline
5-6 & 10 \\ \hline
7 & 11 \\ \hline
8-9 & 12 \\ \hline
10-11 & 13 \\ \hline
12 & 14 \\ \hline
13-14 & 15 \\ \hline
15 & 16 \\ \hline
16 & 17 \\ \hline
17-19 & 18 \\ \hline
20-25 & 20 \\ \hline
\end{tabular}
\caption{Newton iterations for a hexahedral mesh ($\mu = 0.1$)}
\label{table:mu_hex}
}
\end{table}

A higher Poisson's value makes the cube more susceptible to stretching. We can see this effect a bit by comparing the two images in Fig. \ref{fig:mu}, although the difference is not extreme because the Poisson's ratios for the two examples are close to each other. The first image shows a material with a Poisson's ratio of approximately 0.46, and the second image shows a material with a Poisson's ratio approaching 0.5. The model behaves well with these input values, and no artefacts can be seen.
\begin{figure}[!ht]
\centering
\begin{subfigure}{.47\textwidth}
  \centering
  % include first image
  \includegraphics[width=.75\linewidth]{resources/mu_res_new.png}  
  \caption{Step 25 with $\mu = 1.0$}
  \label{fig:mu_1}
\end{subfigure}
\begin{subfigure}{.47\textwidth}
  \centering
  % include second image
  \includegraphics[width=.75\linewidth]{resources/mu_mu_new.png}  
  \caption{Step 25 with $\mu = 0.1$}
  \label{fig:mu_2}
\end{subfigure}
\caption{Results with different values for $\mu$ on a tetrahedral mesh}
\label{fig:mu}
\end{figure}

\newpage
\section{Additional Tests}
\label{s:generalization}
For this section, I changed some parts of the given implementation to perform more tests for this new energy. The first thing I did was to change the code, such that I was able to perform a quasi-static simulation of the stretching of an arbitrary mesh. Similar to the provided code, there are again 25 deformation steps. The implementation expects as input a tetrahedral or hexahedral mesh in the format .ovm (OpenVolumeMesh). In the user interface, several values can be selected:
\begin{itemize}
	\item Mesh type: Describes the cell shape of the mesh. The cell shape can be either \textit{tetrahedral}, \textit{regular hexahedral}, or \textit{irregular hexahedral}.
	\item Lambda: One of the Lamé parameters that determine the Poisson's ratio.
	\item Mu: One of the Lamé parameters that determine the Poisson's ratio.
	\item Stretch axis: Axis along which the mesh is supposed to be stretched. This can be the \textit{x}-, \textit{y}-, or \textit{z}-axis.
	\item Coordinate value for the first boundary: Determines the position at which the first boundary face lies.
	\item Coordinate value for the second boundary: Determines the position at which the second boundary face lies.
	\item Rate of step size: Rate at which the object should be stretched along the axis.
\end{itemize}

The rate of step size corresponds to the variable \verb|stepDelta| in \autoref{lst:newBoundary}. I made this variable adjustable because we are dealing with arbitrary meshes that could potentially be very large or very small. For better results, we might want to change the rate at which we stretch the object.

In order to get the desired results, I had to adjust the code accordingly. Fig. \ref{fig:procedure_generalization} illustrates the modified procedure of the code. The green fields are the steps that are different from the procedure before. Although the writing of the file was necessary before, it is explicitly listed here because the output format of the file has changed. In addition, the general procedure of updating the boundary conditions also stayed the same, but I had to adjust some parts so that the user input is processed correctly.

\begin{figure}[!htb]
\centering
\begin{tikzpicture}[node distance=2cm]
\node (input) [process] {$\mu$, $\lambda$, resolution};
\node (code1) [decision, right of=input, xshift=1.9cm] {Initialize material model};
\node (code6) [io, right of=code1, xshift=1cm] {Write file};
\node (code2) [io, below of=code1, yshift=-0.5cm] {Load mesh};
\node (code3) [io, below of=code2, yshift=-0.5cm] {Convert mesh};
\node (code4) [io, right of=code3, xshift=1cm] {Update boundary conditions};
\node (code5) [decision, below of=code6, yshift=-0.5cm] {Newton solve};
\node (output) [process, right of=code6, xshift=1.9cm] {26 objects};

\draw [arrow] (input) -- node[anchor=south] {Input}(code1);
\draw [arrow] (code1) -- (code2);
\draw [arrow] (code2) -- (code3);
\draw [arrow] (code3) -- (code4);
\draw [arrow] (code4) -- (code5);
\draw [arrow] (code5) -- (code6);
\draw [arrow] (code6) -- node[anchor=south] {Output}(output);
\end{tikzpicture}
\caption{Illustration of the modified procedure} \label{fig:procedure_generalization}
\end{figure}

The initialization of the material model stays the same as before. But now the implementation needs to load the mesh the user provides into the system. It then converts the input mesh into the data structure that was used by the provided code. Additionally, if the user input states that a hexahedral mesh is irregular, each hexahedron gets subdivided into four tetrahedra. This step was necessary because the subsequent steps expect the hexahedral mesh to be regular. Then, the boundary conditions are updated according to the input of the user. The stretching is again done by putting the boundary faces further away from each other along the stretch axis. Afterwards, the Newton solver calculates the final position of each vertex that is not fixed. Finally, the mesh is written into a file of the format .ovm (OpenVolumeMesh).

\subsection{Cylinder}
With the adjusted code, I was able to recreate the example of stretching a cylinder. This example was shown in the paper \acrshort{snh}, and the authors claimed that their model can handle this deformation well, even with a high Poisson's ratio and no parameter tuning. For my experiments, I used a hexahedral mesh consisting of $1'290$ vertices and $1'036$ hexahedra. Similar to the previous examples of the stretching of a cube, Fig. \ref{fig:stretchtest_cylinder} shows step 0 (initial cylinder), 8, 16, and 24 of the deformation. For the parameters, I chose $\lambda = 10.0$, $\mu = 1.0$, and a step size of 0.1, in order to reach a high Poisson's ratio and to get a large stretch of the object.
\begin{figure}[!htbp]
    \centering
    \includegraphics[width=0.24\textwidth]{resources/cylinder_00_new.png}
    \hfill
    \includegraphics[width=0.24\textwidth]{resources/cylinder_08_new.png}
    \hfill
    \includegraphics[width=0.24\textwidth]{resources/cylinder_16_new.png}
    \hfill
    \includegraphics[width=0.24\textwidth]{resources/cylinder_24_new.png}
    \hfill
    \caption{Stretch test on a cylinder}
    \label{fig:stretchtest_cylinder}
\end{figure}

The images verify the claims of the authors. The deformation is captured well and no artifacts can be seen, even for a larger stretch. Therefore, we can assume that we are not restricted to a specific shape of the deformable object. In addition, Table \ref{table:cylinder} illustrates the amount of Newton iterations that were necessary for solving the system. The numbers are a bit higher for a larger stretch compared to the cube, which consists of a similar amount of hexahedra. But they are still in a reasonable interval.

\begin{table}[!htbp]
\parbox{.45\linewidth}{
\centering
\begin{tabular}{ | l | l |}
\hline
\textbf{Step number} & \textbf{Iterations} \\ \hline
1 & 2 \\ \hline
2-7 & 3 \\ \hline
8-12 & 4 \\ \hline
13-14 & 5 \\ \hline
15-16 & 6 \\ \hline
17-18 & 7 \\ \hline
\end{tabular}
}
\hfill
\parbox{.45\linewidth}{
\centering
\begin{tabular}{ | l | l |}
\hline
\textbf{Step number} & \textbf{Iterations} \\ \hline
19-20 & 8 \\ \hline
21 & 9 \\ \hline
22 & 10 \\ \hline
23-24 & 11 \\ \hline
25 & 13 \\ \hline
\end{tabular}
}
\caption{Newton iterations for the deformation of a cylinder}
\label{table:cylinder}
\end{table}

\subsection{Scramble Test}
In order to highlight the robustness of the model, the authors performed a scramble test similar to those in Teran et al. (\cite{teran2005robust}) and Stomakin et al. (\cite{stomakhin2012energetically}). For this test, they randomly placed the vertices of a cube within a space of twice its rest volume. This test illustrates how the model performs under extreme, inverted configurations. Fig. \ref{fig:scramble} shows the results of the scramble test I performed.
\begin{figure}[!htbp]
	\centering
	\begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=0.32\textwidth]{resources/scramble_00_new.png}
        \hfill
        \includegraphics[width=0.32\textwidth]{resources/scramble_01_new.png}
        \hfill
        \includegraphics[width=0.32\textwidth]{resources/scramble_02_new.png}
        \caption{Results after 0, 1, and 2 Newton iterations (from left to right)}
    \end{subfigure}
    \vskip\baselineskip
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=0.32\textwidth]{resources/scramble_03_new.png}
        \hfill
        \includegraphics[width=0.32\textwidth]{resources/scramble_04_new.png}
        \hfill
        \includegraphics[width=0.32\textwidth]{resources/scramble_05_new.png}
        \caption{Results after 10, 40, and 63 Newton iterations (from left to right)}
    \end{subfigure}
    \caption{Scramble test on a cube}
    \label{fig:scramble}
\end{figure}

In Fig. \ref{fig:scramble}, we can see the solution process for 0, 1, 2, 10, 40, and finally 63 Newton iterations with $\mu=1.0$ and $\lambda = 10.0$. For this example, I had to alter the code a bit to get the desired functionalities. The initial hexahedral mesh is a cube consisting of $1'331$ vertices and $1'000$ hexahedra. Just like the authors, I fixed only four corner vertices and scrambled the remaining vertices of the cube within a space of twice the rest volume.

The last image of Fig. \ref{fig:scramble} shows the cube back in its rest state. Hence, the model is able to recover from this extreme deformation after 63 Newton iterations. In conclusion, the model has rest stability even under these inverted configurations.

\subsection{Experiments on a more complex Mesh}
After the experiments with simple meshes as the cube and cylinder, it would be interesting to see how the energy performs on a more complex mesh. For the following two experiments, I chose a tetrahedral mesh consisting of $5'650$ vertices and $20'203$ tetrahedra. The mesh is formed in the shape of a bird. Fig. \ref{fig:bird} shows the object in its rest state from different angles.
\begin{figure}[!htbp]
	\centering
	\begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=0.44\textwidth]{resources/bird_front.png}
        \hfill
        \includegraphics[width=0.44\textwidth]{resources/bird_back.png}
        \caption{Front and back of the mesh (from left to right)}
    \end{subfigure}
    \vskip\baselineskip
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=0.44\textwidth]{resources/bird_above.png}
        \hfill
        \includegraphics[width=0.44\textwidth]{resources/bird_bottom.png} 
        \caption{Top and bottom of the mesh (from left to right)}
    \end{subfigure}
    \caption{Object in its rest state shown from different angles}
    \label{fig:bird}
\end{figure}

For the first deformation, I stretched the bird in four directions: along the left and right wing, the head, and tail. That will give us an extreme stretch to further test the energy. For the parameters, I set $\lambda$ equal to $10.0$, $\mu$ equal to $1.0$, and the step size equal to $0.01$. The result of this deformation after ten steps is shown in Fig. \ref{fig:bird_deformed_stretched}.
\begin{figure}[!htbp]
	\centering
	\begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=0.44\textwidth]{resources/stretched_front.png}
        \hfill
        \includegraphics[width=0.44\textwidth]{resources/stretched_back.png}
        \caption{Front and back of the mesh (from left to right)}
    \end{subfigure}
    \vskip\baselineskip
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=0.44\textwidth]{resources/stretched_top.png}
        \hfill
        \includegraphics[width=0.44\textwidth]{resources/stretched_bottom.png}
        \caption{Top and bottom of the mesh (from left to right)}
    \end{subfigure}
    \caption{Stretched object shown from different angles}
    \label{fig:bird_deformed_stretched}
\end{figure}

As we can see, the wings lost their bend with this extreme stretch, and the head has become almost a straight line. Overall, the deformed object looks as good as it can under these extreme conditions, and the energy behaves well. There are some places where we can imagine which vertices I pulled to perform the stretch. For example, Fig. \ref{fig:bird_deformed_stretched_zigzag} shows how the outer part of the wings form almost a zig-zag pattern. Unfortunately, that was unavoidable because of the configuration of the mesh. If the vertices were aligned in a straight line, this effect would not be seen.
\begin{figure}[!htbp]
	\centering
	\includegraphics[width=0.44\textwidth]{resources/stretched_zigzag.png}
    \caption{Irregularity on the right wing (from the bird's point of view)}
    \label{fig:bird_deformed_stretched_zigzag}
\end{figure}

Additionally, instead of just stretching the object, we should also test how the energy behaves for other deformations. For the next experiment with this mesh, I pushed the two wings together and pulled the body down. With this configuration, we can bend the wings and see how the energy behaves under these conditions. Again, I set $\lambda$ equal to $10.0$, $\mu$ equal to $1.0$, and the step size equal to $0.01$
Fig. \ref{fig:bird_deformed_bend} shows the deformed object after ten steps.
\begin{figure}[!htbp]
	\centering
	\begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=0.44\textwidth]{resources/bent_front.png}
        \hfill
        \includegraphics[width=0.44\textwidth]{resources/bent_back.png}
        \caption{Front and back of the mesh (from left to right)}
    \end{subfigure}
    \vskip\baselineskip
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=0.44\textwidth]{resources/bent_top.png}
        \hfill
        \includegraphics[width=0.44\textwidth]{resources/bent_bottom.png} 
        \caption{Top and bottom of the mesh (from left to right)}
    \end{subfigure}
    \caption{Bent object shown from different angles}
    \label{fig:bird_deformed_bend}
\end{figure}

In the images, we can see that the two wings bend differently, which is caused by the selection of vertices to pull. Fig. \ref{fig:bird_deformed_bend_side} shows the deformed object from both sides to get a better look at the deformation.
\begin{figure}[!htbp]
	\centering
    \includegraphics[width=0.44\textwidth]{resources/bent_side2.png}
    \hfill
    \includegraphics[width=0.44\textwidth]{resources/bent_side1.png} 
    \caption{Side view of bent object}
    \label{fig:bird_deformed_bend_side}
\end{figure}

For both cases, the results are good, and no artefacts can be seen. With these experiments, we can conclude that the energy behaves well even for larger, more complex meshes. In addition, we have now seen different deformations than just the stretching along one axis of the object, and the energy was able to handle these configurations. That suggests that the energy is suited for arbitrary deformations on arbitrary meshes.

\section{Optimization}
\label{s:optimization}
In order to achieve realistic results, we not only need to choose a suitable model but also an appropriate algorithm to get the exact solution or a satisfying approximation within a reasonable amount of time. For the performed simulations, a standard Newton solver augmented with a line search was used. Linear systems were solved by using conjugate gradient implementation. This section gives an overview of these methods.

\subsection{Newton's Method}
The task of the optimization, in this case, is to find an acceptable minimum of the strain energy after changing the boundary conditions. We can formulate this problem more generally as
\[
	\text{minimize} \quad f(x): \mathbb{R}^n \rightarrow \mathbb{R}.
\]
In order to find a minimum, the condition $\nabla f(x) = 0$ has to be satisfied. 
For solving this problem, we can use Newton's method, which iteratively approaches an acceptable minimum. To achieve this, we need to know the correct search direction to approach a minima step by step. The search direction is given by the Newton step, which uses the second derivative of the function $f$:
\[
	\nabla x_{nt} := - \nabla^2 f(x)^{-1} \nabla f(x)
\]
Now we need to know how much we can move in this direction. The line search algorithm can answer this question. It outputs the maximum amount to move in a given search direction. Newton's method can be very fast compared to other methods and produces a solution of high accuracy. The main disadvantage is that the calculation and storage of the second derivative and computing the Newton step can be quite costly (\cite{boyd2004convex}, p. 484-487, 496). Thus, the analysis of the Hessian of the deformation energy was a necessary step to show that the energy is suited for practical applications.

\subsection{Conjugate Gradient}
The conjugate gradient method is an algorithm that solves a system of linear equations. We can write the problem generally as
\[
	\mathbf{A}\mathbf{x} = \mathbf{k},
\]
where $\mathbf{A}$ is a symmetric, positive definite ($n \times n$)-matrix. Both $\mathbf{A}$ and $\mathbf{k}$ are known. The conjugate gradient method delivers an approximation of the exact solution within a certain tolerance. It iteratively searches for an appropriate $\mathbf{x}$, starting with an initial estimate. It usually reaches convergence fast and is computationally efficient (\cite{hestenes1952methods}, p. 409-412). In the code, the conjugate gradient method was used iteratively with the help of the library Eigen, which has already implemented the corresponding functionalities.

\section{Discussion}
The authors of the paper \acrshort{snh} introduced a novel hyperelastic model for the deformation energy. My first approach for this thesis was to dive into the topic of flesh simulation. The most important topics concerning this learning process are introduced and explained in \autoref{c:Background}. The next step was to understand and being able to explain the thought process of the authors. The paper itself can be a bit complicated for somebody who does not yet have a broad knowledge of the field. I documented this step in \autoref{c:Paper}. In the same chapter, it also appears to be clear why a new energy formulation was necessary. None of the existing energies satisfied all of the requirements stated in \autoref{ss:stability}. Some of them even produced severe artefacts or could not preserve the volume. Finally, I conducted some experiments on my own to verify some of the author's claims. The implementation the authors provided helped me during this process, not only for the simulations but also to get a better understanding of the energy. In \autoref{c:Experiments}, I first experimented with different values for the Poisson's ratio and was able to verify the claim that the model behaves well for a wide range of Poisson's ratio, even for one close to 0.5. In addition, I could recreate some other examples they covered in their paper. For each simulation included in this thesis, the model satisfies the requirements the authors listed without the need of using filter parameters. Furthermore, the scramble test validates the robustness of the model, and the deformations on the bird mesh suggest that the energy is suited for arbitrary deformations on arbitrary meshes. But in order to make a final statement of the quality of the energy, it would be necessary to make more specific tests, for example, the behaviour of a hand or an arm. In addition, the results should be compared with the ones produced from other energy formulations, similar to some of the tests the authors included in their paper. Unfortunately, this would have been beyond the scope of this thesis. From the findings I could require during my thesis, it nonetheless appears that there is a great improvement in the quality of the simulation with this new energy model for materials with a high Poisson's ratio.

### 2021-10-19 ba-thesis-masanti/chapter/Introduction.tex
transferred files from gitlab into this github repo

\chapter{Introduction}
\label{c:Introduction}
\textit{``Animation offers a medium of storytelling and visual entertainment which can bring pleasure and information to people of all ages everywhere in the world.''} \\
- Walt Disney

\section{Motivation}
With steadily increasing computational power, the demand for better-looking results is constantly growing. Especially in the field of animation and simulation, various research has been done to avoid mediocre results. In the entertainment sector, these findings were used to present movies of the highest quality for people all over the world. Animation studios like Pixar\textsuperscript{\textcopyright} have made groundbreaking progress over the years. This can easily be observed by comparing today's work with that from ten years ago.

As always, there are different requirements for each use case. In some cases, an exaggerated movement or reaction has a better effect on the viewer. A massive explosion, for example, looks more spectacular in a movie when it is not physically correct. In other scenarios, the animation should come as close as possible to reality. For instance, adding small details like visible breathing or wrinkles offers a way to get more convincing results. A good animation should create the illusion of a character with personality, thoughts, and emotions. But in order to create this illusion, an animated character has to move and physically interact with its environment as it would in reality. Otherwise, the human brain would immediately recognize that some things do not add up. One aspect for achieving this realistic effect is the simulation of the fleshy appearances of virtual characters. In the paper \textit{\acrlong{snh}} (\cite{Smith:2018:SNF:3191713.3180491}), the authors addressed exactly this problem and formulated a new deformation energy for simulating human flesh. This thesis is based heavily on this paper. In the following, I will abbreviate the name of the paper with \textit{\acrshort{snh}}.

But before diving further into the content of the paper, a fundamental background is needed. In order to animate a physical movement, a basic understanding of the physics behind it is necessary. This knowledge requires some experience in the field of continuum mechanics. Unfortunately, for most of the students in computer science, it has yet to be learned. This thesis should help students of computer science who are interested in the field of animation and simulation but are still beginners. Therefore, the goal of this thesis is to explain the necessary physical and mathematical background. In addition, I will go deeper into the thematics of the paper \textit{\acrshort {snh}}. I will go through some of their calculations more detailed to help the reader to follow the thought process of the authors.
I aim to get an understanding of their contribution to the field and extend the code they provided to test the energy with practical experiments.

\section{Structure}
In the following, I will deliver an introduction into the field of continuum mechanics and give a brief overview of the necessary mathematical background. Next, I will go through the ideas mentioned in the paper \acrshort{snh} and include some calculations and visualizations that serve for a better understanding. Lastly, I will give insights into the implementation of the energy and show the results of the practical experiments I conducted.

### 2021-10-19 ba-thesis-masanti/chapter/paper.tex
transferred files from gitlab into this github repo

\chapter{Stable Neo-Hookean Flesh Simulation} \label{c:Paper}
In this chapter, I will examine further the topic of the paper \textit{\acrshort{snh}}, in particular, the calculations and conclusions made by the authors. I will go through each step they did, and my goal is to fill in some gaps to help in understanding the thought process. For this, I will include some of their calculations in more detail and add additional explanations. I would like to note that the information provided in this chapter is taken from the paper \acrshort{snh} if not stated otherwise. For simplification, I will not include a reference in each paragraph.

The structure of this chapter is similar to the one of the paper: At first, I will go through the process of the formulation of the Stable Neo-Hookean energy. This includes pointing out the requirements and looking at existing energies. Finally, I will show that a complete eigenanalysis can be performed on the constructed energy.

\section{Deformation Gradient}
In the following, I will use the definitions involving the deformation gradient $\mathbf{F}$ introduced in \autoref{c:Background}. These definitions are summarized in Table \ref{table:gradient_quantities} for a better overview.

\setlength{\tabcolsep}{0.5em} % for the horizontal padding
{\renewcommand{\arraystretch}{1.1}% for the vertical padding
\begin{table}[!htbp]
\centering
    \begin{tabular}{ | l | l |}
    \hline
    \textbf{Symbol} & \textbf{Definition} \\ \hline
    $\mathbf{F} = \mathbf{RS}$ & Polar decomposition \\ \hline
    $J=\operatorname{det}(\mathbf{F})$ & Relative volume change \\ \hline
    $\mathbf{C}=\mathbf{F}^\mathsf{T} \mathbf{F}$ & Right Cauchy-Green tensor  \\ \hline	
    $I_{C}=\operatorname{tr}(\mathbf{C})$ & First right Cauchy-Green invariant \\ \hline
    \end{tabular}
    \caption[Quantities derived from the Deformation Gradient]{Quantities derived from the deformation gradient}
\label{table:gradient_quantities}
\end{table}

\newpage
\section{Energy Formulation}
In this section, I will go through the process of formulating a new deformation energy. At first, I will explain what properties a deformation energy should have. Secondly, I will analyse existing energies. Finally, I will go through the formulation of the novel energy from the paper \acrshort{snh}.

\subsection{Stability} 
\label{ss:stability}
The core goal of the paper was to model deformations for virtual characters that have human-like features. In order to achieve better results than what has been done in current research, they formulated a new deformation energy. In \autoref{c:Background}, I concluded that the appropriate energy for animating soft tissues such as flesh has to be hyperelastic. Another important property is the stability of the energy. We need a hyperelastic energy that is stable in the following four ways, which were introduced in the paper itself:

\textbf{1. Inversion Stability:} Given some arbitrary object, it is possible that while deforming the object, we can arrive at a zero volume state or even an entire inversion. For example, we can look at the tetrahedron shown in Fig. \ref{fig:inversion_1}. In Fig. \ref{fig:inversion_2}, we see a deformed state of this tetrahedron where the volume is scaled down to zero, and we are left with a simple triangle. In Fig. \ref{fig:inversion_3}, the tetrahedron arrives at an inverted state. The deformation energy has to be able to deal with both cases without creating severe artefacts. That means that the energy has to be singularity-free, meaning that it is defined for every possible point. This property should ideally hold without needing any filters or threshold.
\begin{figure}[!ht]
\centering
\begin{subfigure}{.3\textwidth}
  \centering
  % include first image
  \includegraphics[width=.8\linewidth]{resources/stability_inversion_1.png}  
  \caption{Rest state}
  \label{fig:inversion_1}
\end{subfigure}
\begin{subfigure}{.3\textwidth}
  \centering
  % include first image
  \includegraphics[width=.9\linewidth]{resources/stability_inversion_2.png}  
  \caption{Zero-volume state}
  \label{fig:inversion_2}
\end{subfigure}
\begin{subfigure}{.3\textwidth}
  \centering
  % include second image
  \includegraphics[width=.9\linewidth]{resources/stability_inversion_3.png}  
  \caption{Inverted state}
  \label{fig:inversion_3}
\end{subfigure}
\caption[Inversion of a tetrahedron]{Inversion of a tetrahedron}
\label{fig:inversion}
\end{figure}

\textbf{2. Reflection stability:} While deforming an object, it can occur that we are dealing with reflections. An example of a reflection in 2D is shown in Fig. \ref{fig:reflection}. The coloured triangle is reflected over the y-axis. A matrix that represents a reflection is orthogonal with a determinant equal to $-1$. The deformation energy needs to be well behaved under reflections. This has to hold, regardless of the reflection convention used in the \acrshort{svd} of \textbf{F}. The reflection convention is explained in \autoref{c:Background} in \autoref{ss:svd_deformation_gradient}.
\begin{figure}[!htbp]
	\centering
	\includegraphics[width=0.5\textwidth]{resources/reflection_plot.png}
	\caption[Reflection of a triangle over the y-axis]{Reflection of a triangle over the y-axis}
	\label{fig:reflection}
\end{figure}

\textbf{3. Rest stability:} While deforming an object in a certain way, we apply one or multiple forces to that object, which influences the deformation. But if we remove all the forces, the object should be able to go back into its rest state. This ability was introduced in \autoref{c:Background} as elasticity.

\textbf{4. Meta-stability under degeneracy:} Here we are dealing with a special case of deformation. If we crush a volumetric object into a plane, line, or point, we change the object into a degenerate case. This process is illustrated for a cube in Fig. \ref{fig:meta_stability}. Even with these extreme conditions, the object should still be able to recover into its actual shape and not some other.
\begin{figure}[!htbp]
	\centering
	\includegraphics[width=0.5\textwidth]{resources/metastability.png}
	\caption[Illustration of meta stability]{Illustration of degeneracy}
	\label{fig:meta_stability}
\end{figure}

Based on these four requirements, I will judge the existing models for the deformation energy. These criteria determine whether a proposed energy is suited for simulating the fleshy look or not.

\subsection{Existing Neo-Hookean Energies}
In previous literature, a few energies were proposed, which I will analyse in this section. They are listed in Table \ref{table:energies}. All of these energies were formulated for hyperelastic materials.

\setlength{\tabcolsep}{0.5em} % for the horizontal padding
{\renewcommand{\arraystretch}{1.3}% for the vertical padding
\begin{table}[!htbp]
\centering
    \begin{tabular}{ | l | l |}
    \hline
    \textbf{Energy} & \textbf{Author(s)} \\ \hline
    $\Psi_{Neo}=\frac{\mu}{2}\left(I_{C}-3\right)-\mu \log J+\frac{\lambda}{2}(\log J)^{2}$ & \begin{tabular}{@{}l@{}}e.g. Bonet and Wood 1997 \\ (\cite{bonet1997nonlinear})\end{tabular}  \\ \hline
    $\Psi_{\mathrm{A}}=\frac{\mu}{2}\left(I_{C}-3\right)-\mu \log J+\frac{\lambda}{2}(J-1)^{2}$ & Odgen 1997 (\cite{ogden1997non}) \\ \hline
    $\Psi_{\mathrm{B}}=\frac{\mu}{2}\left(J^{-2 / 3} I_{C}-3\right)+\frac{\lambda}{2}(J-1)^{2}$ & Bower 2009 (\cite{bower2009applied}) \\ \hline
    $\Psi_{\mathrm{C}}=\frac{\mu}{2}\left(J^{-2 / 3} I_{C}-3\right)+\frac{\lambda}{2}(J-1)$ & \begin{tabular}{@{}l@{}}Wang and Yang 2016 \\ (\cite{wang2016descent}) \end{tabular} \\ \hline
    \end{tabular}
    \caption[Summary of proposed energies]{Summary of proposed energies (\cite{Smith:2018:SNF:3191713.3180491})}
\label{table:energies}
\end{table}

According to the Valanis-Landel hypothesis, many hyperelastic energies can be split up into a 1D length, 2D area, and 3D volume term. The energies in Table \ref{table:energies} only contain the length and volume term. Hence, each of these energies can be separated into a 1D length term and a 3D volume term. The 1D length term penalizes the length changes an object undergoes during a deformation, whereas the 3D volume term penalizes the change in volume of the object.

\setlength{\tabcolsep}{0.5em} % for the horizontal padding
{\renewcommand{\arraystretch}{1.3}% for the vertical padding
\begin{table}[!htbp]
\centering
    \begin{tabular}{ | l | l | l |}
    \hline
    \textbf{Energy} & \textbf{1D length term} & \textbf{3D volume term} \\ \hline
    $\Psi_{Neo}$ & $\frac{\mu}{2}\left(I_{C}-3\right)$ & $-\mu \log J+\frac{\lambda}{2}(\log J)^{2}$ \\ \hline
    $\Psi_{\mathrm{A}}$ & $\frac{\mu}{2}\left(I_{C}-3\right)$ & $-\mu \log J+\frac{\lambda}{2}(J-1)^{2}$ \\ \hline
    $\Psi_{\mathrm{B}}$ & $\frac{\mu}{2}\left(J^{-2 / 3} I_{C}-3\right)$ & $\frac{\lambda}{2}(J-1)^{2}$ \\ \hline
    $\Psi_{\mathrm{C}}$ & $\frac{\mu}{2}\left(J^{-2 / 3} I_{C}-3\right)$ & $\frac{\lambda}{2}(J-1)$ \\ \hline
    \end{tabular}
    \caption{Energies split up into their 1D length and 3D volume term}
\label{table:energies_split}
\end{table}

\subsubsection{1D Length Term}
The term that is used for $\Psi_{Neo}$ and $\Psi_{A}$ is defined as
\[
\Psi_{M}=\frac{\mu}{2}\left(I_{C}-3\right).
\]
This energy was originally proposed by Mooney in 1940 (\cite{mooney1940theory}). It is today known as the Neo-Hookean energy because of Rivlin (\cite{rivlin1948large}). If we expand the term with the singular values of the deformation gradient \textbf{F}, we get the following equation:
\[
\Psi_{M}=\frac{\mu}{2}\left(\sigma_{0}^2 + \sigma_{1}^2 + \sigma_{2}^2 - 3\right)
\]
The term reaches its minimum at a zero volume state, meaning at $I_{C}=0$, which leads to $\Psi_{M}=-3$. Because this is not desirable, Mooney added the hard constraint that $J$ should be equal to $1$. Hence, the energy is minimized at a volume-preserving configuration. Note that the energy is singularity free and well defined under inversion.

The second term is defined by
\[
\Psi_{R} = \frac{\mu}{2}\left(J^{-2 / 3} I_{C}-3\right).
\]
It is used in $\Psi_{B}$ and $\Psi_{C}$. This term was introduced by Rivlin in 1948 (\cite{rivlin1948large}). Using the singular values of \textbf{F}, we get the following expression:
\[
\Psi_{R} = \frac{\mu}{2}\left(\frac{\sigma_{0}^2 + \sigma_{1}^2 + \sigma_{2}^2}{(\sigma_{0}  \sigma_{1}  \sigma_{2})^\frac{2}{3}}
 - 3\right)
\]
Unfortunately, this term is not singularity free. If $J$ is equal to zero, the result is not defined anymore.

\subsubsection{3D Volume Term}
The volume term of $\Psi_{Neo}$ is described as
\[
\Psi_{Neo, volume} = -\mu \log J+\frac{\lambda}{2}(\log J)^{2}
\]
and results in numerical problems since the logarithmic function is not defined for $J<0$ and grows unbounded for $J \rightarrow 0$. In conclusion, $\Psi_{Neo, volume}$ is not singularity free. 
The same applies to the 3D volume term of $\Psi_{A}$, namely
\[
\Psi_{A, volume} = -\mu \log J+\frac{\lambda}{2}(J-1)^{2}.
\]
The volume term of $\Psi_{B}$ and $\Psi_{C}$ is of the form
\[
\Psi_{B, volume} = \frac{\lambda}{2}(J-1)^{2}
\]
and does not have these problems. It is bounded, well defined, and invertible. After these observations, the authors of \acrshort{snh} combined the robust length term with the robust volume term and received $\Psi_D$, which is defined as
\[
\Psi_{D} = \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-1)^{2}.
\]
$\Psi_{D}$ is singularity free and well defined under inversion. Unfortunately, it does not satisfy the requirement of being rest stable, which I will discuss in the next section.

In addition, we can see that each of the proposed energies contains a term that is not well defined under certain conditions. That means that each of the energies in Table \ref{table:energies} is not singularity free or well defined under inversion and therefore confirms the need for the formulation of a new energy.

\subsection{Rest Stabilization}
Although $\Psi_{D}$ meets almost all stated requirements, it is not rest stable. We can show that with the \acrlong{pk1} (\acrshort{pk1}). For our case, it is defined as
\begin{equation}\label{eq:pk1}
P(\mathbf{F}) = \frac{\partial \Psi}{\partial \mathbf{F}} (\mathbf{F}).
\end{equation}
With the help of Eq. \eqref{eq:pk1} we can calculate the \acrshort{pk1} of $\Psi_{D}$. For the following calculations, keep in mind that $I_{C} = \operatorname{tr}(\mathbf{F}^\mathsf{T} \mathbf{F})$ and $J = \operatorname{det}(\mathbf{F})$ holds with $\mathbf{F}$ being the deformation gradient. I will use the explicit terms during the calculations for a better understanding.
\begin{align*}
P_{D}(\mathbf{F}) &= \frac{\partial \Psi_{D}}{\partial \mathbf{F}} (\mathbf{F}) = \frac{\partial}{\partial \mathbf{F}} \left[ \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-1)^{2} \right] \\
&= \frac{\partial}{\partial \mathbf{F}} \left[ \frac{\mu}{2}\left(\operatorname{tr}(\mathbf{F}^\mathsf{T} \mathbf{F})-3\right) +\frac{\lambda}{2}(\operatorname{det}(\mathbf{F})-1)^{2} \right] \\
&= \frac{\partial}{\partial \mathbf{F}}  \frac{\mu}{2}\left(\operatorname{tr}(\mathbf{F}^\mathsf{T} \mathbf{F})-3\right) +\frac{\partial}{\partial \mathbf{F}} \frac{\lambda}{2}(\operatorname{det}(\mathbf{F})-1)^{2}
\end{align*}
Looking at the two terms separately, we get:
\begin{align*}
&\frac{\partial}{\partial \mathbf{F}} \frac{\mu}{2} (\operatorname{tr}(\mathbf{F}^\mathsf{T} \mathbf{F}) - 3) = \frac{\mu}{2} \, 2 \mathbf{F} = \mu \mathbf{F}
\\
&\frac{\partial}{\partial \mathbf{F}} \frac{\lambda}{2} (\operatorname{det}(\mathbf{F})-1)^{2} = \frac{\lambda}{2} \frac{\partial \operatorname{det}(\mathbf{F})}{\partial \mathbf{F}} \, 2 (\operatorname{det}(\mathbf{F}) - 1) = \lambda \frac{\partial \operatorname{det}(\mathbf{F})}{\partial \mathbf{F}}(\operatorname{det}(\mathbf{F})-1)
\end{align*}
Hence, $P_{D}$ resolves to
\[
P_{D}(\mathbf{F}) = \mu \mathbf{F} + \lambda \frac{\partial \operatorname{det}(\mathbf{F})}{\partial \mathbf{F}}(\operatorname{det}(\mathbf{F})-1).
\]
In order to find out whether an energy is rest stable or not, we can set the input variable to the identity matrix $\mathbf{I}$. An energy is rest stable if $P(\mathbf{I})=0$ (\cite{Smith:2018:SNF:3191713.3180491}). Unfortunately, this is not the case for $\Psi_{D}$:
\[
P_{D}(\mathbf{I}) = \mu \mathbf{I} + \lambda \frac{\partial \operatorname{det}(\mathbf{I})}{\partial \mathbf{F}}(\operatorname{det}(\mathbf{I})-1) = \mu \mathbf{I} \neq 0
\]
That is problematic because if we simulate a deformation, the object will shrink in volume when it should be back in its rest state. In order to solve this problem, the authors modified $(J-1)^{2}$ to $(J-\alpha)^{2}$. Using this modification, the energy shifts to
\[
\Psi_{E} = \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-\alpha)^{2}.
\]
Now \acrshort{pk1} for $\Psi_E$ can be calculated similarly as before, and we get:
\begin{align*}
P_{E}(\mathbf{F}) &= \frac{\partial \Psi_{E}}{\partial \mathbf{F}} = \frac{\partial}{\partial \mathbf{F}}  \left[ \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-\alpha)^{2} \right] \\
&= \frac{\partial}{\partial \mathbf{F}}  \left[ \frac{\mu}{2}\left(\operatorname{tr}(\mathbf{F}^\mathsf{T} \mathbf{F})-3\right) +\frac{\lambda}{2}(\operatorname{det}(\mathbf{F})-\alpha)^{2} \right] \\
&= \mu \mathbf{F} + \lambda \frac{\partial \operatorname{det}(\mathbf{F})}{\partial \mathbf{F}} (\operatorname{det}(\mathbf{F})-\alpha)
\end{align*}
Solving for an alpha that satisfies $P_{E}(\mathbf{I})=0$ gives us $\alpha=1+\frac{\mu}{\lambda}$. Now $\Psi_{E}$ has to be changed accordingly:
\[
\Psi_{E} = \frac{\mu}{2}\left(I_{C}-3\right) +\frac{\lambda}{2}(J-1-\frac{\mu}{\lambda})^{2}
\]
We can now expand the quadratic and obtain
\[
\Psi_{E} = \frac{\mu}{2}\left(I_{C}-3\right) - \mu\left(J-1\right) + \frac{\lambda}{2}(J-1)^{2} + \left(\frac{\mu}{\lambda}\right)^{2}.
\]
Since constants disappear under differentiation, this expression is functionally equivalent to 
\begin{equation}\label{energy_without_barrier}
\Psi_{E} = \frac{\mu}{2}\left(I_{C}-3\right) - \mu\left(J-1\right) + \frac{\lambda}{2}(J-1)^{2}.
\end{equation}
Note that $\Psi_{E}$ looks very similar to $\Psi_{Neo}$. The difference is that $log(J)$ is replaced with $(J-1)$ in $\Psi_{E}$. Keep in mind that $(J-1)$ is the first term of the Taylor approximation of $\operatorname{log}(J)$ at $J=1$:
\[
\operatorname{log}(J) = \boldsymbol{(J-1)} - \frac{1}{2} (J-1)^{2} + \frac{1}{3} (J-1)^{3} + \text{...}
\]
Thus, $\Psi_{E}$ can be looked at as an approximation of $\Psi_{Neo}$ that is singularity-free and has rest stability. In addition, it has reflection stability because $I_{C}$ contains the squared singular values of $\mathbf{F}$. Hence, any negation convention is irrelevant, and the $J$ term contains the product of the singular values, so the sign convention is again irrelevant. Therefore, $\Psi_{E}$ has inversion, reflection, and rest stability.

\subsection{Meta-Stability under Degeneracy}
We know from the last section that the energy $\Psi_{E}$ has inversion, reflection, and rest stability. Now we are interested in how it behaves under degeneracy. The authors of the paper \textit{\acrshort{snh}} viewed this examination as a Drucker stability analysis (see e.g. \cite{bower2009applied}). Drucker stability describes a set of criteria that a material can satisfy or not. It is a measurement of the stability of a material. The calculations can be found in the supplemental material of \textit{\acrshort{snh}}. I will only present the results here.

The energy remains stable when crushing the object into a \textit{plane}. The object is able to return to its rest state. Thus, no further adjustments need to be done. When crushing the object into a \textit{line}, the energy is meta-stable. The object will self-restore into the correct shape after any perturbations. A possible perturbation could be a momentum. The alternative would be a state that yields singularities, which is not desirable. Hence, we can leave the energy as it is. We can also crush the object to a \textit{point}, which results in $\mathbf{F} = 0$. In this case, the material cannot recover into its rest state. This effect is small for a higher Poisson's ratio. For completeness, the authors nevertheless added a regularized origin barrier:
\[
	\Psi_{origin} = - \frac{\mu}{2}\operatorname{log}(I_C +\delta)
\]
This term eliminates the unwanted behaviour for point compression for all positive Poisson's ratio, without interfering with the other requirements for the energy. It can be shown that the value of $\delta$ should be set to $1$. This proof is also included in the supplemental material of the paper.

We can now write the final energy down as
\begin{equation}\label{eq:stable_energy}
\boxed{\Psi_{new} = \frac{\mu}{2}\left(I_{C}-3\right) + \frac{\lambda}{2}(J-\alpha)^{2} - \frac{\mu}{2} \operatorname{log}\left(I_{C}+1\right).}
\end{equation}
With this adjustment the rest stability term shifts to $\alpha=1+\frac{\mu}{\lambda}-\left(\frac{\mu}{4}\right)\lambda$.

To note here is that the authors mainly introduced this origin barrier because of pedagogical completeness. In practice, the origin barrier was not needed, and the version of the energy without it, formulated in Eq. \eqref{energy_without_barrier}, was used.

\subsection{Lamé Reparameterization}
Because of the origin barrier introduced in the last section, we need to make a reparametrization of the Lamé parameters $\lambda$ and $\mu$. As I explained in \autoref{ss:deformation_energy}, there is a non-linear relationship between the stresses and strains for hyperelastic materials for larger strain predictions. But for infinitesimal deformation, we should still be consistent with Hooke's law. In order to reach this goal, the model needs to reproduce the \acrshort{pk1} of linear elasticity, which is defined as
\begin{equation} \label{eq:reparametrization}
	\mathbf{P}(\mathbf{F}) = 2 \mu_{\text{\textit{Lamé}}} \epsilon + \lambda_{\text{\textit{Lamé}}} \operatorname{tr}(\epsilon) \mathbf{I},
\end{equation}
where $\epsilon = \frac{1}{2} (\mathbf{F} + \mathbf{F}^\mathsf{T}) - \mathbf{I}$ is the linearized strain tensor and $\mu_{\text{\textit{Lamé}}}$ and $\lambda_{\text{\textit{Lamé}}}$ are the Lamé parameters in linear elasticity. If we linearize the stress from Eq. \eqref{eq:stable_energy} and keep it consistent with the form described in Eq. \eqref{eq:reparametrization}, the values shift to $\mu = \frac{4}{3} \mu_{\text{\textit{Lamé}}}$ and $\lambda = \lambda_{\text{\textit{Lamé}}} + \frac{5}{6} \mu_{\text{\textit{Lamé}}}$. The equation for the Poisson's ratio then shifts to 
\[
	\nu = \frac{\lambda - \left( \frac{5}{8} \right) \mu}{2 \left(\lambda + \left( \frac{1}{8} \right) \mu  \right)}.
\]
These reparameterized expressions for the Lamé parameters were used in all of the tests made in the paper \acrshort{snh}. In addition, with these formulations, it can be shown that the energy does not introduce any spurious minima in the range of $\nu \in [0, 0.5)$. The details are again given in the supplemental material of the paper \acrshort{snh}.

\section{Energy Analysis}
In order to simulate physical deformations, we put some constraints on an object and minimize the deformation energy. Thus, we need a minimization tool. In this case, we will use Newton's method. I will further explain Newton's method in \autoref{s:optimization}. But first, we need to know more about the properties of the energy. The goal of this chapter is to show that a complete eigenanalysis can be performed on the new energy, formulated in Eq. \eqref{eq:stable_energy}, which will help us form a qualitative understanding of the energy.

\subsection{First Piola-Kirchhoff Stress (\acrshort{pk1})}
In order to analyse the energy and build the Hessian terms, the first step is to calculate \acrshort{pk1} for Eq. \eqref{eq:stable_energy} with $\alpha=1+\frac{\mu}{\lambda}-\left(\frac{\mu}{4}\right)\lambda$. Again, $I_{C}$ is equal to $\operatorname{tr}(\mathbf{F}^\mathsf{T} \mathbf{F})$, $J$ signifies $\operatorname{det}(\mathbf{F})$, and I am using the explicit terms during the calculations. With this, we can calculate $P_{new}$ by
\begin{align*}
P_{new}(\mathbf{F}) &= \frac{\partial \Psi_{new}}{\partial \mathbf{F}} = \frac{\partial}{\partial \mathbf{F}} \left[ \frac{\mu}{2}\left(I_{C}-3\right) + \frac{\lambda}{2}(J-\alpha)^{2} - \frac{\mu}{2}\operatorname{log}\left(I_{C}+1\right) \right]
\\
&= \frac{\partial}{\partial \mathbf{F}} \left[ \frac{\mu}{2}\left(\operatorname{tr}(\mathbf{F}^\mathsf{T} \mathbf{F})-3\right) + \frac{\lambda}{2}(\operatorname{det}(\mathbf{F})-\alpha)^{2} - \frac{\mu}{2}\operatorname{log}\left(\operatorname{tr}(\mathbf{F}^\mathsf{T} \mathbf{F})+1\right) \right] .
\end{align*}
Similar to before, I am looking at the terms separately:
\begin{align*}
&\frac{\partial}{\partial \mathbf{F}} \frac{\mu}{2}\left(\operatorname{tr}(\mathbf{F}^\mathsf{T} \mathbf{F})-3\right) = \mu \mathbf{F}
\\
&\frac{\partial}{\partial \mathbf{F}} \frac{\lambda}{2}(\operatorname{det}(\mathbf{F})-\alpha)^{2} = \lambda (\operatorname{det}(\mathbf{F})-\alpha)  \frac{\partial \operatorname{det}(\mathbf{F})}{\partial \mathbf{F}} 
\\ 
&\frac{\partial}{\partial \mathbf{F}} \frac{\mu}{2}\operatorname{log}\left(\operatorname{tr}(\mathbf{F}^\mathsf{T} \mathbf{F})+1\right) = \frac{\mu}{2} \, 2 \mathbf{F} \, \frac{1}{\operatorname{tr}(\mathbf{F}^\mathsf{T} \mathbf{F}) + 1} = \mu \mathbf{F} \frac{1}{\operatorname{tr}(\mathbf{F}^\mathsf{T} \mathbf{F}) + 1}
\end{align*}
When we combine these terms again, we get to the final formula of $P_{new}$:
\begin{align*}
P_{new}(\mathbf{F}) &= \mu \mathbf{F} + \lambda (\operatorname{det}(\mathbf{F})-\alpha)  \frac{\partial \operatorname{det}(\mathbf{F})}{\partial \mathbf{F}} - \mu \mathbf{F} \frac{1}{\operatorname{tr}(\mathbf{F}^\mathsf{T} \mathbf{F}) + 1} \\
&= \mu \left( 1 - \frac{1}{\operatorname{tr}(\mathbf{F}^\mathsf{T} \mathbf{F}) + 1}\right) \mathbf{F} + \lambda( \operatorname{det}(\mathbf{F})-\alpha)\frac{\partial  \operatorname{det}(\mathbf{F})}{\partial \mathbf{F}}
\end{align*}
By using $I_{C}$ and $J$, we get the following expression for $P_{new}(\mathbf{F})$:
\[
	P_{new}(\mathbf{F}) = \mu \left( 1 - \frac{1}{I_{C} + 1}\right) \mathbf{F} + \lambda( J-\alpha)\frac{\partial  J}{\partial \mathbf{F}}
\]
A convenient shorthand for computing $\frac{\partial J}{\partial \mathbf{F}}$ is to write the expression as a result of cross products:
\begin{equation}\label{eq:cross_product}
\frac{\partial J}{\partial \mathbf{F}} = \left[ \,\mathbf{f_1} \times \mathbf{f_2}\, \bigg| \,\mathbf{f_2} \times \mathbf{f_0}\, \bigg| \,\mathbf{f_0} \times \mathbf{f_1}\, \right],
\end{equation}
where $\mathbf{f_i}$ signify the column vectors of $\mathbf{F}$ defined in Eq. \eqref{eq:deformation_gradient}. This formulation is also handy when analysing $\frac{\partial^2 J}{\partial \mathbf{F}^2}$.

\subsection{The Energy Hessian Terms}
In the following, I will derive the Hessian terms of the energy. In addition, I will examine the eigenvalues and eigenvectors. This information about the Hessian is important for the optimization process because, with it, we can determine the definiteness of the matrix.

The Hessian matrix will be a ($9 \times 9$)-matrix. It is demanding to keep an overview while working with high dimensional matrices. In order to not lose sight, we can write the Hessian of the energy as a fourth-order matrix-of-matrices by using the scalar notation for $\mathbf{F}$ defined in Eq. \eqref{eq:deformation_gradient}:
\[
\frac{\partial^2 \Psi_{new}}{\partial \mathbf{F}^2} = \frac{\partial P_{new}(\mathbf{F})}{\partial \mathbf{F}} = 
\left[\begin{array}{ccc}{\left[\frac{\partial P_{new}(\mathbf{F})}{\partial f_0}\right]} & {\left[\frac{\partial P_{new}(\mathbf{F})}{\partial f_3}\right]} & {\left[\frac{\partial P_{new}(\mathbf{F})}{\partial f_6}\right]} \\ {\left[\frac{\partial P_{new}(\mathbf{F})}{\partial f_1}\right]} & {\left[\frac{\partial P_{new}(\mathbf{F})}{\partial f_4}\right]} & {\left[\frac{\partial P_{new}(\mathbf{F})}{\partial f_7}\right]} \\ {\left[\frac{\partial P_{new}(\mathbf{F})}{\partial f_2}\right]} & {\left[\frac{\partial P_{new}(\mathbf{F})}{\partial f_5}\right]} & {\left[\frac{\partial P_{new}(\mathbf{F})}{\partial f_8}\right]} \end{array}\right]
\]
The advantage of this form is that we can look at each entry separately, which improves readability. Each entry of the Hessian is defined as
\begingroup
\addtolength{\jot}{0.8em}
\begin{align} \label{eq:final_entries_hessian}
	\frac{\partial P_{new}(\mathbf{F})}{\partial f_i} = \frac{\partial}{\partial f_i} \left[ \mu \left( 1 - \frac{1}{I_{C} + 1}\right) \mathbf{F} + \lambda(J-\alpha)\frac{\partial J}{\partial \mathbf{F}} \right] \nonumber
	\\
	\stackrel{\text{prod.rule}}{=} \underbrace{\frac{\partial \mathbf{F}}{\partial f_i} \mu \left( 1 - \frac{1}{I_{C} + 1}\right)}_{\mathbf{T}_{i}}  + \underbrace{\mu \frac{2}{\left(I_{C} + 1\right)^2} \mathbf{F} f_i}_{_{\mathbf{M}_{i}}}
	\\
	+ \underbrace{\lambda \frac{\partial J}{\partial \mathbf{F}} \frac{\partial J}{\partial f_i}}_{_{\mathbf{G}_{i}}}+ \underbrace{\lambda (J- \alpha) \frac{\partial^2 J}{\partial \mathbf{F}\partial f_i}}_{_{\mathbf{H}_{i}}}. \nonumber
\end{align}
\endgroup
This final equation looks quite complicated. But we can split it up into these four terms: A $\mathbf{T}_i$ (Tikhonov), $\mathbf{M}_i$ (Mu), $\mathbf{G}_i$ (volume Gradient), and a $\mathbf{H}_i$ (volume Hessian) term. In the following, I will examine each of these terms separately. This way, we do not have to deal with one large and complicated expression immediately.

\subsection{The Tikhonov, Mu, and Gradient Terms}
\subsubsection{Tikhonov}
The Tikhonov term from Eq. \eqref{eq:final_entries_hessian} is a ($9 \times 9$)-matrix and can be written in form of a fourth-order matrix-of-matrices. It is defined as
\[
	\frac{\partial \mathbf{F}}{\partial f_i} \mu \left( 1 - \frac{1}{I_{C} + 1}\right).
\]
With the explicit term for $I_{C}$, this expression resolves to
\[
	\frac{\partial \mathbf{F}}{\partial f_i} \mu \left( 1 - \frac{1}{\operatorname{tr}(\mathbf{F}^\mathsf{T} \mathbf{F}) + 1}\right).
\]
Explicitly computing the Tikhonov term is not very difficult. In order to compute this term, we need to calculate $\mathbb{T} = \frac{\partial \mathbf{F}}{\partial f_i}$. So, we have mainly entries of zeros except for the $i$-th entry. Therefore, $\mathbb{T}$ can be calculated by
\[
\mathbb{T} = \left[\begin{array}{ccc}{\begin{bmatrix} 1 & 0 & 0 \\ 0 & 0 & 0 \\ 0 & 0 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 1 & 0 \\ 0 & 0 & 0 \\ 0 & 0 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 0 & 1 \\ 0 & 0 & 0 \\ 0 & 0 & 0 \end{bmatrix}} \\ {\begin{bmatrix} 0 & 0 & 0 \\ 1 & 0 & 0 \\ 0 & 0 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 0 & 0 \\ 0 & 1 & 0 \\ 0 & 0 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 0 & 0 \\ 0 & 0 & 1 \\ 0 & 0 & 0 \end{bmatrix}} \\ {\begin{bmatrix} 0 & 0 & 0 \\ 0 & 0 & 0 \\ 1 & 0 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 0 & 0 \\ 0 & 0 & 0 \\ 0 & 1 & 0 \end{bmatrix}} & {\begin{bmatrix} 0 & 0 & 0 \\ 0 & 0 & 0 \\ 0 & 0 & 1 \end{bmatrix}} \end{array}\right].
\]
If we vectorize $\mathbb{T}$, we get the identity matrix $\mathbf{I} \in \mathbb{R}^{9x9}$, which is of full rank, positive definite, and independent of the values in \textbf{F}: 
\[
\operatorname{vec}(\mathbb{T}) =  \mathbf{\check{T}} = \mathbf{I} = \in \mathbb{R}^{9x9}
\]
In addition, the Tikhonov term serves as a diagonal regularizer for the rest of the energy.

\subsubsection{Mu}
The Mu term from Eq. \eqref{eq:final_entries_hessian} is again a ($9 \times 9$)-matrix and can be written in the form of a fourth-order matrix-of-matrices. It is described by the following expression:
\[
	\mu \frac{2}{\left(I_{C} + 1\right)^2} \mathbf{F} f_i
\]
With the explicit term for $I_{C}$, the Mu term resolves to
\[
	\mu \frac{2}{\left(\operatorname{tr}(\mathbf{F}^\mathsf{T} \mathbf{F} + 1\right)^2} \mathbf{F} f_i.
\]
In order to compute the Mu term, we need to calculate $\mathbb{M} = \mathbf{F} f_i$. That means that the $i$-entry is squared, and the remaining entries do not change. Therefore, $\mathbb{M}$ takes on the following form:
\[
\mathbb{M} = \left[\begin{array}{ccc}{\begin{bmatrix} f_0^2 & f_0f_3 & f_0f_6 \\ f_0f_1 & f_0f_4 & f_0f_7 \\ f_0f_2 & f_0f_5 & f_0f_8 \end{bmatrix}} & {\begin{bmatrix} f_3f_0 & f_3^2 & f_3f_6 \\ f_3f_1 & f_3f_4 & f_3f_7 \\ f_3f_2 & f_3f_5 & f_3f_8 \end{bmatrix}} & {\begin{bmatrix} f_6f_0 & f_6f_3 & f_6^2 \\ f_6f_1 & f_6f_4 & f_6f_7 \\ f_6f_2 & f_6f_5 & f_6f_8 \end{bmatrix}} \\ {\begin{bmatrix} f_1f_0 & f_1f_3 & f_1f_6 \\ f_1^2 & f_1f_4 & f_1f_7 \\ f_1f_2 & f_1f_5 & f_1f_8 \end{bmatrix}} & {\begin{bmatrix} f_4f_0 & f_4f_3 & f_4f_6 \\ f_4f_1 & f_4^2 & f_4f_7 \\ f_4f_2 & f_4f_5 & f_4f_8 \end{bmatrix}} & {\begin{bmatrix} f_7f_0 & f_7f_3 & f_7f_6 \\ f_7f_1 & f_7f_4 & f_7^2 \\ f_7f_2 & f_7f_5 & f_7f_8 \end{bmatrix}} \\ {\begin{bmatrix} f_2f_0 & f_2f_3 & f_2f_6 \\ f_2f_1 & f_2f_4 & f_2f_7 \\ f_2^2 & f_2f_5 & f_2f_8 \end{bmatrix}} & {\begin{bmatrix} f_5f_0 & f_5f_3 & f_5f_6 \\ f_5f_1 & f_5f_4 & f_5f_7 \\ f_5f_2 & f_5^2 & f_5f_8 \end{bmatrix}} & {\begin{bmatrix} f_8f_0 & f_8f_3 & f_8f_6 \\ f_8f_1 & f_8f_4 & f_8f_7 \\ f_8f_2 & f_8f_5 & f_8^2 \end{bmatrix}} \end{array}\right]
\]
Again, $f_i$ stand for the scalar entries of $\mathbf{F}$. When vectorizing $\mathbb{M}$, the diagonal of the resulting matrix $\mathbf{\check{M}}$ consists of the squared values of $f_i$:
\[
\operatorname{vec}(\mathbb{M})= \mathbf{\check{M}} = \begin{bmatrix} f_0^2 & f_1f_0 & f_2f_0 & f_3f_0 & f_4f_0 & f_5f_0 & f_6f_0 & f_7f_0 & f_8f_0 \\ f_0f_1 & f_1^2 & f_2f_1 & f_3f_1 & f_4f_1 & f_5f_1 & f_6f_1 & f_7f_1 & f_8f_1 \\ f_0f_2 & f_1f_2 & f_2^2 & f_3f_2 & f_4f_2 & f_5f_2 & f_6f_2 & f_7f_2 & f_8f_2 \\ f_0f_3 & f_1f_3 & f_2f_3 & f_3^2 & f_4f_3 & f_5f_3 & f_6f_3 & f_7f_3 & f_8f_3 \\ f_0f_4 & f_1f_4 & f_2f_4 & f_3f_4 & f_4^2 & f_5f_4 & f_6f_4 & f_7f_4 & f_8f_4 \\ f_0f_5 & f_1f_5 & f_2f_5 & f_3f_5 & f_4f_5 & f_5^2 & f_6f_5 & f_7f_5 & f_8f_5 \\ f_0f_6 & f_1f_6 & f_2f_6 & f_3f_6 & f_4f_6 & f_5f_6 & f_6^2 & f_7f_6 & f_8f_6 \\ f_0f_7 & f_1f_7 & f_2f_7 & f_3f_7 & f_4f_7 & f_5f_7 & f_6f_7 & f_7^2 & f_8f_7 \\ f_0f_8 & f_1f_8 & f_2f_8 & f_3f_8 & f_4f_8 & f_5f_8 & f_6f_8 & f_7f_8 & f_8^2 \end{bmatrix}
\]
This structure makes it possible to express $\mathbf{\check{M}}$ more conveniently. We can write $\mathbf{\check{M}}$ as an outer product of $\operatorname{vec}(\mathbf{F}) = \mathbf{\check{f}}$:
\[
\mathbf{\check{M}}= \operatorname{vec}(\mathbf{F})\operatorname{vec}(\mathbf{F})^\mathsf{T} = \mathbf{\check{f}} \mathbf{\check{f}}^\mathsf{T}
\]
This matrix is of rank one and has a single non-zero eigenvalue. In order to examine the eigenvalues, we can calculate
\[
\| \mathbf{\check{f}} \|^{2}_{2} = \sum_{n=0}^8 | f_n |^2 = \| \mathbf{F} \|^{2}_{F} = \sum_{n=0}^3 \sigma^2_i = \left( \sigma_0^2 + \sigma_1^2 + \sigma_2^2 \right),
\]
in which $\|\cdot\|_F$ stands for the Frobenius norm introduced in Def. \ref{FN}, and $\sigma_i$ are the singular values from $\mathbf{\Sigma}$ in the \acrshort{svd} of $\mathbf{F}$ stated in Eq. \eqref{eq:svd_simga}. This expression can be obtained by using Eq. \eqref{eq:FN}. The eigenvector of $\mathbf{\check{M}}$ is $\mathbf{\check{f}} / \| \mathbf{\check{f}} \|$. The eigenvalue is always non-negative and large if $\mathbf{F}$ contains a large stretch.

\subsubsection{Volume Gradient}
The volume Gradient term from Eq. \eqref{eq:final_entries_hessian} is also a ($9 \times 9$)-matrix and can be written in the form of a fourth-order matrix-of-matrices. The Gradient term is defined as
\[
	\lambda \frac{\partial J}{\partial \mathbf{F}} \frac{\partial J}{\partial f_i},
\]
with $J=\operatorname{det}(\mathbf{F})$. Since $\lambda$ is just a scalar constant, we are more interested in the term 
\[
\mathbb{G} = \frac{\partial J}{\partial \mathbf{F}} \frac{\partial J}{\partial fi}.
\]
As already mentioned, we can write $\partial J / \partial \mathbf{F}$ in the form of cross products (see Eq. \eqref{eq:cross_product}) to make its computation easier. We can then set $\operatorname{vec}(\partial J / \partial \mathbf{F}) = \mathbf{\check{g}}$ and write the vectorized matrix $\mathbf{\check{G}}$ as an outer product of $\mathbf{\check{g}}$:
\[
\operatorname{vec}(\mathbb{G})) = \mathbf{\check{G}} = \operatorname{vec}\left(\frac{\partial J}{\partial \mathbf{F}}\right) \operatorname{vec}\left(\frac{\partial J}{\partial \mathbf{F}}\right)^\mathsf{T} = \mathbf{\check{g}} \mathbf{\check{g}}^\mathsf{T}
\]
There is again a single non-zero, non-negative eigenvalue. We can calculate it by
\[
\| \mathbf{\check{g}} \|^2_2 = \left\| \frac{\partial J}{\partial \mathbf{F}} \right \|^2_F = \left[ (\sigma_0 \sigma_1)^2 + (\sigma_0 \sigma_2)^2 + (\sigma_1 \sigma_2)^2 \right].
\]
The corresponding eigenvector is $\mathbf{\check{g}} / \| \mathbf{\check{g}} \|$.

\subsection{The Volume Hessian}
\label{ss:volume_hessian}
The volume Hessian term from Eq. \eqref{eq:final_entries_hessian} is again a ($9 \times 9$)-matrix. But this time, the computation is a bit trickier. The term is described by
\[
	\lambda (J- \alpha) \frac{\partial^2 J}{\partial \mathbf{F}\partial f_i}
\]
with $J=\operatorname{det}(\mathbf{F})$. The term that needs special attention is the following:
\[
\mathbb{H} = \frac{\partial^2 J}{\partial \mathbf{F} \partial f_i}
\]
We can write this term again in the form of a fourth-order matrix-of-matrices:
\[
\mathbb{H} = \frac{\partial^2 J}{\partial \mathbf{F} \partial f_i} = \left[\begin{array}{ccc}{\frac{\partial}{\partial \mathbf{F}}\left[\frac{\partial J}{\partial f_0}\right]} & {\frac{\partial}{\partial \mathbf{F}}\left[\frac{\partial J}{\partial f_3}\right]} & {\frac{\partial}{\partial \mathbf{F}}\left[\frac{\partial J}{\partial f_6}\right]} \\ {\frac{\partial}{\partial \mathbf{F}}\left[\frac{\partial J}{\partial f_1}\right]} & {\frac{\partial}{\partial \mathbf{F}}\left[\frac{\partial J}{\partial f_4}\right]} & {\frac{\partial}{\partial \mathbf{F}}\left[\frac{\partial J}{\partial f_7}\right]} \\ {\frac{\partial}{\partial \mathbf{F}}\left[\frac{\partial J}{\partial f_2}\right]} & {\frac{\partial}{\partial \mathbf{F}}\left[\frac{\partial J}{\partial f_5}\right]} & {\frac{\partial}{\partial \mathbf{F}}\left[\frac{\partial J}{\partial f_8}\right]} \end{array}\right]
\]
The entries of $\mathbb{H}$ have a specific form. For example, the first entry resolves to
\begin{align*}
	\frac{\partial}{\partial \mathbf{F}}\left[\frac{\partial J}{\partial f_0}\right] &= \frac{\partial}{\partial \mathbf{F}} \frac{\partial}{\partial f_0} \left[ f_0 f_4 f_8 + f_2 f_3 f_7 + f_1 f_5 f_6 - f_2 f_4 f_6 - f_0 f_5 f_7 - f_1 f_3 f_8 \right]
	\\ 
	&= \frac{\partial}{\partial \mathbf{F}} \left[ f_4 f_8 - f_5 f_7 \right] = 
	\left[ \begin{matrix}
0 & 0 & 0 \\ 0 & f_8 & -f_5 \\ 0 & -f_7 & f_4 \end{matrix} \right].
\end{align*}
Vectorizing this matrix reveals the vector $\left[ 0,\, 0,\, 0,\, 0,\, f_8,-f_7,\,0,-f_5,\,f_4 \right]^\mathsf{T}$.

By repeating this procedure, $\mathbf{\check{H}}$ reveals the structure
\[
\operatorname{vec}(\mathbb{H}) = \mathbf{\check{H}} = \begin{bmatrix} 0 & 0 & 0 & 0 & f_8 & -f_7 & 0 & -f_5 & f_4 \\ 0 & 0 & 0 & -f_8 & 0 & f_6 & f_5 & 0 & -f_3 \\ 0 & 0 & 0 & f_7 & -f_6 & 0 & -f_4 & f_3 & 0 \\ 0 & -f_8 & f_7 & 0 & 0 & 0 & 0 & f_2 & -f_1 \\ f_8 & 0 & -f_6 & 0 & 0 & 0 & -f_2 & 0 & f_0 \\ -f_7 & f_6 & 0 & 0 & 0 & 0 & f_1 & -f_0 & 0 \\ 0 & f_5 & -f_4 & 0 & -f_2 & f_1 & 0 & 0 & 0 \\ -f_5 & 0 & f_3 & f_2 & 0 & -f_0 & 0 & 0 & 0 \\ f_4 & -f_3 & 0 & -f_1 & f_0 & 0 & 0 & 0 & 0 \end{bmatrix}.
\]
When we look at the matrix, we can see a pattern for the entries. $\mathbf{\check{H}}$ is of the form:
\[
\mathbf{\check{H}} = \left[ \begin{matrix}
0 & -\mathbf{\widehat{F_2}} & \mathbf{\widehat{F_1}} \\ \mathbf{\widehat{F_2}} & 0 & -\mathbf{\widehat{F_0}} \\ -\mathbf{\widehat{F_1}} & \mathbf{\widehat{F_0}} & 0 \end{matrix} \right].
\]
Matrices that have this structure are called cross-product matrices. By looking at the entries separately, we can observe that they reveal the same structure. So, each $\mathbf{\widehat{F_i}}$ is also a cross-product matrix. This property is called \textit{self-similarity}. Therefore, $\mathbf{\check{H}}$ is a \textit{self-similar} cross-product matrix.

\subsubsection{Volume Hessian Eigenvalues}
In the following, I will determine the eigenvalues of $\mathbf{\check{H}}$. In order to calculate the eigenvalues of a matrix, we need the corresponding characteristic polynomial. The characteristic polynomial of a square matrix $\mathbf{A}$ is defined by
\[
	p(\epsilon) = \operatorname{det}(\mathbf{A}-\epsilon \, \mathbf{I}),
\]
where $\epsilon$ symbolizes the eigenvalues of $\mathbf{A}$. The eigenvalues can be calculated by setting $p(\epsilon)$ to zero (\cite{Spencer1980}, p. 27-28). Because $\mathbf{\check{H}}$ is a ($9 \times 9$)-matrix, we expect it to have nine eigenvalues: $\epsilon_0$, $\epsilon_2$, ..., $\epsilon_8$. In order to determine the eigenvalues, we can factor $\mathbf{\check{H}}$ into the following two characteristic polynomials:
\begin{align}
p_1(\epsilon) &= \epsilon^3 - \operatorname{tr}(\mathbf{C}) \epsilon - 2 J  \label{vol_hessian_eq1} \\
p_2(\epsilon)&=\epsilon^3 - \operatorname{tr}(\mathbf{C}) \epsilon^2 + \frac{1}{2} \left( \operatorname{tr^2}(\mathbf{C}) - \operatorname{tr}(\mathbf{C}^2) \right) \epsilon - \operatorname{det}(\mathbf{C}) \label{vol_hessian_eq2}
\end{align}
First, I examine $p_2(\epsilon)$ from Eq. \eqref{vol_hessian_eq2}. It is easier to solve because it corresponds to the characteristic polynomial of $\mathbf{C}$. Given its roots $\epsilon_\alpha$, $\epsilon_\beta$, $\epsilon_\gamma$, we can calculate six of the eigenvalues of $\mathbf{\check{H}}$, namely $\pm \sqrt{\epsilon_\alpha}$, $\pm \sqrt{\epsilon_\beta}$, $\pm \sqrt{\epsilon_\gamma}$. Using the singular values of $\mathbf{F}$, these eigenvalues can be written in the following form:
\begin{align}
\label{eq:hessian_eigenvalues1}
\epsilon_3 &= \sqrt{\epsilon_\alpha} = \sigma_0 & \epsilon_6 &= -\sqrt{\epsilon_\alpha} = -\sigma_0 \nonumber \\
\epsilon_4 &=  \sqrt{\epsilon_\beta} = \sigma_1 & \epsilon_7 &=  -\sqrt{\epsilon_\beta} = -\sigma_1 \\
\epsilon_5 &= \sqrt{\epsilon_\gamma} = \sigma_2 & \epsilon_8 &= -\sqrt{\epsilon_\gamma} = -\sigma_2 \nonumber
\end{align}
The remaining eigenvalues can be obtained by using $p_1(\epsilon)$ from Eq. \eqref{vol_hessian_eq1}. This equation represents a depressed cube. A depressed cube is a cubic that can be expressed by
\[
t^3 + q_1t + q_2. 
\]
$p_1(\epsilon)$ can be written in this form with $q_1=-\operatorname{tr}(\mathbf{C})$ and $q_2= -2J$. Using this knowledge, the roots of $p_1(\epsilon)$ and therefore the remaining eigenvalues $\epsilon_0$, $\epsilon_1$, $\epsilon_2$ of $\mathbf{\check{H}}$ can be obtained by
\begin{equation}
\label{eq:hessian_eigenvalues2}
	\epsilon_k = 2 \sqrt{\frac{I_C}{3}} \operatorname{cos}\left[ \frac{1}{3} \left( \operatorname{arccos}\left(\frac{3 J}{I_C} \sqrt{\frac{3}{I_C}} \right) + 2 \pi k \right) \right] \quad  k= 0,1,2.
\end{equation}
These are all eigenvalues of $\mathbf{\check{H}}$. Three of the six eigenvalues ($\epsilon_3$, ..., $\epsilon_8$) have to be negative or equal to zero since the root function yields a positive and a negative value. In addition, the cosine function for calculating $\epsilon_0$, $\epsilon_1$, and $\epsilon_2$ ensures that one or two of these eigenvalues are also negative.

We have now found the eigenvalues of the terms of $\frac{\partial^2 \Psi_{new}}{\partial \mathbf{F}^2}$, described in Eq. \eqref{eq:final_entries_hessian}. We found out that except for the volume Hessian term, all terms only have non-negative eigenvalues. Thus, the volume Hessian is the only source of negative eigenvalues.

In order to investigate the behaviour of the volume Hessian term further, we need to look at $J = \operatorname{det}(\mathbf{F})$ a bit more in detail. $J$ is not convex, which is problematic for the optimization process. Fortunately, the other terms of $\frac{\partial^2 \Psi_{new}}{\partial \mathbf{F}^2}$ serve as an additional regularization, as already stated for the Tikhonov term.

\subsubsection{Volume Hessian Eigenvectors}
In this section, I will show the eigenvectors of $\mathbf{\check{H}}$. According to the eigendecomposition, $\mathbf{\check{H}}$ can be factorized as $\mathbf{\check{H}} = \mathbf{\check{Q}}\mathbf{\Lambda}\mathbf{\check{Q}}^\mathsf{T}$. We can obtain the eigenvectors by computing $\mathbf{\check{Q}}$. To be consistent with the procedure so far, I will use the tensor form symbolized by $\mathbb{Q}$:
\[
\mathbb{Q} = \left[\begin{array}{ccc}{\left[\mathbf{Q}_0\right]} & {\left[\mathbf{Q}_3\right]} & {\left[\mathbf{Q}_6\right]} \\ {\left[\mathbf{Q}_1\right]} & {\left[\mathbf{Q}_4\right]} & {\left[\mathbf{Q}_7\right]} \\ {\left[\mathbf{Q}_2\right]} & {\left[\mathbf{Q}_5\right]} & {\left[\mathbf{Q}_8\right]} \end{array}\right]
\]
Each entry of $\mathbf{\check{Q}}$ is an eigenvector in the form of a ($3 \times 3$)-matrix instead of a vector with nine entries. I am starting with the eigenvalues obtained by Eq. \eqref{vol_hessian_eq2}, namely $\epsilon_3$, $\epsilon_4$, ..., $\epsilon_8$. The eigenvectors corresponding to these eigenvalues can all be written in the following form:
\begin{equation}\label{eq:eigenvectors_vhessian}
\mathbf{Q}_k = \frac{1}{\sqrt{2}} \mathbf{U} \mathbf{D}_k \mathbf{V}^\mathsf{T} \qquad \qquad \text{for } k = 3, 4, ..., 8
\end{equation}
\textbf{U} and \textbf{V} are taken from the \acrshort{svd} of \textbf{F}, and $\frac{1}{\sqrt{2}}$ is a normalization factor. The difference of the eigenvectors lies in the matrix $\mathbf{D}_k$. For each eigenvalue $\epsilon_k$ for $k \in {3,4,...,8}$, $\mathbf{D}_k$ is defined as:
\begin{align*}
&\mathbf{D_3} = \left[ \begin{matrix}
0 & 0 & 0 \\ 0 & 0 & 1 \\ 0 & -1 & 0 \end{matrix} \right] &\mathbf{D}_6 = \left[ \begin{matrix}
0 & 0 & 0 \\ 0 & 0 & 1 \\ 0 & 1 & 0 \end{matrix} \right]
 \\[0.5em]
&\mathbf{D_4} = \left[ \begin{matrix}
0 & 0 & 1 \\ 0 & 0 & 0 \\ -1 & 0 & 0 \end{matrix} \right] &\mathbf{D}_7 = \left[ \begin{matrix}
0 & 0 & 1 \\ 0 & 0 & 0 \\ 1 & 0 & 0 \end{matrix} \right]
 \\[0.5em]
&\mathbf{D_5} = \left[ \begin{matrix}
0 & 1 & 0 \\ -1 & 0 & 0 \\ 0 & 0 & 0 \end{matrix} \right] &\mathbf{D}_8 = \left[ \begin{matrix}
0 & 1 & 0 \\ 1 & 0 & 0 \\ 0 & 0 & 0 \end{matrix} \right]
\end{align*}
These eigenvectors have a unique \textit{pseudo-cross-product} structure. $\mathbf{D_3}$ is a cross-product matrix for the basis vector $[-1, 0, 0]^\mathsf{T}$. In addition, $\mathbf{Q}_6$ differs from $\mathbf{Q}_3$ only because of one sign. Therefore, $\mathbf{D}_3$ has been multiplied by a reflection, which makes $\mathbf{Q}_6$ a reflected pseudo-cross-product matrix. $\mathbf{Q}_4$ and $\mathbf{Q}_5$ are in the same way cross-product matrices for the basis vectors $[0, -1, 0]^\mathsf{T}$ and $[0, 0, -1]^\mathsf{T}$. $\mathbf{Q}_7$ and $\mathbf{Q}_8$ are the corresponding reflected pseudo-cross-product matrices.

The remaining eigenvectors correspond to the eigenvalues $\epsilon_0$, $\epsilon_1$, and $\epsilon_2$ derived from the depressed cubic. They are of the form
\[
\mathbf{Q}_k = \frac{1}{\| \mathbf{D}_k \|_{F}} \mathbf{U} \mathbf{D}_k \mathbf{V}^\mathsf{T} \qquad \qquad \text{for } k = 0, 1, 2.
\]
\textbf{U} and \textbf{V} are again taken from the \acrshort{svd} of \textbf{F}, and $\frac{1}{\| \mathbf{D}_k \|_{F}}$ is the normalization factor. $\mathbf{D}_k$ is a diagonal matrix and is defined as
\[
\mathbf{D}_k = \left[ \begin{matrix}
\sigma_0 \sigma_2 + \sigma_1 \epsilon_k & 0 & 0 \\ 0 & \sigma_1 \sigma_2 + \sigma_0 \epsilon_k & 0 \\ 0 & 0 & \epsilon_k^2 - \sigma_2^2 \end{matrix} \right] \qquad \text{for } k = 0, 1, 2.
\]
Now we have found explicit expressions for all eigenvalues and eigenvectors of the volume Hessian term.

\subsection{The Complete Eigensystem}
Now it is time to analyse the complete system, which will be called $\mathbf{\check{A}}$ in the following. From Eq. \eqref{eq:final_entries_hessian}, we know that $\mathbf{\check{A}}$ is defined as
\[
\mathbf{\check{A}} =  \mu \left( 1 - \frac{1}{I_{C} + 1}\right) \frac{\partial \mathbf{F}}{\partial f_i} + \mu \frac{2}{\left(I_{C} + 1\right)^2} \mathbf{F} f_i + \lambda \frac{\partial J}{\partial \mathbf{F}} \frac{\partial J}{\partial f_i} + \lambda (J- \alpha) \frac{\partial^2 J}{\partial \mathbf{F}\partial f_i}.
\]
With the expressions for each individual term that were derived in the last section, we can write $\mathbf{\check{A}}$ as
\[
	\mathbf{\check{A}} = \mu \left(1-\frac{1}{I_C+1} \right) \mathbf{I} + \mu \frac{2}{(I_C +1)^2} \mathbf{\check{f}\check{f}}^\mathsf{T} + \lambda \mathbf{\check{g}\check{g}}^\mathsf{T} + \lambda (J-\alpha) \mathbf{\check{H}}.
\]
Computing the eigenvalues from a sum of matrices is nontrivial. Fortunately, $\mathbf{\check{A}}$ has a special structure that can be used to obtain the expressions for the eigenvalues and eigenvectors. We can use the knowledge of the eigenvalues and eigenvectors of the individual terms that we have gathered before. For simplification, I do not include the calculations here and present only the results. The core goal of this section is to show that we can compute the eigenvalues and eigenvectors relatively simple. For further information about the exact steps, an interested reader can have a look at the paper \textit{\acrshort{snh}} on p. 12:7 and 12:8.

For the final eigenvalues, we can use the regularization term $\mu_T = \mu(1- \frac{1}{I_C +1})$. The first three eigenvalues can be calculated by
\begin{align*}
	&\epsilon_k = \lambda (J-\alpha) \bar{\epsilon}_k + \mu_T		&\text{for } k = 0, 1, 2.
\end{align*}	
In this expression, $\bar{\epsilon}_k$ are the roots of the equation
\[
	\bar{\epsilon}^3 + c_2 \bar{\epsilon}^2 + c_1 \bar{\epsilon} + c_0 = 0.
\]
The variables $c_0$, $c_1$, and $c_2$ are defined as
\begin{align*}
	c_2 &= - \|\mathbf{\check{g}}\|^2_2 \rho - I_C \eta \\
	c_1 &= - (1+ 2J\rho)I_C - 6 J \eta + \left( \|\mathbf{\check{g}}\|^2_2 I_C - 9J^2 \right) \rho \eta	\\
	c_0 &= - (2 +3J\rho)J + \left( I_C^2 - 4 \|\mathbf{\check{g}}\|^2_2 \right) \eta + 2J \left( I^2_C -3 \|\mathbf{\check{g}}\|^2_2 \right) \rho \eta 
\end{align*}
with 
\begin{align*}
	&\eta = \frac{2\mu}{(I_C+1)^2 \left( \lambda (J-1) - \frac{3}{4}\mu \right)}	,	&\rho = \frac{\lambda}{\lambda (J-1) - \frac{3}{4} \mu}.
\end{align*}
The remaining eigenvalues can be obtained by:
\begin{align*}
	&\epsilon_3 = \lambda(J-\alpha)\sigma_0 + \mu_T	
	&\epsilon_6 = -\lambda (J-\alpha)\sigma_0 + \mu_T \\
	&\epsilon_4 = \lambda(J-\alpha)\sigma_1 + \mu_T	
	&\epsilon_7 = -\lambda (J-\alpha)\sigma_1 + \mu_T \\
	&\epsilon_5 = \lambda(J-\alpha)\sigma_2 + \mu_T	
	&\epsilon_8 = -\lambda (J-\alpha)\sigma_2 + \mu_T
\end{align*}
These are all eigenvalues of this system. We can now focus on the eigenvectors. The eigenvectors corresponding to $\epsilon_0$, $\epsilon_1$, and $\epsilon_2$ can be calculated by
\[
\mathbf{Q}_k = \frac{1}{\| \mathbf{D}_k \|_{F}} \mathbf{U} \mathbf{D}_k \mathbf{V}^\mathsf{T} \qquad \qquad \text{for } k = 0, 1, 2.
\]
We have already seen this structure for the calculation of the eigenvectors of the volume Hessian term. But this time, $\mathbf{D}_k$ is defined differently:
\[
\mathbf{D}_k = \left[ \begin{matrix}
\alpha_0 & 0 & 0 \\ 0 & \alpha_1 & 0 \\ 0 & 0 & \alpha_2 \end{matrix} \right] \qquad \text{for } k = 0, 1, 2.
\]
The diagonal entries of $\mathbf{D}_k$ are the following:
\begin{align*}
\alpha_0 = \, \, \, &\bar{\epsilon}_k \left( \sigma_1 + \sigma_0 \sigma_2 \eta + J \sigma_1 \rho \right)
\\
&+ \sigma_0 \sigma_2 + \sigma_1 \left( \sigma_0^2 - \sigma_1^2 + \sigma_2^2 \right) \eta + J \sigma_0 \sigma_2 \rho
\\
&+ \sigma_0 \left( \sigma_0^2 - \sigma_1^2 \right) \sigma_2 \left( \sigma_1^2 - \sigma_2^2 \right) \rho \, \eta
\\[0.3em]
\alpha_1 = \, \, \, &\bar{\epsilon}_k \left( \sigma_0 + \sigma_1 \sigma_2 \eta + J \sigma_0 \rho \right)
\\
&+ \sigma_1 \sigma_2 - \sigma_0 \left( \sigma_0^2 - \sigma_1^2 - \sigma_2^2 \right) \eta + J \sigma_1 \sigma_2 \rho
\\
&- \sigma_1 \left( \sigma_0^2 - \sigma_1^2 \right) \sigma_2 \left( \sigma_0^2 - \sigma_2^2 \right) \rho \, \eta
\\[0.3em]
\alpha_2 = \, \, \, &\bar{\epsilon}_k^2 - \bar{\epsilon}_k \left( \sigma_0^2 + \sigma_1^2 \right) \left( \eta + \sigma_2^2 \rho \right)
\\
&- \sigma_2^2 - 2J\eta - 2J\sigma_2^2\rho + \left( \left( \sigma_0^2 - \sigma_1^2 \right) \sigma_2 \right)^2 \rho \, \eta
\end{align*}
The remaining six eigenvectors from $\epsilon_3$, $\epsilon_4$, ..., $\epsilon_8$ are the same as we saw for the volume Hessian and can be calculated by Eq. \eqref{eq:eigenvectors_vhessian}. With this, we have found explicit expressions for all of the eigenvalues and eigenvectors of the complete system.

\subsection{Conclusion}
In \autoref{ss:volume_hessian}, we can see by the structure of Eq. \eqref{eq:hessian_eigenvalues1} and Eq. \eqref{eq:hessian_eigenvalues2} that it is possible to factor the Hessian into one ($3 \times 3$)-eigensystem. This system is determined by the three pair-wise roots and the three entangled roots for the eigenvalues. That extends the findings from Teran et al. in \cite{teran2005robust}. Furthermore, we saw that explicit expressions for the eigenvalues and eigenvectors of each Hessian term, as well as for the whole system, can be formed. That is important for the optimization process.

With this analysis, we can conclude that the proposed energy is complex enough to capture a desired level of detail but simple enough to be expressed by closed-form expressions. In the next chapter, I will test the robustness of the model with various scenarios and check whether the claims of the authors hold or not.
